### 2016-12-18 writing/alojdanc/draft.tex
Draft was added

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}

\title{Draft}

\begin{document}
\maketitle

\newcommand{\sn}{\textrm{sn}}
\newcommand{\cn}{\textrm{cn}}
\newcommand{\dn}{\textrm{dn}}
\newcommand{\sd}{\textrm{sd}}
\newcommand{\cd}{\textrm{cd}}
\newcommand{\nd}{\textrm{nd}}
\newcommand{\am}{\textrm{am}}

\subsection*{Модель}

Рассматривается безразмерная версия GPE:
%
\begin{equation}
i \dfrac{\partial \psi}{\partial t} = -\dfrac{1}{2} \dfrac{\partial^2 \psi}{\partial x^2} + U(x) \psi + g |\psi|^2 \psi.
\label{eq:GPE} 
\end{equation}
%
Здесь $\int |\psi|^2 dx = N$, где $N$ -- число атомов.
Потенциал имеет вид $U(x) = h ((x/x_0)^2 - 1)^2$ (или, возможно, другой симметричный double-well потенциал).
Гаильтониан этого уравнения выглядит следующим образом:
%
\begin{equation}
H = \int \Big\{ -\dfrac{1}{2} \psi^\dag \dfrac{d^2 \psi}{dx^2} + \psi^\dag \psi U(x) + \dfrac{g}{2} \psi^{\dag 2} \psi^2  \Big\} dx.
\label{eq:gpe_hamiltonian}
\end{equation}
%

В этой задаче изучается двухмодовое приближение
%
\begin{equation}
\psi = \psi_1(t) \Phi_1(x) + \psi_2(t) \Phi_2(x),
\label{eq:two_modes}
\end{equation}
%
где
%
\begin{equation}
\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}, \quad \Phi_{\pm}(x) = \pm \Phi_{\pm} (-x),
\label{eq:conditions}
\end{equation}
%
а моды $\Phi_{\pm}$ удовлетворяют стационарному уравнению
%
\begin{equation}
\beta_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
\label{eq:stationary}
\end{equation}
%
Полагаем, что для $\Phi_{\pm}$ выполняется условие нормировки $\int \Phi_{\pm}^2 dx = 1$, а значит, что и $\int \Phi_{1,2}^2 dx = 1$.
Также $\int |\psi|^2 dx = \int |\psi_1 \Phi_1 + \psi_2 \Phi_2|^2 = |\psi_1|^2 + |\psi_2|^2 = N$.
Теперь подставим выражение (\ref{eq:two_modes}) в гамильтониан (\ref{eq:gpe_hamiltonian}) и проинтегрируем.
Выражение для гамильтониана принимает вид:
%
\begin{eqnarray*}
\hat{H} & = & (\psi_1^\dag \psi_1 + \psi_2^\dag \psi_2) \Big[ \dfrac{1}{4} \int (\Phi_+')^2 + (\Phi_-')^2  dx + \dfrac{1}{2} \int ((\Phi_+)^2 + (\Phi_-)^2) U(x) dx \Big] \\[10pt]
&& +(\psi_1^\dag \psi_2 + \psi_2^\dag \psi_1) \Big[ \dfrac{1}{4} \int (\Phi_+')^2 - (\Phi_-')^2 dx + \dfrac{1}{2} \int ((\Phi_+)^2 - (\Phi_-)^2)U(x) dx \Big] \\[10pt]
&& +\dfrac{1}{2} \Big[ \psi_1^{\dag 2} \psi_1^2 \dfrac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}) + \psi_2^{\dag 2} \psi_2^2 \dfrac{1}{4}(\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})  \\[10pt]
&& +(\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag) \dfrac{1}{2}(\gamma_{++} - \gamma_{--}) + (\psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_2^{\dag 2} \psi_2 \psi_1) \dfrac{1}{2} (\gamma_{++} - \gamma_{--})\\[10pt]
&& + (\psi_1^{\dag 2} \psi_2^2 + 4 \psi_1^\dag \psi_1 \psi_2^\dag \psi_2 + \psi_1^2 \psi_2^{\dag 2}) \dfrac{1}{4} (\gamma_{++} - 2 \gamma_{+-} + \gamma_{--}) \Big].
\end{eqnarray*}
%
Будем использовать следующие обозначения:
%
\begin{equation}
\begin{array}{c}
	\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\[10pt]
	\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad E = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\[10pt]
	C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\[10pt]
	G = \dfrac{1}{2} \int (\Phi_+')^2 - (\Phi_-')^2 dx + \int ((\Phi_+)^2 - (\Phi_-)^2)U(x) dx.
\end{array}
\label{eq:subs}
\end{equation}
%
Заметим, что $G$ можно выразить по-другому, используя уравнения для стационарных состояний (\ref{eq:stationary}):
%
\begin{equation}
G = \beta_+ - \beta_- - 2E;
\end{equation}
%

Перепишем гамиьльтониан в новых обозначениях, избавившись от первого слагаемого, которое является постоянной ($\psi_1^\dag \psi_1 + \psi_2^\dag \psi_2 \equiv N$).
%
\begin{equation}
\begin{array}{lcl}
	\hat{H} & = & \dfrac{G}{2} (\psi_1^\dag \psi_2 +  \psi_1 \psi_2^\dag) + \dfrac{A}{2} (\psi_1^{\dag 2} \psi_1^2 + \psi_2^{\dag 2} \psi_2^2) \\[10pt]
	& & +\dfrac{E}{2} (\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2) \\[10pt]
	& & +\dfrac{C}{2} (\psi_1^{\dag 2} \psi_2^2 + 4 \psi_1^\dag \psi_1 \psi_2^\dag \psi_2 + \psi_1^2 \psi_2^{\dag 2}).
\end{array}
\label{eq:hamiltonian}
\end{equation}
%

Из этого гамильтониана через уравнения Гейзенберга может быть получена система уравнений, так называемая I2M модель:
%
\begin{equation}
\begin{array}{lcl}
	i \psi_{1,t} & = & (A |\psi_1|^2 + 2C |\psi_2|^2 + \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 + \\[10pt]
	&& + (\dfrac{G}{2} + E |\psi_1|^2 + \dfrac{E}{2} |\psi_2|^2 + C \psi_1^* \psi_2) \psi_2; \\[10pt]
	i \psi_{2,t} & = & (A |\psi_2|^2 + 2C |\psi_1|^2 + \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 + \\[10pt] 
	&& + (\dfrac{G}{2} + E |\psi_2|^2 + \dfrac{E}{2}|\psi_1|^2 + C \psi_2^* \psi_1) \psi_1.
\end{array}
\label{eq:I2M}
\end{equation}
%

Воспользовавшись нормировкой, полученную систему можно упростить, сделав ее, тем самым, похожей на модель из статьи Ananikian, Bergeman.
%
\begin{equation*}
\begin{array}{c}
	i \psi_{1,t} = ((A - 2C) |\psi_1|^2 + \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 + (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_1|^2 + C \psi_1^* \psi_2) \psi_2; \\[10pt]
	i \psi_{2,t} = ((A - 2C) |\psi_2|^2 + \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 + (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_2|^2 + C \psi_2^* \psi_1) \psi_1.
\end{array}
\end{equation*}
%

\subsection*{Переход к операторам спина}

В выражении для гамильтониана перейдем к операторам $S_0$, $S_x$, $S_y$, $S_z$, определенных следующим образом:
%
\begin{equation}
\begin{array}{c}
	S_0 = \dfrac{1}{2} (\psi_1^\dag \psi_1 + \psi_2^\dag \psi_2), \quad S_z = \dfrac{1}{2} (\psi_2^\dag \psi_2 - \psi_1^\dag \psi_1), \\[10pt]
	S_x = \dfrac{1}{2} (\psi_1^\dag \psi_2 + \psi_1 \psi_2^\dag), \quad S_y = \dfrac{i}{2} (\psi_1^\dag \psi_2 - \psi_1 \psi_2^\dag), \\[10pt]
	S_+ = \psi_1 \psi_2^\dag, \quad S_- = \psi_1^\dag \psi_2, \quad S_{\pm} = S_x \pm iS_y.
\end{array}
\end{equation}
%
Выполняется тождество:
%
\begin{equation}
S_0^2 + S_x^2 + S_y^2 + S_z^2 = \dfrac{1}{2}(N^2 + N) = Const.
\label{eq:sum_of_squares}
\end{equation}
%
Тогда
%
\begin{eqnarray*}
&& \psi_1^\dag \psi_2 + \psi_1 \psi_2^\dag = 2S_x; \\
&& \psi_1^{\dag 2} \psi_1^2 + \psi_2^{\dag 2} \psi_2^2 = 2(S_0^2 + S_z^2 - S_0); \\
&& \psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2 = 2(2S_0 - 1) S_x; \\
&& \psi_1^{\dag 2} \psi_2^2 + 4 \psi_1^\dag \psi_1 \psi_2^\dag \psi_2 + \psi_1^2 \psi_2^{\dag 2} = S_-^2 + S_+^2 + 4(S_0^2 - S_z^2).
\end{eqnarray*}
%
%
$$\hat{H} = G S_x + A(S_z^2 + S_0^2 - S_0) + E(2S_0 - 1) S_x + C(S_x^2 - S_y^2 + S_0^2 - 2S_z^2).$$
%
В полученном выражении выразим $S_y^2$ через $S_z^2$ и $S_x^2$ (см. выражение (\ref{eq:sum_of_squares}) и отбросим все постоянные.
%
$$\hat{H} = G S_x + A S_z^2 + E(2S_0 - 1) S_x + C(2 S_x^2 - S_z^2).$$
%
Заметим, что $A - C = 2 \gamma_{+-} = \alpha > 0$, также $2S_0 = N \gg 1$; $2C = \beta$; $EN+G = B$.
Приходим к следующему выражению для гамильтониана:
%
\begin{equation}
\hat{H} = \alpha S_z^2 + \beta S_x^2 + B S_x.
\label{eq:spin_hamiltonian}
\end{equation}

\subsection*{Дифференциальное представление операторов}

В выражении (\ref{eq:spin_hamiltonian}) перейдем к дифференциальному представлению операторов:
%
\begin{equation}
S_z = -i \dfrac{d}{d \phi}, \quad S_x = S \cos \phi - \sin \phi \dfrac{d}{d \phi}, \quad S_y = S \sin \phi + \cos \phi \dfrac{d}{d \phi}.
\label{eq:diff_repr}
\end{equation}
%
Должны выполняться следующие коммутационные соотношения:
%
$$[S_x, S_y] = iS_z, \quad [S_z, S_x] = iS_y, \quad [S_y, S_z] = iS_x.$$
%
Заметим, что
%
\begin{equation}
\begin{array}{lcl}
	S_x^2 & = & (S \cos \phi - \sin \phi \dfrac{d}{d \phi})^2 = \\
	& = & S^2 \cos^2 \phi + S \sin^2 \phi + (\frac{1}{2} - S) \sin 2 \phi \dfrac{d}{d \phi} + \sin^2 \phi \dfrac{d^2}{d \phi^2}.
\end{array}
\end{equation}
%
Выражение для Гамильтониана после некоторых преобразований и отбрасывания постоянных принимает вид:
%
\begin{equation*}
\begin{array}{lcl}
	\hat{H} & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2 \phi) \dfrac{d}{d \phi} \\[10pt]
	&& + BS \cos \phi - \beta S^2 \sin^2 \phi - \beta S \cos^2 \phi.
\end{array}
\end{equation*}
%
Поставим задачу на собственные значения и собственные функции гамильтониана в дифференциальной форме:
%
\begin{equation}
\hat{H} \Phi = E \Phi.
\end{equation}
%
\begin{equation}
\begin{array}{l}
	(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2\phi) \dfrac{d \Phi}{d \phi} \\[10pt]
	+ (E - BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
\end{array}
\end{equation}

\subsection*{Замена переменных}

Избавимся от переодической зависимости при второй производной с помощью замены $\phi \to x$,
%
\begin{equation*}
x = \int \limits_0^\phi \dfrac{d \phi'}{\sqrt{1 - \frac{\beta}{\alpha} \sin^2 \phi'}} = F(\phi, \sqrt{\beta / \alpha}),
\end{equation*}
%
где $F(\phi, \sqrt{\beta / \alpha})$ -- неполный эллиптический интеграл первого рода.
При таком преобразовании
%
\begin{eqnarray*}
\dfrac{d}{d \phi} & = & \dfrac{dx}{d \phi} \dfrac{d}{dx} =  \dfrac{1}{(1 - \frac{\beta}{\alpha} \sin^2 \phi)^{1/2}} \dfrac{d}{dx};\\
\dfrac{d^2}{d \phi^2} & = & \left( \dfrac{dx}{d\phi} \right)^2 \dfrac{d^2}{dx^2} + \left( \dfrac{d^2 x}{d \phi^2} \right) \dfrac{d}{dx} = \\
& = & \dfrac{1}{1 - \frac{\beta}{\alpha} \sin^2 \phi} \dfrac{d^2}{dx^2} + \dfrac{\frac{\beta}{\alpha} \sin \phi \cos \phi}{(1 - \frac{\beta}{\alpha} \sin^2 \phi)^{3/2}} \dfrac{d}{dx}.
\end{eqnarray*}
%
Далее, тригонометричекие функции перейдут в свои эллиптические аналоги: $\sin \phi = \sn x$, $\cos \phi = \cn x$, $1 - \frac{\beta}{\alpha} \sn^2 x = \dn^2 x$.
%
\begin{equation}
\begin{array}{l}
	\alpha \dfrac{d^2 \Phi}{d x^2} + \dfrac{B~\sn x + 2 \beta S~\sn x~\cn x}{\dn x} \dfrac{d \Phi}{dx} \\[10pt]
	+ (E - BS~\cn x + \beta S^2~\sn^2 x + \beta S~\cn^2 x) \Phi = 0.
\end{array}
\end{equation}
%
Далее избавимся от первой производной таким образом: $\Phi = \Psi e^{f(x)}$, где $f(x)$ -- некоторая пока неизвестная функция.
При таком преобразовании:
%
\begin{equation*}
\begin{array}{lcl}
	\dfrac{d}{dx} & \to & \dfrac{d}{dx} + f';\\[10pt]
	\dfrac{d^2}{dx^2} & \to & \dfrac{d^2}{dx^2} + 2f' \dfrac{d}{dx} + f'' + (f')^2.
\end{array}
\end{equation*}
%
Коэффициент при первой производной $d/dx$ обращается в ноль при следующем условии на функцю $f$:
%
\begin{equation}
f' = -\dfrac{B~\sn x + 2 \beta S~\sn x~\cn x}{2 \alpha~\dn x}.
\label{eq:f_condition}
\end{equation}
%
Можно проверить (я проверил), что
%
\begin{equation}
f = S \ln~\dn x + \frac{B}{2 \sqrt{\beta(\alpha - \beta)}} \arctan \left( \sqrt{\frac{\beta}{\alpha - \beta}}~\cn x \right)
\end{equation}
%
удовлетворяет условию (\ref{eq:f_condition}).
Выражение для второй производной:
%
$$f'' = -\frac{1}{2 \alpha} \left( B~\cn x + 2\beta S (\cn^2 x - \sn^2 x) + \frac{\beta B~\sn^2 x~\cn x + 2 \beta^2 S~\sn^2 x~\cn^2 x}{\alpha~\dn^2 x} \right).$$
%
Приходим к следующему уранению:
%
\begin{equation}
\alpha \frac{d^2 \Psi}{dx^2} + (E - V(x)) \Psi = 0,
\label{eq:shrod1}
\end{equation}
%
с потенциалом
%
\begin{equation}
V(x) = \frac{(\frac{1}{4}B^2 - \beta(\alpha - \beta) S (S+1))~\sn^2 x + \alpha B (S + \frac{1}{2})~\cn x}{\alpha~\dn^2 x}.
\end{equation}
%
Введем обозначения $\Lambda = \frac{G}{\alpha S}$, $\lambda = \beta / \alpha$.
Далее полагаем, что $E = 0$, $B = EN + G = G$, $S = N/2 \gg 1$, тогда уравнение (\ref{eq:shrod1} можно переписать в виде
%
\begin{equation}
\frac{d^2 \Psi}{dx^2} + (E - S^2 V(x)) \Psi = 0,
\label{eq:shrod2}
\end{equation}
% 
где
%
\begin{equation}
V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x + \Lambda~\cn x}{\dn^2 x}.
\end{equation}
%
Линейное преобразование пространственной координаты: $\phi \to \phi + \pi$, $x \to x + 2K(\lambda)$, потенциал изменится на
%
\begin{equation}
V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
\end{equation}
%
Построим графики $V(x)$ для различных значений параметров $\Lambda$, $\lambda$.
%
\begin{figure}[Ht!]
\center{\includegraphics[width=1\linewidth]{pic/V_1period_shifted.eps}}
\caption{На 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига}
\end{figure}
%
%\begin{figure}[Ht!]
%\center{\includegraphics[width=1\linewidth]{pic/V_1period_shifted_asym.eps}}
%\caption{На 1-ом периоде функций Якоби ($[-3K; K]$)}
%\end{figure}
%

\subsection*{Фазовый переход в задаче о туннелировании}

Рассмотрим уравнение Ньютона:
%
\begin{equation}
\frac{1}{2} \dot{x}^2 = S^2 V(x) - E.
\end{equation}
%
Тип фазового перехода определяется зависимостью периода колебаний термона от энергии $\tau(E)$.
Если $\tau(E)$ монотонная (монотонно-убывающая), имеет место фазовый переход 1-го рода, а иначе, когда зависимость $\tau(E)$ немонотонная, фазовый переход 2-го рода.

\paragraph{Fock: $\Lambda = 0$.}
Выражение для потенциала:
%
\begin{equation}
V(x) = -\lambda (1 - \lambda)~\sd^2 x.
\end{equation}
%
Используем критерий фазового перехода из статьи Чудновского в PRL.
Разложим $V(x)$ в нуле в ряд тейлора:
%
\begin{equation}
V(x) = -\lambda (1 - \lambda) (2x^2 - 8(1 - 2\lambda)x^4 + o(x^4)).
\end{equation}
%
\textbf{Утверждение} Знак перед 4-й степенью оперделяет локальное поведение $\tau(E)$ вблизи точки $E_0$ исчезнования термона.
Знаку ``$-$'' соответствует убывание периода в окрестности $E_0$, а знаку ``$+$'' -- возрастание.
Это означает, что в случае ``$+$'' имеет место фазовый переход 1-го рода.
Случай ``$-$'' не означает, что функция $\tau(E)$ монотонна, однако мы, в след за работой Чудновского, будем полагать ее в этом случае монотонной (т.е. что ее локальное поведение можно экстраполировать на глобальное).

Результат: при $\lambda < 0.5$ имеет место фазовый переход 2-го рода, при $\lambda > 0.5$ -- 1-го рода.
Этот результат согласуется с численным счетом.
%
\begin{figure}[Ht!]
\center{\includegraphics[width=1\linewidth]{pic/tau_on_E.eps}}
\caption{$\tau(E)$}
\end{figure}
%

\paragraph{Rabi: $\Lambda \gg 1$.}
Выражение для потенциала:
%
\begin{equation}
V(x) = \frac{\frac{1}{4} \Lambda^2 ~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
\end{equation}
%
В этом случае нет симметричной double-well ловушки.

\paragraph{Период малых колебаний}
Рассмотри малые колебания в яме: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
Уравнение, описывающее мылые колебания:
%
\begin{equation}
\ddot{x} - 2S^2 (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) x = 0.
\end{equation}
%
Частота малых колебаний:
%
\begin{equation}
\omega_0 = \sqrt{2S^2 (\lambda (1 - \lambda) - \frac{1}{4} \Lambda^2)}.
\end{equation}
%
Период мылых колебаний
%
\begin{equation}
\tau_0 = \frac{2 \pi}{\omega_0} = \frac{2 \pi}{\sqrt{2S^2 (\lambda (1 - \lambda) - \frac{1}{4} \Lambda^2)}}.
\end{equation}
%
Условие, при котором существует симметричная double-well ловушка, поддерживающая существование термона в окрестности точки $x = 0$:
%
\begin{equation}
\lambda (1 - \lambda) > \frac{1}{4} \Lambda^2.
\end{equation}
%
\end{document}

### 2016-12-20 writing/alojdanc/draft.tex
Fock, Josephson, Rabi regimes

@@
 \center{\includegraphics[width=1\linewidth]{pic/V_1period_shifted.eps}}
-\caption{На 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига}
+\caption{$V(x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига}
 \end{figure}
@@
 \begin{equation}
-V(x) = -\lambda (1 - \lambda)~\sd^2 x.
+V_F (x) = -\lambda (1 - \lambda)~\sd^2 x.
 \end{equation}
+%
+Типичный график потенциала показан на Рис. \ref{pic:potential_fock}
+%
+\begin{figure}[Ht!]
+\center{\includegraphics[width=0.5\linewidth]{pic/V_Fock.eps}}
+\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига, $\lambda = 0.5$}
+\label{pic:potential_fock}
+\end{figure}
 %
@@
 \begin{equation}
-V(x) = -\lambda (1 - \lambda) (2x^2 - 8(1 - 2\lambda)x^4 + o(x^4)).
+V_F (x) = -\lambda (1 - \lambda) (2x^2 - 8(1 - 2\lambda)x^4 + o(x^4)).
 \end{equation}
 %
-\textbf{Утверждение} Знак перед 4-й степенью оперделяет локальное поведение $\tau(E)$ вблизи точки $E_0$ исчезнования термона.
-Знаку ``$-$'' соответствует убывание периода в окрестности $E_0$, а знаку ``$+$'' -- возрастание.
-Это означает, что в случае ``$+$'' имеет место фазовый переход 1-го рода.
-Случай ``$-$'' не означает, что функция $\tau(E)$ монотонна, однако мы, в след за работой Чудновского, будем полагать ее в этом случае монотонной (т.е.
-что ее локальное поведение можно экстраполировать на глобальное).
+
+\textbf{Утверждение.} Знак перед 4-й степенью оперделяет локальное поведение $\tau(E)$ вблизи точки $E_0$ исчезнования термона.
+Знаку ``$+$'' соответствует убывание периода в окрестности $E_0$, а знаку ``$-$'' -- возрастание.
+Это означает, что в случае ``$-$'' имеет место фазовый переход 1-го рода.
+Случай ``$+$'' не означает, что функция $\tau(E)$ монотонна, однако мы, вслед за работой Чудновского, будем полагать ее в этом случае монотонной (т.е.
+что ее локальное поведение можно экстраполировать на глобальное), что влечет а собой фазовый переход 2-го рода.
 
@@
 \begin{figure}[Ht!]
-\center{\includegraphics[width=1\linewidth]{pic/tau_on_E.eps}}
-\caption{$\tau(E)$}
+\center{\includegraphics[width=1\linewidth]{pic/tau_on_E_Fock.eps}}
+\caption{$\tau(E)$, Fock, {\bf qualitative only!}}
 \end{figure}
@@
 
-\paragraph{Rabi: $\Lambda \gg 1$.}
+\paragraph{Josephson: $\Lambda^2 \sim \Lambda$, $\lambda(1 - \lambda) \ll \Lambda^2$.}
+Это переходный режим.
 Выражение для потенциала:
@@
 \begin{equation}
-V(x) = \frac{\frac{1}{4} \Lambda^2 ~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
+V_J(x) = \frac{\frac{1}{4} \Lambda^2 ~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
 \end{equation}
@@
 В этом случае нет симметричной double-well ловушки.
+Типичный график потенциала показан на Рис. \ref{pic:potential_josephson}.
+%
+\begin{figure}[Ht!]
+\center{\includegraphics[width=1\linewidth]{pic/V_Josephson.eps}}
+\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа) после сдвига, $\Lambda = 5$, $\lambda = 0.5$}
+\label{pic:potential_josephson}
+\end{figure}
+%
 
-\paragraph{Период малых колебаний}
-Рассмотри малые колебания в яме: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
+\textbf{Квантовый осциллятор.}
+Рассмотрим в нуле малые колебания квантового гармонического осциллятора: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
+Уравнение квантового осциллятора
+%
+\begin{equation}
+\frac{d^2 \Psi}{dx^2} + (E + S^2 \Lambda - \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
+\end{equation}
+%
+После замены $x \to \sqrt{\frac{S \Lambda}{2}} x$, $\tilde{E} = \frac{2}{S \Lambda} (E + S^2 \Lambda)$:
+%
+\begin{equation}
+\frac{d^2 \Psi}{dx^2} + (\tilde{E} - x^2) \Psi = 0.
+\end{equation}
+%
+Уровни энергии: $\tilde{E} = 2n + 1$ или $E = S \Lambda (n + \frac{1}{2}) - S^2 \Lambda$.
+Собственные функции выражаются через полиномы Эрмита.
+
+\paragraph{Rabi: $\Lambda^2 \gg \Lambda \gg \lambda(1 - \lambda)$.}
+Выражение для потенциала:
+%
+\begin{equation}
+V_R = \frac{1}{4} \Lambda^2 ~\sd^2 x.
+\end{equation}
+%
+Типичный график потенциала показан на Рис. \ref{pic:potential_rabi}.
+%
+\begin{figure}[Ht!]
+\center{\includegraphics[width=1\linewidth]{pic/V_Rabi.eps}}
+\caption{$V_R (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа) после сдвига, $\Lambda = 100$}
+\label{pic:potential_rabi}
+\end{figure}
+%
+В этом случае симметричная double-well ловушка наблюдается на полном $4K(\lambda)$ периоде потенциала.
+Чтобы было удобно, произведем преобразование координат: $x \to x + K(\lambda)$.
+В это случаем $\sd^2 x \to (1 - \lambda)^{-1} \cn^2 x$.
+Барьер окажется в точке $x = 0$.
+уравнение принимает вид:
+%
+\begin{equation}
+\frac{d^2 \Psi}{dx^2} + (E - \frac{S^2 \Lambda^2}{4 (1 - \lambda)} ~\cn^2 x) \Psi = 0.
+\end{equation}
+%
+Далее действуем как и раньше.
+Уравнение Ньютона:
+%
+\begin{equation}
+\frac{1}{2} \dot{x}^2 = S^2 V(x) - E.
+\end{equation}
+%
+$V(x) = \frac{\Lambda^2}{4(1 - \lambda)} ~\cn^2 x$.
+Разложим $V(x)$ в ряд Тейлора:
+%
+\begin{equation}
+V(x) = \frac{\Lambda^2}{4(1 - \lambda)} (1 - x^2 + \frac{1 + \lambda}{3} x^4 + o(x^4)).
+\end{equation}
+%
+Знак перед слагаемым $\sim x^4$ всегда ``$+$'', следовательно имеет место только фазовый переход 2-го рода.
+Это результат согласуется с численным счетом.
+%
+\begin{figure}[Ht!]
+\center{\includegraphics[width=1\linewidth]{pic/tau_on_E_Rabi.eps}}
+\caption{$\tau(E)$, Rabi, {\bf qualitative only!}}
+\end{figure}
+%
+
+\textbf{Квантовый осциллятор.}
+Рассмотрим в нуле малые колебания квантового гармонического осциллятора: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
+Уравнение квантового осциллятора
+%
+\begin{equation}
+\frac{d^2 \Psi}{dx^2} + (E + \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
+\end{equation}
+%
+После замены $x \to \sqrt{\frac{S \Lambda}{2}} x$, $\tilde{E} = \frac{2}{S \Lambda} E$:
+%
+\begin{equation}
+\frac{d^2 \Psi}{dx^2} + (\tilde{E} - x^2) \Psi = 0.
+\end{equation}
+%
+Уровни энергии: $\tilde{E} = 2n + 1$ или $E = S \Lambda (n + \frac{1}{2})$.
+Собственные функции выражаются через полиномы Эрмита.
+
+\paragraph{Период малых колебаний термона.}
+Он связан с температурой фазового перехода.
+Рассмотрим малые колебания в яме: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
 Уравнение, описывающее мылые колебания:
@@
 %
+
 \end{document}

### 2016-12-22 writing/alojdanc/draft.tex
Fixes
Exact instanton-solution in a Fock regime was found

@@
 Введем обозначения $\Lambda = \frac{G}{\alpha S}$, $\lambda = \beta / \alpha$.
-Далее полагаем, что $E = 0$, $B = EN + G = G$, $S = N/2 \gg 1$, тогда уравнение (\ref{eq:shrod1} можно переписать в виде
+Далее полагаем, что $E = 0$, $B = EN + G = G$, $S = N/2 \gg 1$, тогда уравнение (\ref{eq:shrod1}) можно переписать в виде
 %
@@
 \frac{1}{2} \dot{x}^2 = S^2 V(x) - E.
+\label{eq:newton}
 \end{equation}
@@
 V_F (x) = -\lambda (1 - \lambda)~\sd^2 x.
+\label{eq:potential_fock}
 \end{equation}
@@
 
-Результат: при $\lambda < 0.5$ имеет место фазовый переход 2-го рода, при $\lambda > 0.5$ -- 1-го рода.
+\textbf{Результат:} при $\lambda < 0.5$ имеет место фазовый переход 2-го рода, при $\lambda > 0.5$ -- 1-го рода.
 Этот результат согласуется с численным счетом.
@@
 \end{figure}
+%
+
+\textbf{Аналитическое выражения для инстантона.}
+Можно получить аналитичекое выражения для инстантона, которое является сепаратрисным решением уравнения (\ref{eq:newton}) с потенциалом (\ref{eq:potential_fock}).
+В этом случае инстантон представляет собой кинк, который выходит из точки $x(-\infty) = -K(\lambda)$ и входит в $x(+\infty) = +K(\lambda)$.
+Уровень энергии, которому соответствует инстантонное решение найдем из условия покоя в точке $x_0 = x(-\infty) = -K(\lambda)$, $x_0' = \dot{x}(-\infty) = 0$, $E = V_F(x_0) = -\lambda S^2$.
+Тогда первый интеграл уравнения движения для инстантона запсиывается в виде:
+%
+\begin{equation}
+\frac{1}{2 S^2} \dot{x}^2 = \lambda - \lambda (1 - \lambda) ~\sd^2 x = 1 - (1 - \lambda) ~\nd^2 x.
+\end{equation}
+%
+Интегрируем:
+%
+\begin{equation}
+S \sqrt{2} t + C = \int\frac{dx}{\sqrt{1 - (1 - \lambda) ~\nd^2 x}}
+\end{equation}
+%
+Сделаем замену $u = \sn x$, тогда $\cn x = \sqrt{1 - u^2}$, $\dn x = \sqrt{1 - \lambda u^2}$, $du = \cn x ~\dn x dx$.
+%
+\begin{equation}
+S \sqrt{2} t + C = \frac{1}{\sqrt{\lambda}} \int \frac{du}{1 - u^2} = \frac{1}{2\sqrt{\lambda}} (\log(1 + u) - \log(1 - u)).
+\end{equation}
+%
+Откуда, при условии $u(0) = 0$, получается
+%
+\begin{equation}
+u(t) = \sn x = \frac{e^{2S\sqrt{2 \lambda} t} - 1}{e^{2S\sqrt{2 \lambda} t} + 1}.
+\end{equation}
+%
+Можно выразить $x(t)$ в явном виде:
+%
+\begin{equation}
+x(t) = F \left(\arcsin \left( \frac{e^{2S\sqrt{2 \lambda} t} - 1}{e^{2S\sqrt{2 \lambda} t} + 1} \right) , \lambda \right).
+\label{eq:instanton_fock}
+\end{equation}
 %
@@
 Чтобы было удобно, произведем преобразование координат: $x \to x + K(\lambda)$.
-В это случаем $\sd^2 x \to (1 - \lambda)^{-1} \cn^2 x$.
+В этом случае $\sd^2 x \to (1 - \lambda)^{-1} \cn^2 x$.
 Барьер окажется в точке $x = 0$.
@@
 \begin{equation}
-\frac{d^2 \Psi}{dx^2} + (E + \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
+\frac{d^2 \Psi}{dx^2} + (E - \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
 \end{equation}

### 2016-12-23 writing/alojdanc/draft.tex
G -> -G, E -> -E, B -> -B

@@
 	\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\[10pt]
-	\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad E = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\[10pt]
+	\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad E = \dfrac{\gamma_{--} - \gamma_{++}}{2}; \\[10pt]
 	C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\[10pt]
-	G = \dfrac{1}{2} \int (\Phi_+')^2 - (\Phi_-')^2 dx + \int ((\Phi_+)^2 - (\Phi_-)^2)U(x) dx.
+	G = \dfrac{1}{2} \int (\Phi_-')^2 - (\Phi_+')^2 dx + \int ((\Phi_-)^2 - (\Phi_+)^2)U(x) dx.
 \end{array}
@@
 \begin{equation}
-G = \beta_+ - \beta_- - 2E;
+G = \beta_- - \beta_+ - 2E;
 \end{equation}
@@
 \begin{array}{lcl}
-	\hat{H} & = & \dfrac{G}{2} (\psi_1^\dag \psi_2 +  \psi_1 \psi_2^\dag) + \dfrac{A}{2} (\psi_1^{\dag 2} \psi_1^2 + \psi_2^{\dag 2} \psi_2^2) \\[10pt]
-	& & +\dfrac{E}{2} (\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2) \\[10pt]
+	\hat{H} & = & -\dfrac{G}{2} (\psi_1^\dag \psi_2 +  \psi_1 \psi_2^\dag) + \dfrac{A}{2} (\psi_1^{\dag 2} \psi_1^2 + \psi_2^{\dag 2} \psi_2^2) \\[10pt]
+	& & -\dfrac{E}{2} (\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2) \\[10pt]
 	& & +\dfrac{C}{2} (\psi_1^{\dag 2} \psi_2^2 + 4 \psi_1^\dag \psi_1 \psi_2^\dag \psi_2 + \psi_1^2 \psi_2^{\dag 2}).
@@
 \begin{array}{lcl}
-	i \psi_{1,t} & = & (A |\psi_1|^2 + 2C |\psi_2|^2 + \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 + \\[10pt]
-	&& + (\dfrac{G}{2} + E |\psi_1|^2 + \dfrac{E}{2} |\psi_2|^2 + C \psi_1^* \psi_2) \psi_2; \\[10pt]
-	i \psi_{2,t} & = & (A |\psi_2|^2 + 2C |\psi_1|^2 + \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 + \\[10pt] 
-	&& + (\dfrac{G}{2} + E |\psi_2|^2 + \dfrac{E}{2}|\psi_1|^2 + C \psi_2^* \psi_1) \psi_1.
+	i \psi_{1,t} & = & (A |\psi_1|^2 + 2C |\psi_2|^2 - \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 - \\[10pt]
+	&& - (\dfrac{G}{2} + E |\psi_1|^2 + \dfrac{E}{2} |\psi_2|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
+	i \psi_{2,t} & = & (A |\psi_2|^2 + 2C |\psi_1|^2 - \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 - \\[10pt] 
+	&& - (\dfrac{G}{2} + E |\psi_2|^2 + \dfrac{E}{2}|\psi_1|^2 - C \psi_2^* \psi_1) \psi_1.
 \end{array}
@@
 \begin{array}{c}
-	i \psi_{1,t} = ((A - 2C) |\psi_1|^2 + \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 + (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_1|^2 + C \psi_1^* \psi_2) \psi_2; \\[10pt]
-	i \psi_{2,t} = ((A - 2C) |\psi_2|^2 + \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 + (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_2|^2 + C \psi_2^* \psi_1) \psi_1.
+	i \psi_{1,t} = ((A - 2C) |\psi_1|^2 - \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 - (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_1|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
+	i \psi_{2,t} = ((A - 2C) |\psi_2|^2 - \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 - (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_2|^2 - C \psi_2^* \psi_1) \psi_1.
 \end{array}
@@
 %
-$$\hat{H} = G S_x + A(S_z^2 + S_0^2 - S_0) + E(2S_0 - 1) S_x + C(S_x^2 - S_y^2 + S_0^2 - 2S_z^2).$$
+$$\hat{H} = -G S_x + A(S_z^2 + S_0^2 - S_0) - E(2S_0 - 1) S_x + C(S_x^2 - S_y^2 + S_0^2 - 2S_z^2).$$
 %
@@
 %
-$$\hat{H} = G S_x + A S_z^2 + E(2S_0 - 1) S_x + C(2 S_x^2 - S_z^2).$$
+$$\hat{H} = -G S_x + A S_z^2 - E(2S_0 - 1) S_x + C(2 S_x^2 - S_z^2).$$
 %
@@
 \begin{equation}
-\hat{H} = \alpha S_z^2 + \beta S_x^2 + B S_x.
+\hat{H} = \alpha S_z^2 + \beta S_x^2 - B S_x.
 \label{eq:spin_hamiltonian}
@@
 \begin{array}{lcl}
-	\hat{H} & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2 \phi) \dfrac{d}{d \phi} \\[10pt]
-	&& + BS \cos \phi - \beta S^2 \sin^2 \phi - \beta S \cos^2 \phi.
+	\hat{H} & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta (S - \frac{1}{2}) \sin 2 \phi - B \sin \phi) \dfrac{d}{d \phi} \\[10pt]
+	&& - BS \cos \phi - \beta S^2 \sin^2 \phi - \beta S \cos^2 \phi.
 \end{array}
@@
 \begin{array}{l}
-	(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2\phi) \dfrac{d \Phi}{d \phi} \\[10pt]
-	+ (E - BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
+	(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta (S - \frac{1}{2}) \sin 2\phi - B \sin \phi) \dfrac{d \Phi}{d \phi} \\[10pt]
+	+ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
 \end{array}
@@
 \begin{array}{l}
-	\alpha \dfrac{d^2 \Phi}{d x^2} + \dfrac{B~\sn x + 2 \beta S~\sn x~\cn x}{\dn x} \dfrac{d \Phi}{dx} \\[10pt]
-	+ (E - BS~\cn x + \beta S^2~\sn^2 x + \beta S~\cn^2 x) \Phi = 0.
+	\alpha \dfrac{d^2 \Phi}{d x^2} + \dfrac{-B~\sn x + 2 \beta S~\sn x~\cn x}{\dn x} \dfrac{d \Phi}{dx} \\[10pt]
+	+ (E + BS~\cn x + \beta S^2~\sn^2 x + \beta S~\cn^2 x) \Phi = 0.
 \end{array}
@@
 \begin{equation}
-f' = -\dfrac{B~\sn x + 2 \beta S~\sn x~\cn x}{2 \alpha~\dn x}.
+f' = \dfrac{B~\sn x - 2 \beta S~\sn x~\cn x}{2 \alpha~\dn x}.
 \label{eq:f_condition}
@@
 \begin{equation}
-f = S \ln~\dn x + \frac{B}{2 \sqrt{\beta(\alpha - \beta)}} \arctan \left( \sqrt{\frac{\beta}{\alpha - \beta}}~\cn x \right)
+f = S \ln~\dn x - \frac{B}{2 \sqrt{\beta(\alpha - \beta)}} \arctan \left( \sqrt{\frac{\beta}{\alpha - \beta}}~\cn x \right)
 \end{equation}
@@
 %
-$$f'' = -\frac{1}{2 \alpha} \left( B~\cn x + 2\beta S (\cn^2 x - \sn^2 x) + \frac{\beta B~\sn^2 x~\cn x + 2 \beta^2 S~\sn^2 x~\cn^2 x}{\alpha~\dn^2 x} \right).$$
+$$f'' = \frac{1}{2 \alpha} \left( B~\cn x - 2\beta S (\cn^2 x - \sn^2 x) + \frac{\beta B~\sn^2 x~\cn x - 2 \beta^2 S~\sn^2 x~\cn^2 x}{\alpha~\dn^2 x} \right).$$
 %
@@
 \begin{equation}
-V(x) = \frac{(\frac{1}{4}B^2 - \beta(\alpha - \beta) S (S+1))~\sn^2 x + \alpha B (S + \frac{1}{2})~\cn x}{\alpha~\dn^2 x}.
+V(x) = \frac{(\frac{1}{4}B^2 - \beta(\alpha - \beta) S (S+1))~\sn^2 x - \alpha B (S + \frac{1}{2})~\cn x}{\alpha~\dn^2 x}.
 \end{equation}
@@
 \begin{equation}
-V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x + \Lambda~\cn x}{\dn^2 x}.
+V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
 \end{equation}
 %
-Линейное преобразование пространственной координаты: $\phi \to \phi + \pi$, $x \to x + 2K(\lambda)$, потенциал изменится на
+%Линейное преобразование пространственной координаты: $\phi \to \phi + \pi$, $x \to x + 2K(\lambda)$, %потенциал изменится на
 %
-\begin{equation}
-V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
-\end{equation}
+%\begin{equation}
+%V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
+%\end{equation}
 %
@@
 \center{\includegraphics[width=1\linewidth]{pic/V_1period_shifted.eps}}
-\caption{$V(x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига}
+\caption{$V(x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$)}
 \end{figure}
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/V_Fock.eps}}
-\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$) после сдвига, $\lambda = 0.5$}
+\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$), $\lambda = 0.5$}
 \label{pic:potential_fock}
@@
 \center{\includegraphics[width=1\linewidth]{pic/V_Josephson.eps}}
-\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа) после сдвига, $\Lambda = 5$, $\lambda = 0.5$}
+\caption{$V_F (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа), $\Lambda = 5$, $\lambda = 0.5$}
 \label{pic:potential_josephson}
@@
 \center{\includegraphics[width=1\linewidth]{pic/V_Rabi.eps}}
-\caption{$V_R (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа) после сдвига, $\Lambda = 100$}
+\caption{$V_R (x)$ на 1-ом периоде функций Якоби ($[-2K; 2K]$ слева и $[-3K; K]$ справа), $\Lambda = 100$}
 \label{pic:potential_rabi}

### 2016-12-26 phase_transition/cn.m
Potential and modes figure done

@@ -1,0 +1,3 @@
+function [ f ] = cn( x, lambda )
+[~, f, ~] = ellipj(x, lambda);
+end

### 2016-12-26 phase_transition/dn.m

@@ -1,0 +1,3 @@
+function [ f ] = dn( x, lambda )
+[~, ~, f] = ellipj(x, lambda);
+end

### 2016-12-26 phase_transition/preparing_paper.m

@@ -1,0 +1,52 @@
+%% Preparing of different figures for the paper
+% Clearing
+clc; clear
+
+% Libs
+addpath ../finding_stationary_modes/
+
+%% Potential and localized symmetric / antisymmetric modes
+
+% U(x) = h (x^2 - x_0^2)^2
+% U(0) = h x_0^4; U(\pm x_0) = 0
+
+h = 10; x0 = 1;
+U = @(x) h * (x .^ 2 - x0^2) .^ 2;
+
+x = -1.5:0.01:1.5;
+
+figure('Position', [100 100 300 225]); hold on;
+plot(x, U(x), '-', 'LineWidth', 1, 'Color', 'k');
+
+% Nonlinearity parameter
+g = 1;
+
+% Chemical potential
+mu = 8;
+
+% Finding the solutions using the asymptotic behaviour from the article
+% Alfimov, Zezulin, Nonlinearity 20, 2007.
+% There the potential U(x) a x^4 - b x^2 was considered.
+a = h;
+b = - 2 * (x0 ^ 2) * h;
+
+% I use chemical potential correction to put the double-well potential U(x)
+% into U(0) = 0.
+mu_corrected = mu - h * (x0 ^ 2);
+
+params = [mu_corrected, a, b, g];
+xspan = [-3 0];
+
+c_symmetric = get_symmetric_mode_parameter(params, xspan);
+[X, Phi_symmetric] = get_symmetric_mode(params, c_symmetric, xspan);
+
+zero_level = 4;
+plot(X, Phi_symmetric(:, 1) + zero_level, 'LineWidth', 2, 'Color', 'k');
+
+c_asymmetric = get_asymmetric_mode_parameter(params, xspan);
+[X, Phi_asymmetric] = get_asymmetric_mode(params, c_asymmetric, xspan);
+
+plot(X, Phi_asymmetric(:, 1) + zero_level, '--', 'LineWidth', 2, 'Color', 'k');
+plot(X, zero_level * ones(1, length(X)), '-.', 'Color', 'k')
+
+xlabel('x')

### 2016-12-26 phase_transition/sd.m

@@ -1,0 +1,4 @@
+function [ f ] = sd( x, lambda )
+f = sn(x, lambda) ./ dn(x, lambda);
+end
+

### 2016-12-26 phase_transition/sn.m

@@ -1,0 +1,4 @@
+function [ f ] = sn( x, lambda )
+[f, ~, ~] = ellipj(x, lambda);
+end
+

### 2016-12-27 phase_transition/preparing_paper.m
Minor changes and figures

@@ -50,3 +50,129 @@ plot(X, Phi_asymmetric(:, 1) + zero_level, '--', 'LineWidth', 2, 'Color', 'k');
 plot(X, zero_level * ones(1, length(X)), '-.', 'Color', 'k')
 
 xlabel('x')
+
+%% Phase potential in elliptic coordinate with two parameters: \lambda, \Lambda
+clc; clear
+
+lambda = 0.9; Lambda = 2;
+V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
+	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
+
+K = ellipk(sqrt(lambda));
+x = -(4*K):0.01:(4*K);
+
+plot(x, V(x)); grid on
+
+%% Rabi regime
+Lambda = 100;
+lambda = [0 0.25 0.5 0.8];
+linewidth = [2 2 1 1];
+linestyle = {'--'; '-'; '--'; '-'};
+
+% figure('Position', [100 100 500 225]); hold on
+
+% No legend
+figure('Position', [100 100 325 225]); hold on
+
+for i = 1:length(lambda)
+	V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda(i) * (1 - lambda(i))) * (sn(x, lambda(i)) .^ 2) ...
+		- Lambda * cn(x, lambda(i)) ) ./ (dn(x, lambda(i)) .^ 2);
+	K = ellipk(sqrt(lambda(i)));
+	x = -(2*K):0.1:(2*K);
+	
+	plot(x, V(x), linestyle{i}, 'Color', 'black', 'LineWidth', linewidth(i));
+end
+
+h_legend = legend(...
+	  sprintf('\\lambda = %g', lambda(1)), ...
+	  sprintf('\\lambda = %g', lambda(2)), ...
+	  sprintf('\\lambda = %g', lambda(3)), ...
+	  sprintf('\\lambda = %g', lambda(4))  ...
+);
+
+% set(h_legend, 'location', 'northeastoutside');
+
+% Axis
+plot([-5, 5], [0 0], '--', 'Color', 'k');
+
+title(sprintf('\\Lambda = %g', Lambda));
+xlabel('x');
+ylabel('V_0(x)');
+
+%% Josephson regime
+
+Lambda = 0.4;
+lambda = [0 0.25 0.5 0.8];
[…]

### 2016-12-28 writing/phase_transition/phase_transition.tex
Article have been started

%% ****** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.1r of REVTeX, August 2010
%%
%%
%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\DeclarePairedDelimiter\bra{\langle}{\rvert}
\DeclarePairedDelimiter\ket{\lvert}{\rangle}
% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

\begin{document}

% Use the \preprint command to place your local institutional report
% number in the upper righthand corner of the title page in preprint mode.
% Multiple \preprint commands are allowed.
% Use the 'preprintnumbers' class option to override journal defaults
% to display numbers if necessary
%\preprint{}

%Title of paper
\title{Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{lalala}
%\email[]{Your e-mail address}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{}

%Collaboration name if desired (requires use of superscriptaddress
%option in \documentclass). \noaffiliation is required (may also be
%used with the \author command).
%\collaboration can be followed by \email, \homepage, \thanks as well.
%\collaboration{}
%\noaffiliation

\date{\today}

\begin{abstract}
bla-bla-bla
\end{abstract}

% insert suggested PACS numbers in braces on next line
\pacs{}
% insert suggested keywords - APS authors don't need to do this
%\keywords{}

%\maketitle must follow title, authors, abstract, \pacs, and \keywords
\maketitle

\newcommand{\sn}{\textrm{sn}}
\newcommand{\cn}{\textrm{cn}}
\newcommand{\dn}{\textrm{dn}}
\newcommand{\sd}{\textrm{sd}}
\newcommand{\cd}{\textrm{cd}}
\newcommand{\nd}{\textrm{nd}}
\newcommand{\am}{\textrm{am}}
% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{I.	Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
%\subsection{}
%\subsubsection{}
For last decade  investigations of  exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent one of mainstreams of current photonic and semiconductor technologies, see e.g. ~\cite{1,2}.  The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum wells excitons. Practically,  semiconductor microcavities are promising for various optoelectronic applications where quantum  matter-field interface  plays crucial role. In particular,  demonstrations of polariton laser with electrical pump ~\cite{3,4}, amplifiers ~\cite{5}, switches ~\cite{6},  transistors ~\cite{7}, polariton circuits and optical logic elements ~\cite{8,9}. Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true  thermodynamic equilibrium state ~\cite{10,11}.

Non-equilibrium, or, thermodynamically quasi-equilibrium  features of exciton polariton condensates play certain role in various manifestations of their collective  (many body) quantum states such as  superfluidity ~\cite{12,13},  quantized vortices ~\cite{14,15},  soliton formation ~\cite{16},  Josephson oscillations and macroscopic self-trapping ~\cite{17,18}. Since exciton polariton BEC’s in  present experiments examined at high enough (up to the room) temperatures the quantum  character of such a states should be examined even at equilibrium.

The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for practical purposes, see e.g. ~\cite{19}; especially for their possible applications for quantum information science purposes. Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom  made  microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives,  see, e.g., ~\cite{21,22,23}.  In particular, we would like to mention here problems of design ultrafast quantum gates ~\cite{22,23}, creation of relatively long Rabi oscillations ~\cite{19, 20} and quantum annealing problem ~\cite{24} where collective (bosonic) character of polariton BEC could be used. Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology for which   designing  of quantum interferometers and gyroscopes  possessing  high precision measurements with quantum phase states is utilized, cf. ~\cite{25, 26}.

In the paper we consider generic problem of quantum-classical phase transition with  exciton polariton condensates occurring in semiconductor  microcavity in the presence of Josephson effect with them, cf. ~\cite{27}. In general  this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf. ~\cite{28,29,30}. Evidently seminal studies on this topic relay to superconductor devices ~\cite{31} where macroscopic tunneling plays essential role. In particular, it worth to mention here Schrodinger cat state formation ~\cite{32} and design of quantum gates for quantum computing with  superconductor qubits where macroscopic  quantum coherent phase properties are used ~\cite{33}. Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC’s ~\cite{34}, and small ferromagnetic particles, ~\cite{35}. Strictly speaking main discussion is focused on investigation of quantum-classical escape rate transition that takes place in the presence of potential barrier at finite temperatures.

In the paper we propose  \textit{extended  model} for exciton polariton  Josephson junctions when energy of polariton-polariton scattering contributes into the tunneling parameter,  cf. ~\cite{36,37,38} and references therein.  In particularly, we pay our attention to temperature dependent critical phenomena occurring in the presence of macroscopic tunneling  . We aimed at elucidation of necessary criteria  to obtain   quantum phase regimes with trapped exciton polaritons  suitable for creation of exciton polariton qubit gates.

This paper is arranged as follows. In Sec. II, we explain in details our model to realize Josephson junction with exciton polariton condensates.  The extended tight-binding model will be established in this case. In Sec. III we …..In the conclusion, we summarize the results obtained.

\section{II. THE MODEL OD EXCITON POLARITON JOSEPHSON JUNCTION}
We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential  $U(x) = h ((x/x_0)^2 - 1)^2$, , sketched in Fig. 1; $2x_0$ defines 
distance between potential minima, $h$ depth of the potential. The Hamiltonian for the system of weakly interacting exciton polaritons  in an external $U(x)$  can be written in the second quantized form as:
\begin{equation}
\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx.
\label{eq:gpe_hamiltonian}
\end{equation}
where $\hat{\psi} \equiv \hat{\psi}(z,t)$ is polariton  field operator that annihilate a particle at the position $z$ and time $t$, $g$  is two-body (polariton-polariton) scattering length. In the paper we use so-called  two-mode representation of $\hat{\psi}$ supposing 
\begin{equation}
\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
\label{eq:two_modes}
\end{equation}
where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate  wavefunctions which are responsible for it spatial distribution. It is instructive to recast $\Phi_{1,2}(x)$ as
\begin{equation}
\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
\label{eq:conditions}
\end{equation}
where $\Phi_{\pm}(x) = \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real  wavefunctions obeying  stationary Gross-Pitaevskii equations, respectively
\begin{equation}
\mu_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
\label{eq:stationary}
\end{equation}
and  normalization condition $\int \Phi_{\pm}^2 dx = 1$ $\mu_{\pm}$ are chemical  potentials. As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit “hat” design for simplicity). Substituting (\ref{eq:conditions}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to 
\begin{equation}
\begin{array}{lcl}
\hat{H} & = & \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 +  \hat{\psi}_1 \hat{\psi}_2^\dag) + \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) \\[10pt]
& & +\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\[10pt]
& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}).
\end{array}
\label{eq:hamiltonian}
\end{equation}
where  we made denotations 
\begin{equation}
\begin{array}{c}
\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\[10pt]
\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\[10pt]
C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\[10pt]
G = \mu_- - \mu_+ - 2\Gamma;\\[10pt]
\end{array}
\label{eq:subs}
\end{equation}
Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double well potential. It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$. The contribution from relevant coefficients on can be estimated from variational ansatz 
\begin{equation}
\Phi_{\pm} = A_{\pm} \Big[\exp\Big(-\dfrac{(x-x_0)^2}{2a^2}\Big) \pm \exp\Big(-\dfrac{(x+x_0)^2}{2a^2}\Big)\Big]
\label{eq:two_modes_eq}
\end{equation}
where  $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other),   defined from normalization conditions. In Fig.2 the behavior  of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in {+,-}$ as a function of  half of intra-well distance $x_0$ is shown. It is important that at differences between them rapidly vanishes with increasing of distance  $x_0$. We can suppose $\Gamma = C = 0$ for $x_0 >> a$. This limit exactly corresponds to familiar problem of two weakly linked  condensates at zero temperature \underline{- see e.g. ~\cite{39} and cf.  }.
\section{III. The Quantum Phase}
To elucidate important quantum phase features  of our extended Josephson model  it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as 
\begin{subequations}
\begin{align}
\hat{S}_x = \dfrac{1}{2}(\hat{\psi}_1^\dag\hat{\psi}_2+\hat{\psi}_1\hat{\psi}_2^\dag) = s\cos(\phi)-\sin(\phi)\dfrac{d}{d\phi}, \\[10pt]
\quad \hat{S}_y = \dfrac{i}{2}(\hat{\psi}_1^\dag\hat{\psi}_2-\hat{\psi}_1\hat{\psi}_2^\dag) = s\sin(\phi)+\cos(\phi)\dfrac{d}{d\phi}, \\[10pt]
\hat{S}_z = \dfrac{1}{2}(\hat{\psi}_2^\dag\hat{\psi}_2+\hat{\psi}_1^\dag\hat{\psi}_1) = -i\dfrac{d}{d\phi},
\end{align}
\label{eq:pseudo_spin}
\end{subequations}
where $s = \dfrac{N}{2} >> 1$ is large \underline{ $C$ - number}, $\phi$ is phase variable. The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar \underline{ SU(2)} algebra commutation relations
\begin{equation}
[S_x, S_y] = iS_z,  \quad[S_z, S_x] = iS_y,  \quad[S_y, S_z] = iS_x.
\label{eq:commutation_relations}
\end{equation}
After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
\begin{equation}
\begin{array}{lcl}
H & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (B \sin \phi + \beta (s - \frac{1}{2}) \sin 2 \phi) \dfrac{d}{d \phi} \\[10pt]
&& + Bs \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
\end{array}
\label{eq:hamiltinian_s}
\end{equation}
where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = FN + G > 0$. Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = gamma$ supposing $\Gamma = 0$ for simplicity, see Fig.2.
Hamiltonian (\ref{eq:hamiltinian_s}) corresponds to Schrodinger equation
\begin{equation}
\begin{array}{l}
(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2\phi) \dfrac{d \Phi}{d \phi} \\[10pt]
+ (E - BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
\end{array}
\label{eq:Schrodinger}
\end{equation}
where $\Phi \equiv \Phi(phi)$ is  unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. ~\cite{40}. Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:Schrodinger}) can be obtained by applying  so-called phase-state representation, \underline{cf. [  ]}.
\begin{equation}
\ket{\psi} = \dfrac{1}{2\pi}\int_{-\infty}^{+\infty}d\phi\Phi(\phi)\ket{\phi}
\end{equation}
where
\begin{equation}
\ket{\phi} = \dfrac{1}{\sqrt{N!}}\Big[\exp^{i\phi/2}\psi_1^\dagger+\exp^{-i\phi/2}\psi_2^\dag\Big]^N\ket{0}_1\ket{0}
\end{equation}
is macroscopic coherent spin-state (macroscopic qubit state)  that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. ~\cite{41}.
It is possible to eliminate the term with first derivative in  Eq.(\ref{eq:Schrodinger}) applying the transformation
\begin{equation}
\Phi(\phi) = \Psi(x)\exp\Big[s\ln\dn{x}-\dfrac{\Lambda s}{2\sqrt{\lambda(1-\lambda)}}\arctan\Big(\sqrt{\dfrac{\lambda}{1-\lambda}}\cn{x}\Big)\Big]
\label{eq:transformation_of_Phi}
\end{equation}
where $x = \int \limits_0^\phi \dfrac{d \phi'}{\sqrt{1 - \frac{\beta}{\alpha} \sin^2 \phi'}} = F(\phi, \sqrt{\beta / \alpha}) = F(\phi, \sqrt{\lambda})$ is new phase variable, $F(\phi, \sqrt{\lambda})$ is incomplete elliptic integral of the first kind.  In (\ref{eq:transformation_of_Phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha S}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
Inserting (\ref{eq:transformation_of_Phi}) into (\ref{eq:Schrodinger}) we come to  convenient Schrodinger equation
\begin{equation}
\dfrac{d^2\Psi}{dx^2} + (E - V(x))\Psi = 0
\label{eq:Schrodinger_usual}
\end{equation}
for quantum particle with mass $m_{eff} = \dfrac{1}{2}$,  normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(x) = s^2V_0(x)$ with
\begin{equation}
V_0(x) = \dfrac{(\dfrac{1}{4}\Lambda^2-\lambda(1-\lambda))\sn^2{x}-\Lambda\cn{x}}{\dn^2{x}}
\label{eq:potential}
\end{equation}
The results  known for quantum phase mesoscopic Josephson junction model can be recovered  from  (\ref{eq:Schrodinger_usual}), (\ref{eq:potential}) at $\lambda = 0$. 
The dependence of $\lambda$-parameter  on  normalized  half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from    (\ref{eq:subs}), (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5\Big(\exp\Big[\dfrac{2x_0^2}{a^2}\Big]-1\Big)^{-1}$. The limit $\lambda = 0$ obtained for infinitely large intra-well distances $x_0 \to \infty$. On the other hand, parameter grows rapidly at $\dfrac{x_0}{a} \ll 1$. Obviously, in this limit our Josephson junction model inherent based on relatively weak coupling between wells breaks down. Below we  examine case of $0 < \lambda < 1$ that could be obtained at moderate values $\dfrac{x_0}{a}$ of such as $\dfrac{x_0}{a} \geq 0.45$. 
Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf.  ~\cite{40}. The dependences of  trapping potential $V_0(x)$ are shown in Fig. 3. 
\subsection{Rabi regime}
$\Lambda \gg 1$. In this limit the trapping potential reads
\begin{equation}
V_R(x) = \dfrac{1}{4}\Lambda^2\sd^2{x}
\label{eq:rabi_potential}
\end{equation}
It is interesting to note that….
\subsection{Fock regime}
In this regime it is instructive to distinguish two limits.    First, we suppose that inequality $\lambda \ll \lambda < 1$.    In this case from (\ref{eq:potential}) one can obtain
\begin{equation}
V_F(x) = -\lambda(1-\lambda)\sd^2{x}
\label{eq:fock1_potential}
\end{equation}
Another limit that could be studied within Fock regime is relevant to condition $\Lambda^2 < \lambda < \Lambda$. In this case  from (\ref{eq:potential}) we have 
\begin{equation}
V_0(x) = \dfrac{-\Lambda\cn{x}}{\dn^2{x}}
\label{eq:fock2_potential}
\end{equation}
Equation (\ref{eq:fock2_potential}) for negligible    reproduces results for convenient quantum phase model ~\cite{40}. 
\subsection{Josephson regime}
$\Lambda \leq 1$. This regime represents intermediate  case between Rabi and Fock regimes.   In general all terms in (\ref{eq:potential}) should be kept.
\section{IV. Quantum-classical phase transitions}
Strictly speaking,  results  established in previous section are completely valid at  zero temperature. However, in current experiments exciton polariton condensate is observed at finite and high enough temperatures. In this section we find answer to vital question: when quantum approach to the phase problem for exciton polariton Josephson junction is valid?
....
\section{V. Conclusion}
....
% If in two-column mode, t his environment will change to single-column
% format so that long equations can be displayed. Use
% sparingly.
%\begin{widetext}
% put long equation here
%\end{widetext}

% figures should be put into the text as floats.
% Use the graphics or graphicx packages (distributed with LaTeX2e)
% and the \includegraphics macro defined in those packages.
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz,
% and Frank Mittelbach for instance.
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Use the figure* environment if the figure should span across the
% entire page. There is no need to do explicit centering.

% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}

% Surround figure environment with turnpage environment for landscape
% figure
% \begin{turnpage}
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}
% \end{turnpage}

% tables should appear as floats within the text
%
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
% The ruledtabular enviroment adds doubled rules to table and sets a
% reasonable default table settings.
% Use the table* environment to get a full-width table in two-column
% Add \usepackage{longtable} and the longtable (or longtable*}
% environment for nicely formatted long tables. Or use the the [H]
% placement option to break a long table (with less control than 
% in longtable).
% \begin{table}%[H] add [H] placement to break table across pages
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% Lines of table here ending with \\
% \end{tabular}
% \end{ruledtabular}
% \end{table}

% Surround table environment with turnpage environment for landscape
% table
% \begin{turnpage}
% \begin{table}
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% \end{tabular}
% \end{ruledtabular}
% \end{table}
% \end{turnpage}

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
%\appendix
%\section{}

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% put your acknowledgments here.
%\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{list}

\end{document}
%
% ****** End of file apstemplate.tex ******

### 2016-12-28 writing/alojdanc/draft.tex
Potential and modes figure done
Minor changes and figures
New potentials, \Phi_{\pm} was numerically constructed

@@
 Здесь $\int |\psi|^2 dx = N$, где $N$ -- число атомов.
-Потенциал имеет вид $U(x) = h ((x/x_0)^2 - 1)^2$ (или, возможно, другой симметричный double-well потенциал).
+Потенциал имеет вид
+%
+\begin{equation}
+U(x) = h ((x/x_0)^2 - 1)^2.
+\label{eq:gpe_potential}
+\end{equation}
+%
 Гаильтониан этого уравнения выглядит следующим образом:
@@
 \begin{equation}
-\beta_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
+\mu_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
 \label{eq:stationary}
@@
 Также $\int |\psi|^2 dx = \int |\psi_1 \Phi_1 + \psi_2 \Phi_2|^2 = |\psi_1|^2 + |\psi_2|^2 = N$.
+%
+На Рис. \ref{pic:potential_and_modes} показан пример симметричной и антисимметричной моды, $|| \Phi_{\pm} || = 1$.
+Они и соответствующие им значения $\mu_{\pm}$ были построены численно с помощью техники выхода из линейного приближения. 
+%
+\begin{figure}[Ht!]
+\center{\includegraphics[width=0.5\linewidth]{pic/potential_and_modes.eps}}
+\caption{Пример симметричной (толстая сплошная) $\Phi_+(x)$ и антисимметричной $\Phi_-(x)$ (пунктирная) мод уравнения (\ref{eq:stationary}) c параметрами потенциала (\ref{eq:gpe_potential}) $h = 10$, $x_0 = 1$.
+Значения хим.
+потенциалов $\mu_+ = 5.7355$, $\mu_- = 6.5653$.}
+\label{pic:potential_and_modes}
+\end{figure}
+%
+
 Теперь подставим выражение (\ref{eq:two_modes}) в гамильтониан (\ref{eq:gpe_hamiltonian}) и проинтегрируем.
@@
 	\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\[10pt]
-	\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad E = \dfrac{\gamma_{--} - \gamma_{++}}{2}; \\[10pt]
+	\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{--} - \gamma_{++}}{2}; \\[10pt]
 	C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\[10pt]
@@
 \begin{equation}
-G = \beta_- - \beta_+ - 2E;
+G = \mu_- - \mu_+ - 2\Gamma;
 \end{equation}
@@
 	\hat{H} & = & -\dfrac{G}{2} (\psi_1^\dag \psi_2 +  \psi_1 \psi_2^\dag) + \dfrac{A}{2} (\psi_1^{\dag 2} \psi_1^2 + \psi_2^{\dag 2} \psi_2^2) \\[10pt]
-	& & -\dfrac{E}{2} (\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2) \\[10pt]
+	& & -\dfrac{\Gamma}{2} (\psi_1^{\dag 2} \psi_1 \psi_2 + \psi_1^\dag \psi_1^2 \psi_2^\dag + \psi_1^\dag \psi_2^\dag \psi_2^2 + \psi_1 \psi_2^{\dag 2} \psi_2) \\[10pt]
 	& & +\dfrac{C}{2} (\psi_1^{\dag 2} \psi_2^2 + 4 \psi_1^\dag \psi_1 \psi_2^\dag \psi_2 + \psi_1^2 \psi_2^{\dag 2}).
@@
 \begin{array}{lcl}
-	i \psi_{1,t} & = & (A |\psi_1|^2 + 2C |\psi_2|^2 - \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 - \\[10pt]
-	&& - (\dfrac{G}{2} + E |\psi_1|^2 + \dfrac{E}{2} |\psi_2|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
-	i \psi_{2,t} & = & (A |\psi_2|^2 + 2C |\psi_1|^2 - \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 - \\[10pt] 
-	&& - (\dfrac{G}{2} + E |\psi_2|^2 + \dfrac{E}{2}|\psi_1|^2 - C \psi_2^* \psi_1) \psi_1.
+	i \psi_{1,t} & = & (A |\psi_1|^2 + 2C |\psi_2|^2 - \dfrac{\Gamma}{2} \psi_1 \psi_2^*) \psi_1 - \\[10pt]
+	&& - (\dfrac{G}{2} + \Gamma |\psi_1|^2 + \dfrac{\Gamma}{2} |\psi_2|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
+	i \psi_{2,t} & = & (A |\psi_2|^2 + 2C |\psi_1|^2 - \dfrac{\Gamma}{2} \psi_2 \psi_1^*) \psi_2 - \\[10pt] 
+	&& - (\dfrac{G}{2} + \Gamma |\psi_2|^2 + \dfrac{\Gamma}{2}|\psi_1|^2 - C \psi_2^* \psi_1) \psi_1.
 \end{array}
@@
 \begin{array}{c}
-	i \psi_{1,t} = ((A - 2C) |\psi_1|^2 - \dfrac{E}{2} \psi_1 \psi_2^*) \psi_1 - (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_1|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
-	i \psi_{2,t} = ((A - 2C) |\psi_2|^2 - \dfrac{E}{2} \psi_2 \psi_1^*) \psi_2 - (\dfrac{G}{2} + \dfrac{EN}{2} + \dfrac{E}{2} |\psi_2|^2 - C \psi_2^* \psi_1) \psi_1.
+	i \psi_{1,t} = ((A - 2C) |\psi_1|^2 - \dfrac{\Gamma}{2} \psi_1 \psi_2^*) \psi_1 - (\dfrac{G}{2} + \dfrac{\Gamma N}{2} + \dfrac{\Gamma}{2} |\psi_1|^2 - C \psi_1^* \psi_2) \psi_2; \\[10pt]
+	i \psi_{2,t} = ((A - 2C) |\psi_2|^2 - \dfrac{\Gamma}{2} \psi_2 \psi_1^*) \psi_2 - (\dfrac{G}{2} + \dfrac{\Gamma N}{2} + \dfrac{\Gamma}{2} |\psi_2|^2 - C \psi_2^* \psi_1) \psi_1.
 \end{array}
@@
 %
-$$\hat{H} = -G S_x + A(S_z^2 + S_0^2 - S_0) - E(2S_0 - 1) S_x + C(S_x^2 - S_y^2 + S_0^2 - 2S_z^2).$$
+$$\hat{H} = -G S_x + A(S_z^2 + S_0^2 - S_0) - \Gamma (2S_0 - 1) S_x + C(S_x^2 - S_y^2 + S_0^2 - 2S_z^2).$$
 %
@@
 %
-$$\hat{H} = -G S_x + A S_z^2 - E(2S_0 - 1) S_x + C(2 S_x^2 - S_z^2).$$
+$$\hat{H} = -G S_x + A S_z^2 - \Gamma (2S_0 - 1) S_x + C(2 S_x^2 - S_z^2).$$
 %
-Заметим, что $A - C = 2 \gamma_{+-} = \alpha > 0$, также $2S_0 = N \gg 1$; $2C = \beta$; $EN+G = B$.
+Заметим, что $A - C = 2 \gamma_{+-} = \alpha > 0$, также $2S_0 = N \gg 1$; $2C = \beta$; $\Gamma N+G = B$.
 Приходим к следующему выражению для гамильтониана:
@@
 \begin{equation}
-S_z = -i \dfrac{d}{d \phi}, \quad S_x = S \cos \phi - \sin \phi \dfrac{d}{d \phi}, \quad S_y = S \sin \phi + \cos \phi \dfrac{d}{d \phi}.
+S_z = -i \dfrac{d}{d \phi}, \quad S_x = s \cos \phi - \sin \phi \dfrac{d}{d \phi}, \quad S_y = s \sin \phi + \cos \phi \dfrac{d}{d \phi}.
 \label{eq:diff_repr}
@@
 \begin{array}{lcl}
-	S_x^2 & = & (S \cos \phi - \sin \phi \dfrac{d}{d \phi})^2 = \\
-	& = & S^2 \cos^2 \phi + S \sin^2 \phi + (\frac{1}{2} - S) \sin 2 \phi \dfrac{d}{d \phi} + \sin^2 \phi \dfrac{d^2}{d \phi^2}.
+	S_x^2 & = & (s \cos \phi - \sin \phi \dfrac{d}{d \phi})^2 = \\
+	& = & s^2 \cos^2 \phi + s \sin^2 \phi + (\frac{1}{2} - s) \sin 2 \phi \dfrac{d}{d \phi} + \sin^2 \phi \dfrac{d^2}{d \phi^2}.
 \end{array}
@@
 \begin{array}{lcl}
-	\hat{H} & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta (S - \frac{1}{2}) \sin 2 \phi - B \sin \phi) \dfrac{d}{d \phi} \\[10pt]
-	&& - BS \cos \phi - \beta S^2 \sin^2 \phi - \beta S \cos^2 \phi.
+	\hat{H} & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta (s - \frac{1}{2}) \sin 2 \phi - B \sin \phi) \dfrac{d}{d \phi} \\[10pt]
+	&& - B s \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
 \end{array}
@@
 \begin{array}{l}
-	(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta (S - \frac{1}{2}) \sin 2\phi - B \sin \phi) \dfrac{d \Phi}{d \phi} \\[10pt]
-	+ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
+	(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta (s - \frac{1}{2}) \sin 2\phi - B \sin \phi) \dfrac{d \Phi}{d \phi} \\[10pt]
+	+ (E + B s \cos \phi + \beta s^2 \sin^2 \phi + \beta s \cos^2 \phi) = 0.
 \end{array}
@@
 \begin{array}{l}
-	\alpha \dfrac{d^2 \Phi}{d x^2} + \dfrac{-B~\sn x + 2 \beta S~\sn x~\cn x}{\dn x} \dfrac{d \Phi}{dx} \\[10pt]
-	+ (E + BS~\cn x + \beta S^2~\sn^2 x + \beta S~\cn^2 x) \Phi = 0.
+	\alpha \dfrac{d^2 \Phi}{d x^2} + \dfrac{-B~\sn x + 2 \beta s~\sn x~\cn x}{\dn x} \dfrac{d \Phi}{dx} \\[10pt]
+	+ (E + B s~\cn x + \beta s^2~\sn^2 x + \beta s~\cn^2 x) \Phi = 0.
 \end{array}
@@
 \begin{equation}
-f' = \dfrac{B~\sn x - 2 \beta S~\sn x~\cn x}{2 \alpha~\dn x}.
+f' = \dfrac{B~\sn x - 2 \beta s~\sn x~\cn x}{2 \alpha~\dn x}.
 \label{eq:f_condition}
@@
 \begin{equation}
-f = S \ln~\dn x - \frac{B}{2 \sqrt{\beta(\alpha - \beta)}} \arctan \left( \sqrt{\frac{\beta}{\alpha - \beta}}~\cn x \right)
+f = s \ln~\dn x - \frac{B}{2 \sqrt{\beta(\alpha - \beta)}} \arctan \left( \sqrt{\frac{\beta}{\alpha - \beta}}~\cn x \right)
 \end{equation}
@@
 %
-$$f'' = \frac{1}{2 \alpha} \left( B~\cn x - 2\beta S (\cn^2 x - \sn^2 x) + \frac{\beta B~\sn^2 x~\cn x - 2 \beta^2 S~\sn^2 x~\cn^2 x}{\alpha~\dn^2 x} \right).$$
+$$f'' = \frac{1}{2 \alpha} \left( B~\cn x - 2\beta s (\cn^2 x - \sn^2 x) + \frac{\beta B~\sn^2 x~\cn x - 2 \beta^2 s~\sn^2 x~\cn^2 x}{\alpha~\dn^2 x} \right).$$
 %
@@
 \begin{equation}
-V(x) = \frac{(\frac{1}{4}B^2 - \beta(\alpha - \beta) S (S+1))~\sn^2 x - \alpha B (S + \frac{1}{2})~\cn x}{\alpha~\dn^2 x}.
+V(x) = \frac{(\frac{1}{4}B^2 - \beta(\alpha - \beta) s (s+1))~\sn^2 x - \alpha B (s + \frac{1}{2})~\cn x}{\alpha~\dn^2 x}.
 \end{equation}
@@
 Введем обозначения $\Lambda = \frac{G}{\alpha S}$, $\lambda = \beta / \alpha$.
-Далее полагаем, что $E = 0$, $B = EN + G = G$, $S = N/2 \gg 1$, тогда уравнение (\ref{eq:shrod1}) можно переписать в виде
+Далее полагаем, что $\Gamma = 0$, $B = \Gamma N + G = G$, $s = N/2 \gg 1$, тогда уравнение (\ref{eq:shrod1}) можно переписать в виде
 %
 \begin{equation}
-\frac{d^2 \Psi}{dx^2} + (E - S^2 V(x)) \Psi = 0,
+\frac{d^2 \Psi}{dx^2} + (E - s^2 V(x)) \Psi = 0,
 \label{eq:shrod2}
@@
 %
-%Линейное преобразование пространственной координаты: $\phi \to \phi + \pi$, $x \to x + 2K(\lambda)$, %потенциал изменится на
-%
-%\begin{equation}
-%V(x) = \frac{(\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda))~\sn^2 x - \Lambda~\cn x}{\dn^2 x}.
-%\end{equation}
-%
 Построим графики $V(x)$ для различных значений параметров $\Lambda$, $\lambda$.
@@
 %
-%\begin{figure}[Ht!]
-%\center{\includegraphics[width=1\linewidth]{pic/V_1period_shifted_asym.eps}}
-%\caption{На 1-ом периоде функций Якоби ($[-3K; K]$)}
-%\end{figure}
-%
 
@@
 \begin{equation}
-\frac{1}{2} \dot{x}^2 = S^2 V(x) - E.
+\frac{1}{2} \dot{x}^2 = s^2 V(x) - E.
 \label{eq:newton}
@@
 \begin{equation}
-V_F (x) = -\lambda (1 - \lambda) (2x^2 - 8(1 - 2\lambda)x^4 + o(x^4)).
+V_F (x) = -\lambda (1 - \lambda) \left( x^2 + \frac{2\lambda - 1}{3} x^4 + o(x^4) \right).
 \end{equation}
@@
 \begin{equation}
-\frac{1}{2 S^2} \dot{x}^2 = \lambda - \lambda (1 - \lambda) ~\sd^2 x = 1 - (1 - \lambda) ~\nd^2 x.
+\frac{1}{2 s^2} \dot{x}^2 = \lambda - \lambda (1 - \lambda) ~\sd^2 x = 1 - (1 - \lambda) ~\nd^2 x.
 \end{equation}
@@
 \begin{equation}
-S \sqrt{2} t + C = \int\frac{dx}{\sqrt{1 - (1 - \lambda) ~\nd^2 x}}
+s \sqrt{2} t + C = \int\frac{dx}{\sqrt{1 - (1 - \lambda) ~\nd^2 x}}
 \end{equation}
@@
 \begin{equation}
-S \sqrt{2} t + C = \frac{1}{\sqrt{\lambda}} \int \frac{du}{1 - u^2} = \frac{1}{2\sqrt{\lambda}} (\log(1 + u) - \log(1 - u)).
+s \sqrt{2} t + C = \frac{1}{\sqrt{\lambda}} \int \frac{du}{1 - u^2} = \frac{1}{2\sqrt{\lambda}} (\log(1 + u) - \log(1 - u)).
 \end{equation}
@@
 \begin{equation}
-u(t) = \sn x = \frac{e^{2S\sqrt{2 \lambda} t} - 1}{e^{2S\sqrt{2 \lambda} t} + 1}.
+u(t) = \sn x = \frac{e^{2 s \sqrt{2 \lambda} t} - 1}{e^{2S\sqrt{2 \lambda} t} + 1}.
 \end{equation}
@@
 \begin{equation}
-x(t) = F \left(\arcsin \left( \frac{e^{2S\sqrt{2 \lambda} t} - 1}{e^{2S\sqrt{2 \lambda} t} + 1} \right) , \lambda \right).
+x(t) = \sn^{-1} \left( \frac{e^{2s\sqrt{2 \lambda} t} - 1}{e^{2s\sqrt{2 \lambda} t} + 1} \right) = F \left(\arcsin \left( \frac{e^{2s\sqrt{2 \lambda} t} - 1}{e^{2s\sqrt{2 \lambda} t} + 1} \right) , \lambda \right).
 \label{eq:instanton_fock}
@@
 \begin{equation}
-\frac{d^2 \Psi}{dx^2} + (E + S^2 \Lambda - \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
+\frac{d^2 \Psi}{dx^2} + (E + s^2 \Lambda - \left( \frac{s \Lambda}{2} \right)^2 x^2) \Psi = 0.
 \end{equation}
 %
-После замены $x \to \sqrt{\frac{S \Lambda}{2}} x$, $\tilde{E} = \frac{2}{S \Lambda} (E + S^2 \Lambda)$:
+После замены $x \to \sqrt{\frac{s \Lambda}{2}} x$, $\tilde{E} = \frac{2}{s \Lambda} (E + s^2 \Lambda)$:
 %
@@
 %
-Уровни энергии: $\tilde{E} = 2n + 1$ или $E = S \Lambda (n + \frac{1}{2}) - S^2 \Lambda$.
+Уровни энергии: $\tilde{E} = 2n + 1$ или $E = s \Lambda (n + \frac{1}{2}) - s^2 \Lambda$.
 Собственные функции выражаются через полиномы Эрмита.
@@
 \begin{equation}
-\frac{d^2 \Psi}{dx^2} + (E - \frac{S^2 \Lambda^2}{4 (1 - \lambda)} ~\cn^2 x) \Psi = 0.
+\frac{d^2 \Psi}{dx^2} + (E - \frac{s^2 \Lambda^2}{4 (1 - \lambda)} ~\cn^2 x) \Psi = 0.
 \end{equation}
@@
 \begin{equation}
-\frac{1}{2} \dot{x}^2 = S^2 V(x) - E.
+\frac{1}{2} \dot{x}^2 = s^2 V(x) - E.
 \end{equation}
@@
 \begin{equation}
-\frac{d^2 \Psi}{dx^2} + (E - \left( \frac{S \Lambda}{2} \right)^2 x^2) \Psi = 0.
+\frac{d^2 \Psi}{dx^2} + (E - \left( \frac{s \Lambda}{2} \right)^2 x^2) \Psi = 0.
 \end{equation}
 %
-После замены $x \to \sqrt{\frac{S \Lambda}{2}} x$, $\tilde{E} = \frac{2}{S \Lambda} E$:
+После замены $x \to \sqrt{\frac{s \Lambda}{2}} x$, $\tilde{E} = \frac{2}{s \Lambda} E$:
 %
@@
 %
-Уровни энергии: $\tilde{E} = 2n + 1$ или $E = S \Lambda (n + \frac{1}{2})$.
+Уровни энергии: $\tilde{E} = 2n + 1$ или $E = s \Lambda (n + \frac{1}{2})$.
 Собственные функции выражаются через полиномы Эрмита.
@@
 Он связан с температурой фазового перехода.
-Рассмотрим малые колебания в яме: $\sn~x \sim x$, $\cn~x \sim 1$, $\dn~x \sim 1$.
+Рассмотрим малые колебания в яме:
+%
+\begin{equation}
+\begin{array}{l}
+	\sd^2 x = x^2 + o(x^2); \\[10pt]
+	\frac{\cn x}{\dn^2 x} = 1 + \frac{2\lambda - 1}{2} x^2 + o(x^2).
+\end{array}
+\end{equation}
+%
 Уравнение, описывающее мылые колебания:
@@
 \begin{equation}
-\ddot{x} - 2S^2 (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) x = 0.
+\ddot{x} - s^2 \left( \frac{1}{2} \Lambda^2 - (2\lambda - 1)\Lambda - 2 \lambda (1 - \lambda) \right) x = 0.
 \end{equation}
@@
 \begin{equation}
-\omega_0 = \sqrt{2S^2 (\lambda (1 - \lambda) - \frac{1}{4} \Lambda^2)}.
+\omega_0 = s \sqrt{2 \lambda (1 - \lambda) + (2\lambda - 1)\Lambda - \frac{1}{2} \Lambda^2}.
 \end{equation}
@@
 \begin{equation}
-\tau_0 = \frac{2 \pi}{\omega_0} = \frac{2 \pi}{\sqrt{2S^2 (\lambda (1 - \lambda) - \frac{1}{4} \Lambda^2)}}.
+\tau_0 = \frac{2 \pi}{\omega_0} = \frac{2 \pi}{s \sqrt{2 \lambda (1 - \lambda) + (2\lambda - 1)\Lambda - \frac{1}{2} \Lambda^2}}.
 \end{equation}
@@
 \begin{equation}
-\lambda (1 - \lambda) > \frac{1}{4} \Lambda^2.
+2 \lambda (1 - \lambda) + (2\lambda - 1)\Lambda - \frac{1}{2} \Lambda^2 > 0.
 \end{equation}

### 2016-12-28 phase_transition/preparing_paper.m

@@ -15,41 +15,64 @@ U = @(x) h * (x .^ 2 - x0^2) .^ 2;
 
 x = -1.5:0.01:1.5;
 
-figure('Position', [100 100 300 225]); hold on;
-plot(x, U(x), '-', 'LineWidth', 1, 'Color', 'k');
-
 % Nonlinearity parameter
 g = 1;
 
 % Chemical potential
-mu = 8;
+% mu = 8;
 
-% Finding the solutions using the asymptotic behaviour from the article
-% Alfimov, Zezulin, Nonlinearity 20, 2007.
-% There the potential U(x) a x^4 - b x^2 was considered.
+xspan = [-3 0];
+
 a = h;
 b = - 2 * (x0 ^ 2) * h;
+
+% Symmetric mode, mu = 5.7355, mu_corrected = -4.2645
+% I found this chemical potential with using of my finding normalized modes
+% procedure based on the asymptotic behaviour from the article Alfimov, Zezulin,
+% Nonlinearity 20, 2007. There the potential U(x) a x^4 - b x^2 was considered.
+mu = 5.7355;
 
 % I use chemical potential correction to put the double-well potential U(x)
 % into U(0) = 0.
 mu_corrected = mu - h * (x0 ^ 2);
-
 params = [mu_corrected, a, b, g];
-xspan = [-3 0];
 
 c_symmetric = get_symmetric_mode_parameter(params, xspan);
 [X, Phi_symmetric] = get_symmetric_mode(params, c_symmetric, xspan);
 
-zero_level = 4;
-plot(X, Phi_symmetric(:, 1) + zero_level, 'LineWidth', 2, 'Color', 'k');
+% Asymmetric mode, mu = 6.5653, mu_corrected = -3.4347
+% I found this chemical potential in the same way
+mu = 6.5653;
+
+mu_corrected = mu - h * (x0 ^ 2);
+params = [mu_corrected, a, b, g];
 
 c_asymmetric = get_asymmetric_mode_parameter(params, xspan);
 [X, Phi_asymmetric] = get_asymmetric_mode(params, c_asymmetric, xspan);
 
-plot(X, Phi_asymmetric(:, 1) + zero_level, '--', 'LineWidth', 2, 'Color', 'k');
[…]

### 2017-01-07 writing/phase_transition/phase_transition.tex
Refactoring

@@
-%% ****** Start of file apstemplate.tex ****** %
-%%
-%%
-%%   This file is part of the APS files in the REVTeX 4 distribution.
-%%   Version 4.1r of REVTeX, August 2010
-%%
-%%
-%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
-%%
-%%   See the REVTeX 4 README file for restrictions and more information.
-%%
-%
-% This is a template for producing manuscripts for use with REVTEX 4.0
-% Copy this file to another name and then work on that file.
-% That way, you always have this original template file to use.
-%
-% Group addresses by affiliation; use superscriptaddress for long
-% author lists, or if there are many overlapping affiliations.
-% For Phys. Rev. appearance, change preprint to twocolumn.
-% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
-%  Add 'draft' option to mark overfull boxes with black boxes
-%  Add 'showpacs' option to make PACS codes appear
-%  Add 'showkeys' option to make keywords appear
-\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
-%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
-%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
-%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
+\documentclass[aps, pre, preprint, groupedaddress, superscriptaddress, showkeys, showpacs] {revtex4-1}
+
 \usepackage{amsmath}
@@
 \usepackage{epstopdf}
+
+% For the debug usage only
+\usepackage{color}
+
 \DeclarePairedDelimiter\bra{\langle}{\rvert}
 \DeclarePairedDelimiter\ket{\lvert}{\rangle}
-% You should use BibTeX and apsrev.bst for references
-% Choosing a journal automatically selects the correct APS
-% BibTeX style file (bst file), so only uncomment the line
-% below if necessary.
-%\bibliographystyle{apsrev4-1}
+
+% Remove ugly line above reverences
+\def\bibsection{\section*{\refname}}
 
@@
 
-% Use the \preprint command to place your local institutional report
-% number in the upper righthand corner of the title page in preprint mode.
-% Multiple \preprint commands are allowed.
-% Use the 'preprintnumbers' class option to override journal defaults
-% to display numbers if necessary
-%\preprint{}
-
-%Title of paper
 \title{Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions}
 
-% repeat the \author .. \affiliation  etc. as needed
-% \email, \thanks, \homepage, \altaffiliation all apply to the current
-% author. Explanatory text should go in the []'s, actual e-mail
-% address or url should go in the {}'s for \email and \homepage.
-% Please use the appropriate macro foreach each type of information
+\author{A. P. Alodjanc}
+\email{alexander\_ap@list.ru}
+\affiliation{ITMO University, St. Petersburg 197101, Russia}
 
-% \affiliation command applies to all authors since the last
-% \affiliation command. The \affiliation command should follow the
-% other information
-% \affiliation can be followed by \email, \homepage, \thanks as well.
-\author{lalala}
-%\email[]{Your e-mail address}
-%\homepage[]{Your web page}
-%\thanks{}
-%\altaffiliation{}
-\affiliation{}
-
-%Collaboration name if desired (requires use of superscriptaddress
-%option in \documentclass). \noaffiliation is required (may also be
-%used with the \author command).
-%\collaboration can be followed by \email, \homepage, \thanks as well.
-%\collaboration{}
-%\noaffiliation
+\author{M. E. Lebedev}
+\email{m.lebedev@lmc.ifmo.ru}
+\affiliation{ITMO University, St. Petersburg 197101, Russia}
 
@@
 \begin{abstract}
-bla-bla-bla
+Abstract will be placed here.
 \end{abstract}
 
-% insert suggested PACS numbers in braces on next line
-\pacs{}
-% insert suggested keywords - APS authors don't need to do this
-%\keywords{}
+\pacs{\dots}
+\keywords{\dots}
 
-%\maketitle must follow title, authors, abstract, \pacs, and \keywords
 \maketitle
@@
 \newcommand{\am}{\textrm{am}}
-% body of paper here - Use proper section commands
-% References should be done using the \cite, \ref, and \label commands
-\section{I.	Introduction}
-% Put \label in argument of \section for cross-referencing
-%\section{\label{}}
-%\subsection{}
-%\subsubsection{}
+
+% For the debug usage only
+\newcommand{\red}{\color{red}}
+
+\section{Introduction \label{sec:introduction}}
+
 For last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent one of mainstreams of current photonic and semiconductor technologies, see e.g.
-~\cite{1,2}.
+\cite{1,2}.
 The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum wells excitons.
 Practically, semiconductor microcavities are promising for various optoelectronic applications where quantum  matter-field interface plays crucial role.
-In particular,  demonstrations of polariton laser with electrical pump ~\cite{3,4}, amplifiers ~\cite{5}, switches ~\cite{6},  transistors ~\cite{7}, polariton circuits and optical logic elements ~\cite{8,9}.
-Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true  thermodynamic equilibrium state ~\cite{10,11}.
+In particular, demonstrations of polariton laser with electrical pump \cite{3,4}, amplifiers \cite{5}, switches \cite{6}, transistors \cite{7}, polariton circuits and optical logic elements \cite{8,9}.
+Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{10,11}.
 
-Non-equilibrium, or, thermodynamically quasi-equilibrium  features of exciton polariton condensates play certain role in various manifestations of their collective  (many body) quantum states such as  superfluidity ~\cite{12,13},  quantized vortices ~\cite{14,15},  soliton formation ~\cite{16},  Josephson oscillations and macroscopic self-trapping ~\cite{17,18}.
-Since exciton polariton BEC’s in  present experiments examined at high enough (up to the room) temperatures the quantum  character of such a states should be examined even at equilibrium.
+Non-equilibrium, or, thermodynamically quasi-equilibrium features of exciton polariton condensates play certain role in various manifestations of their collective (many body) quantum states such as superfluidity \cite{12,13}, quantized vortices \cite{14,15}, soliton formation \cite{16}, Josephson oscillations and macroscopic self-trapping \cite{17,18}.
+Since exciton polariton BEC's in present experiments examined at high enough (up to the room) temperatures the quantum character of such a states should be examined even at equilibrium.
 
 The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for practical purposes, see e.g.
-~\cite{19}; especially for their possible applications for quantum information science purposes.
-Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom  made  microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives,  see, e.g., ~\cite{21,22,23}.
-In particular, we would like to mention here problems of design ultrafast quantum gates ~\cite{22,23}, creation of relatively long Rabi oscillations ~\cite{19, 20} and quantum annealing problem ~\cite{24} where collective (bosonic) character of polariton BEC could be used.
+\cite{19}; especially for their possible applications for quantum information science purposes.
+Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom made microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives, see, e.g.
+\cite{21,22,23}.
+In particular, we would like to mention here problems of design ultrafast quantum gates \cite{22,23}, creation of relatively long Rabi oscillations \cite{19, 20} and quantum annealing problem \cite{24} where collective (bosonic) character of polariton BEC could be used.
 Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology for which designing of quantum interferometers and gyroscopes possessing high precision measurements with quantum phase states is utilized, cf.
-~\cite{25, 26}.
+\cite{25, 26}.
 
 In the paper we consider generic problem of quantum-classical phase transition with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect with them, cf.
-~\cite{27}.
-In general  this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf.
-~\cite{28,29,30}.
-Evidently seminal studies on this topic relay to superconductor devices ~\cite{31} where macroscopic tunneling plays essential role.
-In particular, it worth to mention here Schrodinger cat state formation ~\cite{32} and design of quantum gates for quantum computing with  superconductor qubits where macroscopic  quantum coherent phase properties are used ~\cite{33}.
-Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC’s ~\cite{34}, and small ferromagnetic particles, ~\cite{35}.
+\cite{27}.
+In general this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf. \cite{28,29,30}.
+Evidently seminal studies on this topic relay to superconductor devices \cite{31} where macroscopic tunneling plays essential role.
+In particular, it worth to mention here Schr\"odinger cat state formation \cite{32} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{33}.
+Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{34}, and small ferromagnetic particles, \cite{35}.
 Strictly speaking main discussion is focused on investigation of quantum-classical escape rate transition that takes place in the presence of potential barrier at finite temperatures.
@@
 In the paper we propose \textit{extended model} for exciton polariton Josephson junctions when energy of polariton-polariton scattering contributes into the tunneling parameter, cf.
-~\cite{36,37,38} and references therein.
-In particularly, we pay our attention to temperature dependent critical phenomena occurring in the presence of macroscopic tunneling  .
+\cite{36,37,38} and references therein.
+In particularly, we pay our attention to temperature dependent critical phenomena occurring in the presence of macroscopic tunneling.
 We aimed at elucidation of necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for creation of exciton polariton qubit gates.
@@
 This paper is arranged as follows.
-In Sec.
-II, we explain in details our model to realize Josephson junction with exciton polariton condensates.
-The extended tight-binding model will be established in this case.
-In Sec.
-III we …..In the conclusion, we summarize the results obtained.
+In Sec. \ref{sec:model} we explain in details our model to realize Josephson junction with exciton polariton condensates.
+The extended tight-binding model will be established in this case. In Sec. \ref{sec:quantum_phase} we \dots.
+In the conclusion, we summarize the results obtained.
 
-\section{II. THE MODEL OD EXCITON POLARITON JOSEPHSON JUNCTION}
-We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential  $U(x) = h ((x/x_0)^2 - 1)^2$, , sketched in Fig.
-1; $2x_0$ defines
-distance between potential minima, $h$ depth of the potential.
+\section{THE MODEL OD EXCITON POLARITON JOSEPHSON JUNCTION \label{sec:model}}
+
+We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched on the Fig.
+\ref{pic:potential_sym_asym}; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
+% 
+\begin{figure}[ht]
+\center{\includegraphics[width=0.65\linewidth]{pic/potential_sym_asym.png}}
+\caption{
+Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
+The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
+\label{pic:potential_sym_asym}
+}
+\end{figure}
+%
 The Hamiltonian for the system of weakly interacting exciton polaritons in an external $U(x)$ can be written in the second quantized form as:
+%
 \begin{equation}
-\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx.
+\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
 \label{eq:gpe_hamiltonian}
 \end{equation}
-where $\hat{\psi} \equiv \hat{\psi}(z,t)$ is polariton  field operator that annihilate a particle at the position $z$ and time $t$, $g$  is two-body (polariton-polariton) scattering length.
+%
+where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ is two-body (polariton-polariton) scattering length.
 In the paper we use so-called two-mode representation of $\hat{\psi}$ supposing
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
-It is instructive to recast $\Phi_{1,2}(x)$ as
+It's instructive to recast $\Phi_{1,2}(x)$ as
+%
 \begin{equation}
 \Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
-\label{eq:conditions}
+\label{eq:basic_modes}
 \end{equation}
-where $\Phi_{\pm}(x) = \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real  wavefunctions obeying  stationary Gross-Pitaevskii equations, respectively
+%
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real wavefunctions obeying stationary Gross-Pitaevskii equations, respectively
+%
 \begin{equation}
@@
 \end{equation}
-and  normalization condition $\int \Phi_{\pm}^2 dx = 1$ $\mu_{\pm}$ are chemical  potentials.
-As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit “hat” design for simplicity).
-Substituting (\ref{eq:conditions}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
+%
+and normalization condition $\int \Phi_{\pm}^2 dx = 1$.
+Here $\mu_{\pm}$ are chemical potentials.
+As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit ``hat'' design for simplicity).
+Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
+% 
 \begin{equation}
 \begin{array}{lcl}
-\hat{H} & = & \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 +  \hat{\psi}_1 \hat{\psi}_2^\dag) + \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) \\[10pt]
-& & +\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\[10pt]
-& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}).
+\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
+& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
+& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
 \end{array}
@@
 \end{equation}
-where  we made denotations 
+%
+where we made some denotations
+%
 \begin{equation}
 \begin{array}{c}
-\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\[10pt]
-\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\[10pt]
-C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\[10pt]
-G = \mu_- - \mu_+ - 2\Gamma;\\[10pt]
+\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\
+\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\
+C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\
+G = \mu_- - \mu_+ - 2\Gamma.
 \end{array}
@@
 \end{equation}
+%
+
 Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double well potential.
-It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
+It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate
+%
+\begin{equation}
+G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2).
+\label{eq:tunneling_rate}
+\end{equation}
+%
 The contribution from relevant coefficients on can be estimated from variational ansatz
+%
 \begin{equation}
-\Phi_{\pm} = A_{\pm} \Big[\exp\Big(-\dfrac{(x-x_0)^2}{2a^2}\Big) \pm \exp\Big(-\dfrac{(x+x_0)^2}{2a^2}\Big)\Big]
+\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]
 \label{eq:two_modes_eq}
 \end{equation}
+%
 where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
-In Fig.2 the behavior  of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in {+,-}$ as a function of  half of intra-well distance $x_0$ is shown.
+In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of intra-well distance $x_0$ is shown.
 It is important that at differences between them rapidly vanishes with increasing of distance $x_0$.
 We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked  condensates at zero temperature \underline{- see e.g.
-~\cite{39} and cf.
-}.
-\section{III. The Quantum Phase}
+This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature \underline{- see e.g. ~\cite{39} and cf. }.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.65\linewidth]{pic/ypm_x0.png}}
+\caption{Dependence of $\gamma_{ij} / g$ versus $x_0 / a$ \label{pic:gamma_pm_vs_g}}
+\end{figure}
+%
+
+\section{The Quantum Phase \label{sec:quantum_phase}}
+
 To elucidate important quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
+% 
 \begin{subequations}
 \begin{align}
-\hat{S}_x = \dfrac{1}{2}(\hat{\psi}_1^\dag\hat{\psi}_2+\hat{\psi}_1\hat{\psi}_2^\dag) = s\cos(\phi)-\sin(\phi)\dfrac{d}{d\phi}, \\[10pt]
-\quad \hat{S}_y = \dfrac{i}{2}(\hat{\psi}_1^\dag\hat{\psi}_2-\hat{\psi}_1\hat{\psi}_2^\dag) = s\sin(\phi)+\cos(\phi)\dfrac{d}{d\phi}, \\[10pt]
-\hat{S}_z = \dfrac{1}{2}(\hat{\psi}_2^\dag\hat{\psi}_2+\hat{\psi}_1^\dag\hat{\psi}_1) = -i\dfrac{d}{d\phi},
+\hat{S}_x = \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos(\phi) - \sin(\phi) \dfrac{d}{d \phi}, \\
+\quad \hat{S}_y = \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin(\phi) + \cos(\phi) \dfrac{d}{d \phi}, \\
+\hat{S}_z = \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
 \end{align}
@@
 \end{subequations}
-where $s = \dfrac{N}{2} >> 1$ is large \underline{ $C$ - number}, $\phi$ is phase variable.
-The operators determined in Eq.
-(\ref{eq:pseudo_spin}) obey familiar \underline{ SU(2)} algebra commutation relations
+%
+where $s = \dfrac{N}{2} >> 1$ is large {\red $C$ - number}, $\phi$ is phase variable.
+The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations
+%
 \begin{equation}
@@
 \end{equation}
+%
 After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
+%
 \begin{equation}
 \begin{array}{lcl}
-H & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (B \sin \phi + \beta (s - \frac{1}{2}) \sin 2 \phi) \dfrac{d}{d \phi} \\[10pt]
-&& + Bs \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
+H & = & -(\alpha - \beta \sin^2 \phi) \dfrac{d^2}{d \phi^2} - (\beta(s-\dfrac{1}{2})\sin{2\phi} - B\sin{\phi}) \dfrac{d}{d \phi} \\
+&& - Bs \cos \phi - \beta s^2 \sin^2 \phi - \beta s \cos^2 \phi.
 \end{array}
@@
 \end{equation}
-where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = FN + G > 0$.
-Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = gamma$ supposing $\Gamma = 0$ for simplicity, see Fig.2.
+%
+where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
+Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig. \ref{pic:gamma_pm_vs_g}
+
 Hamiltonian (\ref{eq:hamiltinian_s}) corresponds to Schrodinger equation
+%
 \begin{equation}
 \begin{array}{l}
-(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (B \sin \phi + \beta (S - \frac{1}{2}) \sin 2\phi) \dfrac{d \Phi}{d \phi} \\[10pt]
-+ (E - BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
+(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta(s - \dfrac{1}{2})\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
++ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
 \end{array}
-\label{eq:Schrodinger}
+\label{eq:schrodinger}
 \end{equation}
-where $\Phi \equiv \Phi(phi)$ is  unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf.
-~\cite{40}.
-Noticing that Eqs.
-(\ref{eq:hamiltinian_s}), (\ref{eq:Schrodinger}) can be obtained by applying  so-called phase-state representation, \underline{cf.
-[  ]}.
+%
+where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{40}.
+Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
+%
 \begin{equation}
-\ket{\psi} = \dfrac{1}{2\pi}\int_{-\infty}^{+\infty}d\phi\Phi(\phi)\ket{\phi}
+\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
 \end{equation}
+%
 where
+%
 \begin{equation}
-\ket{\phi} = \dfrac{1}{\sqrt{N!}}\Big[\exp^{i\phi/2}\psi_1^\dagger+\exp^{-i\phi/2}\psi_2^\dag\Big]^N\ket{0}_1\ket{0}
+\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
 \end{equation}
-is macroscopic coherent spin-state (macroscopic qubit state)  that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. ~\cite{41}.
-It is possible to eliminate the term with first derivative in  Eq.(\ref{eq:Schrodinger}) applying the transformation
+%
+is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{41}.
+It is possible to eliminate the term with first derivative in Eq.(\ref{eq:schrodinger}) applying the transformation
+%
 \begin{equation}
-\Phi(\phi) = \Psi(x)\exp\Big[s\ln\dn{x}-\dfrac{\Lambda s}{2\sqrt{\lambda(1-\lambda)}}\arctan\Big(\sqrt{\dfrac{\lambda}{1-\lambda}}\cn{x}\Big)\Big]
-\label{eq:transformation_of_Phi}
+\Phi(\phi) = \Psi(z) \exp \Big( s \log \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
+\label{eq:transformation_of_phi}
 \end{equation}
-where $x = \int \limits_0^\phi \dfrac{d \phi'}{\sqrt{1 - \frac{\beta}{\alpha} \sin^2 \phi'}} = F(\phi, \sqrt{\beta / \alpha}) = F(\phi, \sqrt{\lambda})$ is new phase variable, $F(\phi, \sqrt{\lambda})$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_Phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha S}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
-Inserting (\ref{eq:transformation_of_Phi}) into (\ref{eq:Schrodinger}) we come to  convenient Schrodinger equation
+%
+where
+%
+\begin{equation}
+z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \sqrt{\lambda})
+\end{equation}
+is new phase variable; $F(\phi, \sqrt{\lambda})$ is incomplete elliptic integral of the first kind.
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
+
+Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we come to convenient Schr\"odinger equation
+%
 \begin{equation}
 \dfrac{d^2\Psi}{dx^2} + (E - V(x))\Psi = 0
-\label{eq:Schrodinger_usual}
+\label{eq:schrodinger_usual}
 \end{equation}
-for quantum particle with mass $m_{eff} = \dfrac{1}{2}$,  normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(x) = s^2V_0(x)$ with
+%
+for quantum particle with mass $m_{eff} = \dfrac{1}{2}$, normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(x) = s^2 V_0(x)$ with
+%
 \begin{equation}
-V_0(x) = \dfrac{(\dfrac{1}{4}\Lambda^2-\lambda(1-\lambda))\sn^2{x}-\Lambda\cn{x}}{\dn^2{x}}
+V_0(x) = \frac{ (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) \sn^2{x} - \Lambda \cn{x}}{\dn^2{x}}
 \label{eq:potential}
 \end{equation}
-The results  known for quantum phase mesoscopic Josephson junction model can be recovered  from  (\ref{eq:Schrodinger_usual}), (\ref{eq:potential}) at $\lambda = 0$. 
-The dependence of $\lambda$-parameter  on  normalized  half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from    (\ref{eq:subs}), (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5\Big(\exp\Big[\dfrac{2x_0^2}{a^2}\Big]-1\Big)^{-1}$.
+%
+
+The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:schrodinger_usual}), (\ref{eq:potential}) at $\lambda = 0$.
+The dependence of the $\lambda$ parameter on normalized half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:subs}), (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
 The limit $\lambda = 0$ obtained for infinitely large intra-well distances $x_0 \to \infty$.
@@
 Below we examine case of $0 < \lambda < 1$ that could be obtained at moderate values $\dfrac{x_0}{a}$ of such as $\dfrac{x_0}{a} \geq 0.45$.
-Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf.
-~\cite{40}.
-The dependences of  trapping potential $V_0(x)$ are shown in Fig.
-3.
+
+Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf. \cite{40}.
+The dependences of trapping potential $V_0(x)$ are shown in Fig. \ref{phase_potential}.
+The period of the functions is determined as $4K(\lambda)$.
+%
+\begin{figure}[ht]
+\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=100.png} \\ a}
+\end{minipage}
+\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=05.png} \\ b}
+\end{minipage}
+\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=001.png} \\ c}
+\end{minipage}
+\caption{
+Effective potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of  elliptic integral phase coordinate $z$.
+Points $A, B$ and $C$ in (b) corresponds to minima of the potential occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
+\end{figure}
+%
+
 \subsection{Rabi regime}
-$\Lambda \gg 1$. In this limit the trapping potential reads
+
+Here we suppose that $\Lambda \gg 1$.
+In this limit the trapping potential reads
+%
 \begin{equation}
-V_R(x) = \dfrac{1}{4}\Lambda^2\sd^2{x}
+V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}
 \label{eq:rabi_potential}
 \end{equation}
-It is interesting to note that….
+%
+It is interesting to note that even in this case the role of $\lambda$-parameter is evident --- see Fig. \ref{phase_potential}a.
+
 \subsection{Fock regime}
-In this regime it is instructive to distinguish two limits.    First, we suppose that inequality $\lambda \ll \lambda < 1$.    In this case from (\ref{eq:potential}) one can obtain
+
+In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with limiting value of the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In this regime we distinguish two limits.
+First, we suppose that inequality $\Lambda \ll \lambda \ll 1$ is holds.
+In this case from (\ref{eq:potential}) one can obtain
+%
 \begin{equation}
-V_F(x) = -\lambda(1-\lambda)\sd^2{x}
+V_F(z) = -\lambda(1 - \lambda) \sd^2{z}
 \label{eq:fock1_potential}
-\end{equation}
-Another limit that could be studied within Fock regime is relevant to condition $\Lambda^2 < \lambda < \Lambda$. In this case  from (\ref{eq:potential}) we have 
+\end{equation}.
+%
+
+{\red Mathieu equaiton and it's spectrum}
+
+Another limit that could be studied within Fock regime is relevant to condition $\lambda \ll \Lambda \ll 1$.
+In this case from (\ref{eq:potential}) we have
+% 
 \begin{equation}
-V_0(x) = \dfrac{-\Lambda\cn{x}}{\dn^2{x}}
+V_0(z) \simeq -\Lambda \cos{z}
 \label{eq:fock2_potential}
 \end{equation}
-Equation (\ref{eq:fock2_potential}) for negligible    reproduces results for convenient quantum phase model ~\cite{40}. 
+%
+Equation (\ref{eq:fock2_potential}) deals with negligible $\lambda$; it is reproduces results for convenient quantum phase model \cite{40}.
+
+Practically, Fock regime interesting for high precision measurements.
+In particular, the dispersion of the quantum phase in this case approaches to so-called Heisenberg limit {\red $< (\Delta\phi)^2 > \propto \dfrac{1}{N^2}$} which is the minimal accessible error for the phase measurement in respect of total particle number.
+
 \subsection{Josephson regime}
-$\Lambda \leq 1$. This regime represents intermediate  case between Rabi and Fock regimes.   In general all terms in (\ref{eq:potential}) should be kept.
-\section{IV. Quantum-classical phase transitions}
+
+Here we suppose that {\red $\Lambda < 1$}.
+This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
+In general all terms in (\ref{eq:potential}) should be kept.
+The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
+If $2\lambda < \Lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
+Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
+{\red equation for small oscillations}
+
+In the other limit, for $2 \lambda > \Lambda$, two minima of $V_0(z)$ with coordinates
+%
+\begin{equation}
+\cn{z_{min}} = \frac{\Lambda (2 \lambda - 1)}{0.5 \Lambda^2 - 2 \lambda (1 - \lambda)}
+\label{eq:z_minima}
+\end{equation}
+%
+appears both for Josephson and Fock regimes, cf. Fig. \ref{phase_potential}b,c.  
+The depth of the potential minima depends on the $\lambda$ parameter.
+It is interesting to note that for {\red $\lambda > \dots$} potential $V_0(z)$ presumes local minimum at \dots
+
+Practically two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
+\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.[ ]}.
+However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
+Another interesting phenomena that can be obtained with potential in Fig. \ref{phase_potential}b is connected with some analogies in cosmology and quantum field theory.
+In particular, in our recent work {\red [ ]} we discuss Higgs field generation by using exciton polaritons in semiconductor Bragg mirror structures as an on table analog of known cosmological phenomenon, {\red cf.
+[ ]}.
+In this paper we continue our physical analogies with false vacuum decay (marked by the point $C$ in Fig. \ref{phase_potential}b) that can be established here, {\red cf. [ ]}.
+
+\section{Quantum-classical phase transitions \label{sec:quantum_classical}}
+
 Strictly speaking, results established in previous section are completely valid at zero temperature.
@@
 In this section we find answer to vital question: when quantum approach to the phase problem for exciton polariton Josephson junction is valid?
-....
-\section{V. Conclusion}
-....
-% If in two-column mode, t his environment will change to single-column
-% format so that long equations can be displayed. Use
-% sparingly.
-%\begin{widetext}
-% put long equation here
-%\end{widetext}
 
-% figures should be put into the text as floats.
-% Use the graphics or graphicx packages (distributed with LaTeX2e)
-% and the \includegraphics macro defined in those packages.
-% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz,
-% and Frank Mittelbach for instance.
-%
-% Here is an example of the general form of a figure:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Use the figure* environment if the figure should span across the
-% entire page. There is no need to do explicit centering.
+\dots
 
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
+\section{Conclusion \label{sec:conclusion}}
 
-% Surround figure environment with turnpage environment for landscape
-% figure
-% \begin{turnpage}
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
-% \end{turnpage}
-
-% tables should appear as floats within the text
-%
-% Here is an example of the general form of a table:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
-% \begin{tabular}{} command.
-% The ruledtabular enviroment adds doubled rules to table and sets a
-% reasonable default table settings.
-% Use the table* environment to get a full-width table in two-column
-% Add \usepackage{longtable} and the longtable (or longtable*}
-% environment for nicely formatted long tables. Or use the the [H]
-% placement option to break a long table (with less control than 
-% in longtable).
-% \begin{table}%[H] add [H] placement to break table across pages
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% Lines of table here ending with \\
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-
-% Surround table environment with turnpage environment for landscape
-% table
-% \begin{turnpage}
-% \begin{table}
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-% \end{turnpage}
-
-% Specify following sections are appendices. Use \appendix* if there
-% only one appendix.
-%\appendix
-%\section{}
-
-% If you have acknowledgments, this puts in the proper section head.
-%\begin{acknowledgments}
-% put your acknowledgments here.
-%\end{acknowledgments}
+\dots
 
@@
 \end{document}
-%
-% ****** End of file apstemplate.tex ******

### 2017-01-07 writing/phase_transition/phase_transition.tex
Mathieu spectrum and other minor changes

@@
 We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature \underline{- see e.g. ~\cite{39} and cf. }.
+This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{39} and cf. }.
 %
@@
 \begin{equation}
-\dfrac{d^2\Psi}{dx^2} + (E - V(x))\Psi = 0
+\frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
 \label{eq:schrodinger_usual}
@@
 %
-for quantum particle with mass $m_{eff} = \dfrac{1}{2}$, normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(x) = s^2 V_0(x)$ with
+for quantum particle with mass $m_{eff} = \dfrac{1}{2}$, normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(z) = s^2 V_0(z)$ with
 %
 \begin{equation}
-V_0(x) = \frac{ (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) \sn^2{x} - \Lambda \cn{x}}{\dn^2{x}}
+V_0(z) = \frac{ (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) \sn^2{z} - \Lambda \cn{z}}{\dn^2{z}}
 \label{eq:potential}
@@
 \begin{equation}
-V_F(z) = -\lambda(1 - \lambda) \sd^2{z}
+V_F(z) = -\lambda(1 - \lambda) \sd^2{z}.
 \label{eq:fock1_potential}
@@
 
-{\red Mathieu equaiton and it's spectrum}
+{\red
+Using the fact that $\lambda$ is small we can replace the potential (\ref{eq:fock1_potential}) with
+%
+\begin{equation}
+V_F(z) \sim -\lambda (1 - \lambda) \sin^2{z},
+\end{equation}
+%
+and our Schrodinger equation transforms to the so-called Mathieu equation
+%
+\begin{equation}
+\frac{d^2 \Psi}{d z^2} + (a - 2q  \cos{2z}) \Psi = 0.
+\end{equation}
+%
+where $a = E + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
+We recall our boundary condition: $\Psi(z + 2\pi) = \Psi(z)$.
+So, spectrum consist of all Mathieu functions $ce_0(z, q)$, $ce_1(z, q)$, $se_1(z, q)$, \dots, which are $2\pi$-periodic, and corresponding eigenvalues $a$ can be found using series expansions in powers of $q$ (see Abramowitz and Stegun).
+}
 

### 2017-01-09 writing/phase_transition/phase_transition.tex
Bibliography OK

@@
 For last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent one of mainstreams of current photonic and semiconductor technologies, see e.g.
-\cite{1,2}.
+\cite{Sanvitto,Guillet}.
 The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum wells excitons.
 Practically, semiconductor microcavities are promising for various optoelectronic applications where quantum  matter-field interface plays crucial role.
-In particular, demonstrations of polariton laser with electrical pump \cite{3,4}, amplifiers \cite{5}, switches \cite{6}, transistors \cite{7}, polariton circuits and optical logic elements \cite{8,9}.
-Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{10,11}.
+In particular, demonstrations of polariton laser with electrical pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
+Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
 
-Non-equilibrium, or, thermodynamically quasi-equilibrium features of exciton polariton condensates play certain role in various manifestations of their collective (many body) quantum states such as superfluidity \cite{12,13}, quantized vortices \cite{14,15}, soliton formation \cite{16}, Josephson oscillations and macroscopic self-trapping \cite{17,18}.
+Non-equilibrium, or, thermodynamically quasi-equilibrium features of exciton polariton condensates play certain role in various manifestations of their collective (many body) quantum states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
 Since exciton polariton BEC's in present experiments examined at high enough (up to the room) temperatures the quantum character of such a states should be examined even at equilibrium.
@@
 The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for practical purposes, see e.g.
-\cite{19}; especially for their possible applications for quantum information science purposes.
+\cite{Dominici}; especially for their possible applications for quantum information science purposes.
 Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom made microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives, see, e.g.
-\cite{21,22,23}.
-In particular, we would like to mention here problems of design ultrafast quantum gates \cite{22,23}, creation of relatively long Rabi oscillations \cite{19, 20} and quantum annealing problem \cite{24} where collective (bosonic) character of polariton BEC could be used.
+\cite{Demirchyan,Pagel,Kyriienko,Solnyshkov_2015}.
+In particular, we would like to mention here problems of design ultrafast quantum gates \cite{Kyriienko,Solnyshkov_2015}, creation of relatively long Rabi oscillations \cite{Dominici, Demirchyan} and quantum annealing problem \cite{Yan} where collective (bosonic) character of polariton BEC could be used.
 Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology for which designing of quantum interferometers and gyroscopes possessing high precision measurements with quantum phase states is utilized, cf.
-\cite{25, 26}.
+\cite{Gulevich, Pezze}.
 
 In the paper we consider generic problem of quantum-classical phase transition with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect with them, cf.
-\cite{27}.
-In general this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf. \cite{28,29,30}.
-Evidently seminal studies on this topic relay to superconductor devices \cite{31} where macroscopic tunneling plays essential role.
-In particular, it worth to mention here Schr\"odinger cat state formation \cite{32} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{33}.
-Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{34}, and small ferromagnetic particles, \cite{35}.
+\cite{Chudnovsky_1997}.
+In general this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf. \cite{Caldeira,Larkin,Riseborough}.
+Evidently seminal studies on this topic relay to superconductor devices \cite{Ankerhold} where macroscopic tunneling plays essential role.
+In particular, it worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{Makhlin}.
+Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
 Strictly speaking main discussion is focused on investigation of quantum-classical escape rate transition that takes place in the presence of potential barrier at finite temperatures.
@@
 In the paper we propose \textit{extended model} for exciton polariton Josephson junctions when energy of polariton-polariton scattering contributes into the tunneling parameter, cf.
-\cite{36,37,38} and references therein.
+\cite{Borgh,Solnyshkov_2008,Sarchi} and references therein.
 In particularly, we pay our attention to temperature dependent critical phenomena occurring in the presence of macroscopic tunneling.
@@
 We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{39} and cf. }.
+This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{Raghavan} and cf. }.
 %
@@
 %
-where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{40}.
+where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{Anglin}.
 Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
@@
 %
-is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{41}.
+is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
 It is possible to eliminate the term with first derivative in Eq.(\ref{eq:schrodinger}) applying the transformation
@@
 
-Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf. \cite{40}.
+Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf. \cite{Anglin}.
 The dependences of trapping potential $V_0(x)$ are shown in Fig. \ref{phase_potential}.
@@
 %
-Equation (\ref{eq:fock2_potential}) deals with negligible $\lambda$; it is reproduces results for convenient quantum phase model \cite{40}.
+Equation (\ref{eq:fock2_potential}) deals with negligible $\lambda$; it is reproduces results for convenient quantum phase model \cite{Anglin}.
 

### 2017-01-09 phase_transition/CFDS.m
Trying to use CFDS for numerical calculation of gammas

@@ -1,0 +1,114 @@
+function [Grid, U, Norm] = CFDS( params, X0, U0 )
+% Solving the equation: i u_t = -u_{xx} - (\alpha + \cos 2x) |u|^2 u
+
+% Accuracy of interation process
+eps = 1e-12;
+
+[~, a, b, gN] = parse_params(params);
+
+% Zero linear potential
+% V = @(x) 0;
+
+% Double-well linear potential
+V = @(x) potential(a, b, x);
+
+% Nonlinear cosine potential
+% g = @(x) alpha + cos(2 * x);
+
+% Repulsive nonlinearity
+g = @(x) -gN;
+
+xstep = 0.03;
+xspan = [X0(1), X0(end)];
+xgrid = xspan(1):xstep:xspan(2);
+Nx = length(xgrid);
+
+tstep = 0.03;
+tspan = [0 100];
+tgrid = tspan(1):tstep:tspan(2);
+Nt = length(tgrid);
+
+[Grid{1}, Grid{2}] = meshgrid(xgrid, tgrid);
+U = zeros(Nt, Nx);
+
+% Initial condition
+U(1, :) = resample(X0, U0, xgrid);
+
+% Perturbation (?)
+
+U(1, 1) = 0;
+U(1, end) = 0;
+
+figure
+plot(U(1, :))
+
+% Norm of the solution
+Norm = zeros(1, Nt);
+
+Norm(1) = simpson(abs(U(1, :)) .^ 2, xstep);
+
+% Prepare tridiagonal sparse linear operator: Lv = F(v, v')
+	
+% -1 diagonal
+Ljm1 = 0.5 / (xstep ^ 2) * ones(1, Nx - 2);
+Ljm1 = [Ljm1 0];
+	
+% +1 diagonal
+Ljp1 = 0.5 / (xstep ^ 2) * ones(1, Nx - 2);
+Ljp1 = [0 Ljp1];
+
+% Dissipation (?)
+% Dissip = 1i * dissipation(xgrid);
+
+for i = 2:Nt
+	% 0 diagonal
+	Lj = 1i / tstep - 1 / (xstep ^ 2) - 0.5 * (V(xgrid) - 0.5 * g(xgrid) .* (abs(U(i - 1, :)) .^ 2));
+	
+	% Without dissipation
+	L = diag(Lj) + diag(Ljm1, -1) + diag(Ljp1, +1);
+	
+	% With dissipation
[…]

### 2017-01-09 phase_transition/dissipation.m

@@ -1,0 +1,17 @@
+function d = dissipation(xgrid)
+
+dissip_stength = 10;
+
+l = 0.1 * (xgrid(end) - xgrid(1));
+L = xgrid(end);
+
+d = zeros(1, length(xgrid));
+
+sel = (xgrid > (L - l));
+d(sel) = dissip_stength * ((xgrid(sel) - (L - l)) .^ 2);
+
+sel = (xgrid < (-L + l));
+d(sel) = dissip_stength * ((xgrid(sel) + (L - l)) .^ 2);
+
+end
+

### 2017-01-09 phase_transition/preparing_paper.m

@@ -196,6 +196,45 @@ title(sprintf('\\Lambda = %g', Lambda));
 xlabel('z');
 ylabel('V_0(z)');
 
+%% Using CFDS to calculate \gamma_{\pm \pm} numerically
+clc; clear
+
+h = 10; x0 = 1;
+U = @(x) h * (x .^ 2 - x0^2) .^ 2;
+
+% Nonlinearity parameter
+g = 1;
+
+% Chemical potential
+% mu = 8;
+
+xspan = [-3 0];
+
+a = h;
+b = - 2 * (x0 ^ 2) * h;
+
+% Symmetric mode, mu = 5.7355, mu_corrected = -4.2645
+% I found this chemical potential with using of my finding normalized modes
+% procedure based on the asymptotic behaviour from the article Alfimov, Zezulin,
+% Nonlinearity 20, 2007. There the potential U(x) a x^4 - b x^2 was considered.
+mu = 5.7355;
+
+% I use chemical potential correction to put the double-well potential U(x)
+% into U(0) = 0.
+mu_corrected = mu - h * (x0 ^ 2);
+params = [mu_corrected, a, b, g];
+
+c_symmetric = get_symmetric_mode_parameter(params, xspan);
+[X, Phi_symmetric] = get_symmetric_mode(params, c_symmetric, xspan);
+
+%%
+
+[Grid, Phi, Norm] = CFDS( params, X, Phi_symmetric(:, 1).' );
+
+
+
+
+
 
 
 

### 2017-01-09 phase_transition/resample.m

@@ -1,0 +1,14 @@
+function  Y = resample(X0, Y0, X)
+% Interpolate the solution (Y0) from one grid (X0) to another (X)
+
+Y = zeros(size(X));
+
+sel = find((X <= X0(end)) & (X >= X0(1)));
+Y(sel) = spline(X0, Y0, X(sel));
+
+sel = find((X > X0(end)) | (X < X0(1)));
+if ~isempty(sel)
+	Y(sel) = 0; %zero tails
+end;
+
+end

### 2017-01-10 finding_stationary_modes/get_symmetric_mode.m
Hell year! I found a... breather, lots of breathers

@@ -18,10 +18,10 @@ init = [ asympt_params(xstart)
 ode_params = @(x, f) ode(x, f, params);
 [X, Phi] = RK4(ode_params, xspan, init, 1024);
 
-X = [X -X(end:-1:1)];
+X = [X -X(end-1:-1:1)];
 Phi = [
 	Phi(:, 1), Phi(:, 2);
-	Phi(end:-1:1, 1), -Phi(end:-1:1, 2)
+	Phi(end-1:-1:1, 1), -Phi(end-1:-1:1, 2)
 ];
 
 end

### 2017-01-10 phase_transition/CFDS.m

@@ -23,7 +23,7 @@ xspan = [X0(1), X0(end)];
 xgrid = xspan(1):xstep:xspan(2);
 Nx = length(xgrid);
 
-tstep = 0.03;
+tstep = 0.01;
 tspan = [0 100];
 tgrid = tspan(1):tstep:tspan(2);
 Nt = length(tgrid);
@@ -104,6 +104,9 @@ for i = 2:Nt
 	end
 	
 	plot(abs(U(i, :))); drawnow
+	
+	pause(1e-2);
+	
 	Norm(i) = simpson(abs(U(i, :)) .^ 2, xstep);
 	
 	% Logging

### 2017-01-10 phase_transition/preparing_paper.m

@@ -229,6 +229,7 @@ c_symmetric = get_symmetric_mode_parameter(params, xspan);
 
 %%
 
+params = [mu_corrected, a-5, b+10, g];
 [Grid, Phi, Norm] = CFDS( params, X, Phi_symmetric(:, 1).' );
 
 

### 2017-01-12 writing/phase_transition/phase_transition.tex
Phase transition 85% done

@@
 \email{m.lebedev@lmc.ifmo.ru}
+\affiliation{ITMO University, St. Petersburg 197101, Russia}
+
+\author{D. A. Dolinina}
+\email{dasha.doly@gmail.com}
 \affiliation{ITMO University, St. Petersburg 197101, Russia}
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=0.65\linewidth]{pic/potential_sym_asym.png}}
+\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
 \caption{
@@
 \begin{equation}
-\begin{array}{c}
+\begin{array}{l}
 \gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\
-\quad A = \dfrac{\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}}{4}; \quad \Gamma = \dfrac{\gamma_{++} - \gamma_{--}}{2}; \\
-C = \dfrac{\gamma_{++} + \gamma_{--} - 2\gamma_{+-}}{4}; \\
-G = \mu_- - \mu_+ - 2\Gamma.
+A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}); \quad \Gamma = \frac{1}{2} (\gamma_{++} - \gamma_{--}); \\
+C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-}); \quad G = \mu_- - \mu_+ - 2\Gamma.
 \end{array}
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=0.65\linewidth]{pic/ypm_x0.png}}
+\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.png}}
 \caption{Dependence of $\gamma_{ij} / g$ versus $x_0 / a$ \label{pic:gamma_pm_vs_g}}
@@
 \begin{align}
-\hat{S}_x = \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos(\phi) - \sin(\phi) \dfrac{d}{d \phi}, \\
-\quad \hat{S}_y = \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin(\phi) + \cos(\phi) \dfrac{d}{d \phi}, \\
-\hat{S}_z = \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
+\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos{\phi} - \sin{\phi} \dfrac{d}{d \phi}, \\
+\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
+\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
 \end{align}
@@
 \begin{equation}
-z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \sqrt{\lambda})
+z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)
 \end{equation}
-is new phase variable; $F(\phi, \sqrt{\lambda})$ is incomplete elliptic integral of the first kind.
+is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
 In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
@@
 The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
-If $2\lambda < \Lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
+If $\Lambda < 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
 Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
@@
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for {\red $\lambda > \dots$} potential $V_0(z)$ presumes local minimum at \dots
+It is interesting to note that for {\red $\Lambda > 1 + 2\lambda + \sqrt{1 + 8\lambda}$} potential $V_0(z)$ presumes local minimum at {\red $\pm 2 K(\lambda)$}.
 
@@
 
+Here we describe our approach to study the order of the phase transition and its temperature.
+According to works of Owerre, Chudnovsky, Garanin et al. order of these transition can be determined from the period of oscillation $\tau(E)$ near the bottom of the potential.
+Monotonically increasing $\tau(E)$ gives a second-order transition while nonmonotonic behaviour of $\tau(E)$ give a first-order transition.
+
+We determiine the temperature of the transition like Owerre does.
+At very low temperature, transition occur by quantum tunneling through the barrieer and the rate is governed by $\Gamma \sim e^{-B}$, where $B$ is the instanton action.
+At high temperature the particle has the possibility of hopping over the barrier, in this case the rate is governed by $\Gamma \sim e^{-\Delta V / T}$, where $\Delta V$ is the energy barrier.
+At a critical point these two transition rate are equal, there exist a crossover (first-order transition) temperature $T_{I}$ from quantum to a thermal regime, it's estimated as $T_{I} = \Delta V / B$.
+
+The crossover temperature in the case of second-order transition can be estimated as $T_{II} = \omega_0 / 2 \pi$, where $\omega_0$ is a oscillation frequency of the thermon near the top of the barrier.
+
+First, let's find out the dependence of the order on the parameters $\lambda$, $\Lambda$.
+Expand the potential $V_0(z)$ into a Taylor series:
+%
+\begin{equation}
+\begin{array}{lcl}
+V_0(z) & = & \left( \frac{1}{4}\Lambda^2 - \lambda (1 - \lambda) \right) \left( z^2 + \frac{2\lambda - 1}{3} z^4 + o(z^4) \right) \\ && - \Lambda \left( 1 + \frac{2\lambda - 1}{2} z^2 + \frac{16\lambda^2 - 16\lambda + 1}{24} z^4 + o(z^4) \right) \\
+& = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
+&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
+\end{array}
+\label{eq:potential_teylor}
+\end{equation}
+%
+Classical equation of motion for the thermon reads as
+%
+\begin{equation}
+\ddot{z} = s^2 \frac{d V_0}{dz}.
+\label{eq:thermon}
+\end{equation}
+%
+Equation for the small ocsillation near the top of the barrier:
+%
+\begin{equation}
+\ddot{z} - s^2 \left( \tfrac{1}{2} \Lambda^2 - (2\lambda - 1) \Lambda - 2 \lambda (1 - \lambda) \right) z = 0.
+\label{eq:thermon_small}
+\end{equation}
+%
+It follows from (\ref{eq:thermon_small}) that, as mentioned above, when $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.
+
+It's possible to show (for ex. using Poincare-Lindstedt method), that local behaviour of $\tau(E)$ is determined by the sign of the 4th degree in expansion (\ref{eq:potential_teylor}).
+If potential has the form $-x^2 - x^4$ than $\tau(E)$ increase near the critical value $E_0$ (where the thermon vanish) and the 1st order phase transition take place.
+In other case, if potential has the form $-x^2 + x^4$ than $\tau(E)$ decrease near the $E_0$ and the 2nd order phase transition occurs.
+So, the border between 1st and 2nd phase transition is determined by the equaiton
+%
+\begin{equation}
+\frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} = 0.
+\end{equation}
+%
+Taking in account the barrier existence condition, and conditions on $\lambda$, $\Lambda$ parameters one can derive the analytic expression of the border
+%
+\begin{equation}
+\Lambda = \frac{1 - 16\lambda + 16\lambda^2 + \sqrt{1 + 32\lambda - 32\lambda^2}}{4(2\lambda - 1)}.
+\label{eq:order_border}
+\end{equation}
+%
+We summarize our results on a picture below.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
+\caption{Phase transition diagram}
+\end{figure}
+%
+
+Consider the imaginary-time action
+%
+\begin{equation}
+S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
+\label{eq:thermon_action_1}
+\end{equation}
+%
+Periodic, with $\tau_p = \hbar / k_B T$, solutions of (\ref{eq:thermon}) satisfy the relation
+%
+\begin{equation}
+\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
+\label{eq:total_energy}
+\end{equation}
+%
+where $\tau_p$ is a thermon period corresponding to the energy level $E(\tau_p)$;
+%
+\begin{equation}
+\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
+\label{eq:thermon_period}
+\end{equation}
+%
+here $z_{1,2}(E)$ -- turning points.
+Using (\ref{eq:total_energy}) rewrite (\ref{eq:thermon_action_1}) in a form 
+%
+\begin{equation}
+S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
+\label{eq:thermon_action_2}
+\end{equation}
+%
+We draw dependence $S(T)$ and $\tau_p(E)$ for the cases of the 1st and 2nd order phase transition.
+For the sake of convenience we suppose that $V_0(z) = 0$ at minima surrounding the barrier.
+So, $E = 0$ corrensponds to the separatrices instanton solution (May be we should make corresponding transformation earlier).
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=\linewidth]{pic/action_period_1st_order_transition.eps}}
+\caption{1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$}
+\end{figure}
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition.eps}}
+\caption{2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
+\end{figure}
+%
+
+Now let's compute the temperature of the phase transition.
+It follows from (\ref{eq:thermon_small}) that the frequency of small thermon oscillation near the top of the barrier can be computted as follows
+%
+\begin{equation}
+\omega_0 = s \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
+\label{eq:period_small}
+\end{equation}
+%
+The temperature of the 2nd-order transition can be estimated as
+\begin{equation}
+T_{II} = (s  / 2 \pi) \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
+\end{equation}
+
 \dots
@@
 
-\dots
+\pagebreak
 

### 2017-01-12 phase_transition/preparing_paper.m

@@ -196,46 +196,94 @@ title(sprintf('\\Lambda = %g', Lambda));
 xlabel('z');
 ylabel('V_0(z)');
 
-%% Using CFDS to calculate \gamma_{\pm \pm} numerically
+%% Phase transition diagram
+
+figure('Position', [100 100 325 250]); hold on
+axis([0 1 0 2]); xlabel('\lambda'); ylabel('\Lambda')
+set(gca, 'XTick', [0 0.5 1]); set(gca, 'YTick', [0 0.5 1 2]);
+
+Lambda = @(lambda) (1 - 16 * lambda + 16 * (lambda .^ 2) + ...
+	sqrt(1 + 32 * lambda - 32 * (lambda .^ 2))) ./ (4 * (2 * lambda - 1));
+
+% Avoid NaN at zero denominator
+lambda = 0.51:0.01:1;
+plot([0.5 lambda], [0 Lambda(lambda)], 'LineWidth', 2, 'Color', 'black');
+
+lambda = 0:0.01:1;
+plot(lambda, 2 * lambda, 'Color', 'black');
+
+plot([1 1], [0 2], 'Color', 'black');
+plot([0 0], [0 1], 'Color', 'black');
+
+%% S(T) plotting
 clc; clear
 
-h = 10; x0 = 1;
-U = @(x) h * (x .^ 2 - x0^2) .^ 2;
+s = 1; % ~ Number of particles
 
-% Nonlinearity parameter
-g = 1;
+% Potential
+lambda = 0.9; Lambda = 0.1; % 1st-order transition
+% lambda = 0.5; Lambda = 0.5; % 2nd-order transition
 
-% Chemical potential
-% mu = 8;
+V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
+	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
 
-xspan = [-3 0];
+% Put barrier into zero E0 = V(0)
+[~, V_min] = fminsearch(V, 0); % (!)
 
-a = h;
-b = - 2 * (x0 ^ 2) * h;
+Vb = @(x) V(x) - V_min;
 
-% Symmetric mode, mu = 5.7355, mu_corrected = -4.2645
-% I found this chemical potential with using of my finding normalized modes
-% procedure based on the asymptotic behaviour from the article Alfimov, Zezulin,
[…]

### 2017-01-12 phase_transition/roots_near_equilibrium.m

@@ -1,0 +1,28 @@
+function [ xleft, xright ] = roots_near_equilibrium( f )
+%
+% INPUT:
+%
+
+% Step
+step = 0.01;
+
+% Convergence
+delta = 1e-12;
+
+x0 = 0;
+x1 = x0 + step;
+
+while true
+	if sign(f(x0)) == sign(f(x1))
+		x0 = x1;
+		x1 = x1 + step;
+	else
+		x_root = dichotomy(f, x0, x1, delta);
+		break
+	end
+end
+
+xright = abs(x_root);
+xleft = -xright;
+
+end

### 2017-01-13 writing/phase_transition/phase_transition.tex
Two figures combined in one

@@
 
-\author{A. P. Alodjanc}
-\email{alexander\_ap@list.ru}
-\affiliation{ITMO University, St. Petersburg 197101, Russia}
-
 \author{M. E. Lebedev}
@@
 \email{dasha.doly@gmail.com}
+\affiliation{ITMO University, St. Petersburg 197101, Russia}
+
+\author{A. P. Alodjanc}
+\email{alexander\_ap@list.ru}
 \affiliation{ITMO University, St. Petersburg 197101, Russia}
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=\linewidth]{pic/action_period_1st_order_transition.eps}}
-\caption{1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$}
-\end{figure}
-%
-\begin{figure}[ht]
-\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition.eps}}
-\caption{2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
+\center{\includegraphics[width=\linewidth]{pic/action_period_combined.eps}}
+\caption{(a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
 \end{figure}

### 2017-01-13 phase_transition/preparing_paper.m
Owerre paper was checked. The potentials are identical up to constant factor

@@ -286,4 +286,18 @@ plot(E, tau_p, 'LineWidth', 2, 'Color', 'black')
 %% Frequency of the small thermon oscillations
 omega0 = s * sqrt(-0.5 * Lambda^2 + (2 * lambda - 1) * Lambda + 2 * lambda * (1 - lambda));
 
+%% Owerre potential
+clc; clear
 
+lambda = 0.8; Lambda = 0.2;
+V_owerre = @(x) lambda * ((cn(x, lambda) - (Lambda / (2 * lambda))) .^ 2) ./ (dn(x, lambda) .^ 2);
+V_me = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
+	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
+
+[~, V_min] = fminsearch(V_me, 0); % (!)
+
+x = -10:0.01:10;
+
+figure; hold on;
+plot(x, V_owerre(x), 'Color', 'black', 'LineWidth', 2);
+plot(x, V_me(x) - V_min, 'Color', 'red');

### 2017-01-13 finding_stationary_modes/get_asymmetric_mode_parameter.m
It's better... Minor changes in the finding modes procedure

@@ -6,7 +6,7 @@ function [ c_asymmetric ] = get_asymmetric_mode_parameter( params, xspan )
 
 get_phi_end_params = @(C) get_phi_end(params, C, xspan);
 
-c0 = 0.01; cstep = 1;
+c0 = 0.01; cstep = 0.1;
 phi_end_0 = get_phi_end_params(c0);
 
 c1 = c0 + cstep;

### 2017-01-13 finding_stationary_modes/get_symmetric_mode_parameter.m

@@ -6,7 +6,7 @@ function [ c_symmetric ] = get_symmetric_mode_parameter( params, xspan )
 
 get_phix_end_params = @(C) get_phix_end(params, C, xspan);
 
-c0 = 0.01; cstep = 1;
+c0 = 0.01; cstep = 0.1;
 phix_end_0 = get_phix_end_params(c0);
 
 c1 = c0 + cstep;

### 2017-01-13 finding_stationary_modes/plot_phi_end.m

@@ -1,6 +1,6 @@
 function plot_phi_end( params, xspan )
 
-C = linspace(0, 2, 100);
+C = linspace(0, 1, 50);
 Phi_end = zeros(1, length(C));
 
 for i = 1:length(C)

### 2017-01-19 writing/phase_transition/phase_transition.tex
Tunneling thought the small barrier done.

@@
 \begin{equation}
-\frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
+\frac{1}{2 m} \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
 \label{eq:schrodinger_usual}
@@
 %
-for quantum particle with mass $m_{eff} = \dfrac{1}{2}$, normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(z) = s^2 V_0(z)$ with
+for quantum particle with ``mass'' $m = \dfrac{1}{2 \alpha}$, energy $E$, moving in the potential $V(z) = \alpha s^2 V_0(z)$ with
 %
@@
 %
-where $a = E + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
+where $a = E / \alpha + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
 We recall our boundary condition: $\Psi(z + 2\pi) = \Psi(z)$.
@@
 The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
-If $\Lambda < 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
-Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
-{\red equation for small oscillations}
+If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
+Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like {\red equation for small oscillations}.
 
-In the other limit, for $2 \lambda > \Lambda$, two minima of $V_0(z)$ with coordinates
+In the other limit, for $\Lambda < 2 \lambda$, two minima of $V_0(z)$ with coordinates
 %
 \begin{equation}
-\cn{z_{min}} = \frac{\Lambda (2 \lambda - 1)}{0.5 \Lambda^2 - 2 \lambda (1 - \lambda)}
+\cn{z_{min}} = \frac{\Lambda}{2 \lambda}
 \label{eq:z_minima}
@@
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for {\red $\Lambda > 1 + 2\lambda + \sqrt{1 + 8\lambda}$} potential $V_0(z)$ presumes local minimum at {\red $\pm 2 K(\lambda)$}.
+It is interesting to note that for {\red $\Lambda > 1 + 2\lambda + \sqrt{1 + 8\lambda}$} potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$.
 
 Practically two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
-\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.[ ]}.
+\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.
+[ ]}.
 However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
@@
 At high temperature the particle has the possibility of hopping over the barrier, in this case the rate is governed by $\Gamma \sim e^{-\Delta V / T}$, where $\Delta V$ is the energy barrier.
-At a critical point these two transition rate are equal, there exist a crossover (first-order transition) temperature $T_{I}$ from quantum to a thermal regime, it's estimated as $T_{I} = \Delta V / B$.
+At a critical point these two transition rate are equal, there exist a crossover (first-order transition) temperature $T_{c}^{(1)}$ from quantum to a thermal regime, it's estimated as $T_{c}^{(1)} = \Delta V / B$.
 
-The crossover temperature in the case of second-order transition can be estimated as $T_{II} = \omega_0 / 2 \pi$, where $\omega_0$ is a oscillation frequency of the thermon near the top of the barrier.
+The crossover temperature in the case of second-order transition can be estimated as $T_{c}^{(2)} = \omega_0 / 2 \pi$, where $\omega_0$ is a oscillation frequency of the thermon near the top of the barrier.
 
@@
 %
+% \begin{equation}
+% \begin{array}{lcl}
+% V_0(z) & = & \left( \frac{1}{4}\Lambda^2 - \lambda (1 - \lambda) \right) \left( z^2 + \frac{2\lambda - 1}{3} z^4 + o(z^4) \right) \\ && - \Lambda \left( 1 + \frac{2\lambda - 1}{2} z^2 + \frac{16\lambda^2 - 16\lambda + 1}{24} z^4 + o(z^4) \right) \\
+% & = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
+% && + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
+% \end{array}
+% \label{eq:potential_teylor}
+% \end{equation}
+%
 \begin{equation}
 \begin{array}{lcl}
-V_0(z) & = & \left( \frac{1}{4}\Lambda^2 - \lambda (1 - \lambda) \right) \left( z^2 + \frac{2\lambda - 1}{3} z^4 + o(z^4) \right) \\ && - \Lambda \left( 1 + \frac{2\lambda - 1}{2} z^2 + \frac{16\lambda^2 - 16\lambda + 1}{24} z^4 + o(z^4) \right) \\
-& = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
+V_0(z) & = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
 && + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
@@
 \begin{equation}
-\ddot{z} = s^2 \frac{d V_0}{dz}.
+m \ddot{z} = \alpha s^2 \frac{d V_0}{dz}.
 \label{eq:thermon}
@@
 \begin{equation}
-\ddot{z} - s^2 \left( \tfrac{1}{2} \Lambda^2 - (2\lambda - 1) \Lambda - 2 \lambda (1 - \lambda) \right) z = 0.
+m \ddot{z} - \alpha s^2 \left( \tfrac{1}{2} \Lambda^2 - (2\lambda - 1) \Lambda - 2 \lambda (1 - \lambda) \right) z = 0.
 \label{eq:thermon_small}
@@
 \begin{equation}
-S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
+S(T) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau
 \label{eq:thermon_action_1}
@@
 \begin{equation}
-\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
+\tfrac{1}{2} m \dot{z}^2 = V(z) - E(\tau_p),
 \label{eq:total_energy}
@@
 \begin{equation}
-\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
+\tau_p(E) = \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \sqrt{V(z) - E} ~dz,
 \label{eq:thermon_period}
@@
 \begin{equation}
-S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
+S(T) = 2 \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \sqrt{V(z) - E} ~dz + E \tau_p (E).
 \label{eq:thermon_action_2}
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=\linewidth]{pic/action_period_combined.eps}}
-\caption{(a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_1st_order_transition.eps} \\ (a)}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_2nd_order_transition.eps} \\ (b)}
+\end{minipage}
+\caption{(a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$; parameters: $\hbar = 1$, $k_B = 1$, $\alpha = 1$, $s = 1$; the solid liine correspond to the thermon action, $S_T(T)$; the dashed line corresponds to the thermodynamic action, $S_0(T) = \hbar \Delta V / k_b T$.
+\label{pic:action_period}}
 \end{figure}
@@
 \begin{equation}
-\omega_0 = s \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
+\omega_0 = 2 \alpha s \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}.
 \label{eq:period_small}
@@
 %
-The temperature of the 2nd-order transition can be estimated as
+The temperature of the 2nd-order transition can be computed as
+%
 \begin{equation}
-T_{II} = (s  / 2 \pi) \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
+T_{c}^{(2)} = (\alpha s / \pi) \sqrt{\lambda (1 - \lambda) + (2 \lambda - 1) \tfrac{\Lambda}{2} - \tfrac{1}{4} \Lambda^2}.
 \end{equation}
+%
+
+The temperature of the 1st-order transition can be estimated as
+%
+\begin{equation}
+T_{c}^{(1)} = \frac{\Delta V}{B},
+\end{equation}
+%
+where $\Delta V$ -- high of the potential barrier and $B$ is a instanton action which can be calculated as $B = S(E_{min})$.
+Excluding some constant form the hamiltonian we can rewrite our potential in a form
+%
+\begin{equation}
+\widetilde{V}_0(z) = \frac{\lambda (\cn{z} - \tfrac{\Lambda}{2 \lambda})^2}{\dn^2{z}}.
+\end{equation}
+%
+It's convenient, because when the barrier exist at the point $z = 0$, ($\Lambda < 2 \lambda$), $\widetilde{V}_0(z_{min}) = 0$ and $E_{min} = 0$.
+Action of the instanton trajectory can be obtained by integration
+%
+\begin{equation}
+\begin{array}{c}
+B = S(E_{min}) = 2 \sqrt{2 m} \int_{-z_{min}}^{+z_{min}} \sqrt{\alpha s^2 \widetilde{V}_0(z)} ~dz = \\
+= 2 s \left[ \log \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right];
+\end{array}
+\end{equation}
+%
+here $z_{min} = \frac{\Lambda}{2 \lambda}$.
+So, $T_{c}^{(1)} = \frac{\Delta V}{B}$, $\Delta V = \alpha s^2 \widetilde{V}_0(0) = \alpha s^2 \lambda (1 - \frac{\Lambda}{2 \lambda})^2$.
+You can see on Fig.\ref{pic:action_period}(a) an example of such estimation (left red line).
+It's differ form real value of tempereture (right red line) by $\sim 1.2\%$.
 

### 2017-01-19 phase_transition/preparing_paper.m

@@ -219,12 +219,14 @@ plot([0 0], [0 1], 'Color', 'black');
 clc; clear
 
 s = 1; % ~ Number of particles
+alpha = 1; % Parameter, lambda = beta / alpha
+mass = 1 / (2 * alpha);
 
 % Potential
 lambda = 0.9; Lambda = 0.1; % 1st-order transition
 % lambda = 0.5; Lambda = 0.5; % 2nd-order transition
 
-V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
+V = @(x) alpha * (s^2) * ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
 
 % Put barrier into zero E0 = V(0)
@@ -232,6 +234,7 @@ V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2)
 
 Vb = @(x) V(x) - V_min;
 
+figure
 x = -2:0.01:2;
 plot(x, Vb(x));
 
@@ -254,13 +257,13 @@ for i = 1:length(E)
 	fprintf('%i\n', i);
 	
 	[xleft, xright] = roots_near_equilibrium(@(x) -s^2 * Vb(x) + E(i));
-	tau_p(i) = sqrt(2) * integral(@(x) 1 ./ sqrt(s^2 * Vb(x) - E(i)),...
-		xleft, xright, 'AbsTol', 1e-6);
+	tau_p(i) = sqrt(2 * mass) * integral(@(x) 1 ./ sqrt(alpha * s^2 * Vb(x) - E(i)),...
+		xleft, xright, 'AbsTol', 1e-8);
 
 	T(i) = planck_const / (boltzmann_const * tau_p(i));
 
-	S(i) = 2 * sqrt(2) * integral(@(x) sqrt(s^2 * Vb(x) - E(i)),...
-		xleft, xright, 'AbsTol', 1e-6) + ...
+	S(i) = 2 * sqrt(2 * mass) * integral(@(x) sqrt(alpha * s^2 * Vb(x) - E(i)),...
+		xleft, xright, 'AbsTol', 1e-8) + ...
 		E(i) * tau_p(i);
 	
 	S0(i) = V0 * tau_p(i);
[…]

### 2017-01-20 phase_transition/preparing_paper.m
1st order temperature estimation is bad, owerre is also mistaken

@@ -77,7 +77,7 @@ set(h_axis(1), 'XLabel', 'x');
 %% Phase potential in elliptic coordinate with two parameters: \lambda, \Lambda
 clc; clear
 
-lambda = 0.9; Lambda = 2;
+lambda = 0.7; Lambda = 0.61;
 V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
 
@@ -206,7 +206,7 @@ Lambda = @(lambda) (1 - 16 * lambda + 16 * (lambda .^ 2) + ...
 	sqrt(1 + 32 * lambda - 32 * (lambda .^ 2))) ./ (4 * (2 * lambda - 1));
 
 % Avoid NaN at zero denominator
-lambda = 0.51:0.01:1;
+lambda = 0.501:0.001:1;
 plot([0.5 lambda], [0 Lambda(lambda)], 'LineWidth', 2, 'Color', 'black');
 
 lambda = 0:0.01:1;
@@ -215,7 +215,7 @@ plot(lambda, 2 * lambda, 'Color', 'black');
 plot([1 1], [0 2], 'Color', 'black');
 plot([0 0], [0 1], 'Color', 'black');
 
-%% S(T) plotting
+%% S(T) plotting, barrier at z = 0, minima at z_{min} = \cn^{-1} (\Lambda / (2 \lambda))
 clc; clear
 
 s = 1; % ~ Number of particles
@@ -223,8 +223,9 @@ alpha = 1; % Parameter, lambda = beta / alpha
 mass = 1 / (2 * alpha);
 
 % Potential
-lambda = 0.9; Lambda = 0.1; % 1st-order transition
+% lambda = 0.9; Lambda = 0.1; % 1st-order transition
 % lambda = 0.5; Lambda = 0.5; % 2nd-order transition
+lambda = 0.6; Lambda = 0; % 1st
 
 V = @(x) alpha * (s^2) * ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
[…]

### 2017-01-26 writing/phase_transition/phase_transition.tex
Numerical finding of the 1st-order transition temperature, fixes, additional text, figs refactoring

--- 2017-01-13 writing/phase_transition/phase_transition.tex
@@
 
-\author{A. P. Alodjanc}
+\author{A. P. Alodjants}
 \email{alexander\_ap@list.ru}
@@
 
-The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for practical purposes, see e.g.
+The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical purposes, see e.g.
 \cite{Dominici}; especially for their possible applications for quantum information science purposes.
 Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom made microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives, see, e.g.
-\cite{Demirchyan,Pagel,Kyriienko,Solnyshkov_2015}.
-In particular, we would like to mention here problems of design ultrafast quantum gates \cite{Kyriienko,Solnyshkov_2015}, creation of relatively long Rabi oscillations \cite{Dominici, Demirchyan} and quantum annealing problem \cite{Yan} where collective (bosonic) character of polariton BEC could be used.
-Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology for which designing of quantum interferometers and gyroscopes possessing high precision measurements with quantum phase states is utilized, cf.
-\cite{Gulevich, Pezze}.
+\cite{Demirchyan,Pagel,Kyriienko,Solnyshkov_2015, Dominici}.
+Especially it is important to stress quantum annealing problem \cite{Yan} that is very actual now and where collective (bosonic) character of polariton BEC could be used.
+In particular, as it is shown recently in \cite{Lewenstein} global minimum of energy landscape can be reached at finite temperatures via a combination of thermal annealing and quantum tunneling.
 
-In the paper we consider generic problem of quantum-classical phase transition with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect with them, cf.
-\cite{Chudnovsky_1997}.
-In general this area of research is based on dissipative tunneling problem or, tunneling at certain temperatures models, cf. \cite{Caldeira,Larkin,Riseborough}.
-Evidently seminal studies on this topic relay to superconductor devices \cite{Ankerhold} where macroscopic tunneling plays essential role.
-In particular, it worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{Makhlin}.
+Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology purposes for which designing of quantum interferometers and gyroscopes possessing high precision measurements with quantum phase states is utilized, cf.
+\cite{Pezze, Gulevich}.
+
+In the paper we consider generic problem  of quantum-classical phase transition (see e.g.\cite{Chudnovsky_1997}) with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect, cf.
+\cite{Aleiner, Shelykh_2008, Borgh_2010}.
+In general this problem relates to dissipative tunneling problem or, tunneling at finite (non-zero) temperatures models, cf. \cite{Caldeira, Larkin, Riseborough}.
+Traditionally  seminal studies on this topic are based on consideration of superconductor devices \cite{Ankerhold} where macroscopic tunneling plays essential role.
+In particular, it is worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{Makhlin}.
 Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
@@
 
-In the paper we propose \textit{extended model} for exciton polariton Josephson junctions when energy of polariton-polariton scattering contributes into the tunneling parameter, cf.
-\cite{Borgh,Solnyshkov_2008,Sarchi} and references therein.
-In particularly, we pay our attention to temperature dependent critical phenomena occurring in the presence of macroscopic tunneling.
+In the paper we propose \textit{extended model} for exciton polariton Josephson junctions that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter, cf.
+\cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
+In particularly, we pay our attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
 We aimed at elucidation of necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for creation of exciton polariton qubit gates.
@@
 In Sec. \ref{sec:model} we explain in details our model to realize Josephson junction with exciton polariton condensates.
-The extended tight-binding model will be established in this case. In Sec. \ref{sec:quantum_phase} we \dots.
+The extended tight-binding model will be established in this case.
+In Sec. \ref{sec:quantum_phase} we \dots.
 In the conclusion, we summarize the results obtained.
@@
 
-We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched on the Fig.
+We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched in the Fig.
 \ref{pic:potential_sym_asym}; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
@@
 where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ is two-body (polariton-polariton) scattering length.
-In the paper we use so-called two-mode representation of $\hat{\psi}$ supposing
+In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator supposing
 %
@@
 \end{equation}
-%
-
-Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double well potential.
-It is implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate
-%
-\begin{equation}
-G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2).
-\label{eq:tunneling_rate}
-\end{equation}
-%
+Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double-well potential.
+The ``additional'' terms with $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize density induced and pair tunneling, respectively.
+Generally, our model implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
 The contribution from relevant coefficients on can be estimated from variational ansatz
@@
 We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature {\red see e.g. \cite{Raghavan} and cf. }.
+This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
 %
@@
 
-To elucidate important quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
+To elucidate purely quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
 % 
@@
 %
-where $s = \dfrac{N}{2} >> 1$ is large {\red $C$ - number}, $\phi$ is phase variable.
-The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations
-%
-\begin{equation}
-[S_x, S_y] = iS_z, \quad[S_z, S_x] = iS_y, \quad[S_y, S_z] = iS_x.
-\label{eq:commutation_relations}
-\end{equation}
-%
+where $s = \dfrac{N}{2} >> 1$ is large { C - number}, $\phi$ is the phase variable.
+The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations $[S_x, S_y] = iS_z, \quad[S_z, S_x] = iS_y, \quad[S_y, S_z] = iS_x$.
+
 After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
@@
 
-Hamiltonian (\ref{eq:hamiltinian_s}) corresponds to Schrodinger equation
+Schrodinger equation with Hamiltonian (\ref{eq:hamiltinian_s}) looks like  
 %
@@
 is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
-It is possible to eliminate the term with first derivative in Eq.(\ref{eq:schrodinger}) applying the transformation
+It is possible to eliminate the term with first derivative in Eq. (\ref{eq:schrodinger}) applying the transformation
 %
 \begin{equation}
-\Phi(\phi) = \Psi(z) \exp \Big( s \log \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
+\Phi(\phi) = \Psi(z) \exp \Big( s \ln \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
 \label{eq:transformation_of_phi}
@@
 %
-where
+where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
+
+Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to convenient Schr\"odinger equation
 %
 \begin{equation}
-z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)
-\end{equation}
-is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
-
-Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we come to convenient Schr\"odinger equation
-%
-\begin{equation}
-\frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
+\frac{1}{2 m} \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
 \label{eq:schrodinger_usual}
@@
 %
-for quantum particle with mass $m_{eff} = \dfrac{1}{2}$, normalized energy $E \equiv \dfrac{E}{\alpha}$ moving in the potential $V(z) = s^2 V_0(z)$ with
+for quantum particle with ``mass'' $m = \dfrac{1}{2 \alpha}$, energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
 %
@@
 Effective potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of  elliptic integral phase coordinate $z$.
-Points $A, B$ and $C$ in (b) corresponds to minima of the potential occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
+Points $z_{1,2}$ and $z_{3}$ in (b) corresponds to global and local minima of the potential, correspondingly,  occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
 \end{figure}
@@
 
-\subsection{Rabi regime}
+\textit{Rabi regime} $\Lambda \gg 1$. In this limit the trapping potential reads $V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}$.
+Physically, for any value of $\lambda$ -- parameter taken from the domain $\lambda <1$ we can obtain phase (Rabi) oscillations.
+In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and cf. \cite{Anglin}.
+Below we are not interesting in this regime.
 
-Here we suppose that $\Lambda \gg 1$.
-In this limit the trapping potential reads
+\textit{Josephson regime} $1/N^2\ll\Lambda <1$.
+This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
+The behavior of the phase depends on the ratio between parameters $\Lambda$ and $\lambda$.
+If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
+Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like {\red equation for small oscillations}.
+
+In the other limit, for $\Lambda < 2 \lambda$, quantum particle is trapped at two minima of $V_0(z)$ $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
+Fig.
+\ref{phase_potential}b,c.
+The depth of the potential minima depends on the $\lambda$ parameter.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$ that is marked by red point $C$ in Fig.3b.
+
+\textit{Fock regime} $\Lambda \ll 1/N^2$.
+In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with limiting value of the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In this regime we distinguish two limits.
+First, we suppose that inequality $\Lambda \ll \lambda < 1$ is holds.
+In this case small enough $\lambda$ from (\ref{eq:potential}) one can obtain
+%
+{\red
+
 %
 \begin{equation}
-V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}
-\label{eq:rabi_potential}
-\end{equation}
-%
-It is interesting to note that even in this case the role of $\lambda$-parameter is evident --- see Fig. \ref{phase_potential}a.
-
-\subsection{Fock regime}
-
-In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with limiting value of the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
-In this regime we distinguish two limits.
-First, we suppose that inequality $\Lambda \ll \lambda \ll 1$ is holds.
-In this case from (\ref{eq:potential}) one can obtain
-%
-\begin{equation}
-V_F(z) = -\lambda(1 - \lambda) \sd^2{z}.
-\label{eq:fock1_potential}
-\end{equation}.
-%
-
-{\red
-Using the fact that $\lambda$ is small we can replace the potential (\ref{eq:fock1_potential}) with
-%
-\begin{equation}
-V_F(z) \sim -\lambda (1 - \lambda) \sin^2{z},
+V_F(z) \simeq -\lambda (1 - \lambda) \sin^2{z},
 \end{equation}
@@
 
-Another limit that could be studied within Fock regime is relevant to condition $\lambda \ll \Lambda \ll 1$.
-In this case from (\ref{eq:potential}) we have
-% 
-\begin{equation}
-V_0(z) \simeq -\Lambda \cos{z}
-\label{eq:fock2_potential}
-\end{equation}
-%
-Equation (\ref{eq:fock2_potential}) deals with negligible $\lambda$; it is reproduces results for convenient quantum phase model \cite{Anglin}.
-
-Practically, Fock regime interesting for high precision measurements.
-In particular, the dispersion of the quantum phase in this case approaches to so-called Heisenberg limit {\red $< (\Delta\phi)^2 > \propto \dfrac{1}{N^2}$} which is the minimal accessible error for the phase measurement in respect of total particle number.
-
-\subsection{Josephson regime}
-
-Here we suppose that {\red $\Lambda < 1$}.
-This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
-In general all terms in (\ref{eq:potential}) should be kept.
-The behavior of effective potential $V_0(z)$ depends on the ratio between parameters $\Lambda$ and $\lambda$.
-If $\Lambda < 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
-Frequency of small amplitude ($z \ll 1$) oscillations can be find from (\ref{eq:potential}) and looks like
-{\red equation for small oscillations}
-
-In the other limit, for $2 \lambda > \Lambda$, two minima of $V_0(z)$ with coordinates
-%
-\begin{equation}
-\cn{z_{min}} = \frac{\Lambda (2 \lambda - 1)}{0.5 \Lambda^2 - 2 \lambda (1 - \lambda)}
-\label{eq:z_minima}
-\end{equation}
-%
-appears both for Josephson and Fock regimes, cf. Fig. \ref{phase_potential}b,c.  
-The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for {\red $\Lambda > 1 + 2\lambda + \sqrt{1 + 8\lambda}$} potential $V_0(z)$ presumes local minimum at {\red $\pm 2 K(\lambda)$}.
-
-Practically two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
-\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.[ ]}.
-However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
-Another interesting phenomena that can be obtained with potential in Fig. \ref{phase_potential}b is connected with some analogies in cosmology and quantum field theory.
-In particular, in our recent work {\red [ ]} we discuss Higgs field generation by using exciton polaritons in semiconductor Bragg mirror structures as an on table analog of known cosmological phenomenon, {\red cf.
-[ ]}.
-In this paper we continue our physical analogies with false vacuum decay (marked by the point $C$ in Fig. \ref{phase_potential}b) that can be established here, {\red cf. [ ]}.
+Another limit that could be studied within Fock regime is relevant to condition $\lambda \ll \Lambda$. In this case from (\ref{eq:potential}) we have $V_0(z) \simeq -\Lambda \cos{z}$.
+In fact, this limit that deals with negligible $\lambda$ reproduces results for convenient quantum phase model \cite{Anglin}.
 
@@
 Strictly speaking, results established in previous section are completely valid at zero temperature.
-However, in current experiments exciton polariton condensate is observed at finite and high enough temperatures.
-In this section we find answer to vital question: when quantum approach to the phase problem for exciton polariton Josephson junction is valid?
+However, in current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures.
+In this section we find answer to vital question: when quantum approach to the phase problem for Josephson junction utilizing weakly coupled exciton polariton condensate channels is valid?
 
-Here we describe our approach to study the order of the phase transition and its temperature.
-According to works of Owerre, Chudnovsky, Garanin et al. order of these transition can be determined from the period of oscillation $\tau(E)$ near the bottom of the potential.
-Monotonically increasing $\tau(E)$ gives a second-order transition while nonmonotonic behaviour of $\tau(E)$ give a first-order transition.
+To give an answer to this question we consider the effective $W$ -- like potential represented in Fig. \ref{phase_potential}b,c inherent to the Josephson, or Fock regimes, respectively.
+To be more specific we examine here thermodynamically equilibrium system at finite temperature $T$.
+Transition between to stable states (say, between points $z_{1,2}$ in Fig.\ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
+Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is height of the barrier between two states with minimum of potential energy) the particle undergoes hopping over the barrier governed by familiar thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$, cf.
+\cite{Larkin}.
+On the other hand, in the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with the rate $\Gamma \sim e^{-B}$, where $B$ is the instanton action.
+As it is discussed previously transition (crossover) between this two limits exhibits universal features of first or second order phase transitions which can be interpreted as phase transition between classical and quantum regimes, \cite{Chudnovsky_1997, Larkin, Owerre}.
+Now we elucidate conditions for their realization for exciton polariton Josephson junction problem.
 
-We determiine the temperature of the transition like Owerre does.
-At very low temperature, transition occur by quantum tunneling through the barrieer and the rate is governed by $\Gamma \sim e^{-B}$, where $B$ is the instanton action.
-At high temperature the particle has the possibility of hopping over the barrier, in this case the rate is governed by $\Gamma \sim e^{-\Delta V / T}$, where $\Delta V$ is the energy barrier.
-At a critical point these two transition rate are equal, there exist a crossover (first-order transition) temperature $T_{I}$ from quantum to a thermal regime, it's estimated as $T_{I} = \Delta V / B$.
+Our description is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
+The imaginary-time action obtained within WKB method approaches as
+%
+\begin{equation}
+S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau.
+\label{eq:thermon_action_1}
+\end{equation}
+%
+The decay rate $\Gamma \sim e^{-S_{min}}$ according our approach can be expressed through the minimal value $S_{min}$ of the action.
+The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion for the thermon oscillating inside the inverted potential $-V(z)$, that is 
+%
+\begin{equation}
+m \ddot{z} = \frac{d V}{dz}.
+\label{eq:thermon}
+\end{equation}
+%
+Periodic solutions for of Eq. (18) satisfy the relation
+%
+\begin{equation}
+\tfrac{1}{2} m \dot{z}^2 = V(z) - E(\tau_p),
+\label{eq:total_energy}
+\end{equation}
+%
+where $\tau_p = \hbar / k_B T$ is a thermon period corresponding to the energy $E(\tau_p)$;
+%
+\begin{equation}
+\tau_p(E) = \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \sqrt{V(z) - E} ~dz.
+\label{eq:thermon_period}
+\end{equation}
+%
+In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are turning points, cf. Fig. \ref{phase_potential}b.
+The Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at energy $E = 0$ and temperature $T = 0$ characterize instanton solution.
+The Eq. (\ref{eq:thermon_action_1}) with (\ref{eq:total_energy}) for thermon action can be rewritten in a form 
+%
+\begin{equation}
+S_T = 2 \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \sqrt{V(z) - E} ~dz + E \tau_p (E).
+\label{eq:thermon_action_2}
+\end{equation}
+%
 
-The crossover temperature in the case of second-order transition can be estimated as $T_{II} = \omega_0 / 2 \pi$, where $\omega_0$ is a oscillation frequency of the thermon near the top of the barrier.
+To determine thermodynamic properties of the system it is necessary to know small amplitude oscillations behavior of the particle at the bottom, $z=0$, of inverted potential $-V(z)$.
+The action in this case reads, {\red cf. \dots}:
+%
+\begin{equation}
+S_0 = \Delta V \tau_p (E).
+\label{eq:thermal_action}
+\end{equation}
+%
 
-First, let's find out the dependence of the order on the parameters $\lambda$, $\Lambda$.
-Expand the potential $V_0(z)$ into a Taylor series:
+Expansion of the potential $V(z)$ excluding constant value $V(0)$ gives:
 %
@@
 \begin{array}{lcl}
-V_0(z) & = & \left( \frac{1}{4}\Lambda^2 - \lambda (1 - \lambda) \right) \left( z^2 + \frac{2\lambda - 1}{3} z^4 + o(z^4) \right) \\ && - \Lambda \left( 1 + \frac{2\lambda - 1}{2} z^2 + \frac{16\lambda^2 - 16\lambda + 1}{24} z^4 + o(z^4) \right) \\
-& = & -\Lambda + \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
-&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
+V_0(z) & = &\left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
+&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (1 - \lambda) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
 \end{array}
@@
 %
-Classical equation of motion for the thermon reads as
-%
-\begin{equation}
-\ddot{z} = s^2 \frac{d V_0}{dz}.
-\label{eq:thermon}
-\end{equation}
-%
-Equation for the small ocsillation near the top of the barrier:
-%
-\begin{equation}
-\ddot{z} - s^2 \left( \tfrac{1}{2} \Lambda^2 - (2\lambda - 1) \Lambda - 2 \lambda (1 - \lambda) \right) z = 0.
-\label{eq:thermon_small}
-\end{equation}
-%
-It follows from (\ref{eq:thermon_small}) that, as mentioned above, when $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.
-
-It's possible to show (for ex. using Poincare-Lindstedt method), that local behaviour of $\tau(E)$ is determined by the sign of the 4th degree in expansion (\ref{eq:potential_teylor}).
-If potential has the form $-x^2 - x^4$ than $\tau(E)$ increase near the critical value $E_0$ (where the thermon vanish) and the 1st order phase transition take place.
-In other case, if potential has the form $-x^2 + x^4$ than $\tau(E)$ decrease near the $E_0$ and the 2nd order phase transition occurs.
-So, the border between 1st and 2nd phase transition is determined by the equaiton
-%
-\begin{equation}
-\frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (\lambda - 1) (2\lambda - 1)}{3} = 0.
-\end{equation}
-%
-Taking in account the barrier existence condition, and conditions on $\lambda$, $\Lambda$ parameters one can derive the analytic expression of the border
+In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the first order phase transition occurs.
+If $-V(z)$ behaves as $z^2 + z^4$ second order phase transition take place.
+Phase boundary between 1st and 2nd order phase transition is determined by the relation
 %
@@
 %
-We summarize our results on a picture below.
+We summarize our results in the Fig.\ref{pic:phase_boundary}. 
 %
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
-\caption{Phase transition diagram}
+\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$, $\lambda$ - parameter plane. \label{pic:phase_boundary}}
 \end{figure}
@@
 
-Consider the imaginary-time action
+The crossover temperature of second-order phase transition $T_{c}^{(2)} = \hbar \omega_0/ 2 \pi k_B$ is 
 %
 \begin{equation}
-S(T) = \oint (\tfrac{1}{2} \dot{z}^2 + s^2 V_0(z)) d \tau
-\label{eq:thermon_action_1}
+T_{c}^{(2)} = (\hbar \alpha s / \pi k_B) \sqrt{\lambda (1 - \lambda) + (2 \lambda - 1) \tfrac{\Lambda}{2} - \tfrac{1}{4} \Lambda^2},
+\label{eq:second_order}
 \end{equation}
 %
-Periodic, with $\tau_p = \hbar / k_B T$, solutions of (\ref{eq:thermon}) satisfy the relation
-%
-\begin{equation}
-\tfrac{1}{2} \dot{z}^2 = s^2 V_0(z) - E(\tau_p),
-\label{eq:total_energy}
-\end{equation}
-%
-where $\tau_p$ is a thermon period corresponding to the energy level $E(\tau_p)$;
-%
-\begin{equation}
-\tau_p(E) = \sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz,
-\label{eq:thermon_period}
-\end{equation}
-%
-here $z_{1,2}(E)$ -- turning points.
-Using (\ref{eq:total_energy}) rewrite (\ref{eq:thermon_action_1}) in a form 
-%
-\begin{equation}
-S(T) = 2\sqrt{2} \int_{z_1(E)}^{z_2(E)} \sqrt{s^2 V_0(z) - E} ~dz + E \tau_p (E).
-\label{eq:thermon_action_2}
-\end{equation}
-%
-We draw dependence $S(T)$ and $\tau_p(E)$ for the cases of the 1st and 2nd order phase transition.
-For the sake of convenience we suppose that $V_0(z) = 0$ at minima surrounding the barrier.
-So, $E = 0$ corrensponds to the separatrices instanton solution (May be we should make corresponding transformation earlier).
+where $\omega_0 = 2 \alpha s \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon near the bottom of inverted potential.
+From (\ref{eq:second_order}) follows that, for $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.
 %
 \begin{figure}[ht]
-\center{\includegraphics[width=\linewidth]{pic/action_period_combined.eps}}
-\caption{(a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$}
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_2nd_order_transition.eps} \\ (a)}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_1st_order_transition.eps} \\ (b)}
+\end{minipage}
+\caption{Dependences of minimal action $S_{min}$ (ABC-curve) as a function of dimensionless temperature $ T= \hbar / k_B \tau_p$ for (a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$; parameters: $\hbar = 1$, $k_B = 1$, $\alpha = 1$, $s = 1$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
+\label{pic:action_period}}
 \end{figure}
@@
 
-Now let's compute the temperature of the phase transition.
-It follows from (\ref{eq:thermon_small}) that the frequency of small thermon oscillation near the top of the barrier can be computted as follows
+Fig. \ref{pic:action_period}a displays second-order phase transition from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
+The crossover occurs at the critical point $T_{c}^{(2)}$ where $S_T = S_0$ and {\red $E = E_0 = \dots$}.
+The inset demonstrate monotonic dependence of thermon period $\tau_p$ on energy $E$ that is inherent to second-order phase transition.
+Closest to the critical point with energy $E=E_0$ thermon undergoes small amplitude oscillations.
+
+In Fig. \ref{pic:action_period}b we represent results exhibiting first-order phase transition.
+It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of thermon period $\tau_p$ on energy $E$ is non-monotonic (see inset in Fig.
+\ref{pic:phase_boundary}b).
+The critical temperature $T_{c}^{(1)}$ belongs to the temperature domain $T_{min} < T_{c}^{(1)} < T_{max}$ and can be find out numerically by solving Eqs.(\ref{eq:thermon_period}) - (\ref{eq:thermal_action}) under the condition $S_T = S_0$.
+
+Analytically critical temperature $T_{c}^{(1)}$ one possible to approach as $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
+After some straightforward calculations for $B$ we obtain
 %
 \begin{equation}
-\omega_0 = s \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
-\label{eq:period_small}
+\begin{array}{c}
+B = S(E_{min}) = 2 s \left[ \log \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right].
+\end{array}
+\label{eq:B_action}
 \end{equation}
 %
-The temperature of the 2nd-order transition can be estimated as
-\begin{equation}
-T_{II} = (s  / 2 \pi) \sqrt{2 \lambda (1 - \lambda) + (2 \lambda - 1) \Lambda - \tfrac{1}{2} \Lambda^2}.
-\end{equation}
+
+In current experiments it is much more easier to manipulate be the density of exciton polaritons instead of their temperature that is even difficult to identify due the some the non-equilibrium processes occurring in real microcavity samples, see e.g.
+\cite{Sanvitto,Guillet}.
+For instance, the density of polariton gas can be manipulated by using the optical pump.
+In Fig.
+\ref{pic:temperatures} we plot numerically calculated critical temperature of 1st and 2nd order phase transitions against $\Lambda$-parameter for experimentally accessible semiconductor Josephson junction samples.
+The solid (green) line corresponds to analytical solution obtained with  Eq. (\ref{eq:B_action}).
+Since the $\Lambda$-parameter is inversionally proportional to the density of exciton polariton gas (so-called blue shift) Fig.
+\ref{pic:temperatures} establishes important correspondence between critical temperatures discussed in the paper and relevant exciton polariton densities.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_temperatures.eps}}
+\caption{\dots}
+\label{pic:temperatures}
+\end{figure}
+%
+
+\section{Phase transitions in the presence of non-equilibrium processes 
+\label{sec:phase_transition}}
 
@@
 \section{Conclusion \label{sec:conclusion}}
+
+Practically, Fock regime interesting for high precision measurements.
+In particular, the dispersion of the quantum phase in this case approaches to so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ which is the minimal accessible error for the phase measurement in respect of total particle number.
+
+Practically two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
+\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.
+[ ]}.
+However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
+Another interesting phenomena that can be obtained with potential in Fig. \ref{phase_potential}b is connected with some analogies in cosmology and quantum field theory.
+In particular, in our recent work {\red [ ]} we discuss Higgs field generation by using exciton polaritons in semiconductor Bragg mirror structures as an on table analog of known cosmological phenomenon, {\red cf.
+[ ]}.
+In this paper we continue our physical analogies with false vacuum decay (marked by the point $C$ in Fig. \ref{phase_potential}b) that can be established here, {\red cf. [ ]}.
 

### 2017-01-26 phase_transition/inv_cn.m

@@ -1,0 +1,4 @@
+function [ f ] = inv_cn( x, lambda )
+f = elliptic12(acos(x), lambda);
+end
+

### 2017-01-26 phase_transition/iterational_process.m

@@ -1,0 +1,21 @@
+function [ E ] = iterational_process( Vb, V0, mass, E0 )
+
+eps = 1e-6;
+
+while true
+	[xleft, xright] = roots_near_equilibrium(@(x) -Vb(x) + E0);
+	period = sqrt(2 * mass) * integral(@(x) 1 ./ sqrt(Vb(x) - E0),...
+		xleft, xright, 'AbsTol', 1e-6);
+
+	E = V0 - (2 * sqrt(2 * mass) / period) * integral(@(x) sqrt(Vb(x) - E0),...
+		xleft, xright, 'AbsTol', 1e-6);
+	
+	if abs(E - E0) < eps
+		return
+	else
+		E0 = E;
+	end
+end
+
+end
+

### 2017-01-26 phase_transition/preparing_paper.m

@@ -77,14 +77,18 @@ set(h_axis(1), 'XLabel', 'x');
 %% Phase potential in elliptic coordinate with two parameters: \lambda, \Lambda
 clc; clear
 
-lambda = 0.7; Lambda = 0.61;
+lambda = 0.8; Lambda = 0.5;
 V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
 
 K = ellipk(sqrt(lambda));
 x = -(4*K):0.01:(4*K);
 
-plot(x, V(x)); grid on
+plot(x, V(x)); hold on; grid on
+x_max = inv_cn(-2 * (1 - lambda) / Lambda, lambda);
+
+plot([-x_max -x_max], [0 V(x_max)], 'Color', 'red');
+plot([+x_max +x_max], [0 V(x_max)], 'Color', 'red');
 
 %% Rabi regime
 Lambda = 100;
@@ -223,9 +227,8 @@ alpha = 1; % Parameter, lambda = beta / alpha
 mass = 1 / (2 * alpha);
 
 % Potential
-% lambda = 0.9; Lambda = 0.1; % 1st-order transition
+lambda = 0.9; Lambda = 0.1; % 1st-order transition
 % lambda = 0.5; Lambda = 0.5; % 2nd-order transition
-lambda = 0.6; Lambda = 0; % 1st
 
 V = @(x) alpha * (s^2) * ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
@@ -246,7 +249,7 @@ planck_const = 1;
 boltzmann_const = 1;
 
 % Energy level
-E = linspace(0.001, V0, 150);
+E = linspace(0.001, V0 - 0.001, 150);
 
 T = zeros(1, length(E));
 S = zeros(1, length(E)); S0 = S;
@@ -256,13 +259,13 @@ fprintf('Total number of iteration: %i\n', length(E));
 for i = 1:length(E)
 	fprintf('%i\n', i);
 	
-	[xleft, xright] = roots_near_equilibrium(@(x) -s^2 * Vb(x) + E(i));
[…]

### 2017-01-26 phase_transition/roots_near_equilibrium.m

@@ -1,28 +1,0 @@
-function [ xleft, xright ] = roots_near_equilibrium( f )
-%
-% INPUT:
-%
-
-% Step
-step = 0.01;
-
-% Convergence
-delta = 1e-12;
-
-x0 = 0;
-x1 = x0 + step;
-
-while true
-	if sign(f(x0)) == sign(f(x1))
-		x0 = x1;
-		x1 = x1 + step;
-	else
-		x_root = dichotomy(f, x0, x1, delta);
-		break
-	end
-end
-
-xright = abs(x_root);
-xleft = -xright;
-
-end

### 2017-01-27 writing/phase_transition/phase_transition.tex
Non-symmetric barrier done

@@
 The extended tight-binding model will be established in this case.
-In Sec. \ref{sec:quantum_phase} we \dots.
+In Sec. \ref{sec:quantum_phase} we {\red \dots }.
 In the conclusion, we summarize the results obtained.
@@
 If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
-Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like {\red equation for small oscillations}.
+Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like { \red $\omega_{0, quantum} = 2 \alpha s \sqrt{\frac{1}{4} \Lambda^2 - \frac{\Lambda}{2} (2\lambda - 1) - \lambda(1 - \lambda)}$ }.
 
@@
 \begin{array}{lcl}
-V_0(z) & = &\left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
-&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (1 - \lambda) (2\lambda - 1)}{3} \right) z^4 + o(z^4).
+V(z) & = & \alpha s^2 \Big[ \left( \frac{1}{4} \Lambda^2  - \frac{2\lambda - 1}{2} \Lambda - \lambda (1 - \lambda) \right) z^2 \\
+&& + \left( \frac{2\lambda - 1}{12} \Lambda^2 - \frac{16\lambda^2 - 16\lambda + 1}{24} \Lambda - \frac{\lambda (1 - \lambda) (2\lambda - 1)}{3} \right) z^4 + o(z^4) \Big].
 \end{array}
@@
 
+{\red
+
+Another type of barrier --- upper barrier.
+Exist when $\Lambda > 2(1 - \lambda)$.
+Potential presumes local minima at $\pm 2K(\lambda)$ and local maxima at $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
+Equation for the thermon yeilds small ocsilation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \alpha s \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
+The crossover temperature of second-order phase transition
+%
+\begin{equation}
+T_{c}^{(2)} = (\hbar \alpha s / 2 \pi k_B) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}.
+\label{eq:second_order_2}
+\end{equation}
+%
+With the aim of analytical determining of the phase transition order let's write the Taylor series for $V(z)$ near the vicinity of $z_{max}$.
+Expansion of the potential $V(z)$ excluding constant value $V(z_{max})$ gives:
+%
+\begin{equation}
+V(\tilde{z}) = \alpha s^2 \Big[ -\tfrac{1}{4} \left( \tfrac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda) \right) \tilde{z}^2 
++ \tfrac{1}{2} \tfrac{\Lambda \sqrt{\Lambda^2 - 4(1 - \lambda)^2}}{\sqrt{1 - \lambda} \sqrt{\Lambda^2 + 4 \lambda (1 - \lambda}} \tilde{z}^3 + o(\tilde{z}^4) \Big],
+\label{eq:potential_teylor_2}
+\end{equation}
+%
+where $\tilde{z} = z - z_{max}$.
+It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
+We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs.
+\ref{pic:action_period_2}, \ref{pic:temperatures_2}, and summarize our results on the Fig.
+\ref{pic:phase_boundary_combined}.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/action_period_2nd_order_transition_b2.eps}}
+\caption{\dots}
+\label{pic:action_period_2}
+\end{figure}
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_temperatures_b2.eps}}
+\caption{\dots}
+\label{pic:temperatures_2}
+\end{figure}
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
+\caption{\dots \label{pic:phase_boundary_combined}}
+\end{figure}
+%
+
+}
+
 \section{Phase transitions in the presence of non-equilibrium processes 

### 2017-01-27 phase_transition/preparing_paper.m

@@ -77,18 +77,19 @@ set(h_axis(1), 'XLabel', 'x');
 %% Phase potential in elliptic coordinate with two parameters: \lambda, \Lambda
 clc; clear
 
-lambda = 0.8; Lambda = 0.5;
+lambda = 0.25; Lambda = 1.5;
 V = @(x) ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
 
 K = ellipk(sqrt(lambda));
 x = -(4*K):0.01:(4*K);
 
-plot(x, V(x)); hold on; grid on
-x_max = inv_cn(-2 * (1 - lambda) / Lambda, lambda);
+figure('Position', [100 100 325 225]); hold on
+plot(x, V(x), 'Color', 'black'); hold on
 
-plot([-x_max -x_max], [0 V(x_max)], 'Color', 'red');
-plot([+x_max +x_max], [0 V(x_max)], 'Color', 'red');
+% x_max = inv_cn(-2 * (1 - lambda) / Lambda, lambda);
+% plot([-x_max -x_max], [0 V(x_max)], 'Color', 'red');
+% plot([+x_max +x_max], [0 V(x_max)], 'Color', 'red');
 
 %% Rabi regime
 Lambda = 100;
@@ -200,7 +201,7 @@ title(sprintf('\\Lambda = %g', Lambda));
 xlabel('z');
 ylabel('V_0(z)');
 
-%% Phase transition diagram
+%% Phase transition diagram, combined for two barriers
 
 figure('Position', [100 100 325 250]); hold on
 axis([0 1 0 2]); xlabel('\lambda'); ylabel('\Lambda')
@@ -215,6 +216,7 @@ plot([0.5 lambda], [0 Lambda(lambda)], 'LineWidth', 2, 'Color', 'black');
 
 lambda = 0:0.01:1;
 plot(lambda, 2 * lambda, 'Color', 'black');
+plot(lambda, 2 * (1 - lambda), 'Color', 'black');
 
 plot([1 1], [0 2], 'Color', 'black');
 plot([0 0], [0 1], 'Color', 'black');
[…]

### 2017-02-09 writing/phase_transition/phase_transition.tex
Intermediate commit

@@
 %
-We summarize our results in the Fig.\ref{pic:phase_boundary}. 
+We summarize our results in the Fig.\ref{pic:phase_boundary_combined}. 
 %
 \begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram.eps}}
-\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$, $\lambda$ - parameter plane. \label{pic:phase_boundary}}
+\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
+\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$,$\lambda$-parameter plane \label{pic:phase_boundary_combined}}
 \end{figure}
@@
 It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of thermon period $\tau_p$ on energy $E$ is non-monotonic (see inset in Fig.
-\ref{pic:phase_boundary}b).
+\ref{pic:action_period}b).
 The critical temperature $T_{c}^{(1)}$ belongs to the temperature domain $T_{min} < T_{c}^{(1)} < T_{max}$ and can be find out numerically by solving Eqs.(\ref{eq:thermon_period}) - (\ref{eq:thermal_action}) under the condition $S_T = S_0$.
@@
 
-{\red
-
 Another type of barrier --- upper barrier.
@@
 It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
-We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs.
-\ref{pic:action_period_2}, \ref{pic:temperatures_2}, and summarize our results on the Fig.
-\ref{pic:phase_boundary_combined}.
+We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs. \ref{pic:action_period_temperature_2}, and summarize our results on the Fig. \ref{pic:phase_boundary_combined}.
 %
 \begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/action_period_2nd_order_transition_b2.eps}}
-\caption{\dots}
-\label{pic:action_period_2}
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition_b2.eps} \\ (a)}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=\linewidth]{pic/phase_transition_temperatures_b2.eps} \\ (b)}
+\end{minipage}
+\caption{\dots \label{pic:action_period_temperature_2}}
 \end{figure}
 %
-\begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_temperatures_b2.eps}}
-\caption{\dots}
-\label{pic:temperatures_2}
-\end{figure}
-%
-\begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
-\caption{\dots \label{pic:phase_boundary_combined}}
-\end{figure}
-%
-
-}
-
 \section{Phase transitions in the presence of non-equilibrium processes 

### 2017-02-09 phase_transition/preparing_paper.m

@@ -589,30 +589,136 @@ d1f = @(x) (Vb(x + eps) - Vb(x - eps)) / eps;
 d2f = @(x) (Vb(x + eps) - 2 * Vb(x) + Vb(x - eps)) / (eps^2);
 d3f = @(x) (Vb(x + 2 * eps) - 2 * Vb(x + eps) + 2 * Vb(x - eps) - Vb(x - 2 * eps)) / (2 * eps^2);
 
+%% Dynamic transition
+clc; clear
+
+omega_m = 0; u = 5;
+kapa = 0.002;
+
+df = @(t, f) [2*f(3); 2*omega_m*f(3) - u*exp(-2*kapa*t)*f(1)*f(3); -2*f(1) - 2*omega_m*f(2) + u*exp(-2*kapa*t)*f(1)*f(2)];
+
+f0 = [0.87; 0.493; 0];
+% f0 = [0.29 0.957 0];
+
+[T, F] = RK4(df, [0 100], f0, 2048);
+
+plot3(F(:, 1), F(:, 2), F(:, 3), 'green'); hold on;
+
+% S0 = sqrt((F(:, 1).^2) + (F(:, 2).^2) + (F(:, 3).^2));
+% plot(T, F(:, 1) ./ S0); hold on
+
+% omega_m = 0; u = 5;
+% df = @(t, f) [2*f(3); 2*omega_m*f(3) - u*f(1)*f(3); -2*f(1) - 2*omega_m*f(2) + u*f(1)*f(2)];
+% f0 = [0.29; 0.957; 0];
+% [T, F] = RK4(df, [0 20], f0, 2048);
+% plot3(F(:, 1), F(:, 2), F(:, 3), 'Color', 'red');
+
+%%
+clc; clear
+
+alpha = 1; beta = 0.9; B = 1;
+kappa = 0.002;
+
+a = @(t) alpha * exp(-2*kappa*t);
+b = @(t) beta * exp(-2*kappa*t);
+
+df = @(t, f) [2*b(t) * f(2) * f(3) - B*f(3);
+	-2*a(t) * f(1) * f(3);
+	2*(a(t) - b(t)) * f(1) * f(2) + B * f(1)];
+
+R = 1;
+S10 = 0; S20 = 0.62;
+S30 = sqrt(R^2 - S10^2 - S20^2); 
+f0 = [S10; S20; S30];
+
+[T, F] = RK4(df, [0 250], f0, 4*1024);
[…]

### 2017-02-14 writing/phase_transition/phase_transition.tex
Dissipation: outset

@@
 \section{Phase transitions in the presence of non-equilibrium processes 
-\label{sec:phase_transition}}
+\label{sec:non-equilibrium}}
 
-\dots
+Consider the influence of the dissipation in our system.
+Supposing that $\Gamma = 0$, system with dissipation can be derived from hamiltonian and reads as
+%
+\begin{equation}
+\begin{array}{lcl}
+i \psi_{1, t} & = & -i \kappa \psi_1 +  \alpha |\psi_1|^2 \psi_1 - (B/2 - \beta \psi_1^* \psi_2) \psi_2; \\
+i \psi_{2, t} & = & -i \kappa \psi_2 + \alpha |\psi_2|^2 \psi_2 - (B/2 - \beta \psi_2^* \psi_1) \psi_1.
+\end{array}
+\end{equation}
+%
+Change of variables: $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t)$.
+System takes form
+%
+\begin{equation}
+\begin{array}{lcl}
+i \Psi_{1, t} & = & \alpha(t) |\Psi_1|^2 \Psi_1 - (B/2 - \beta(t) \Psi_1^* \Psi_2) \Psi_2; \\
+i \Psi_{2, t} & = & \alpha(t) |\Psi_2|^2 \Psi_2 - (B/2 - \beta(t) \Psi_2^* \Psi_1) \Psi_1.
+\end{array}
+\end{equation}
+%
+It's equivalent to the non-dissipative system with time dependent parameters $\alpha(t) = \alpha \exp(-2 \kappa t)$, $\beta(t) = \beta \exp(-2 \kappa t)$.
+Hamiltoninan in terms of Stocks operators (\ref{eq:pseudo_spin}):
+%
+\begin{equation}
+\hat{H} = \alpha(t) \hat{S}_z^2 + \beta(t) \hat{S}_x^2 - B \hat{S}_x.
+\end{equation}
+%
+Equaitions on the mean-values of operators:
+% 
+\begin{equation}
+\begin{array}{lcl}
+\dot{S}_z & = &  2 \beta(t) S_x S_y - B S_y; \\
+\dot{S}_x & = & -2 \alpha(t) S_z S_y; \\
+\dot{S}_y & = & 2(\alpha(t) - \beta(t)) S_z S_z + B S_z.
+\end{array}
+\end{equation}
+%
+Invariant of the system
+%
+\begin{equation}
+S_x^2 + S_y^2 + S_z^2 = S_0^2 = R^2,
+\end{equation}
+%
+where $R$ -- is a radius of the Poincare sphere.
+Non-dissipative system has a bifurcation at the critical values of $\beta^* = B / 2R$.
+
+It can be transformed to the equation on the phase difference $\phi$ and $S_z$ as follows
+%
+\begin{equation}
+\begin{array}{lcl}
+\dot{S}_z & = & B \sqrt{1 - S_z^2} \sin \phi - 2 \beta(t) (1 - S_z^2) \sin \phi \cos \phi; \\[10pt]
+\dot{\phi} & = &  -2 \alpha(t) S_z + 2 \beta(t) S_z \cos^2 \phi - \dfrac{B S_z \cos \phi}{\sqrt{1 - S_z^2}}.
+\end{array}
+\end{equation}
+%
+We studied its dynamic numerically.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.7\linewidth]{pic/phase_potential_dissipation.eps}}
+\caption{\dots}
+\label{pic:phase}
+\end{figure}
+%
+Non-dissipative system hase two different regimes depend on different values of $B$: blue and red.
+Case blue ($\beta > \beta^*$) corresponds to the existence of barrier, and the red case ($\beta < \beta^*$) corresponds to the absence of the barrier.
+
+Linearization ($z \ll 1$, $\phi \ll 1$) of the system:
+%
+\begin{equation}
+\begin{array}{lcl}
+\dot{z} & = & (B - 2\beta(t)) \phi; \\
+\dot{\phi} & = & (2 \beta(t) - 2 \alpha(t) - B) z.
+\end{array}
+\end{equation}
+%
+Adiabaticity condition:
+%
+\begin{equation}
+\dfrac{1}{\omega^2(t)} \Big| \dfrac{d \omega}{d t} \Big| \ll 1.
+\end{equation}
+%
+It allows us to reduce linear system to the harmonic oscillator equaiton with slowly evolving frequency:
+%
+\begin{equation}
+\ddot{\phi} + \omega^2(t) \phi = 0,
+\end{equation}
+%
+$\omega(t) = (B - 2\beta(t))(B - 2 \beta(t) + 2 \alpha(t))$.
+We can approximate its solution as
+%
+\begin{equation}
+\phi(\tau) \approx A / \sqrt{\omega(\tau)} \cos (\omega(\tau) \tau),
+\end{equation}
+%
+where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$.
 

### 2017-02-14 phase_transition/preparing_paper.m

@@ -588,141 +588,3 @@ z_max = inv_cn(-2 * (1 - lambda) / Lambda, lambda);
 d1f = @(x) (Vb(x + eps) - Vb(x - eps)) / eps;
 d2f = @(x) (Vb(x + eps) - 2 * Vb(x) + Vb(x - eps)) / (eps^2);
 d3f = @(x) (Vb(x + 2 * eps) - 2 * Vb(x + eps) + 2 * Vb(x - eps) - Vb(x - 2 * eps)) / (2 * eps^2);
-
-%% Dynamic transition
-clc; clear
-
-omega_m = 0; u = 5;
-kapa = 0.002;
-
-df = @(t, f) [2*f(3); 2*omega_m*f(3) - u*exp(-2*kapa*t)*f(1)*f(3); -2*f(1) - 2*omega_m*f(2) + u*exp(-2*kapa*t)*f(1)*f(2)];
-
-f0 = [0.87; 0.493; 0];
-% f0 = [0.29 0.957 0];
-
-[T, F] = RK4(df, [0 100], f0, 2048);
-
-plot3(F(:, 1), F(:, 2), F(:, 3), 'green'); hold on;
-
-% S0 = sqrt((F(:, 1).^2) + (F(:, 2).^2) + (F(:, 3).^2));
-% plot(T, F(:, 1) ./ S0); hold on
-
-% omega_m = 0; u = 5;
-% df = @(t, f) [2*f(3); 2*omega_m*f(3) - u*f(1)*f(3); -2*f(1) - 2*omega_m*f(2) + u*f(1)*f(2)];
-% f0 = [0.29; 0.957; 0];
-% [T, F] = RK4(df, [0 20], f0, 2048);
-% plot3(F(:, 1), F(:, 2), F(:, 3), 'Color', 'red');
-
-%%
-clc; clear
-
-alpha = 1; beta = 0.9; B = 1;
-kappa = 0.002;
-
-a = @(t) alpha * exp(-2*kappa*t);
-b = @(t) beta * exp(-2*kappa*t);
-
-df = @(t, f) [2*b(t) * f(2) * f(3) - B*f(3);
-	-2*a(t) * f(1) * f(3);
-	2*(a(t) - b(t)) * f(1) * f(2) + B * f(1)];
-
-R = 1;
-S10 = 0; S20 = 0.62;
-S30 = sqrt(R^2 - S10^2 - S20^2); 
-f0 = [S10; S20; S30];
-
[…]

### 2017-02-14 phase_transition/preparing_paper_dissipation.m

@@ -1,0 +1,281 @@
+%% ?????????? ??? ??????? ??? exp(-2 * kappa * t)
+
+%% Libs
+addpath ../finding_stationary_modes/
+
+%% Phase in the presence of the dissipation
+clc; clear
+
+% Hamiltonian
+% H = \alpha S_z^2 + \beta S_x^2 - B S_x
+
+% System of equaiton
+% \dot{S}_z = 2 \beta S_x S_y - B S_y
+% \dot{S}_x = -2 \alpha S_z S_y
+% \dot{S}_y = 2 (\alpha - \beta)  S_z S_x + B S_z
+
+% Dissipation
+% \alpha \to \alpha \exp(-\kappa t)
+% \beta \to \beta \exp(-\kappa t)
+
+alpha = 1; beta = 0.9; B = 1; R = 1;
+lambda_1 = beta / alpha;
+Lambda_1 = B / (alpha * R); % s = R (?)
+
+alpha_dissip = @(t, alpha, kappa) alpha * exp(-kappa * t);
+beta_dissip  = @(t, beta, kappa) beta  * exp(-kappa * t);
+
+% S = [S_z; S_x; S_y]
+dS = @(t, S, alpha, beta, kappa) [
+	2 * beta_dissip(t, beta, kappa) * S(2) * S(3) - B * S(3);
+	-2 * alpha_dissip(t, alpha, kappa) * S(1) * S(3);
+	2 * (alpha_dissip(t, alpha, kappa) - beta_dissip(t, beta, kappa)) * S(1) * S(2) + B * S(1)
+];
+
+% S_x^2 + S_y^2 + S_z^2 = S_0^2 = R^2
+% Initial condition
+Sz0 = 0; Sx0 = 0.62;
+Sy0 = sqrt(R^2 - Sx0^2 - Sz0^2);
+
+% Phase
+% \phi = \tan^{-1} (S_y / S_x)
+
+% (I) Phase with dissipation
+% Parameter fo the dissipation
+kappa = 0.004;
+T_fin = 300;
+
+% RK parameters
+dS_kappa = @(t, S) dS(t, S, alpha, beta, kappa);
+tspan = [0 T_fin]; S0 = [Sz0; Sx0; Sy0]; N = 2^14;
+[T, S_dissip] = RK4(dS_kappa, tspan, S0, N);
+phase_dissip = atan(S_dissip(:, 3) ./ S_dissip(:, 2));
+
+figure; hold on
[…]

### 2017-02-20 writing/phase_transition/phase_transition.tex
After A.P. revision

--- 2017-02-09 writing/phase_transition/phase_transition.tex
@@
 \begin{abstract}
-Abstract will be placed here.
+We consider the quantum phase problem for low branch exciton polariton condensate Josephson junctions operating at finite temperatures and polariton lifetime.
+The process of quantum tunneling we characterized by thermon lifetime.
+We have shown that classical (thermal) activation and quantum tunneling for the phase  represent two regimes depending on polariton condensate parameters and distance between the junctions.
+The transition between this two regimes   exhibits universal features of first or second order phase transition depending on the potential shape for the relative phase.
+Notably, scale of the crytical temperature  characterized by polariton interaction strength only.
+We have shown that polariton condensate junction device runs in classical way for ten of Kelvins temperatures and typical polariton densities used in current experiments with narrow band semiconductor samples.
+Purely  quantum phase regime can be obtained even in the presence of dissipation at one or two order lower temperatures and relatively short operating time scales (few of picoseconds), and   opens kindly new possibilities for exciton polariton BEC applications in scalable quantum computing and quantum metrology.
 \end{abstract}
@@
 
-We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$, sketched in the Fig.
-\ref{pic:potential_sym_asym}; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
+We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
 % 
-\begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
-\caption{
-Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
-The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
-\label{pic:potential_sym_asym}
-}
-\end{figure}
+%\begin{figure}[ht]
+%\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
+%\caption{
+%Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
+%The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
+%\label{pic:potential_sym_asym}
+
+%\end{figure}
 %
@@
 \begin{equation}
-\hat{H} = \int \Big\{ -\dfrac{1}{2} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
+\hat{H} = \int \Big\{ -\dfrac{\hbar^2}{2m} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
 \label{eq:gpe_hamiltonian}
@@
 %
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric $\Phi_+$ and antisymmetric $\Phi_-$ real wavefunctions obeying stationary Gross-Pitaevskii equations, respectively
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$.
 %
-\begin{equation}
-\mu_{\pm} \Phi_{\pm} = -\dfrac{1}{2} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
-\label{eq:stationary}
-\end{equation}
+%\begin{equation}
+%\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
+%\label{eq:stationary}
+%\end{equation}
 %
@@
 %
-where we made some denotations
-%
-\begin{equation}
-\begin{array}{l}
-\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, \quad i,j \in \{+,-\}; \\
-A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-}); \quad \Gamma = \frac{1}{2} (\gamma_{++} - \gamma_{--}); \\
-C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-}); \quad G = \mu_- - \mu_+ - 2\Gamma.
-\end{array}
-\label{eq:subs}
-\end{equation}
+where we made some denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$;
+$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$; $\Gamma = \frac{1}{2} (\gamma_{++} - \gamma_{--})$; $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$; $G = \mu_- - \mu_+ - 2\Gamma$.
+
 Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double-well potential.
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.png}}
-\caption{Dependence of $\gamma_{ij} / g$ versus $x_0 / a$ \label{pic:gamma_pm_vs_g}}
+\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.eps}}
+\caption{Dependence of $\gamma_{ij} / g$ on $x_0 / a$ \label{pic:gamma_pm_vs_g}}
 \end{figure}
@@
 %
-where $s = \dfrac{N}{2} >> 1$ is large { C - number}, $\phi$ is the phase variable.
-The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations $[S_x, S_y] = iS_z, \quad[S_z, S_x] = iS_y, \quad[S_y, S_z] = iS_x$.
+where  $\phi$ is the phase variable.
+The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations $[S_i, S_j] = i\epsilon_{ijk}S_k,  i,j,k=x,y,z$.
 
@@
 where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
-Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig. \ref{pic:gamma_pm_vs_g}
-
-Schrodinger equation with Hamiltonian (\ref{eq:hamiltinian_s}) looks like  
+Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig.
+\ref{pic:gamma_pm_vs_g}.
+We also assume macroscopically large particle number, that is $s = \dfrac{N}{2} >> 1$ is C - number.
+Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain
 %
@@
 \begin{array}{l}
-(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta(s - \dfrac{1}{2})\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
-+ (E + BS \cos \phi + \beta S^2 \sin^2 \phi + \beta S \cos^2 \phi) = 0.
+(\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta s\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
++ s(B \cos \phi + \beta s \sin^2 \phi) = 0.
 \end{array}
@@
 where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{Anglin}.
-Noticing that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
+%ng that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
 %
-\begin{equation}
-\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
-\end{equation}
+%\begin{equation}
+%\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
+%\end{equation}
 %
-where
+%where
 %
-\begin{equation}
-\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
-\end{equation}
+%\begin{equation}
+%\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
+%\end{equation}
 %
-is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
+%is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
 It is possible to eliminate the term with first derivative in Eq. (\ref{eq:schrodinger}) applying the transformation
@@
 where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_phi}) we have introduced dimension-less vital parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ completely characterizing our model.
-
-Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to convenient Schr\"odinger equation
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role in our model.
+Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to Schr\"odinger-like equation
 % 
 \begin{equation}
-\frac{1}{2 m} \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
+\alpha \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
 \label{eq:schrodinger_usual}
@@
 %
-for quantum particle with ``mass'' $m = \dfrac{1}{2 \alpha}$, energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
+for quantum particle with the ``mass''  $m = \dfrac{\hbar^2}{2 \alpha}$ and energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
 %
@@
 
-The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:schrodinger_usual}), (\ref{eq:potential}) at $\lambda = 0$.
-The dependence of the $\lambda$ parameter on normalized half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:subs}), (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
-The limit $\lambda = 0$ obtained for infinitely large intra-well distances $x_0 \to \infty$.
+The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian}), (\ref{eq:potential}) at $\lambda = 0$.
+The dependence of the $\lambda$ parameter on normalized half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
+The limit $\lambda = 0$ corresponds to  infinitely large intra-well distances with $x_0 \to \infty$.
 On the other hand, parameter grows rapidly at $\dfrac{x_0}{a} \ll 1$.
@@
 
-Analysis of the quantum phase for exciton polariton junctions we examine in three domains of  governed parameter $\Lambda$, cf. \cite{Anglin}.
+Analysis of the quantum phase could be examined in three domains of vital parameter $\Lambda$, cf. \cite{Anglin}.
 The dependences of trapping potential $V_0(x)$ are shown in Fig. \ref{phase_potential}.
@@
 \begin{figure}[ht]
-\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=100.png} \\ a}
-\end{minipage}
-\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=05.png} \\ b}
-\end{minipage}
-\begin{minipage}[htbp]{0.32\linewidth}	{\includegraphics[width=1\linewidth]{pic/potential_L=001.png} \\ c}
-\end{minipage}
+\begin{center}\includegraphics[width=1\linewidth]{pic/potentials.eps}
+\end{center}
 \caption{
 Effective potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of  elliptic integral phase coordinate $z$.
-Points $z_{1,2}$ and $z_{3}$ in (b) corresponds to global and local minima of the potential, correspondingly,  occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
+Points $\pm z_{min}$ and $\pm z_{max}$ in (b) corresponds to global minima and maxima of the potential, correspondingly, occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
 \end{figure}
@@
 In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and cf. \cite{Anglin}.
-Below we are not interesting in this regime.
 
@@
 The behavior of the phase depends on the ratio between parameters $\Lambda$ and $\lambda$.
-If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses minima at $z = 0$ and $V(0) = -\Lambda$.
-Frequency of small amplitude ($z \ll 1$) oscillations can be obtained from (\ref{eq:potential}) and looks like { \red $\omega_{0, quantum} = 2 \alpha s \sqrt{\frac{1}{4} \Lambda^2 - \frac{\Lambda}{2} (2\lambda - 1) - \lambda(1 - \lambda)}$ }.
+If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses only one minima at $z = 0$ and $V(0) = -\Lambda$. 
+%Frequency of small amplitude ($z \ll 1$) oscillations %can be obtained from (\ref{eq:potential}) and looks like { \red $\omega_{0, quantum} = \frac{2 \alpha s}{\hbar} \sqrt{\frac{1}{4} \Lambda^2 - \frac{\Lambda}{2} (2\lambda - 1) - \lambda(1 - \lambda)}$ }.
 
-In the other limit, for $\Lambda < 2 \lambda$, quantum particle is trapped at two minima of $V_0(z)$ $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
+In the other limit, for $\Lambda < 2 \lambda$, quantum particle is trapped at two minima of $V_0(z)$ that correspond to $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
 Fig.
@@
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$ that is marked by red point $C$ in Fig.3b.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$ that is marked by red point $C$ in Fig. 3b.
 
 \textit{Fock regime} $\Lambda \ll 1/N^2$.
-In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with limiting value of the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
-In this regime we distinguish two limits.
-First, we suppose that inequality $\Lambda \ll \lambda < 1$ is holds.
-In this case small enough $\lambda$ from (\ref{eq:potential}) one can obtain
+In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms into Mathieu equation that implies spectrum consisting from all Mathieu functions.
+% $ce_0(z, q)$, $ce_1(z, q)$, $se_1(z, q)$, \dots, which are $2\pi$-periodic, and corresponding eigenvalues $a$ can be found using series expansions in powers of $q$.
+%from (\ref{eq:potential}) one can obtain
 %
-{\red
+%{\red
 
 %
-\begin{equation}
-V_F(z) \simeq -\lambda (1 - \lambda) \sin^2{z},
-\end{equation}
+%\begin{equation}
+%V_F(z) \simeq -\lambda (1 - \lambda) \sin^2{z},
+%\end{equation}
 %
-and our Schrodinger equation transforms to the so-called Mathieu equation
+%and our 
+%transforms into Mathieu equation;
 %
-\begin{equation}
-\frac{d^2 \Psi}{d z^2} + (a - 2q  \cos{2z}) \Psi = 0.
-\end{equation}
+%\begin{equation}
+%\frac{d^2 \Psi}{d z^2} + (a - 2q  \cos{2z}) \Psi = 0.
+%\end{equation}
 %
-where $a = E / \alpha + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
-We recall our boundary condition: $\Psi(z + 2\pi) = \Psi(z)$.
-So, spectrum consist of all Mathieu functions $ce_0(z, q)$, $ce_1(z, q)$, $se_1(z, q)$, \dots, which are $2\pi$-periodic, and corresponding eigenvalues $a$ can be found using series expansions in powers of $q$ (see Abramowitz and Stegun).
-}
+%where $a = E / \alpha + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
+%We recall our boundary condition: $\Psi(z + 2\pi) = \Psi(z)$.
 
-Another limit that could be studied within Fock regime is relevant to condition $\lambda \ll \Lambda$. In this case from (\ref{eq:potential}) we have $V_0(z) \simeq -\Lambda \cos{z}$.
-In fact, this limit that deals with negligible $\lambda$ reproduces results for convenient quantum phase model \cite{Anglin}.
+%In another limit $\lambda \ll \Lambda$ 
+%that might  be studied within Fock regime is relevant to condition . In this case from (\ref{eq:potential}) 
+%we have $V_0(z) \simeq -\Lambda \cos{z}$.
+%In fact, this limit that deals with negligible $\lambda$ reproduces results for convenient quantum phase model \cite{Anglin}.
 
@@
 However, in current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures.
-In this section we find answer to vital question: when quantum approach to the phase problem for Josephson junction utilizing weakly coupled exciton polariton condensate channels is valid?
+In this section we find answer to vital question: when quantum approach to the phase problem for Josephson junction with coupled exciton polariton condensates is valid?
 
-To give an answer to this question we consider the effective $W$ -- like potential represented in Fig. \ref{phase_potential}b,c inherent to the Josephson, or Fock regimes, respectively.
-To be more specific we examine here thermodynamically equilibrium system at finite temperature $T$.
-Transition between to stable states (say, between points $z_{1,2}$ in Fig.\ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
+To give an answer to this question we consider the effective $W$ -- like potential represented in Fig. \ref{phase_potential}b,c inherent to  Josephson (or, Fock) regimes, respectively.
+To be more specific we examine thermodynamically equilibrium system at finite temperature $T$.
+Transition between two stable states (say, between points $z_{1,2}$ in Fig.
+\ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
 Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is height of the barrier between two states with minimum of potential energy) the particle undergoes hopping over the barrier governed by familiar thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$, cf.
 \cite{Larkin}.
-On the other hand, in the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with the rate $\Gamma \sim e^{-B}$, where $B$ is the instanton action.
-As it is discussed previously transition (crossover) between this two limits exhibits universal features of first or second order phase transitions which can be interpreted as phase transition between classical and quantum regimes, \cite{Chudnovsky_1997, Larkin, Owerre}.
-Now we elucidate conditions for their realization for exciton polariton Josephson junction problem.
+On the other hand, in the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with vanishing rate.
+%with the rate $\Gamma \sim e^{-B/\hbar}$, where $B$ is the instanton action.
+%Now we elucidate conditions for their realization for exciton polariton Josephson junction problem.
 
-Our description is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
-The imaginary-time action obtained within WKB method approaches as
+Our description for exciton polariton Josephson junction problem is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
+The imaginary-time action obtained within WKB method approaches as $S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau$.
 %
-\begin{equation}
-S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau.
-\label{eq:thermon_action_1}
-\end{equation}
+%\begin{equation}
+%S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau.
+%\label{eq:thermon_action_1}
+%\end{equation}
 %
-The decay rate $\Gamma \sim e^{-S_{min}}$ according our approach can be expressed through the minimal value $S_{min}$ of the action.
-The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion for the thermon oscillating inside the inverted potential $-V(z)$, that is 
+The decay rate $\Gamma \sim e^{-S_{min}/\hbar}$ according our approach can be expressed through the minimal value $S_{min}$ of the action.
+The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion $m \ddot{z} = \frac{d V}{dz}$ written for the thermon that  oscillates inside the inverted potential $-V(z)$.
 %
-\begin{equation}
-m \ddot{z} = \frac{d V}{dz}.
-\label{eq:thermon}
-\end{equation}
+%\begin{equation}
+%m \ddot{z} = \frac{d V}{dz}.
+%\label{eq:thermon}
+%\end{equation}
 %
-Periodic solutions for of Eq. (18) satisfy the relation
+Periodic solutions of this equation satisfy the relation
 %
@@
 \begin{equation}
-\tau_p(E) = \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \sqrt{V(z) - E} ~dz.
+\tau_p(E) = \sqrt{2 m} \int_{z_1(E)}^{z_2(E)} \frac{dz}{\sqrt{V(z) - E}}.
 \label{eq:thermon_period}
@@
 The Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at energy $E = 0$ and temperature $T = 0$ characterize instanton solution.
-The Eq. (\ref{eq:thermon_action_1}) with (\ref{eq:total_energy}) for thermon action can be rewritten in a form 
+Combining  equation for $S(E)$ 
+%(\ref{eq:thermon_action_1}) 
+with (\ref{eq:total_energy}) we obtain  
 %
@@
 
-To determine thermodynamic properties of the system it is necessary to know small amplitude oscillations behavior of the particle at the bottom, $z=0$, of inverted potential $-V(z)$.
-The action in this case reads, {\red cf. \dots}:
+To determine thermodynamic properties of the system it is necessary to know small amplitude oscillations  at the bottom, $z=0$, of inverted potential $-V(z)$.
+The action in this case reads: 
 %
@@
 %
-In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the first order phase transition occurs.
-If $-V(z)$ behaves as $z^2 + z^4$ second order phase transition take place.
-Phase boundary between 1st and 2nd order phase transition is determined by the relation
+In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the second order phase transition occurs.
+If $-V(z)$ behaves as $z^2 + z^4$ first order phase transition take place.
+Phase boundary between 1st and 2nd order phase transitions is determined by the relation
 %
@@
 %
-We summarize our results in the Fig.\ref{pic:phase_boundary_combined}. 
+We summarize our results in the Fig. \ref{pic:phase_boundary_combined}.  First order phase transition occurs in the shaded region for two type of potentials only. 
 %
@@
 \begin{equation}
-T_{c}^{(2)} = (\hbar \alpha s / \pi k_B) \sqrt{\lambda (1 - \lambda) + (2 \lambda - 1) \tfrac{\Lambda}{2} - \tfrac{1}{4} \Lambda^2},
+T_{c}^{(2)} = T_{0} \sqrt{\lambda (1 - \lambda) + (2 \lambda - 1) \tfrac{\Lambda}{2} - \tfrac{1}{4} \Lambda^2},
 \label{eq:second_order}
@@
 %
-where $\omega_0 = 2 \alpha s \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon near the bottom of inverted potential.
+where  $\omega_0 = \frac{2 \alpha s}{\hbar} \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon near the bottom of inverted potential, $T_{0}=\alpha N / 2\pi k_B$ is critical temperature $T_{c}^{(2)}=T_{0}$ taken at $\Lambda=2\lambda-1$.
+The characteristic temperature $T_{0}$ discussed above implies important time scale $\tau_0=2\pi\hbar/ \alpha N$ that can be understood as thermon ``lifetime''.
 From (\ref{eq:second_order}) follows that, for $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.
+
 %
@@
 \end{minipage}
-\caption{Dependences of minimal action $S_{min}$ (ABC-curve) as a function of dimensionless temperature $ T= \hbar / k_B \tau_p$ for (a) 1st-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 2nd-order transition, $\lambda = 0.5$, $\Lambda = 0.5$; parameters: $\hbar = 1$, $k_B = 1$, $\alpha = 1$, $s = 1$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
+\caption{Dependences of  minimal action $S_{min}$ (ABC-curve) taken in $s\hbar$ units as a function of reduced temperature $ T/T_{0}$ for (a) 2nd-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 1st-order transition, $\lambda = 0.5$, $\Lambda = 0.5$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
+The inset shows dependences of  dimensionless $\tau_p / \tau_0$ versus energy $E$ given in  $\alpha s^2$ units.
 \label{pic:action_period}}
@@
 
-Fig. \ref{pic:action_period}a displays second-order phase transition from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
-The crossover occurs at the critical point $T_{c}^{(2)}$ where $S_T = S_0$ and {\red $E = E_0 = \dots$}.
+The Fig. \ref{pic:action_period}a displays second-order phase transition from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
+The crossover occurs at the critical point $T_{c}^{(2)}$ where $S_T = S_0$ and {$E = E_0$}.
 The inset demonstrate monotonic dependence of thermon period $\tau_p$ on energy $E$ that is inherent to second-order phase transition.
@@
 
-Analytically critical temperature $T_{c}^{(1)}$ one possible to approach as $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
+Analytically critical temperature $T_{c}^{(1)}$ meight be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
 After some straightforward calculations for $B$ we obtain
@@
 \begin{array}{c}
-B = S(E_{min}) = 2 s \left[ \log \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right].
+B = S(E_{min}) = 2 s \hbar \left[ \ln \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right].
 \end{array}
@@
 
-In current experiments it is much more easier to manipulate be the density of exciton polaritons instead of their temperature that is even difficult to identify due the some the non-equilibrium processes occurring in real microcavity samples, see e.g.
+In current experiments it is much more easier to manipulate be the density of exciton polaritons instead of their temperature due to some  non-equilibrium processes occurring in real microcavity samples, see e.g.
 \cite{Sanvitto,Guillet}.
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_temperatures.eps}}
-\caption{\dots}
-\label{pic:temperatures}
+\caption
+{Dependence of dimensionless critical temperature $T_{c}/T_{0}$ as a function of parameter $\Lambda$. Solid (green) line corresponds to analytical solution for  $T_{c}^{(1)}$.     
+\label{pic:temperatures}}
 \end{figure}
@@
 
-Another type of barrier --- upper barrier.
-Exist when $\Lambda > 2(1 - \lambda)$.
+Now let us briefly discuss decay of the upper state that is relevant to the point C in ..... and exist for $\Lambda > 2(1 - \lambda)$.
 Potential presumes local minima at $\pm 2K(\lambda)$ and local maxima at $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
-Equation for the thermon yeilds small ocsilation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \alpha s \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
-The crossover temperature of second-order phase transition
+Equation for the thermon yields 
+%small ocsillation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \frac{\alpha s}{\hbar} \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
+crossover temperature of second-order phase transition $T_{c}^{(2)} = (T_{0}/ 2) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$, cf.... 
+%
+%\begin{equation}
+%T_{c}^{(2)} = (T_{0}/ 2) %\sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}.
+%\label{eq:second_order_2}
+%\end{equation}
+%
+By expanding the potential $V(z)$ near the vicinity of $z_{max}$ it is possible to show that only second-order phase transition appear for this case.
+
+%With the aim of analytical determining of the phase transition order let's write the Taylor series for $V(z)$ near the vicinity of $z_{max}$.
+%Expansion of the potential $V(z)$ excluding constant value $V(z_{max})$ gives:
+%
+%\begin{equation}
+%V(\tilde{z}) = \alpha s^2 \Big[ -\tfrac{1}{4} \left( \tfrac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda) \right) \tilde{z}^2 
+%+ \tfrac{1}{2} \tfrac{\Lambda \sqrt{\Lambda^2 - 4(1 - \lambda)^2}}{\sqrt{1 - \lambda} \sqrt{\Lambda^2 + 4 \lambda (1 - \lambda}} \tilde{z}^3 + o(\tilde{z}^4) \Big],
+%\label{eq:potential_teylor_2}
+%\end{equation}
+%
+%where $\tilde{z} = z - z_{max}$.
+%It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
+% We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs. \ref{pic:action_period_temperature_2}, and summarize our results on the Fig. \ref{pic:phase_boundary_combined}.
+%
+%\begin{figure}[ht]
+%\begin{minipage}[h]{0.49\linewidth}
+%\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition_b2.eps} \\ (a)}
+%\end{minipage}
+%\hfill
+%\begin{minipage}[h]{0.49\linewidth}
+%\center{\includegraphics[width=\linewidth]{pic/phase_transition_temperatures_b2.eps} \\ (b)}
+%\end{minipage}
+%\caption{\dots \label{pic:action_period_temperature_2}}
+%\end{figure}
+%
+\section{Phase transitions in the presence of dissipation 
+\label{sec:non-equilibrium}}
+
+The obtained above results for phase transitions are valid in true thermodynamically equilibrium limit.
+Notably  exciton polariton condensates in current experiments are out of   thermal  equilibrium, cf.
+[   ].
+It is obvious that for quantum tunneling effects observation  characteristic time scale $\tau_0$ should be shorter than time scales which relay to non-equilibrium processes.
+More precisely, in this case we require fulfillment of  inequality
+
+\begin{equation}
+ \tau_{0}\ll\tau_{pol},
+ \label{eq:lifetime}  
+\end{equation}
+where $\tau_{pol}$ characterizes  exciton polariton lifetime.
+However, in realistic (experimental) situation with exction polariton BEC it will be hard to obey to condition {\eqref{eq:lifetime}.
+In this case it is necessary to analyze dynamics of the system.
+ Below we consider the influence of the dissipation to the phase properties in adiabatic limit.
+
+We start from mean field  equations obtained from  (\ref{eq:hamiltonian}) for  $\Gamma = 0$,  which reads as 
 %
 \begin{equation}
-T_{c}^{(2)} = (\hbar \alpha s / 2 \pi k_B) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}.
-\label{eq:second_order_2}
+i \dot{\psi}_{1,2} = -i \kappa \psi_{1,2} +  \alpha |\psi_{1,2}|^2 \psi_{1,2} - (B/2 - \beta \psi_{1,2}^* \psi_{2,1}) \psi_{2,1}, 
+\label{eq:GP}
 \end{equation}
 %
-With the aim of analytical determining of the phase transition order let's write the Taylor series for $V(z)$ near the vicinity of $z_{max}$.
-Expansion of the potential $V(z)$ excluding constant value $V(z_{max})$ gives:
+where we also introduced dissipation rate term with $\kappa \simeq 1/\tau_{pol}$.
+By introducing new variables  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t)$ for mean field pseudo-spin  parameters (\ref{eq:pseudo_spin}) from ({\ref{eq:GP}}) we obtain
+%
+%\begin{equation}
+%\begin{array}{lcl}
+%i \Psi_{1, t} & = & \alpha(t) |\Psi_1|^2 \Psi_1 - (B/2 - \beta(t) \Psi_1^* \Psi_2) \Psi_2; \\
+%i \Psi_{2, t} & = & \alpha(t) |\Psi_2|^2 \Psi_2 - (B/2 - \beta(t) \Psi_2^* \Psi_1) \Psi_1.
+%\end{array}
+%\end{equation}
+%
+%Hamiltoninan in terms of Stocks operators (\ref{eq:pseudo_spin}):
+%
+%\begin{equation}
+%\hat{H} = \alpha(t) \hat{S}_z^2 + \beta(t) %\hat{S}_x^2 - B \hat{S}_x.
+%\end{equation}
+%
+%Equaitions on the mean-values of operators:
 % 
 \begin{equation}
-V(\tilde{z}) = \alpha s^2 \Big[ -\tfrac{1}{4} \left( \tfrac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda) \right) \tilde{z}^2 
-+ \tfrac{1}{2} \tfrac{\Lambda \sqrt{\Lambda^2 - 4(1 - \lambda)^2}}{\sqrt{1 - \lambda} \sqrt{\Lambda^2 + 4 \lambda (1 - \lambda}} \tilde{z}^3 + o(\tilde{z}^4) \Big],
-\label{eq:potential_teylor_2}
+\begin{array}{lcl}
+\dot{S}_z & = &  2 \beta(t) S_x S_y - B S_y; \\
+\dot{S}_x & = & -2 \alpha(t) S_z S_y; \\
+\dot{S}_y & = & 2(\alpha(t) - \beta(t)) S_z S_z + B S_z.
+\end{array}
+\label{eq:pseudo-spin}
 \end{equation}
 %
-where $\tilde{z} = z - z_{max}$.
-It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
-We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs. \ref{pic:action_period_temperature_2}, and summarize our results on the Fig. \ref{pic:phase_boundary_combined}.
+
+Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for  non-dissipative system but with time dependent parameters $\alpha(t) = \alpha \exp(-2 \kappa t)$, $\beta(t) = \beta \exp(-2 \kappa t)$, cf.
+....
+
+Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\beta^* = B / 2R$, where $R$ is  radius of the Bloch  sphere, i.e. $R^2=S_x^2 + S_y^2 + S_z^2$.
+%
+%\begin{equation}
+%\end{equation}
+%
+%where $R$ -- is a radius of the Poincare sphere.
+%Non-dissipative system has a bifurcation at the critical values of .
+
+In Fig.
+\ref{pic:phase} we represent phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of reduced time.
+Non-dissipative system has two different regimes depending on  $B$ -- parameter values; blue and red curves in the Fig.
+\ref{pic:phase}, respectively.
+Blue  curve characterizes by condition $\beta > \beta^*$ and  corresponds to the existence of barrier for potential energy (see inset to Fig.
+\ref{pic:phase}).
+Contrary,  red curve establishes phase properties below the threshold ($\beta < \beta^*$) that corresponds to the absence of the barrier.
+
+In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}) exciton polariton
+system starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value
+of $\beta^*$ due to decreasing of total number of particles. 
+%It can be transformed to the equation on the phase difference $\phi$ and $S_z$ as follows
+%
+%\begin{equation}
+%\begin{array}{lcl}
+%\dot{S}_z & = & B \sqrt{1 - S_z^2} \sin \phi - 2 \beta(t) (1 - S_z^2) \sin \phi \cos \phi; \\[10pt]
+%\dot{\phi} & = &  -2 \alpha(t) S_z + 2 %\beta(t) S_z \cos^2 \phi - \dfrac{B S_z \cos \phi}{\sqrt{1 - S_z^2}}.
+%\end{array}
+%\end{equation}
+%
+%We studied its dynamic numerically.
 %
 \begin{figure}[ht]
-\begin{minipage}[h]{0.49\linewidth}
-\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition_b2.eps} \\ (a)}
-\end{minipage}
-\hfill
-\begin{minipage}[h]{0.49\linewidth}
-\center{\includegraphics[width=\linewidth]{pic/phase_transition_temperatures_b2.eps} \\ (b)}
-\end{minipage}
-\caption{\dots \label{pic:action_period_temperature_2}}
+\center{\includegraphics[width=0.7\linewidth]{pic/phase_potential_dissipation.eps}}
+\caption{Normalized phase difference as a function of dimensionless time for {\red \dots}.
+For red, blue and black curves initial conditions are {\red \dots}, respectively. Inset demonstrates potential behavior for red and blue curves respectively.
+\label{pic:phase}}
 \end{figure}
 %
-\section{Phase transitions in the presence of non-equilibrium processes 
-\label{sec:phase_transition}}
+Adiabaticity condition reads, cf. {\red [ ]}:
+%
+\begin{equation}
+\dfrac{1}{\omega^2(t)} \Big| \dfrac{d \omega}{d t} \Big| \ll 1.
+\end{equation}
+%
+where $\omega(t) = \sqrt{(B - 2\beta(t))(B - 2 \beta(t) + 2 \alpha(t))}$ is small amplitude oscillations slowly depending on time.
 
-\dots
+%It allows us to reduce linear system to the harmonic oscillator equaiton with slowly evolving frequency:
+%
+%\begin{equation}
+%\ddot{\phi} + \omega^2(t) \phi = 0,
+%\end{equation}
+%
+The solution of the phase in this case can be given as 
+\begin{equation}
+\phi(\tau) \approx A / \sqrt{\omega(\tau)} \cos (\omega(\tau) \tau),
+\end{equation}
+%
+where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$.
+
+Physically, behavior of the system in the presence of dissipation showed in Fig.
+\ref{pic:phase} establishes non-equilibrium phase transition from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
 
@@
 
-Practically, Fock regime interesting for high precision measurements.
-In particular, the dispersion of the quantum phase in this case approaches to so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ which is the minimal accessible error for the phase measurement in respect of total particle number.
+Let us summarize the results obtained.
+In the paper we examine quantum phase properties for  Josephson junctions created from coupled exciton polariton condensates in the limit of finite temperatures and dissipation.
+We obtain  various shape of phase potentials depending on the $\Lambda$ and $\lambda$ parameters characterizing condensate junctions.
+The W-shape potential at finite temperature admits two regimes which are  purely quantum tunneling regime through the barrier or classical regime of thermal activation.
+Transition (crossover) between this two limits exhibits universal features of first or second order phase transitions which can be interpreted as phase transition between classical and quantum regimes.
+It is important that critical temperature of transition depends on some  characteristic temperature  parameter $T_{0}$ (see e.g.
+(\ref{eq:second_order})) that depends on polariton-polariton interaction (so-called blue shift) $\alpha N$.
+For experimentally observed values of polariton interaction strength, that implies,say,  $\alpha N=0.3meV$, taken for narrow-band semiconductor samples, the  $T_{0}$ is about $0.6K$ which is less than  typical temperature of condensation, or, temperature of Berezinsky-Kosterlitz-Thouless phase transition considered at thermal equilibrium,cf.
+{\red [ ]}.
+Hence, at large enough temperatures (few tens of Kelvins and more) which are relevant to current experiments with non-equilibrium  exciton polariton condensate junction device operates in classical way.
 
-Practically two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
+The influence of dissipation effects to this picture is evident from our analysis.
+The thermon lifetime for given  estimations is about $7ps$ that comparable with polariotn lifetime $\tau_{pol}$ in the cavity, cf.
+{\eqref{eq:lifetime} and [ ].
+Thus, the observation of quantum tunneling become possible only within short time intervals when the dissipation cannot essentially affected to the system.
+Otherwise, after some time interval dissipation leads to crossover in the phase dynamics  and breaking  the evolution of quantum phase in W--potential, see \ref{pic:phase}).
+
+At the temperatures (or relevant polariton gas densities) sufficiently below the temperature $T_{0}$ of phase transition the exciton polariton condensate junctions are capable for various applications where quantum tunneling effect is crucial.
+First, it is quantum annealing with exciton polariton condensates that can be enhanced with the help of bosonic stimulation phenomena {\red [ ]}.
+
+Second, quantum tunneling effect can be explored for design exciton polariton phase qubits, cf.
+{\red [ ]}.
+In order, two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
 \ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.
@@
 However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
-Another interesting phenomena that can be obtained with potential in Fig. \ref{phase_potential}b is connected with some analogies in cosmology and quantum field theory.
-In particular, in our recent work {\red [ ]} we discuss Higgs field generation by using exciton polaritons in semiconductor Bragg mirror structures as an on table analog of known cosmological phenomenon, {\red cf.
-[ ]}.
-In this paper we continue our physical analogies with false vacuum decay (marked by the point $C$ in Fig. \ref{phase_potential}b) that can be established here, {\red cf. [ ]}.
 
-\pagebreak
+Third, the quantum regime of exciton polariton junctions can be useful for creation of  interferometers with exciton polariton condensates(see e.g.
+[   ]) for quantum metrology purposes, {\red [ ]}.
+In particular, we speak here about measurement of the phase shift with high precision accuracy.
+It is possible to show that for the Fock regime described by us in the paper the dispersion of the quantum phase approaches to so-callrd Heisenberg limit  ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is
+minimal accessible error for the phase measurement in respect of total particle number.
 

### 2017-02-20 phase_transition/preparing_paper.m

@@ -74,6 +74,46 @@ set(h_axis(1), 'XLabel', 'x');
 
 % Then click Edit -> Current object properties -> Undock -> Compress
 
+%% gamma_{+-} with variational approximation
+clc; clear
+
+% Variational anzatz
+phi_p = @(x, x0, a) (exp(-((x - x0) .^ 2) / (2 * a^2)) ...
+    +exp(-((x + x0) .^ 2) / (2 * a^2)));
+
+phi_m = @(x, x0, a) (exp(-((x - x0) .^ 2) / (2 * a^2)) ...
+    -exp(-((x + x0) .^ 2) / (2 * a^2)));
+
+get_int = @(f) integral(f, -40, 40, 'RelTol', 1e-10, 'AbsTol', 1e-6);
+
+h = 1;
+U = @(x, x0) h * ((x / x0) .^ 2 - 1) .^ 2;
+
+a = 3;
+x0 = 0:0.1:10;
+
+gamma_pp = zeros(1, length(a));
+gamma_pm = gamma_pp; gamma_mm = gamma_pp;
+
+for i = 1:length(x0)
+    phi_p_norm = sqrt( get_int(@(x) phi_p(x, x0(i), a) .^ 2) );
+    phi_m_norm = sqrt( get_int(@(x) phi_m(x, x0(i), a) .^ 2) );
+    
+    fp = @(x) (1 / phi_p_norm) * phi_p(x, x0(i), a); % phi_p_normalized
+    fm = @(x) (1 / phi_m_norm) * phi_m(x, x0(i), a); % phi_m_normalized
+    
+    gamma_pp(i) = get_int(@(x) (fp(x) .^ 4) );
+    gamma_pm(i) = get_int(@(x) (fp(x) .^ 2) .* (fm(x) .^ 2));
+    gamma_mm(i) = get_int(@(x) (fm(x) .^ 4) );
+end
+
+figure('Position', [100 100 325 225]); hold on
+x = x0 / a;
+plot(x, gamma_pp, x, gamma_pm, x, gamma_mm);
+xlabel('x_0 / a')
+ylabel('\gamma_{ij} / g')
+legend('\gamma_{++}', '\gamma{+-}', '\gamma_{--}')
+
 %% Phase potential in elliptic coordinate with two parameters: \lambda, \Lambda
 clc; clear
 
@@ -129,15 +169,15 @@ ylabel('V_0(z)');
 
 %% Josephson regime
 
-% Lambda = 0.5;
+Lambda = 0.5;
[…]

### 2017-02-27 writing/phase_transition/phase_transition.tex
pre-final version

@@
 \author{M. E. Lebedev}
-\email{m.lebedev@lmc.ifmo.ru}
 \affiliation{ITMO University, St. Petersburg 197101, Russia}
@@
 \author{D. A. Dolinina}
-\email{dasha.doly@gmail.com}
 \affiliation{ITMO University, St. Petersburg 197101, Russia}
+
+\author{S. M. Arakelian}
+\affiliation{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}
+
+\author{Tien-Chang Lu}
+\affiliation{Department of Photonics, National Chiao Tung University, Hsinchu 300, Taiwan}
+
+\author{A. V. Kavokin}
+\affiliation{Spin Optics Laboratory, St. Petersburg State University, Ul’anovskaya, Peterhof, St. Petersburg 198504, Russia}
+\affiliation{School of Physics and Astronomy, University of Southampton, SO17 1BJ Southampton, United Kingdom}
 
@@
 \affiliation{ITMO University, St. Petersburg 197101, Russia}
+\affiliation{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}
 
@@
 \begin{abstract}
-We consider the quantum phase problem for low branch exciton polariton condensate Josephson junctions operating at finite temperatures and polariton lifetime.
-The process of quantum tunneling we characterized by thermon lifetime.
-We have shown that classical (thermal) activation and quantum tunneling for the phase  represent two regimes depending on polariton condensate parameters and distance between the junctions.
-The transition between this two regimes   exhibits universal features of first or second order phase transition depending on the potential shape for the relative phase.
-Notably, scale of the crytical temperature  characterized by polariton interaction strength only.
-We have shown that polariton condensate junction device runs in classical way for ten of Kelvins temperatures and typical polariton densities used in current experiments with narrow band semiconductor samples.
-Purely  quantum phase regime can be obtained even in the presence of dissipation at one or two order lower temperatures and relatively short operating time scales (few of picoseconds), and   opens kindly new possibilities for exciton polariton BEC applications in scalable quantum computing and quantum metrology.
+We consider the problem of achievement of quantum regime for  relative phase of trapped in W -- potential low branch exciton polariton condensates taken at finite temperatures and finite polariton lifetime.
+Non-standard Bose-Hubbard model of  exciton polariton Josephson junction (EPJJ) that produces complex potential energy landscape (PEL) consisting from set of barriers and wells for the phase is proposed.
+We have shown that classical (thermal) activation and quantum tunneling for the phase  represent two regimes depending on temperature, polariton condensate density and distance between the junctions.
+The transition between this two regimes   exhibits universal features of first or second order phase transition (PT) depending on the PEL for relative phase.
+In the presence of dissipation quantum system exhibits non-equilibrium PT from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
+The obtained results are discussed in details in the framework of quantum annealing problem with exciton polariton condensates.
+
 \end{abstract}
@@
 
-For last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent one of mainstreams of current photonic and semiconductor technologies, see e.g.
+For last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent important mainstream of current photonic and semiconductor technologies, see e.g.
 \cite{Sanvitto,Guillet}.
@@
 Practically, semiconductor microcavities are promising for various optoelectronic applications where quantum  matter-field interface plays crucial role.
-In particular, demonstrations of polariton laser with electrical pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
-Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
+In particular, it is worth to mention demonstrations of polariton laser with electrical pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
+Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition (PT) condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
+Non-equilibrium features of exciton polariton condensates play important role in various manifestations of their collective (many body) states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
 
-Non-equilibrium, or, thermodynamically quasi-equilibrium features of exciton polariton condensates play certain role in various manifestations of their collective (many body) quantum states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
-Since exciton polariton BEC's in present experiments examined at high enough (up to the room) temperatures the quantum character of such a states should be examined even at equilibrium.
+Recently Yongbao Sun et al,  in Ref.
+\cite{Snoke_2017} reports observation of quasi-equilibrium low branch exciton polariton condensate in high Q-factor microcavity possessing very high photon lifetime, that is $135ps$.
+Notably, exciton polaritons with long lifetime are promising candidates for current quantum technologies, cf.
+\cite{Demirchyan}.
+However, since exciton polariton BEC's in present experiments are observed at high enough (up to the room) temperatures the quantum abilities of such a states should be examined even at full thermal equilibrium.
 
-The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical purposes, see e.g.
-\cite{Dominici}; especially for their possible applications for quantum information science purposes.
+The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical purposes and especially for their possible applications in quantum information science, see e.g.
+\cite{Dominici}.
 Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom made microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives, see, e.g.
 \cite{Demirchyan,Pagel,Kyriienko,Solnyshkov_2015, Dominici}.
-Especially it is important to stress quantum annealing problem \cite{Yan} that is very actual now and where collective (bosonic) character of polariton BEC could be used.
-In particular, as it is shown recently in \cite{Lewenstein} global minimum of energy landscape can be reached at finite temperatures via a combination of thermal annealing and quantum tunneling.
 
-Another promising area of potential applications of quantum exciton polariton states is connected with quantum metrology purposes for which designing of quantum interferometers and gyroscopes possessing high precision measurements with quantum phase states is utilized, cf.
-\cite{Pezze, Gulevich}.
+Especially it is important to stress here quantum annealing problem physically based on searching algorithm for the global minimum of a potential energy landscape (PEL) consisting from set of barriers and wells, see e.g.
+\cite{Santoro, Das}.
+In purely classical  (thermal) regime physical system overcomes arbitrary barrier at finite temperature with the help of thermal activation process if the thermal energy is enough.
+Contrary, in quantum limit the same system undergoes quantum tunneling through the barrier.
+Obviously, the shape of the barrier plays essential role in this case, cf.
+\cite{Das, Lewenstein}.
+In order, as it is shown recently  in \cite{Lewenstein} annealing algorithm implies in general case combination of thermal annealing and quantum tunneling.
+The
+collective (bosonic) character of polariton condensation could be used in this case to acceleration of search physical algorithm \cite{Yan}.
 
-In the paper we consider generic problem  of quantum-classical phase transition (see e.g.\cite{Chudnovsky_1997}) with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect, cf.
-\cite{Aleiner, Shelykh_2008, Borgh_2010}.
-In general this problem relates to dissipative tunneling problem or, tunneling at finite (non-zero) temperatures models, cf. \cite{Caldeira, Larkin, Riseborough}.
-Traditionally  seminal studies on this topic are based on consideration of superconductor devices \cite{Ankerhold} where macroscopic tunneling plays essential role.
-In particular, it is worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates for quantum computing with superconductor qubits where macroscopic quantum coherent phase properties are used \cite{Makhlin}.
-Latterly the problem of quantum tunneling and quantum-classical phase transition problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
+In the paper we consider generic problem  of quantum-classical phase transition (PT) with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect, cf.
+\cite{Chudnovsky_1997,Aleiner, Shelykh_2008, Borgh_2010}.
+To be more specific we examine simply two junction model.
+
+In general this problem relates to dissipative tunneling problem or, tunneling at finite (non-zero) temperatures, cf. \cite{Caldeira, Larkin, Riseborough}.
+Traditionally,  studies in this field are limited by consideration of superconductor devices \cite{Ankerhold} where macroscopic quantum tunneling phenomena plays essential role.
+In particular, it is worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates with superconductor qubits for quantum computing where macroscopic quantum coherence for the phase is important \cite{Makhlin}.
+Recently the problem of quantum tunneling and quantum-classical PT problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
 Strictly speaking main discussion is focused on investigation of quantum-classical escape rate transition that takes place in the presence of potential barrier at finite temperatures.
 
-In the paper we propose \textit{extended model} for exciton polariton Josephson junctions that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter, cf.
+In the paper we propose \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter matrix elements, cf.
 \cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
 In particularly, we pay our attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
-We aimed at elucidation of necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for creation of exciton polariton qubit gates.
+We aimed at elucidation of necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for quantum annealing purposes and creation of exciton polariton qubit gates.
 
 This paper is arranged as follows.
-In Sec. \ref{sec:model} we explain in details our model to realize Josephson junction with exciton polariton condensates.
-The extended tight-binding model will be established in this case.
-In Sec. \ref{sec:quantum_phase} we {\red \dots }.
-In the conclusion, we summarize the results obtained.
+In Sec. \ref{sec:model} we explain in details  extended model of EPJJ under the tight-binding approach. 
+In Sec.
+\ref{sec:quantum_phase} we give description of quantum phase for our model and discuss various regimes for it.
+Section \ref{sec:quantum_classical} establishes main results obtained in the paper.
+In order, we consider quantum-classical PT problem for various PEL's for quantum phase in the framework of our model at finite temperatures.
+The influence of non-equilibrium effects with microcavity exciton polaritons possessing finite lifetime is discussed in \ref{sec:non-equilibrium}.
+In Conclusion we summarize the results obtained.
 
-\section{THE MODEL OD EXCITON POLARITON JOSEPHSON JUNCTION \label{sec:model}}
+\section{THE MODEL OF EPJJ \label{sec:model}}
 
-We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines distance between potential minima, $h$ depth of the potential.
+We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines distance between potential minima, $h$ is depth of the potential.
 % 
@@
 %\label{pic:potential_sym_asym}
-
 %\end{figure}
 %
-The Hamiltonian for the system of weakly interacting exciton polaritons in an external $U(x)$ can be written in the second quantized form as:
+The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the second quantized form as:
 %
 \begin{equation}
-\hat{H} = \int \Big\{ -\dfrac{\hbar^2}{2m} \hat{\psi}^\dag \dfrac{d^2 \hat{\psi}}{dx^2} + \hat{\psi}^\dag \hat{\psi} U(x) + \dfrac{g}{2} \hat{\psi}^{\dag 2} \hat{\psi}^2  \Big\} dx,
+\hat{H} = \int \hat{\psi}^\dag\Big\{ -\dfrac{\hbar^2}{2m_{pol}}  \dfrac{d^2 }{dx^2} + U(x) + \dfrac{g}{2} \hat{\psi}^{\dag} \hat{\psi}  \Big\}\hat{\psi} dx,
 \label{eq:gpe_hamiltonian}
@@
 %
-where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ is two-body (polariton-polariton) scattering length.
+where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ describes two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
 In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator supposing
@@
 where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
-It's instructive to recast $\Phi_{1,2}(x)$ as
+It's instructive to represent  $\Phi_{1,2}(x)$ as
 %
@@
 %
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$.
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii (GP) equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
 %
@@
 %
-and normalization condition $\int \Phi_{\pm}^2 dx = 1$.
-Here $\mu_{\pm}$ are chemical potentials.
-As a result an operator $\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2} = N$ characterizes total number of particles (here and thereafter we omit ``hat'' design for simplicity).
+and normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is chemical potential.
+As a result an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes total number of particles.
 Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
@@
 %
-where we made some denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$;
-$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$; $\Gamma = \frac{1}{2} (\gamma_{++} - \gamma_{--})$; $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$; $G = \mu_- - \mu_+ - 2\Gamma$.
+where we made denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
+$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.
 
-Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton BEC trapped in double-well potential.
+Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton condensates trapped in double-well potential.
 The ``additional'' terms with $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize density induced and pair tunneling, respectively.
@@
 \begin{equation}
-\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]
+\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big],
 \label{eq:two_modes_eq}
@@
 where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
-In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of intra-well distance $x_0$ is shown.
-It is important that at differences between them rapidly vanishes with increasing of distance $x_0$.
+In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of inter-well distance $x_0$ is shown.
+It is important that differences between various $\gamma_{ij}$ rapidly vanish with increasing the inter-well distance $2x_0$.
 We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.eps}}
-\caption{Dependence of $\gamma_{ij} / g$ on $x_0 / a$ \label{pic:gamma_pm_vs_g}}
+\caption{Dependences of normalized matrix elements $\gamma_{ij} / g$ on $x_0 / a$. \label{pic:gamma_pm_vs_g}}
 \end{figure}
@@
 \quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
-\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
+\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 - \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
 \end{align}
@@
 \end{subequations}
-%
 where  $\phi$ is the phase variable.
 The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations $[S_i, S_j] = i\epsilon_{ijk}S_k,  i,j,k=x,y,z$.
-
 After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
@@
 \ref{pic:gamma_pm_vs_g}.
-We also assume macroscopically large particle number, that is $s = \dfrac{N}{2} >> 1$ is C - number.
+We also assume macroscopically large particle number, i.e.
+the $s = N/2 >> 1$ is C - number.
 Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain
@@
 (\alpha - \beta \sin^2 \phi) \dfrac{d^2 \Phi}{d \phi^2} + (\beta s\sin{2\phi}-B\sin{\phi})) \dfrac{d \Phi}{d \phi} \\
-+ s(B \cos \phi + \beta s \sin^2 \phi) = 0.
++ (E + B s \cos \phi + \beta s^2 \sin^2 \phi) \Phi = 0,
 \end{array}
@@
 \begin{equation}
-\Phi(\phi) = \Psi(z) \exp \Big( s \ln \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big)
+\Phi(\phi) = \Psi(z) \exp \Big( s \ln \dn{z} - \dfrac{\Lambda s}{2 \sqrt{\lambda (1 - \lambda)}} \arctan \Big( \sqrt{\dfrac{\lambda}{1 - \lambda}} \cn{z} \Big) \Big),
 \label{eq:transformation_of_phi}
@@
 where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role in our model.
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role for our model.
 Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to Schr\"odinger-like equation
@@
 %
-for quantum particle with the ``mass''  $m = \dfrac{\hbar^2}{2 \alpha}$ and energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
+characterizing quantum particle with the ``mass''  $m = \dfrac{\hbar^2}{2 \alpha}$ and energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
 %
 \begin{equation}
-V_0(z) = \frac{ (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) \sn^2{z} - \Lambda \cn{z}}{\dn^2{z}}
+V_0(z) = \frac{ (\frac{1}{4} \Lambda^2 - \lambda (1 - \lambda)) \sn^2{z} - \Lambda \cn{z}}{\dn^2{z}}.
 \label{eq:potential}
@@
 
-The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian}), (\ref{eq:potential}) at $\lambda = 0$.
-The dependence of the $\lambda$ parameter on normalized half of intra-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
-The limit $\lambda = 0$ corresponds to  infinitely large intra-well distances with $x_0 \to \infty$.
-On the other hand, parameter grows rapidly at $\dfrac{x_0}{a} \ll 1$.
-Obviously, in this limit our Josephson junction model inherent based on relatively weak coupling between wells breaks down.
-Below we examine case of $0 < \lambda < 1$ that could be obtained at moderate values $\dfrac{x_0}{a}$ of such as $\dfrac{x_0}{a} \geq 0.45$.
+The dependences of trapping potential $V_0(z)$ on phase variable $z$ are shown in Fig. \ref{phase_potential}. The period of the functions is  $4K(\lambda)$.
+The dependence of the $\lambda$ parameter on normalized half of inter-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
+The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
+This limit corresponds to  infinitely large inter-well distances, with $x_0 \to \infty$.
+On the other hand, $\lambda$ -- parameter grows rapidly at $\dfrac{x_0}{a} \ll 1$.
+Obviously, in this limit our EPJJ model that based on assumption of relatively weak coupling between the wells breaks down.
 
-Analysis of the quantum phase could be examined in three domains of vital parameter $\Lambda$, cf. \cite{Anglin}.
-The dependences of trapping potential $V_0(x)$ are shown in Fig. \ref{phase_potential}.
-The period of the functions is determined as $4K(\lambda)$.
+Below we are focusing on $\lambda$ -- parameters which belong to segment of $0 < \lambda < 1$ and might be obtained at moderate values of $\dfrac{x_0}{a}$ which are $\dfrac{x_0}{a} \geq 0.45$.
+
 %
@@
 \caption{
-Effective potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of  elliptic integral phase coordinate $z$.
-Points $\pm z_{min}$ and $\pm z_{max}$ in (b) corresponds to global minima and maxima of the potential, correspondingly, occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
+Effective dimension-less potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of  elliptic integral phase coordinate $z$.
+Points $\pm z_{min}$ and $\pm z_{max}$ in (b) relay to global minima and maxima of the potential, correspondingly, occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
 \end{figure}
@@
 
+Analysis of the quantum phase can be performed  in three domains determined by vital $\Lambda$--parameter values, cf. \cite{Anglin}.
+
 \textit{Rabi regime} $\Lambda \gg 1$. In this limit the trapping potential reads $V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}$.
-Physically, for any value of $\lambda$ -- parameter taken from the domain $\lambda <1$ we can obtain phase (Rabi) oscillations.
+Physically, for any value of $\lambda$ -- parameter taken from the domain 0$<\lambda <1$ we can obtain (Rabi) oscillations for quantum phase.
 In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and cf. \cite{Anglin}.
+
+\textit{Fock regime} $\Lambda \ll 1/N^2$.
+In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms into Mathieu equation that implies spectrum consisting from all Mathieu functions.
 
@@
 
-In the other limit, for $\Lambda < 2 \lambda$, quantum particle is trapped at two minima of $V_0(z)$ that correspond to $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
+In the other limit, for $\Lambda < 2 \lambda$, quantum "particle" is trapped at two minima of $V_0(z)$ that corresponds to $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
 Fig.
@@
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$ that is marked by red point $C$ in Fig. 3b.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$, see Fig. 3b.
 
-\textit{Fock regime} $\Lambda \ll 1/N^2$.
-In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
-In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms into Mathieu equation that implies spectrum consisting from all Mathieu functions.
 % $ce_0(z, q)$, $ce_1(z, q)$, $se_1(z, q)$, \dots, which are $2\pi$-periodic, and corresponding eigenvalues $a$ can be found using series expansions in powers of $q$.
@@
 
-\section{Quantum-classical phase transitions \label{sec:quantum_classical}}
+\section{Annealing problem versus Quantum-classical PT's \label{sec:quantum_classical}}
 
-Strictly speaking, results established in previous section are completely valid at zero temperature.
-However, in current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures.
-In this section we find answer to vital question: when quantum approach to the phase problem for Josephson junction with coupled exciton polariton condensates is valid?
+Strictly speaking, results established in previous section are valid at zero temperature.
+However, in current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures \cite{Sanvitto,Guillet}.
+In this section we find conditions when quantum approach to the phase problem for Josephson junction with coupled exciton polariton condensates is valid.
+This conditions, in fact, responsible for ability of our system to perform quantum annealing algorithm \cite{Das}.
 
-To give an answer to this question we consider the effective $W$ -- like potential represented in Fig. \ref{phase_potential}b,c inherent to  Josephson (or, Fock) regimes, respectively.
-To be more specific we examine thermodynamically equilibrium system at finite temperature $T$.
-Transition between two stable states (say, between points $z_{1,2}$ in Fig.
+To  be more specific we consider the tunneling in  effective $W$ -- like potential represented in Fig.
+\ref{phase_potential}b  inherent to  Josephson regime.
+We examine thermodynamically equilibrium system of exciton polaritons at finite temperature $T$.
+Transition between two stable states (say, between points $-z_{min}$ and $+z_{min}$ in Fig.
 \ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
-Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is height of the barrier between two states with minimum of potential energy) the particle undergoes hopping over the barrier governed by familiar thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$, cf.
+Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is height of the barrier between two states with minimum of potential energy) the particle jumps over the barrier governed by familiar thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$, cf.
 \cite{Larkin}.
-On the other hand, in the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with vanishing rate.
+This process inherent to classical (thermal) annealing problem \cite{Das}.
+
+In the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with vanishing rate, that is important especially for quantum annealing scheme. 
 %with the rate $\Gamma \sim e^{-B/\hbar}$, where $B$ is the instanton action.
@@
 
-Our description for exciton polariton Josephson junction problem is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
+Our description is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
 The imaginary-time action obtained within WKB method approaches as $S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau$.
@@
 %
-The decay rate $\Gamma \sim e^{-S_{min}/\hbar}$ according our approach can be expressed through the minimal value $S_{min}$ of the action.
-The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion $m \ddot{z} = \frac{d V}{dz}$ written for the thermon that  oscillates inside the inverted potential $-V(z)$.
+The decay rate $\Gamma \sim e^{-S_{min}/\hbar}$ according to our approach can be expressed through the minimal value $S_{min}$ of the action.
+The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion $m \ddot{z} = \frac{d V}{dz}$ written for the thermon "particle" that  oscillates inside the inverted potential $-V(z)$.
 %
@@
 %
-Periodic solutions of this equation satisfy the relation
+Periodic solutions of this equation satisfy
 %
@@
 In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are turning points, cf. Fig. \ref{phase_potential}b.
-The Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at energy $E = 0$ and temperature $T = 0$ characterize instanton solution.
+The Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at energy $E = 0$ and temperature $T = 0$ characterize instanton solution with infinite period.
 Combining  equation for $S(E)$ 
 %(\ref{eq:thermon_action_1}) 
-with (\ref{eq:total_energy}) we obtain  
+with (\ref{eq:total_energy}) we arrive to 
 %
@@
 %
-We summarize our results in the Fig. \ref{pic:phase_boundary_combined}.  First order phase transition occurs in the shaded region for two type of potentials only. 
+
+We summarize our results in Fig.
+\ref{pic:phase_boundary_combined}.
+An insets demonstrate various type of  phase potentials $V_0(z)$ inherent to our EPJJ model.
+First order PT occurs for two type of potentials in the shaded region bounded by bold  (red) curve.
+Second order PT's appear for potential landscapes taken from  dark area.
 %
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
-\caption{Diagram of the phase boundary for  first- and second-order  phase transitions in $\Lambda$,$\lambda$-parameter plane \label{pic:phase_boundary_combined}}
+\caption{Diagram of the phase boundary for  1st- and 2nd-order  PT's in $\Lambda$,$\lambda$-parameters plane. The PEL's are shown in the windows. \label{pic:phase_boundary_combined}}
 \end{figure}
@@
 
-The crossover temperature of second-order phase transition $T_{c}^{(2)} = \hbar \omega_0/ 2 \pi k_B$ is 
+The crossover temperature $T_{c}^{(2)} = \hbar \omega_0/ 2 \pi k_B$ of 2nd-order PT transition  is 
 %
@@
 %
-where  $\omega_0 = \frac{2 \alpha s}{\hbar} \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon near the bottom of inverted potential, $T_{0}=\alpha N / 2\pi k_B$ is critical temperature $T_{c}^{(2)}=T_{0}$ taken at $\Lambda=2\lambda-1$.
-The characteristic temperature $T_{0}$ discussed above implies important time scale $\tau_0=2\pi\hbar/ \alpha N$ that can be understood as thermon ``lifetime''.
-From (\ref{eq:second_order}) follows that, for $\Lambda \ge 2\lambda$ there is no barrier at $z = 0$.
+where  $\omega_0 = \frac{2 \alpha s}{\hbar} \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon "particle" near the bottom of inverted potential,  $T_{0}=\alpha N / 2\pi k_B$ is some characteristic temperature that inherent to exciton polariton system.
+The $T_{0}$  implies important time scale $\tau_0=2\pi\hbar/ \alpha N$ that can be understood as thermon particle ``lifetime''.
+Notably, as it is follows from (\ref{eq:second_order}) there is no barrier at $z = 0$ for $\Lambda \ge 2\lambda$ -- see white domain in Fig.
+\ref{pic:phase_boundary_combined}.
+
+Figure \ref{pic:action_period}a displays 2nd-order PT from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
+The crossover occurs at the critical temperature $T_{c}^{(2)}$ where $S_T = S_0$ and {$E = E_0$}.
+The inset demonstrate monotonic dependence of normalized thermon period $\tau_p/\tau_0$ on energy $E$ that is inherent to second-order phase transition.
+Closest to the critical point with energy $E=E_0$ thermon undergoes small amplitude oscillations.
 
@@
 \end{minipage}
-\caption{Dependences of  minimal action $S_{min}$ (ABC-curve) taken in $s\hbar$ units as a function of reduced temperature $ T/T_{0}$ for (a) 2nd-order transition, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 1st-order transition, $\lambda = 0.5$, $\Lambda = 0.5$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
-The inset shows dependences of  dimensionless $\tau_p / \tau_0$ versus energy $E$ given in  $\alpha s^2$ units.
+\caption{Dependences of  minimal action $S_{min}$ (ABC-(blue) curve) taken in $s\hbar$ units as a function of normalized temperature $ T/T_{0}$ for (a) 2nd-order PT, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 1st-order PT, $\lambda = 0.5$, $\Lambda = 0.5$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
+The inset shows dependences of normalized thermon period $\tau_p / \tau_0$ versus energy $E$ given in  $\alpha s^2$ units.
 \label{pic:action_period}}
@@
 
-The Fig. \ref{pic:action_period}a displays second-order phase transition from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
-The crossover occurs at the critical point $T_{c}^{(2)}$ where $S_T = S_0$ and {$E = E_0$}.
-The inset demonstrate monotonic dependence of thermon period $\tau_p$ on energy $E$ that is inherent to second-order phase transition.
-Closest to the critical point with energy $E=E_0$ thermon undergoes small amplitude oscillations.
-
-In Fig. \ref{pic:action_period}b we represent results exhibiting first-order phase transition.
-It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of thermon period $\tau_p$ on energy $E$ is non-monotonic (see inset in Fig.
-\ref{pic:action_period}b).
+In Fig. \ref{pic:action_period}b we represent results exhibiting 1st-order PT inherent to narrow shadow domain in Fig.\ref{pic:phase_boundary_combined}.
+It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of normalized thermon period  $\tau_p / \tau_0$ on energy $E$ is non-monotonic, see inset in Fig.
+\ref{pic:action_period}b.
 The critical temperature $T_{c}^{(1)}$ belongs to the temperature domain $T_{min} < T_{c}^{(1)} < T_{max}$ and can be find out numerically by solving Eqs.(\ref{eq:thermon_period}) - (\ref{eq:thermal_action}) under the condition $S_T = S_0$.
 
-Analytically critical temperature $T_{c}^{(1)}$ meight be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
+Analytically critical temperature $T_{c}^{(1)}$ might be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
 After some straightforward calculations for $B$ we obtain
@@
 
-In current experiments it is much more easier to manipulate be the density of exciton polaritons instead of their temperature due to some  non-equilibrium processes occurring in real microcavity samples, see e.g.
-\cite{Sanvitto,Guillet}.
-For instance, the density of polariton gas can be manipulated by using the optical pump.
+In experiments with exciton polaritons it is much more easier to manipulate by polariton density instead of the temperature, see e.g. \cite{Sanvitto,Guillet}.
+For instance, the density of polariton gas can be changed by using external optical pump.
 In Fig.
-\ref{pic:temperatures} we plot numerically calculated critical temperature of 1st and 2nd order phase transitions against $\Lambda$-parameter for experimentally accessible semiconductor Josephson junction samples.
-The solid (green) line corresponds to analytical solution obtained with  Eq. (\ref{eq:B_action}).
+\ref{pic:temperatures} we plot numerically calculated critical temperature of 1st and 2nd order PTs against $\Lambda$-parameter for experimentally accessible semiconductor Josephson junction samples.
+Bold (green) line corresponds to analytical solution obtained with  Eq. (\ref{eq:B_action}).
 Since the $\Lambda$-parameter is inversionally proportional to the density of exciton polariton gas (so-called blue shift) Fig.
@@
 \caption
-{Dependence of dimensionless critical temperature $T_{c}/T_{0}$ as a function of parameter $\Lambda$. Solid (green) line corresponds to analytical solution for  $T_{c}^{(1)}$.     
+{Dependence of normalized critical temperature $T_{c}/T_{0}$ as a function of parameter $\Lambda$. Bold (green) line corresponds to analytical solution for  $T_{c}^{(1)}$.     
 \label{pic:temperatures}}
@@
 
-Now let us briefly discuss decay of the upper state that is relevant to the point C in ..... and exist for $\Lambda > 2(1 - \lambda)$.
-Potential presumes local minima at $\pm 2K(\lambda)$ and local maxima at $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
-Equation for the thermon yields 
+Now let us consider decay of the upper state that is relevant to  upper minima located at $\pm 2K(\lambda)$ in Fig.\ref{phase_potential}b and exists for $\Lambda > 2(1 - \lambda)$.
+Physically this problem presumes tunneling through the barrier located at one of the point $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
 %small ocsillation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \frac{\alpha s}{\hbar} \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
-crossover temperature of second-order phase transition $T_{c}^{(2)} = (T_{0}/ 2) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$, cf.... 
+By expanding the potential $V(z)$ near the vicinity of $z_{max}$ it is possible to show that only 2nd-order PT with temperature $T_{c}^{(2)} = (T_{0}/ 2) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$ appear in this case.
+
+Let us briefly discuss observation feasibility of quantum-classical PT for exciton polariton BEC's obtained in experiments.
+In particular, for experimentally accessible polariton interaction strength $\alpha N=0.6meV$, given for narrow-band semiconductor samples, the  $T_{0}$ is about $1.2K$ that is comparable with typical temperature of condensation, or, with temperature of Berezinsky-Kosterlitz-Thouless PT considered for dilute weakly interacting exciton polariton gas being at thermal equilibrium,cf.
+\cite{Sanvitto,Guillet}.
+Practically some enhancement of $T_{0}$ is possible by increasing of exciton polariton density and by improvement of experiment conditions, cf.
+\cite{Snoke_2017}.
 %
@@
 %
-By expanding the potential $V(z)$ near the vicinity of $z_{max}$ it is possible to show that only second-order phase transition appear for this case.
 
@@
 %
-\section{Phase transitions in the presence of dissipation 
+\section{PT's in the presence of dissipation 
 \label{sec:non-equilibrium}}
 
-The obtained above results for phase transitions are valid in true thermodynamically equilibrium limit.
-Notably  exciton polariton condensates in current experiments are out of   thermal  equilibrium, cf.
-[   ].
-It is obvious that for quantum tunneling effects observation  characteristic time scale $\tau_0$ should be shorter than time scales which relay to non-equilibrium processes.
+The obtained results for PTs are valid in true thermodynamical equilibrium limit possessing infinite exciton polariton lifetime $\tau_{pol}$.
+Obviously, for finite $\tau_{pol}$  characteristic time $\tau_0$ that is responsible for quantum tunneling effects observation  should be shorter than time scales describing non-equilibrium processes with exciton polaritons.
 More precisely, in this case we require fulfillment of  inequality
@@
 \begin{equation}
- \tau_{0}\ll\tau_{pol},
+ \tau_{0}\ll\tau_{pol}.
  \label{eq:lifetime}  
 \end{equation}
-where $\tau_{pol}$ characterizes  exciton polariton lifetime.
-However, in realistic (experimental) situation with exction polariton BEC it will be hard to obey to condition {\eqref{eq:lifetime}.
-In this case it is necessary to analyze dynamics of the system.
- Below we consider the influence of the dissipation to the phase properties in adiabatic limit.
 
-We start from mean field  equations obtained from  (\ref{eq:hamiltonian}) for  $\Gamma = 0$,  which reads as 
+For estimations given above, characteristic  temperature $T_{0}=1.2K$ corresponds to thermon effective lifetime  $3.5ps$.
+Excepting  recent experimental results  described in Ref.
+\cite{Snoke_2017} where polariton lifetime attains  $275ps$ at resonance, it might  be hard to adhere to  condition {\eqref{eq:lifetime} in current experiments with exction polariton condensates.
+
+We consider the influence of the dissipation to  EPJJ phase properties in adiabatic limit, cf. \cite{Sols}.
+We start from mean field GP equations obtained from  (\ref{eq:hamiltonian}) for  $\Gamma = 0$ ($B = G$),  which reads as 
 %
 \begin{equation}
-i \dot{\psi}_{1,2} = -i \kappa \psi_{1,2} +  \alpha |\psi_{1,2}|^2 \psi_{1,2} - (B/2 - \beta \psi_{1,2}^* \psi_{2,1}) \psi_{2,1}, 
+i \hbar \dot{\psi}_{1,2} = -i \kappa \psi_{1,2} + (A|\psi_{1,2}|^2 + 2C |\psi_{2,1}|^2) \psi_{1,2} - (B/2 - C \psi_{1,2}^* \psi_{2,1}) \psi_{2,1}. 
 \label{eq:GP}
@@
 %
-where we also introduced dissipation rate term with $\kappa \simeq 1/\tau_{pol}$.
-By introducing new variables  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t)$ for mean field pseudo-spin  parameters (\ref{eq:pseudo_spin}) from ({\ref{eq:GP}}) we obtain
+In (\ref{eq:GP}) we introduced dissipation  term with $\kappa \simeq 1/\tau_{pol}$.
+Defining new variables  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\ref{eq:pseudo_spin}) from ({\ref{eq:GP}}) we obtain
 %
@@
 \begin{array}{lcl}
-\dot{S}_z & = &  2 \beta(t) S_x S_y - B S_y; \\
-\dot{S}_x & = & -2 \alpha(t) S_z S_y; \\
-\dot{S}_y & = & 2(\alpha(t) - \beta(t)) S_z S_z + B S_z.
+\dot{S}_z & = &  2 \beta'(t) S_x S_y - S_y; \\
+\dot{S}_x & = & -2 \alpha'(t) S_z S_y; \\
+\dot{S}_y & = & 2(\alpha'(t) - \beta'(t)) S_z S_x + S_z.
 \end{array}
@@
 %
-
-Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for  non-dissipative system but with time dependent parameters $\alpha(t) = \alpha \exp(-2 \kappa t)$, $\beta(t) = \beta \exp(-2 \kappa t)$, cf.
-....
-
-Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\beta^* = B / 2R$, where $R$ is  radius of the Bloch  sphere, i.e. $R^2=S_x^2 + S_y^2 + S_z^2$.
+Here we explore the dimensionless time $t' = t B / \hbar$.
+Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for  non-dissipative system but with time dependent parameters $\alpha'(t) = (\alpha / B) \exp(-2 \kappa t')$, $\beta'(t) = (\beta / B) \exp(-2 \kappa t')$, cf.\cite{Sedov}.
+Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\beta^* = B / 2R$, where $R$ is  radius of the Bloch  sphere, i.e.
+$R^2=S_x^2 + S_y^2 + S_z^2$.
 %
@@
 In Fig.
-\ref{pic:phase} we represent phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of reduced time.
-Non-dissipative system has two different regimes depending on  $B$ -- parameter values; blue and red curves in the Fig.
+\ref{pic:phase} we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of time.
+Non-dissipative system has two different regimes depending on the values of  $B$ -- parameter, that is blue and red curves in the Fig.
 \ref{pic:phase}, respectively.
-Blue  curve characterizes by condition $\beta > \beta^*$ and  corresponds to the existence of barrier for potential energy (see inset to Fig.
+Blue  curve is plotted under the condition $\beta' > \beta^*$ and  corresponds to the existence of barrier for potential energy (see inset to Fig.
 \ref{pic:phase}).
-Contrary,  red curve establishes phase properties below the threshold ($\beta < \beta^*$) that corresponds to the absence of the barrier.
+Contrary,  red curve establishes phase properties below the threshold ($\beta' < \beta^*$) that corresponds to the absence of the barrier.
 
-In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}) exciton polariton
-system starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value
+In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}) phase of EPJJ starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value
 of $\beta^*$ due to decreasing of total number of particles. 
@@
 \center{\includegraphics[width=0.7\linewidth]{pic/phase_potential_dissipation.eps}}
-\caption{Normalized phase difference as a function of dimensionless time for {\red \dots}.
-For red, blue and black curves initial conditions are {\red \dots}, respectively. Inset demonstrates potential behavior for red and blue curves respectively.
+\caption{Normalized phase difference as a function of time for $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$. Initial conditions
+for red, blue and black curves  are $S_z(0) = 0$, $S_x(0) = 0.62$, $S_y(0) = 0.78$, and $\phi(0) = 0.9$, respectively. Inset demonstrates potential behavior for red and blue curves respectively.
 \label{pic:phase}}
@@
 %
-Adiabaticity condition reads, cf. {\red [ ]}:
+In Fig.\ref{pic:phase} this transition occurs at the time about $20ps$ for given value of dissipation rate $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$.
+
+Adiabaticity condition reads, cf. {\cite{Sols}:
 %
@@
 where $\omega(t) = \sqrt{(B - 2\beta(t))(B - 2 \beta(t) + 2 \alpha(t))}$ is small amplitude oscillations slowly depending on time. 
-
 %It allows us to reduce linear system to the harmonic oscillator equaiton with slowly evolving frequency:
@@
 
-Physically, behavior of the system in the presence of dissipation showed in Fig.
-\ref{pic:phase} establishes non-equilibrium phase transition from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
+Physically, behavior of the phase in the presence of dissipation showed in Fig.
+\ref{pic:phase} establishes non-equilibrium PT from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
 
@@
 Let us summarize the results obtained.
-In the paper we examine quantum phase properties for  Josephson junctions created from coupled exciton polariton condensates in the limit of finite temperatures and dissipation.
-We obtain  various shape of phase potentials depending on the $\Lambda$ and $\lambda$ parameters characterizing condensate junctions.
-The W-shape potential at finite temperature admits two regimes which are  purely quantum tunneling regime through the barrier or classical regime of thermal activation.
-Transition (crossover) between this two limits exhibits universal features of first or second order phase transitions which can be interpreted as phase transition between classical and quantum regimes.
+In the paper we examine quantum phase properties for  extended EPJJs created with the help of coupled exciton polariton condensates taken at finite temperatures and finite exciton polariton lifetime.
+We have shown that  PEL with set of barriers and wells (various W--like potentials) can be achieved for our model  depending on the $\Lambda$ and $\lambda$ parameters which characterize condensate junctions.
+The W-shape potential at finite temperatures admits two regimes which are  purely quantum tunneling regime through the barrier or classical regime of thermal activation.
+Transition (crossover) between this two limits exhibits universal features of 1st or 2nd order PTs which can be interpreted as PT between classical and quantum regimes.
 It is important that critical temperature of transition depends on some  characteristic temperature  parameter $T_{0}$ (see e.g.
-(\ref{eq:second_order})) that depends on polariton-polariton interaction (so-called blue shift) $\alpha N$.
-For experimentally observed values of polariton interaction strength, that implies,say,  $\alpha N=0.3meV$, taken for narrow-band semiconductor samples, the  $T_{0}$ is about $0.6K$ which is less than  typical temperature of condensation, or, temperature of Berezinsky-Kosterlitz-Thouless phase transition considered at thermal equilibrium,cf.
-{\red [ ]}.
-Hence, at large enough temperatures (few tens of Kelvins and more) which are relevant to current experiments with non-equilibrium  exciton polariton condensate junction device operates in classical way.
+(\ref{eq:second_order})) that depends on polariton-polariton interaction length (so-called blue shift) $\alpha N$.
+It is expected that  at the temperatures sufficiently higher than  $T_{0}$ the EPJJ device operates in classical way.
 
 The influence of dissipation effects to this picture is evident from our analysis.
-The thermon lifetime for given  estimations is about $7ps$ that comparable with polariotn lifetime $\tau_{pol}$ in the cavity, cf.
-{\eqref{eq:lifetime} and [ ].
-Thus, the observation of quantum tunneling become possible only within short time intervals when the dissipation cannot essentially affected to the system.
-Otherwise, after some time interval dissipation leads to crossover in the phase dynamics  and breaking  the evolution of quantum phase in W--potential, see \ref{pic:phase}).
+The observation of quantum tunneling processes become possible only within short time intervals when the dissipation cannot essentially affected to the system.
+Otherwise, after some time interval dissipation leads to crossover in the phase dynamics and destroy the W--potential as whole, see Fig. \ref{pic:phase}.
+For moderate dissipation rates and at the temperatures (or relevant polariton gas densities) sufficiently below the temperature of $T_{0}$   the EPJJ device is  capable for various applications where quantum tunneling effect is crucial.
 
-At the temperatures (or relevant polariton gas densities) sufficiently below the temperature $T_{0}$ of phase transition the exciton polariton condensate junctions are capable for various applications where quantum tunneling effect is crucial.
-First, it is quantum annealing with exciton polariton condensates that can be enhanced with the help of bosonic stimulation phenomena {\red [ ]}.
+First, it is quantum information processing and especially quantum annealing problem  with exciton polariton condensates that can be enhanced with the help of bosonic stimulation phenomena {\cite{Yan}.
+Notably the results obtained by us can be implemented  here in new way.
+In order, quantum tunneling effect might be utilized  for design exciton polariton phase qubits similarly to superconductor devices, but in optical wavelength domain, cf.
+\cite{Makhlin}.
+Actually,  two minima located at the points $-z_{min}$ and $+z_{max}$ of $W$-shape quantum phase potential in Fig.
+\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively.
+However, in our case such qubits much more easier to tailor by external optical or electrical pump.
+As a result, quantum annealing problem can be experimentally solved
+with help of this type of qubits, cf.\cite{Johnson}.
 
-Second, quantum tunneling effect can be explored for design exciton polariton phase qubits, cf.
-{\red [ ]}.
-In order, two minima located at the points $A$ and $B$ of $W$-shape quantum phase potential in Fig.
-\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively, {\red cf.
-[ ]}.
-However, in our case such qubits much more easier to tailor by external optical or electrical pump {\red [ ]}.
+Another promising area of potential applications of obtained results with quantum exciton polariton states is connected with quantum metrology purposes.
+More precisely, EPJJs can be useful for creation of interferometers and/or gyroscopes operating with the phase of  exciton polariton condensates in quantum regime, cf.
+\cite{Pezze, Gulevich}.
+We speak here about measurement of the phase shift with high precision accuracy.
+It is possible to show that for the Fock regime described by us in the paper the dispersion of the quantum phase approaches to so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is minimal accessible error for the phase measurement in respect of total particle number.
+The results relate to this problem we will publish in forthcoming papers.
 
-Third, the quantum regime of exciton polariton junctions can be useful for creation of  interferometers with exciton polariton condensates(see e.g.
-[   ]) for quantum metrology purposes, {\red [ ]}.
-In particular, we speak here about measurement of the phase shift with high precision accuracy.
-It is possible to show that for the Fock regime described by us in the paper the dispersion of the quantum phase approaches to so-callrd Heisenberg limit  ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is
-minimal accessible error for the phase measurement in respect of total particle number.
-
+\section{Acknowledgement
+ \label{sec:acknowledgement}}
+We  acknowledge financial support from RFBR, Grants No. 15-52-52001 and No. 14-
+02-97503. 
 % Create the reference section using BibTeX:

### 2017-02-27 phase_transition/iterational_process.m

@@ -1,13 +1,14 @@
-function [ E ] = iterational_process( Vb, V0, mass, E0 )
+function [ E ] = iterational_process( Vb, V0, E0 )
 
 eps = 1e-6;
 
 while true
-	[xleft, xright] = roots_near_equilibrium(@(x) -Vb(x) + E0);
-	period = sqrt(2 * mass) * integral(@(x) 1 ./ sqrt(Vb(x) - E0),...
+	[xleft, xright] = roots_near_x0(@(x) -Vb(x) + E0, 0);
+	% [xleft, xright] = roots_near_equilibrium(@(x) -Vb(x) + E0);
+	period = integral(@(x) 1 ./ sqrt(Vb(x) - E0),...
 		xleft, xright, 'AbsTol', 1e-6);
 
-	E = V0 - (2 * sqrt(2 * mass) / period) * integral(@(x) sqrt(Vb(x) - E0),...
+	E = V0 - (2 / period) * integral(@(x) sqrt(Vb(x) - E0),...
 		xleft, xright, 'AbsTol', 1e-6);
 	
 	if abs(E - E0) < eps

### 2017-02-27 phase_transition/preparing_paper.m

@@ -410,19 +410,19 @@ boltzmann_const = 1;
 
 % 2nd order
 % Frequency of the small thermon oscillations
-omega0 = @(lambda, Lambda) 2 * alpha * s * sqrt(lambda * (1 - lambda) + 0.5 * (2 * lambda - 1) * Lambda - 0.25 * Lambda^2);
-T_2nd = @(lambda, Lambda) omega0(lambda, Lambda) / (2 * pi);
+% omega0 = @(lambda, Lambda) 2 * alpha * s * sqrt(lambda * (1 - lambda) + 0.5 * (2 * lambda - 1) * Lambda - 0.25 * Lambda^2);
+T_2nd = @(lambda, Lambda) (1 / pi) * sqrt(lambda * (1 - lambda) + 0.5 * (2 * lambda - 1) * Lambda - 0.25 * Lambda^2);
 
 % 1st order
 % Action on the thermon
-B = @(lambda, Lambda) 2 * s * (log((2 * sqrt(lambda) + sqrt(4 * lambda^2 - Lambda^2)) ...
+B = @(lambda, Lambda) 2 * (log((2 * sqrt(lambda) + sqrt(4 * lambda^2 - Lambda^2)) ...
 	/ ((2 * sqrt(lambda) - sqrt(4 * lambda^2 - Lambda^2)))) ...
 	- (Lambda / sqrt(lambda * (1 - lambda))) ...
 	* atan(sqrt((1 - lambda) * (2 * lambda - Lambda) * (2 * lambda + Lambda)) / Lambda));
 
-V0 = @(lambda, Lambda) alpha * s^2 * (1 - Lambda / (2 * lambda))^2;
+V0 = @(lambda, Lambda) (1 - Lambda / (2 * lambda))^2;
 
-lambda = 0.75;
+lambda = 0.9;
 
 % Border
 Lambda_border =  (1 - 16 * lambda + 16 * (lambda .^ 2) + ...
@@ -431,11 +431,16 @@ Lambda_border =  (1 - 16 * lambda + 16 * (lambda .^ 2) + ...
 Lambda_1st = 0:0.01:Lambda_border;
 t_1st = zeros(1, length(Lambda_1st));
 
+t_1st_estimation = zeros(1, length(Lambda_1st));
+for i = 1:length(Lambda_1st)
+	t_1st_estimation(i) = V0(lambda, Lambda_1st(i)) / B(lambda, Lambda_1st(i));
+end
+
[…]

### 2017-02-27 phase_transition/preparing_paper_dissipation.m

@@ -22,14 +22,14 @@ alpha = 1; beta = 0.9; B = 1; R = 1;
 lambda_1 = beta / alpha;
 Lambda_1 = B / (alpha * R); % s = R (?)
 
-alpha_dissip = @(t, alpha, kappa) alpha * exp(-kappa * t);
-beta_dissip  = @(t, beta, kappa) beta  * exp(-kappa * t);
+alpha_dissip = @(t, alpha, kappa) (alpha / B) * exp(-2 * kappa * t);
+beta_dissip  = @(t, beta, kappa) (beta / B) * exp(-2 * kappa * t);
 
 % S = [S_z; S_x; S_y]
 dS = @(t, S, alpha, beta, kappa) [
-	2 * beta_dissip(t, beta, kappa) * S(2) * S(3) - B * S(3);
+	2 * beta_dissip(t, beta, kappa) * S(2) * S(3) - S(3);
 	-2 * alpha_dissip(t, alpha, kappa) * S(1) * S(3);
-	2 * (alpha_dissip(t, alpha, kappa) - beta_dissip(t, beta, kappa)) * S(1) * S(2) + B * S(1)
+	2 * (alpha_dissip(t, alpha, kappa) - beta_dissip(t, beta, kappa)) * S(1) * S(2) + S(1)
 ];
 
 % S_x^2 + S_y^2 + S_z^2 = S_0^2 = R^2
@@ -63,7 +63,7 @@ phase = atan(S_barrier(:, 3) ./ S_barrier(:, 2));
 plot(T, phase, 'Color', 'blue');
 
 % (III) Phase in a new regime without dissipation
-t_new_regime = 200; % Look at the figure
+t_new_regime = 250; % Look at the figure
 new_alpha = alpha_dissip(t_new_regime, alpha, kappa);
 new_beta  = beta_dissip(t_new_regime, beta, kappa);
 
@@ -91,8 +91,7 @@ legend( ...
 	sprintf('\\kappa = 0, \\lambda = %g, \\Lambda = %g', lambda_1, Lambda_1), ...
 	sprintf('\\kappa = 0, \\lambda = %g, \\Lambda = %g', lambda_2, Lambda_2))
 
-title('\Delta \phi = arctan(-S_y / S_x)')
-xlabel('t'); ylabel('\Delta \phi')
+xlabel('t'); ylabel('\phi')
 
 %% Potential transformation
[…]

### 2017-03-06 writing/phase_transition/phase_transition.tex
Restuctured, picture with phase on dissipation was improved

@@
 
+% For the debug usage only
+\newcommand{\red}{\color{red}}
+\newcommand{\blue}{\color{blue}}
+
 \begin{document}
 
-\title{Quantum-Classical Phase Transition for Exciton-Polariton Josephson Junctions}
+\title{{Exciton-polariton Josephson junctions at finite temperatures}}
 
@@
 We consider the problem of achievement of quantum regime for relative phase of trapped in W -- potential low branch exciton polariton condensates taken at finite temperatures and finite polariton lifetime.
-Non-standard Bose-Hubbard model of  exciton polariton Josephson junction (EPJJ) that produces complex potential energy landscape (PEL) consisting from set of barriers and wells for the phase is proposed.
-We have shown that classical (thermal) activation and quantum tunneling for the phase  represent two regimes depending on temperature, polariton condensate density and distance between the junctions.
-The transition between this two regimes   exhibits universal features of first or second order phase transition (PT) depending on the PEL for relative phase.
-In the presence of dissipation quantum system exhibits non-equilibrium PT from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
-The obtained results are discussed in details in the framework of quantum annealing problem with exciton polariton condensates.
+Non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by complex potential energy landscapes (PEL) consisting of sets of barriers and wells is proposed.
+We have shown that the classical (thermal) activation and quantum tunneling for the phase represent two regimes depending on temperature, polariton condensate density and distance between the junctions.
+The transition between these two regimes exhibits universal features of first or second order phase transition (PT) depending on the PEL for the relative phase of two polariton condensates.
+In the presence of dissipation quantum system exhibits the non-equilibrium PT from quantum {\blue (where tunneling is possible)} to classical regime, where the tunelling is efficient and where it is suppressed, respectively.
+The obtained results are discussed in details in the framework of the quantum annealing problem with exciton polariton condensates.
 
@@
 
-% For the debug usage only
-\newcommand{\red}{\color{red}}
-
 \section{Introduction \label{sec:introduction}}
 
-For last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represent important mainstream of current photonic and semiconductor technologies, see e.g.
-\cite{Sanvitto,Guillet}.
-The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum wells excitons.
-Practically, semiconductor microcavities are promising for various optoelectronic applications where quantum  matter-field interface plays crucial role.
-In particular, it is worth to mention demonstrations of polariton laser with electrical pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
-Although exciton polariton condensates exhibits Bose-Einstein statistics under the phase transition (PT) condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
+In the last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represented an important mainstream of current photonic and semiconductor studies, see e.g.
+\cite{Sanvitto, Guillet}.
+The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum well excitons.
+Semiconductor microcavities are promising for various optoelectronic applications where the quantum  matter-field interface plays crucial role.
+In particular, it is worth to mention demonstrations of a polariton laser with electrical injection pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
+Although exciton polariton condensates exhibit Bose-Einstein statistics  above the lasing threshold under the phase transition (PT) condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
 Non-equilibrium features of exciton polariton condensates play important role in various manifestations of their collective (many body) states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
@@
 Recently Yongbao Sun et al, in Ref.
-\cite{Snoke_2017} reports observation of quasi-equilibrium low branch exciton polariton condensate in high Q-factor microcavity possessing very high photon lifetime, that is $135ps$.
-Notably, exciton polaritons with long lifetime are promising candidates for current quantum technologies, cf.
+\cite{Snoke_2017} reported observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity possessing very a comparatively very long photon lifetime of $135ps$.
+Notably, exciton polaritons with long lifetime are promising candidates for quantum technologies, cf.
 \cite{Demirchyan}.
-However, since exciton polariton BEC's in present experiments are observed at high enough (up to the room) temperatures the quantum abilities of such a states should be examined even at full thermal equilibrium.
+However, since exciton polariton BEC's in present experiments are observed at high enough (up to the room) temperatures the quantum properties of such a states should be examined even at full thermal equilibrium.
 
-The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical purposes and especially for their possible applications in quantum information science, see e.g.
+The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical applications and especially for their possible applications in quantum information technologies, see e.g.
 \cite{Dominici}.
@@
 
-Especially it is important to stress here quantum annealing problem physically based on searching algorithm for the global minimum of a potential energy landscape (PEL) consisting from set of barriers and wells, see e.g.
+Especially it is important to stress here quantum annealing problem physically based on the searching algorithm for the global minimum of a potential energy landscape (PEL) consisting of a set of barriers and wells, see e.g.
 \cite{Santoro, Das}.
-In purely classical  (thermal) regime physical system overcomes arbitrary barrier at finite temperature with the help of thermal activation process if the thermal energy is enough.
-Contrary, in quantum limit the same system undergoes quantum tunneling through the barrier.
-Obviously, the shape of the barrier plays essential role in this case, cf.
+In purely classical  (thermal) regime the {bosonic quasipartcles cross barriers stochastically} at finite temperature with the help of thermal activation process if the thermal energy is enough.
+Contrary, in a quantum limit the same system undergoes quantum tunneling through the barrier.
+Obviously, the shape of the barrier plays an essential role in this case, cf.
 \cite{Das, Lewenstein}.
-In order, as it is shown recently  in \cite{Lewenstein} annealing algorithm implies in general case combination of thermal annealing and quantum tunneling.
+It has been shown recently in \cite{Lewenstein} that the annealing algorithm relies in general case on combination of thermal annealing and quantum tunneling.
 The
-collective (bosonic) character of polariton condensation could be used in this case to acceleration of search physical algorithm \cite{Yan}.
+collective (bosonic) character of polariton condensation could be used for the acceleration of the physical implementation of the search algorithm \cite{Yan}.
 
-In the paper we consider generic problem  of quantum-classical phase transition (PT) with exciton polariton condensates occurring in semiconductor microcavity in the presence of Josephson effect, cf.
+In the paper we consider a generic problem of quantum-classical phase transition (PT) with exciton polariton condensates formed in a semiconductor microcavity in the presence of Josephson effect, cf.
 \cite{Chudnovsky_1997,Aleiner, Shelykh_2008, Borgh_2010}.
-To be more specific we examine simply two junction model.
+To be more specific we examine simply a two junction model.
 
@@
 Traditionally,  studies in this field are limited by consideration of superconductor devices \cite{Ankerhold} where macroscopic quantum tunneling phenomena plays essential role.
-In particular, it is worth to mention here Schr\"odinger cat state formation \cite{Leggett} and design of quantum gates with superconductor qubits for quantum computing where macroscopic quantum coherence for the phase is important \cite{Makhlin}.
-Recently the problem of quantum tunneling and quantum-classical PT problem have been applied to other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
-Strictly speaking main discussion is focused on investigation of quantum-classical escape rate transition that takes place in the presence of potential barrier at finite temperatures.
+In particular, it is worth to mention here the Schr\"odinger cat state formation \cite{Leggett} and the 	design of quantum gates with superconductor qubits for quantum computing where a macroscopic quantum coherence for the phase is important \cite{Makhlin}.
+Recently the problem of quantum tunneling and quantum-classical PT problem have been examined for other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
 
-In the paper we propose \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter matrix elements, cf.
+In the paper we consider an \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter matrix elements, cf.
 \cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
-In particularly, we pay our attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
-We aimed at elucidation of necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for quantum annealing purposes and creation of exciton polariton qubit gates.
+In particularly, we pay attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
+We aimed at formulating necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for realisation of quantum annealing purposes and creation of exciton polariton qubit gates.
 
 This paper is arranged as follows.
-In Sec. \ref{sec:model} we explain in details  extended model of EPJJ under the tight-binding approach. 
 In Sec.
-\ref{sec:quantum_phase} we give description of quantum phase for our model and discuss various regimes for it.
-Section \ref{sec:quantum_classical} establishes main results obtained in the paper.
-In order, we consider quantum-classical PT problem for various PEL's for quantum phase in the framework of our model at finite temperatures.
+\ref{sec:quantum_phase} we introduce the quantum phase model for extended model of EPJJ of the coupled condensates and discuss various regimes for it at zero temperature and infinite exciton polariton lifetime.
+Section \ref{sec:quantum_classical} establishes  results obtained for quantum-classical PT problem and considered for quantum phase  at finite temperatures.
 The influence of non-equilibrium effects with microcavity exciton polaritons possessing finite lifetime is discussed in \ref{sec:non-equilibrium}.
 In Conclusion we summarize the results obtained.
+In Appendix \ref{sec:model} we explain in details  extended model of EPJJ within the tight-binding approach. 
+\section{The Quantum Phase Model \label{sec:quantum_phase}}
 
-\section{THE MODEL OF EPJJ \label{sec:model}}
-
-We start by describing the problem of equilibrium exciton polariton condensate trapping in symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines distance between potential minima, $h$ is depth of the potential.
-% 
-%\begin{figure}[ht]
-%\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
-%\caption{
-%Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
-%The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
-%\label{pic:potential_sym_asym}
-%\end{figure}
-%
-The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the second quantized form as:
+We start with the Hamiltonain 
 %
 \begin{equation}
-\hat{H} = \int \hat{\psi}^\dag\Big\{ -\dfrac{\hbar^2}{2m_{pol}}  \dfrac{d^2 }{dx^2} + U(x) + \dfrac{g}{2} \hat{\psi}^{\dag} \hat{\psi}  \Big\}\hat{\psi} dx,
-\label{eq:gpe_hamiltonian}
+\hat{H} = \alpha \hat{S}_z^2 + \beta \hat{S}_x^2 - B \hat{S}_x.
+\label{eq:hamiltonian_spin}
 \end{equation}
-%
-where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ describes two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
-In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator supposing
-%
-\begin{equation}
-\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
-\label{eq:two_modes}
-\end{equation}
-%
-where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
-It's instructive to represent  $\Phi_{1,2}(x)$ as
-%
-\begin{equation}
-\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
-\label{eq:basic_modes}
-\end{equation}
-%
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii (GP) equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
-%
-%\begin{equation}
-%\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
-%\label{eq:stationary}
-%\end{equation}
-%
-and normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is chemical potential.
-As a result an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes total number of particles.
-Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
-% 
-\begin{equation}
-\begin{array}{lcl}
-\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
-& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
-& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
-\end{array}
-\label{eq:hamiltonian}
-\end{equation}
-%
-where we made denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
-$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.
-
-Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton condensates trapped in double-well potential.
-The ``additional'' terms with $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize density induced and pair tunneling, respectively.
-Generally, our model implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
-The contribution from relevant coefficients on can be estimated from variational ansatz
-%
-\begin{equation}
-\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big],
-\label{eq:two_modes_eq}
-\end{equation}
-%
-where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
-In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of inter-well distance $x_0$ is shown.
-It is important that differences between various $\gamma_{ij}$ rapidly vanish with increasing the inter-well distance $2x_0$.
-We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
-%
-\begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.eps}}
-\caption{Dependences of normalized matrix elements $\gamma_{ij} / g$ on $x_0 / a$. \label{pic:gamma_pm_vs_g}}
-\end{figure}
-%
-
-\section{The Quantum Phase \label{sec:quantum_phase}}
-
-To elucidate purely quantum phase features of our extended Josephson model it is fruitful to recast Hamiltonian (\ref{eq:hamiltonian}) through the pseudo-spin operators defined as
+that characterize weakly interacting exciton polariton condensate Josephson junction device in terms of pseudo-spin operators $\hat{S}_i$, $i=x,y,z$.
+The parameters $\alpha$, $\beta$ and $B$ reflect  Josephson junction properties and determined in Appendix \ref{sec:model}. 
+Here we propose quantum mechanical approach to the EPJJ  phase recasting pseudo-spin operators in  (\ref{eq:hamiltonian_spin}) through the differential representation defined as
 % 
@@
 \begin{align}
-\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) = s \cos{\phi} - \sin{\phi} \dfrac{d}{d \phi}, \\
-\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) = s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
-\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 - \hat{\psi}_1^\dag \hat{\psi}_1) = -i\dfrac{d}{d \phi},
+\hat{S}_x = & s \cos{\phi} - \sin{\phi} \dfrac{d}{d \phi}, \\
+\quad \hat{S}_y = & s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
+\hat{S}_z = & -i\dfrac{d}{d \phi}
 \end{align}
-\label{eq:pseudo_spin}
+\label{eq:pseudo_spin_diff}
 \end{subequations}
+%
 where  $\phi$ is the phase variable.
-The operators determined in Eq. (\ref{eq:pseudo_spin}) obey familiar $SU(2)$ algebra commutation relations $[S_i, S_j] = i\epsilon_{ijk}S_k,  i,j,k=x,y,z$.
-After straitforward calculations from (\ref{eq:hamiltonian}) one can obtain
+The operators determined in Eq. (\ref{eq:pseudo_spin_diff}) in \eqref{eq:hamiltonian_spin}
+ obey familiar $SU(2)$ algebra commutation relations $[\hat{S}_i, \hat{S}_j] = i\epsilon_{ijk}\hat{S}_k,  i,j,k=x,y,z$.
+After straitforward calculations from (\ref{eq:hamiltonian_spin}) one can obtain
 %
@@
 %
-where $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
-Below we chose $x_0$ obeying to condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity, see Fig.
-\ref{pic:gamma_pm_vs_g}.
-We also assume macroscopically large particle number, i.e.
-the $s = N/2 >> 1$ is C - number.
-Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain
+We also assume macroscopically large particle number, i.e. the $s = N/2 >> 1$ is C - number. Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain   
 %
@@
 The dependences of trapping potential $V_0(z)$ on phase variable $z$ are shown in Fig. \ref{phase_potential}. The period of the functions is  $4K(\lambda)$.
-The dependence of the $\lambda$ parameter on normalized half of inter-well distance $\dfrac{x_0}{a}$ can be estimated from (\ref{eq:two_modes_eq}) and reads as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
-The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
+The dependence of the $\lambda$ parameter on normalized half of inter-well distance $\dfrac{x_0}{a}$ can be estimated as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
+The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
 This limit corresponds to  infinitely large inter-well distances, with $x_0 \to \infty$.
@@
 \textit{Fock regime} $\Lambda \ll 1/N^2$.
-In purely quantum limit the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$ with the phase wavefunction $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In purely quantum limit 
+%the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$%
+the phase wavefunction approaches $\Phi(\phi) \to (2\pi)^{-1/2}$.
 In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms into Mathieu equation that implies spectrum consisting from all Mathieu functions.
@@
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$, see Fig. 3b.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$, see Fig. 1b.
 
@@
 
-Strictly speaking, results established in previous section are valid at zero temperature.
-However, in current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures \cite{Sanvitto,Guillet}.
+In current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures \cite{Sanvitto,Guillet}.
 In this section we find conditions when quantum approach to the phase problem for Josephson junction with coupled exciton polariton condensates is valid.
@@
 \ref{phase_potential}b  inherent to  Josephson regime.
-We examine thermodynamically equilibrium system of exciton polaritons at finite temperature $T$.
+We examine thermodynamically equilibrium (with infinitely large  exciton polariton lifetime) system of exciton polaritons at finite temperature $T$.
+Noticing, that in  recent experiments  described in Ref.
+\cite{Snoke_2017} polariton lifetime attains  $275ps$ at resonance that seems to be enough to justify the quantum processes described below.
+
 Transition between two stable states (say, between points $-z_{min}$ and $+z_{min}$ in Fig.
@@
 
-The obtained results for PTs are valid in true thermodynamical equilibrium limit possessing infinite exciton polariton lifetime $\tau_{pol}$.
-Obviously, for finite $\tau_{pol}$  characteristic time $\tau_0$ that is responsible for quantum tunneling effects observation  should be shorter than time scales describing non-equilibrium processes with exciton polaritons.
+Let us now consider more realistic physical situation with EPJJ that valid for finite exciton polariton lifetime $\tau_{pol}$.
+Obviously, for finite $\tau_{pol}$  characteristic time $\tau_0$ that is responsible for quantum tunneling effects  should be shorter than typical time scales describing non-equilibrium processes with exciton polaritons.
 More precisely, in this case we require fulfillment of  inequality
-
  \begin{equation}
@@
 
-For estimations given above, characteristic  temperature $T_{0}=1.2K$ corresponds to thermon effective lifetime  $3.5ps$.
-Excepting  recent experimental results  described in Ref.
-\cite{Snoke_2017} where polariton lifetime attains  $275ps$ at resonance, it might  be hard to adhere to  condition {\eqref{eq:lifetime} in current experiments with exction polariton condensates.
+In order,  characteristic  temperature $T_{0}=1.2K$ corresponds to thermon effective lifetime  $\tau_{0}=3.5ps$ for estimations given above.
+Here we examine situation when exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
+Namely  this situation is realized in most of current experiments with non-equilibrium exciton polariton condensates, see e.g.
+[   ].
 
-We consider the influence of the dissipation to  EPJJ phase properties in adiabatic limit, cf. \cite{Sols}.
-We start from mean field GP equations obtained from  (\ref{eq:hamiltonian}) for  $\Gamma = 0$ ($B = G$),  which reads as 
-%
+Below we consider the influence of the dissipation to  EPJJ quantum phase properties in adiabatic limit, cf. \cite{Sols}.
+We start from GP equations obtained from  (\ref{eq:hamiltonian}) for mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$  at $\Gamma = 0$ ($B = G$),  which reads as 
 \begin{equation}
@@
 \end{equation}
+In (\ref{eq:GP}) we introduced dissipation  term with $\kappa \simeq \hbar/\tau_{pol}$.
+Defining new variables $\Psi_{1,2}$ by using  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\eqref{eq:pseudo_spin}) from {\ref{eq:GP}} we obtain
 %
-In (\ref{eq:GP}) we introduced dissipation  term with $\kappa \simeq 1/\tau_{pol}$.
-Defining new variables  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\ref{eq:pseudo_spin}) from ({\ref{eq:GP}}) we obtain
 %
-%\begin{equation}
-%\begin{array}{lcl}
-%i \Psi_{1, t} & = & \alpha(t) |\Psi_1|^2 \Psi_1 - (B/2 - \beta(t) \Psi_1^* \Psi_2) \Psi_2; \\
-%i \Psi_{2, t} & = & \alpha(t) |\Psi_2|^2 \Psi_2 - (B/2 - \beta(t) \Psi_2^* \Psi_1) \Psi_1.
-%\end{array}
-%\end{equation}
-%
-%Hamiltoninan in terms of Stocks operators (\ref{eq:pseudo_spin}):
-%
-%\begin{equation}
-%\hat{H} = \alpha(t) \hat{S}_z^2 + \beta(t) %\hat{S}_x^2 - B \hat{S}_x.
-%\end{equation}
-%
-%Equaitions on the mean-values of operators:
 % 
@@
 Here we explore the dimensionless time $t' = t B / \hbar$.
-Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for  non-dissipative system but with time dependent parameters $\alpha'(t) = (\alpha / B) \exp(-2 \kappa t')$, $\beta'(t) = (\beta / B) \exp(-2 \kappa t')$, cf.\cite{Sedov}.
-Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\beta^* = B / 2R$, where $R$ is  radius of the Bloch  sphere, i.e.
-$R^2=S_x^2 + S_y^2 + S_z^2$.
-%
-%\begin{equation}
-%\end{equation}
-%
-%where $R$ -- is a radius of the Poincare sphere.
-%Non-dissipative system has a bifurcation at the critical values of .
+This system describe dynamics of normalized mean field pseudo-spin parameters on the Bloch sphere with $S_x^2 + S_y^2 + S_z^2 = 1$.
+Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for non-dissipative system but with time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa t')$, cf.\cite{Sedov}.
+Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to solid black curve in Fig.1b.
 
 In Fig.
-\ref{pic:phase} we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of time.
-Non-dissipative system has two different regimes depending on the values of  $B$ -- parameter, that is blue and red curves in the Fig.
+\ref{pic:phase}a we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of time.
+Non-dissipative system has two different regimes depending on the values of  $\beta$ -- parameter, that is blue and red curves in the Fig.
 \ref{pic:phase}, respectively.
-Blue  curve is plotted under the condition $\beta' > \beta^*$ and  corresponds to the existence of barrier for potential energy (see inset to Fig.
-\ref{pic:phase}).
-Contrary,  red curve establishes phase properties below the threshold ($\beta' < \beta^*$) that corresponds to the absence of the barrier.
+Blue  curve is plotted under the condition $\beta' > 1/2$ and  corresponds to the existence of barrier for potential energy -- see Fig.
+\ref{pic:phase}b.
+Contrary,  red curve establishes phase properties below the threshold ($\beta' <1/2$) that corresponds to the absence of the barrier.
 
-In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}) phase of EPJJ starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value
-of $\beta^*$ due to decreasing of total number of particles. 
+In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}a) phase of EPJJ starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value 1/2
+due to decreasing of total number of particles. 
 %It can be transformed to the equation on the phase difference $\phi$ and $S_z$ as follows
@@
 \begin{figure}[ht]
-\center{\includegraphics[width=0.7\linewidth]{pic/phase_potential_dissipation.eps}}
-\caption{Normalized phase difference as a function of time for $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$. Initial conditions
-for red, blue and black curves  are $S_z(0) = 0$, $S_x(0) = 0.62$, $S_y(0) = 0.78$, and $\phi(0) = 0.9$, respectively. Inset demonstrates potential behavior for red and blue curves respectively.
+\center{\includegraphics[width=\linewidth]{pic/phase_potential_dissipation.eps}}
+\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \alpha s / \hbar$) vs time for $\kappa/\hbar = 0.1 THz$.
+Initial conditions are $S_z(0) = S_x(0) = 0$, $S_y(0) = 1$, and $\phi(0) = \pi / 2$, respectively.
 \label{pic:phase}}
@@
 %
-In Fig.\ref{pic:phase} this transition occurs at the time about $20ps$ for given value of dissipation rate $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$.
+%\begin{figure}[ht]
+%\center{\includegraphics[width=0.5\linewidth]{pic/temperature_on_dissipation.eps}}
+%\caption{Dependance of $T_c^{(2)}$ on $\kappa t$ for $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$, $B = 1$
+%\label{pic:temperature_dissipation}}
+%\end{figure}
+%
 
-Adiabaticity condition reads, cf. {\cite{Sols}:
+The Fig. \ref{pic:phase}c exhibits suppression of critical temperature of phase transition $T_{c}^{(2)}$ that occurs at the timepoint $t_0=...$ for  $\tau_{pol} \sim \hbar/\kappa= 10 ps$.
+
+Physically, behavior of the phase in the presence of dissipation showed in Fig.
+\ref{pic:phase} establishes non-equilibrium PT from regime where tunneling is possible to the regime where tunneling is suppressed.
+However, this regime happening at $t>t_0$ cannot be interpreted immediately as classical one.
+
+Actually, adiabaticity condition reads, cf. {\cite{Sols}:
 %
@@
 \begin{equation}
-\phi(\tau) \approx A / \sqrt{\omega(\tau)} \cos (\omega(\tau) \tau),
+\phi(\tau) \approx \dfrac{A}{\omega(\tau)} \cos (\omega(\tau) \tau),
 \end{equation}
 %
-where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$.
-
-Physically, behavior of the phase in the presence of dissipation showed in Fig.
-\ref{pic:phase} establishes non-equilibrium PT from quantum (where tunneling is possible) to the classical regime where tunneling is escaped.
+where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$. At large enough times 
+$\omega(t) \approx$ $B$  and permanent-like temporal oscillations for the Josephson junction phase $\phi$ are occurs, see Fig.
+5a and cf.
+[   ].
+To determine quantum (or, classical) character of this oscillations quantum fluctuations should be examined.
 
@@
 The observation of quantum tunneling processes become possible only within short time intervals when the dissipation cannot essentially affected to the system.
-Otherwise, after some time interval dissipation leads to crossover in the phase dynamics and destroy the W--potential as whole, see Fig. \ref{pic:phase}.
+Otherwise, after some time interval dissipation leads to crossover in the phase dynamics and destroy the W--potential as whole, see Fig.
+\ref{pic:phase}.
+In this case permanent oscillations of Josephson junction phase occurs within adiabatic approach.
+To determine quantum either classical properties of this oscillations it is necessary to study fluctuations of the exciton polariton system beyond the semiclassical approach represented in Sec.\ref{sec:non-equilibrium}}.
 For moderate dissipation rates and at the temperatures (or relevant polariton gas densities) sufficiently below the temperature of $T_{0}$   the EPJJ device is  capable for various applications where quantum tunneling effect is crucial.
@@
 02-97503.
+
+\appendix
+\section{THE MODEL OF EPJJ \label{sec:model}}
+
+To derive Eq.(\ref{eq:hamiltonian_spin}) we consider equilibrium exciton polariton condensate trapped in a symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines the distance between potential minima, $h$ is depth of the potential.
+% 
+%\begin{figure}[ht]
+%\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
+%\caption{
+%Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
+%The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
+%\label{pic:potential_sym_asym}
+%\end{figure}
+%
+The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the second quantized form as:
+%
+\begin{equation}
+\hat{H} = \int \hat{\psi}^\dag\Big\{ -\dfrac{\hbar^2}{2m_{pol}}  \dfrac{d^2 }{dx^2} + U(x) + \dfrac{g}{2} \hat{\psi}^{\dag} \hat{\psi}  \Big\}\hat{\psi} dx,
+\label{eq:gpe_hamiltonian}
+\end{equation}
+%
+where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ describes two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
+In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator supposing
+%
+\begin{equation}
+\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
+\label{eq:two_modes}
+\end{equation}
+%
+where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
+It's instructive to represent  $\Phi_{1,2}(x)$ as
+%
+\begin{equation}
+\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
+\label{eq:basic_modes}
+\end{equation}
+%
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii (GP) equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
+%
+%\begin{equation}
+%\mu_{\pm} \Phi_{\m} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
+%\label{eq:stationary}
+%\end{equation}
+%
+and normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is chemical potential.
+As a result an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes total number of particles.
+Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
+% 
+\begin{equation}
+\begin{array}{lcl}
+\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
+& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
+& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
+\end{array}
+\label{eq:hamiltonian}
+\end{equation}
+%
+where we made denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
+$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.
+
+Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton condensates trapped in double-well potential.
+The ``additional'' terms with $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize density induced and pair tunneling, respectively.
+Generally, our model implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
+
+The contribution from relevant coefficients on can be estimated from variational ansatz $\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]$,
+%
+%\begin{equation}
+%\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big],
+%\label{eq:two_modes_eq}
+%\end{equation}
+%
+where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
+% In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of inter-well distance $x_0$ is shown.
+It is important that differences between various $\gamma_{ij}$ rapidly vanish with increasing the inter-well distance $2x_0$.
+We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
+This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
+%
+%\begin{figure}[ht]
+%\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.eps}}
+%\caption{Dependences of normalized matrix elements $\gamma_{ij} / g$ on $x_0 / a$. \label{pic:gamma_pm_vs_g}}
+%\end{figure}
+%
+Now let us introduce the pseudo spin operators
+%
+\begin{subequations}
+\begin{align}
+\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\
+\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) \\
+\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 - \hat{\psi}_1^\dag \hat{\psi}_1).
+\end{align}
+\label{eq:pseudo_spin}
+\end{subequations}
+%
+Inserting (\ref{eq:pseudo_spin}) into the (\ref{eq:hamiltonian}) we arrive at Eq.(1)  
+with 
+%the equation
+%
+%\begin{equation}
+%\hat{H} = \alpha \hat{S}_z^2 + \beta %\hat{S}_x^2 - B \hat{S}_x,
+%\label{eq:hamiltonain_spin_appendix}
+%\end{equation}
+%
+$\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
+We also chose $x_0$ obeying the condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity.
+
 % Create the reference section using BibTeX:

### 2017-03-06 phase_transition/preparing_paper_dissipation.m

@@ -1,5 +1,3 @@
-%% ?????????? ??? ??????? ??? exp(-2 * kappa * t)
-
 %% Libs
 addpath ../finding_stationary_modes/
 
@@ -18,7 +16,7 @@ clc; clear
 % \alpha \to \alpha \exp(-\kappa t)
 % \beta \to \beta \exp(-\kappa t)
 
-alpha = 1; beta = 0.9; B = 1; R = 1;
+alpha = 1; beta = 0.5; B = 0.1; R = 1;
 lambda_1 = beta / alpha;
 Lambda_1 = B / (alpha * R); % s = R (?)
 
@@ -34,7 +32,7 @@ dS = @(t, S, alpha, beta, kappa) [
 
 % S_x^2 + S_y^2 + S_z^2 = S_0^2 = R^2
 % Initial condition
-Sz0 = 0; Sx0 = 0.62;
+Sz0 = 0; Sx0 = 0;
 Sy0 = sqrt(R^2 - Sx0^2 - Sz0^2);
 
 % Phase
@@ -42,12 +40,12 @@ Sy0 = sqrt(R^2 - Sx0^2 - Sz0^2);
 
 % (I) Phase with dissipation
 % Parameter fo the dissipation
-kappa = 0.004;
-T_fin = 300;
+kappa = 0.05;
+T_fin = 70;
 
 % RK parameters
 dS_kappa = @(t, S) dS(t, S, alpha, beta, kappa);
-tspan = [0 T_fin]; S0 = [Sz0; Sx0; Sy0]; N = 2^14;
+tspan = [0 T_fin]; S0 = [Sz0; Sx0; Sy0]; N = 2^12;
 [T, S_dissip] = RK4(dS_kappa, tspan, S0, N);
 phase_dissip = atan(S_dissip(:, 3) ./ S_dissip(:, 2));
 
@@ -63,7 +61,7 @@ phase = atan(S_barrier(:, 3) ./ S_barrier(:, 2));
 plot(T, phase, 'Color', 'blue');
 
 % (III) Phase in a new regime without dissipation
-t_new_regime = 250; % Look at the figure
+t_new_regime = 65; % Look at the figure
 new_alpha = alpha_dissip(t_new_regime, alpha, kappa);
 new_beta  = beta_dissip(t_new_regime, beta, kappa);
 
@@ -87,35 +85,46 @@ plot(T, phase, 'Color', 'red');
 
 % Legend
 legend( ...
[…]

### 2017-03-15 writing/phase_transition/phase_transition.tex
phase_transition: revision, nice potential picture

@@
 \affiliation{School of Physics and Astronomy, University of Southampton, SO17 1BJ Southampton, United Kingdom}
+\affiliation{Istituto CNR-SPIN, Viale del Politecnico 1, I-00133, Rome, Italy}
 
@@
 \begin{abstract}
-We consider the problem of achievement of quantum regime for relative phase of trapped in W -- potential low branch exciton polariton condensates taken at finite temperatures and finite polariton lifetime.
-Non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by complex potential energy landscapes (PEL) consisting of sets of barriers and wells is proposed.
-We have shown that the classical (thermal) activation and quantum tunneling for the phase represent two regimes depending on temperature, polariton condensate density and distance between the junctions.
-The transition between these two regimes exhibits universal features of first or second order phase transition (PT) depending on the PEL for the relative phase of two polariton condensates.
-In the presence of dissipation quantum system exhibits the non-equilibrium PT from quantum {\blue (where tunneling is possible)} to classical regime, where the tunelling is efficient and where it is suppressed, respectively.
+We consider finite temperature effects in a non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by a complex potential energy landscapes (PEL) consisting of sets of barriers and wells.
+We have shown that the transition between  thermal  activation (classical) and tunneling (quantum) regimes exhibits universal features of the first and second order phase transition (PT) depending on the PEL for two polariton condensates.
+In the presence of dissipation the relative phase of two condensates exhibits non-equilibrium PT from quantum regime characterized by efficient tunneling of polaritons to the regime of permanent Josephson or Rabi oscillations, where the tunneling is suppressed, respectively.
 The obtained results are discussed in details in the framework of the quantum annealing problem with exciton polariton condensates.
@@
 
-In the last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures represented an important mainstream of current photonic and semiconductor studies, see e.g.
+In the last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures became and important area of research in photonics and semiconductor physics, see e.g.
 \cite{Sanvitto, Guillet}.
-The microcavity exciton polaritons are bosonic quasiparticles representing  admixtures of the quantized cavity mode and quantum well excitons.
+Microcavity exciton polaritons are bosonic quasiparticles representing admixtures of quantized cavity photons mode and quantum well excitons.
 Semiconductor microcavities are promising for various optoelectronic applications where the quantum  matter-field interface plays crucial role.
-In particular, it is worth to mention demonstrations of a polariton laser with electrical injection pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
-Although exciton polariton condensates exhibit Bose-Einstein statistics  above the lasing threshold under the phase transition (PT) condition and macroscopic occupation of the ground state at certain pumping rate that is less than for convenient lasers, they are not in true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
-Non-equilibrium features of exciton polariton condensates play important role in various manifestations of their collective (many body) states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
+In particular, it is worth to mention experimental demonstrations of a polariton laser with electrical injection pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
+Although exciton polariton condensates exhibit the Bose-Einstein statistics above the lasing threshold and are characterized by a macroscopic occupation of the ground state at certain pumping rate that is less than the threshold pumping for convenient lasers, they are not in a true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
+Non-equilibrium features of exciton polariton condensates play an important role in various manifestations of their collective (many body) states such as superfluidity \cite{Carusotto_2013,Amo_2009}, quantized vortices \cite{Lagoudakis_2008,Lagoudakis_2009}, soliton formation \cite{Sich}, Josephson oscillations and macroscopic self-trapping \cite{Abbarchi,Lagoudakis_2010}.
 
 Recently Yongbao Sun et al, in Ref.
-\cite{Snoke_2017} reported observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity possessing very a comparatively very long photon lifetime of $135ps$.
+\cite{Snoke_2017} reported the observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity possessing a comparatively very long photon lifetime of $135ps$.
 Notably, exciton polaritons with long lifetime are promising candidates for quantum technologies, cf.
 \cite{Demirchyan}.
-However, since exciton polariton BEC's in present experiments are observed at high enough (up to the room) temperatures the quantum properties of such a states should be examined even at full thermal equilibrium.
+However, since exciton polariton BEC's in present experiments are observed at high enough temperatures the quantum properties of such a states should be examined even at full thermal equilibrium.
 
-The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates behavior is very actual for their practical applications and especially for their possible applications in quantum information technologies, see e.g.
+The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates is very important for their possible applications in quantum information technologies, see e.g.
 \cite{Dominici}.
@@
 
-Especially it is important to stress here quantum annealing problem physically based on the searching algorithm for the global minimum of a potential energy landscape (PEL) consisting of a set of barriers and wells, see e.g.
+Especially, it is important to emphasize here quantum annealing problem physically based on the searching algorithm for the global minimum of a potential energy landscape (PEL) consisting of a set of barriers and wells, see e.g.
 \cite{Santoro, Das}.
-In purely classical  (thermal) regime the {bosonic quasipartcles cross barriers stochastically} at finite temperature with the help of thermal activation process if the thermal energy is enough.
+In a purely classical  (thermal) regime the {bosonic quasipartcles cross barriers stochastically} at finite temperature with the help of thermal activation process if the thermal energy is large enough.
 Contrary, in a quantum limit the same system undergoes quantum tunneling through the barrier.
@@
 
-In the paper we consider a generic problem of quantum-classical phase transition (PT) with exciton polariton condensates formed in a semiconductor microcavity in the presence of Josephson effect, cf.
-\cite{Chudnovsky_1997,Aleiner, Shelykh_2008, Borgh_2010}.
-To be more specific we examine simply a two junction model.
+In this paper we consider theoretically the finite temperature effects for exciton polariton condensates formed in a semiconductor microcavity in the presence of the Josephson effect, cf.
+\cite{Aleiner, Shelykh_2008, Borgh_2010}.
+In particular, we are interesting in generic problem of quantum-classical phase transition (PT) explicitly examined for a two junction model \cite{Chudnovsky_1997}.
 
-In general this problem relates to dissipative tunneling problem or, tunneling at finite (non-zero) temperatures, cf. \cite{Caldeira, Larkin, Riseborough}.
-Traditionally,  studies in this field are limited by consideration of superconductor devices \cite{Ankerhold} where macroscopic quantum tunneling phenomena plays essential role.
+In general, this problem is related to the dissipative tunneling problem or tunneling at finite (non-zero) temperatures, cf. \cite{Caldeira, Larkin, Riseborough}.
+Traditionally,  studies in this field are limited by consideration of superconductor devices \cite{Ankerhold} where macroscopic quantum tunneling phenomena plays an essential role.
 In particular, it is worth to mention here the Schr\"odinger cat state formation \cite{Leggett} and the 	design of quantum gates with superconductor qubits for quantum computing where a macroscopic quantum coherence for the phase is important \cite{Makhlin}.
-Recently the problem of quantum tunneling and quantum-classical PT problem have been examined for other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
+Recently, the problem of quantum tunneling and quantum-classical PT problem have been examined for other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
 
-In the paper we consider an \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes into the tunneling parameter matrix elements, cf.
+In the paper we consider an \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes to the tunneling parameter matrix elements, cf.
 \cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
 In particularly, we pay attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
-We aimed at formulating necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for realisation of quantum annealing purposes and creation of exciton polariton qubit gates.
+We aimed at formulating necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for realisation of quantum annealing algorythms and creation of exciton polariton qubit gates.
 
-This paper is arranged as follows.
+This paper is organised as follows.
 In Sec.
 \ref{sec:quantum_phase} we introduce the quantum phase model for extended model of EPJJ of the coupled condensates and discuss various regimes for it at zero temperature and infinite exciton polariton lifetime.
-Section \ref{sec:quantum_classical} establishes  results obtained for quantum-classical PT problem and considered for quantum phase  at finite temperatures.
-The influence of non-equilibrium effects with microcavity exciton polaritons possessing finite lifetime is discussed in \ref{sec:non-equilibrium}.
-In Conclusion we summarize the results obtained.
-In Appendix \ref{sec:model} we explain in details  extended model of EPJJ within the tight-binding approach. 
+Section \ref{sec:quantum_classical} presents the results obtained for a quantum-classical PT problem and addresses the quantum phase at finite temperatures.
+The influence of non-equilibrium effects with microcavity exciton polaritons possessing a finite lifetime is discussed in \ref{sec:non-equilibrium}.      
+In Conclusion, we summarize the obtained results.
+In the Appendix \ref{sec:model} we explain in details  extended model of EPJJ within the tight-binding approximation.
+
 \section{The Quantum Phase Model \label{sec:quantum_phase}}
 
-We start with the Hamiltonain 
+{\red
+
+We consider a system of two exciton-polariton condensates localised in lateral potential traps in a planar semiconductor microcavity.
+The condensates are separated by a potential barrier $U(x)$.
+Polaritons are pumped to the condensates from a reservoir of incoherent excitons.
+They decay radiatively.
+We account for the repulsive intereaction between exciton-polaritons.
+The finite temperature of the polariton gas is accounted for in the thermal equilibrium approximation.
+We use two-mode representation of the $\hat{\psi}$ - operator that describe the behaviour of the condensates:
 %
 \begin{equation}
-\hat{H} = \alpha \hat{S}_z^2 + \beta \hat{S}_x^2 - B \hat{S}_x.
+\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x).
+\end{equation}
+%
+Here $\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}$ where $\Phi_{\pm}(x)$ are symmetric and antisymmetric real wavefuntions obeying the stationary Gross-Pitaevsky equation $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$.
+
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/potential_picture.eps}}
+\caption{ \dots \label{pic:potential_picture}}
+\end{figure}
+%
+
+We can express the Hamiltonian of such systems in terms of pseudo-spin operators as follows:
+%
+\begin{equation}
+\hat{H} = \alpha \hat{S}_z^2 + \beta \hat{S}_x^2 - B \hat{S}_x
 \label{eq:hamiltonian_spin}
 \end{equation}
-that characterize weakly interacting exciton polariton condensate Josephson junction device in terms of pseudo-spin operators $\hat{S}_i$, $i=x,y,z$.
-The parameters $\alpha$, $\beta$ and $B$ reflect  Josephson junction properties and determined in Appendix \ref{sec:model}. 
+Is characterizes a weakly interacting exciton polariton condensate Josephson junction device.
+The parameters $\alpha = 2 \gamma_{+-}$, $\beta = \dfrac{\gamma_{++} + \gamma_{--} - 2 \gamma_{+-}}{2}$ and $B = \mu_- - \mu_+$, $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$ reflect Josephson junction properties, see Appendix \ref{sec:model} for details.
+}
 Here we propose quantum mechanical approach to the EPJJ  phase recasting pseudo-spin operators in  (\ref{eq:hamiltonian_spin}) through the differential representation defined as
@@
  obey familiar $SU(2)$ algebra commutation relations $[\hat{S}_i, \hat{S}_j] = i\epsilon_{ijk}\hat{S}_k,  i,j,k=x,y,z$.
-After straitforward calculations from (\ref{eq:hamiltonian_spin}) one can obtain
+After straightforward calculations from (\ref{eq:hamiltonian_spin}) one can obtain
 %
@@
 %
-We also assume macroscopically large particle number, i.e. the $s = N/2 >> 1$ is C - number. Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain   
+We also assume macroscopically large number of particles, i.e. the $s = N/2 >> 1$ is C - number. Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain   
 %
@@
 where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{G}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role for our model.
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{B}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role for our model.
 Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to Schr\"odinger-like equation
@@
 %
-
 Analysis of the quantum phase can be performed  in three domains determined by vital $\Lambda$--parameter values, cf. \cite{Anglin}.
@@
 \ref{phase_potential}b  inherent to  Josephson regime.
-We examine thermodynamically equilibrium (with infinitely large  exciton polariton lifetime) system of exciton polaritons at finite temperature $T$.
+We examine thermodynamically equilibrium  system of exciton polaritons at finite temperature $T$ that is the system with infinitely large  exciton polariton lifetime.
 Noticing, that in  recent experiments  described in Ref.
-\cite{Snoke_2017} polariton lifetime attains  $275ps$ at resonance that seems to be enough to justify the quantum processes described below.
+\cite{Snoke_2017} polariton lifetime attains  $275ps$ at resonance that seems to be enough to justify the equilibrium  processes described below.
 
@@
 This process inherent to classical (thermal) annealing problem \cite{Das}.
-
 In the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with vanishing rate, that is important especially for quantum annealing scheme. 
@@
 Let us briefly discuss observation feasibility of quantum-classical PT for exciton polariton BEC's obtained in experiments.
-In particular, for experimentally accessible polariton interaction strength $\alpha N=0.6meV$, given for narrow-band semiconductor samples, the  $T_{0}$ is about $1.2K$ that is comparable with typical temperature of condensation, or, with temperature of Berezinsky-Kosterlitz-Thouless PT considered for dilute weakly interacting exciton polariton gas being at thermal equilibrium,cf.
+In particular, for experimentally accessible polariton interaction strength $\alpha N=0.6meV$, given for narrow-band semiconductor samples, the  $T_{0}$ is about $1.2K$ that corresponds to to thermon effective lifetime  $\tau_{0}=3.5ps$.
+The value of $T_{0}$ is comparable with typical temperature of condensation, or, with temperature of Berezinsky-Kosterlitz-Thouless PT considered for dilute weakly interacting exciton polariton gas being at thermal equilibrium,cf.
 \cite{Sanvitto,Guillet}.
@@
 
-In order,  characteristic  temperature $T_{0}=1.2K$ corresponds to thermon effective lifetime  $\tau_{0}=3.5ps$ for estimations given above.
+In order,  condition (\ref{eq:lifetime}) is fulfilled in [19].
 Here we examine situation when exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
 Namely  this situation is realized in most of current experiments with non-equilibrium exciton polariton condensates, see e.g.
-[   ].
+[1,2, 16-18].
 
-Below we consider the influence of the dissipation to  EPJJ quantum phase properties in adiabatic limit, cf. \cite{Sols}.
+To be more specific we consider the influence of the dissipation to  EPJJ quantum phase properties in adiabatic limit, cf. \cite{Sols}.
 We start from GP equations obtained from  (\ref{eq:hamiltonian}) for mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$  at $\Gamma = 0$ ($B = G$),  which reads as 
@@
 In (\ref{eq:GP}) we introduced dissipation  term with $\kappa \simeq \hbar/\tau_{pol}$.
-Defining new variables $\Psi_{1,2}$ by using  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\eqref{eq:pseudo_spin}) from {\ref{eq:GP}} we obtain
+Defining new variables $\Psi_{1,2}$ as  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\eqref{eq:pseudo_spin}) from (\ref{eq:GP}) we obtain
 %
@@
 \begin{array}{lcl}
-\dot{S}_z & = &  2 \beta'(t) S_x S_y - S_y; \\
 \dot{S}_x & = & -2 \alpha'(t) S_z S_y; \\
-\dot{S}_y & = & 2(\alpha'(t) - \beta'(t)) S_z S_x + S_z.
+\dot{S}_y & = & 2(\alpha'(t) - \beta'(t)) S_z S_x + S_z. \\
+\dot{S}_z & = &  2 \beta'(t) S_x S_y - S_y;
 \end{array}
@@
 Here we explore the dimensionless time $t' = t B / \hbar$.
-This system describe dynamics of normalized mean field pseudo-spin parameters on the Bloch sphere with $S_x^2 + S_y^2 + S_z^2 = 1$.
-Now set of Eqs.\ ({\ref{eq:pseudo-spin}}) looks similar to one taken for non-dissipative system but with time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa t')$, cf.\cite{Sedov}.
+
+Set of Eqs.\ ({\ref{eq:pseudo-spin}}) discrebes dynamics of normalized mean field pseudo-spin parameters on the Bloch sphere with $S_x^2 + S_y^2 + S_z^2 = 1$.
+Equations  \ ({\ref{eq:pseudo-spin}}) looks similar to one taken for non-dissipative system but with time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa' t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa' t')$, $\kappa' = \kappa / B$, cf.\cite{Sedov}.
 Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to solid black curve in Fig.1b.
@@
 In Fig.
-\ref{pic:phase}a we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function of time.
-Non-dissipative system has two different regimes depending on the values of  $\beta$ -- parameter, that is blue and red curves in the Fig.
+\ref{pic:phase}a we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function on time.
+Non-dissipative system has two different regimes depending on the values of  $\beta$ -- parameter, that is blue  (labeled as 1) and red (labeled as 3) curves in the Fig.
 \ref{pic:phase}, respectively.
-Blue  curve is plotted under the condition $\beta' > 1/2$ and  corresponds to the existence of barrier for potential energy -- see Fig.
+Blue  curve is plotted under the condition $\beta' > 1/2$ and  corresponds to the quantum regime with existence of barrier for potential energy -- see Fig.
 \ref{pic:phase}b.
-Contrary,  red curve establishes phase properties below the threshold ($\beta' <1/2$) that corresponds to the absence of the barrier.
+Contrary,  red curve establishes phase properties below the threshold ($\beta' <1/2$) that corresponds to the absence of the barrier but upon the same temperature.
 
-In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}a) phase of EPJJ starts from one of potential  minimum. It evolves adiabatically and then  crosses the critical value 1/2
-due to decreasing of total number of particles. 
+In the presence of dissipation (solid black curve in Fig.
+\ref{pic:phase}a) phase of EPJJ starts from one of potential  minimum.
+We suppose that the temperature of the system is not sufficient for thermal activation and quantum tunneling is possible.
+Then, the system evolves adiabatically and then  crosses the critical value 1/2
+due to decreasing of total number of particles. The final (temporal) state represents Josephson or, Rabi oscillation regime.
 %It can be transformed to the equation on the phase difference $\phi$ and $S_z$ as follows
@@
 
-The Fig. \ref{pic:phase}c exhibits suppression of critical temperature of phase transition $T_{c}^{(2)}$ that occurs at the timepoint $t_0=...$ for  $\tau_{pol} \sim \hbar/\kappa= 10 ps$.
+Figures \ref{pic:phase}b and \ref{pic:phase}c  exhibits suppression of of $W$--like potential and relevant enhancement of reduced thermon period $\tau_{p} / \tau_0$ which occur  at timepoint $t_0 = 11.5 ps$ for  $\tau_{pol} \sim \hbar/\kappa= 10 ps$, respectively.
 
-Physically, behavior of the phase in the presence of dissipation showed in Fig.
+Thus, behavior of the phase in the presence of dissipation showed in Fig.
 \ref{pic:phase} establishes non-equilibrium PT from regime where tunneling is possible to the regime where tunneling is suppressed.
 However, this regime happening at $t>t_0$ cannot be interpreted immediately as classical one.
-
 Actually, adiabaticity condition reads, cf. {\cite{Sols}:
@@
 %
-where $\omega(t) = \sqrt{(B - 2\beta(t))(B - 2 \beta(t) + 2 \alpha(t))}$ is small amplitude oscillations slowly depending on time. 
+where $\omega(t) = B \sqrt{(1 - 2 \beta'(t))(1 - 2 \beta'(t) + 2 \alpha'(t))}/ \hbar $ is small amplitude oscillations slowly depending on time, cf. {\cite{Sedov}. 
 %It allows us to reduce linear system to the harmonic oscillator equaiton with slowly evolving frequency:
@@
 where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$. At large enough times 
-$\omega(t) \approx$ $B$  and permanent-like temporal oscillations for the Josephson junction phase $\phi$ are occurs, see Fig.
-5a and cf.
-[   ].
-To determine quantum (or, classical) character of this oscillations quantum fluctuations should be examined.
+$\omega(t) \approx$ $B/ \hbar $  and permanent Rabi  oscillations for the Josephson junction phase $\phi$ are established, see Fig.
+5a and cf.{\cite{Permamemt}.
+To determine quantum (or, classical) character of this oscillations purely quantum approache to the problem should be considered.
 
@@
 \ref{pic:phase}.
-In this case permanent oscillations of Josephson junction phase occurs within adiabatic approach.
+In this case permanent Rabi  oscillations of Josephson junction phase occurs within adiabatic approach.
 To determine quantum either classical properties of this oscillations it is necessary to study fluctuations of the exciton polariton system beyond the semiclassical approach represented in Sec.\ref{sec:non-equilibrium}}.
@@
 \label{sec:acknowledgement}}
-We  acknowledge financial support from RFBR, Grants No. 15-52-52001 and No. 14-
-02-97503.
+We acknowledge financial support from RFBR, Grants No. 15-52-52001 and No. 14-02-97503.
+A. Kavokin acknowledges the support from HORIZON 2020 RISE project CoExAn (Grant No. 644076).
 
 \appendix
-\section{THE MODEL OF EPJJ \label{sec:model}}
+\section{EXTENDED  MODEL OF EPJJ \label{sec:model}}
 
@@
 %
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii (GP) equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
 %

### 2017-03-15 phase_transition/preparing_paper.m

@@ -634,3 +634,38 @@ z_max = inv_cn(-2 * (1 - lambda) / Lambda, lambda);
 d1f = @(x) (Vb(x + eps) - Vb(x - eps)) / eps;
 d2f = @(x) (Vb(x + eps) - 2 * Vb(x) + Vb(x - eps)) / (eps^2);
 d3f = @(x) (Vb(x + 2 * eps) - 2 * Vb(x + eps) + 2 * Vb(x - eps) - Vb(x - 2 * eps)) / (2 * eps^2);
+
+%% Nice picture with potential
+clc; clear
+
+% f = @(x, y) (((x .^ 2) - 1) .^ 2) + ((y .^ 2) - 1) .^ 2;
+f = @(x, y) (((x .^ 2) - 1) .^ 2) + y .^ 2 + y .^ 4;
+% f = @(x, y) (((x .^ 2) - 1.2) .^ 2) - exp(0.5*y .^ 2);
+% f = @(x, y) (x .^ 2 + y .^ 2 - 1) .^ 2;
+
+x = -1.5:0.02:1.5;
+y = -0.8:0.02:0.8;
+
+[X, Y] = meshgrid(x, y);
+Z = f(X, Y);
+% Z(((abs(X) > 1) | (abs(Y) > 1)) & (Z > 1)) = 1;
+% Z(Z > 2) = 2;
+a = 1;
+Z(Z > a) = a;
+% Z((X + Y) < -1.3) = NaN;
+
+surf(X, Y, Z, 'EdgeColor','none');
+colormap cool
+grid off
+
+
+
+
+
+
+
+
+
+
+
+

### 2017-03-15 hegel/RK4.m
hegel: start working on project

@@ -1,0 +1,20 @@
+function [ T, Y ] = OdeSolver( ode, tspan, y0, N )
+
+n = length(y0);
+h = (tspan(2) - tspan(1)) / N;
+T = tspan(1):h:tspan(2);
+
+Y = zeros(N+1,n);
+k = zeros(4,n);
+
+Y(1,:) = y0;
+for i = 1:N
+	k(1,:) = h*ode(T(i), Y(i,:));
+	k(2,:) = h*ode(T(i) + h/2, Y(i,:) + 1/2 * k(1,:));
+	k(3,:) = h*ode(T(i) + h/2, Y(i,:) + 1/2 * k(2,:));
+	k(4,:) = h*ode(T(i) + h, Y(i,:) + k(3,:));
+	Y(i+1,:) = Y(i,:) + (1/6)*(k(1,:) + 2*k(2,:) + 2*k(3,:) + k(4,:));
+end
+
+end
+

### 2017-03-15 hegel/asympt.m

@@ -1,0 +1,11 @@
+function f = asympt( params, C, x )
+% Asymtotical behaviour on the -\infty
+%
+% INPUT:
+%	C - constant of the asymptote
+
+[omega, ~] = parse_params(params);
+
+f = C * (-x)^(0.5 * (omega - 1)) * exp(-(x^2) / 2);
+
+end

### 2017-03-15 hegel/asympt_diff.m

@@ -1,0 +1,7 @@
+function df = asympt_diff( params, C, x )
+
+eps = 1e-6;
+df = (asympt(params, C, x + eps) - asympt(params, C, x - eps)) / (2 * eps);
+
+end
+

### 2017-03-15 hegel/dichotomy.m

@@ -1,0 +1,16 @@
+function zero = dichotomy (func, a, b, eps)
+
+fa = func(a);
+while ((abs(b-a) / 2) >= eps)
+	c = (a + b) / 2;
+	fc = func(c);
+	if sign(fc) ~= sign(fa)
+		b = c;
+	else
+		a = c;
+		fa = fc;
+	end
+end
+zero = (a + b) / 2;
+
+end

### 2017-03-15 hegel/get_symmetric_mode.m

@@ -1,0 +1,19 @@
+function [ X, U ] = get_symmetric_mode( params, C, xspan )
+% Calculate a symmetric mode using the parameter C of the asymptotic 'asympt'
+%
+% INPUT:
+%
+
+xstart = xspan(1);
+
+init = [ asympt(params, C, xstart), asympt_diff(params, C, xstart) ];
+
+[X, U] = f_solve(params, xspan, init, 1024);
+
+X = [X -X(end-1:-1:1)];
+U = [
+	U(:, 1), U(:, 2);
+	U(end-1:-1:1, 1), -U(end-1:-1:1, 2)
+];
+
+end

### 2017-03-15 hegel/get_u_end.m

@@ -1,0 +1,11 @@
+function u_end = get_u_end( params, C, xspan )
+
+xstart = xspan(1);
+init = [asympt(params, C, xstart), asympt_diff(params, C, xstart)];
+
+[~, U] = f_solve(params, xspan, init, 1024);
+
+u_end = U(end, 1);
+
+end
+

### 2017-03-15 hegel/get_ux_end.m

@@ -1,0 +1,10 @@
+function ux_end = get_ux_end( params, C, xspan )
+
+xstart = xspan(1);
+init = [asympt(params, C, xstart), asympt_diff(params, C, xstart)];
+
+[~, U] = f_solve(params, xspan, init, 1024);
+
+ux_end = U(end, 2);
+
+end

### 2017-03-15 hegel/main.m

@@ -1,0 +1,111 @@
+%%
+clc; clear
+
+eps = 1e-6;
+omega = 4; Omega = 0.5;
+params = [omega Omega];
+
+intervals = 1024;
+ode_params = @(t, f) ode(t, f, params);
+
+psi_end = []; psi_diff_end = [];
+
+x0 = -10;
+
+C = 0;
+cstep = 0.01;
+
+while true
+	init = [asympt(params, C, x0) asympt_diff(params, C, x0)];
+	[T, Psi] = RK4(ode_params, [x0 0], init, intervals);
+	
+	if abs(Psi(end, 1)) > 10
+		break
+	else
+		fprintf('psi_end = %g\n', Psi(end, 1));
+		
+		psi_end = [psi_end Psi(end, 1)];
+		psi_diff_end = [psi_diff_end Psi(end, 2)];
+		
+		C = C + cstep;
+	end
+end
+
+%%
+% Branch with linear analog; \omega = 1.
+clc; clear
+
+omega = 0.99; Omega = 18;
+params = [omega Omega];
+xspan = [-10 0];
+
+get_psix_end_params = @(C) get_psix_end(params, C, xspan);
+
+c0 = 0.01;
+cstep = 0.5;
+psix_end_0 = get_psix_end_params(c0); 
+
+eps = 1e-6;
+
+while true
+	c1 = c0 + cstep;
+	psix_end_1 = get_psix_end_params(c1)
+	
+	if sign(psix_end_0) ~= sign(psix_end_1)
+		cmode = dichotomy(get_psix_end_params, c0, c1, eps);
+		break
+	else
+		c0 = c1;
+	end
+end
+
+[X, Psi] = get_symmetric_mode(params, cmode, xspan);
+plot(X, Psi)
+
+%%
+% Continue solution branch on the parameter \omega
+
+omega_shift = omega - 0.001;
+params_shift = [omega_shift, Omega];
+
+get_psix_end_params_shift = @(C) get_psix_end(params_shift, C, xspan);
+cmode_shift = newton( ...
+	get_psix_end_params_shift, ...
+	numerical_diff(get_psix_end_params, 1e-6), ...
+	cmode);
+
+%%
+% Let's look on our mode (\omega = 1) while varying the parmeter \omega
+
+for i = 1:100
+	omega
+	cmode
+	
+	omega_shift = omega - 0.01;
+	params_shift = [omega_shift, Omega];
+	
[…]

### 2017-03-15 hegel/mex/Solver.h

@@ -1,0 +1,83 @@
+#ifndef SOLVER_H_
+#define SOLVER_H_
+
+#include <cstring>
+#include <iostream>
+// #include <initializer_list>
+
+#include "Point.h"
+#include "Solution.h"
+#include "OdeProblem.h"
+
+namespace NR
+{
+
+//const double UPPER_BOUND = 10000000000000.0;
+const double UPPER_BOUND = 100000.0;
+	
+template <int dim>
+class Solver
+{
+public:
+	Solution<dim> Solve(OdeProblem<dim> OP, const int intCount)
+	//Solution<dim> Solve(OdeProblem<dim> OP, const double step)
+	{
+		Solution<dim> sol;
+		sol.nodesCount = intCount + 1;
+		/*
+		int intCount = floor((OP.tspan[1] - OP.tspan[0]) / step);
+		sol.nodesCount = intCount + 1;
+		sol.step = (OP.tspan[1] - OP.tspan[0]) / intCount; 
+		*/
+		sol.step = (OP.tspan[1] - OP.tspan[0]) / intCount;
+		sol.points = new Point<dim>[sol.nodesCount];
+		sol.isInfinit = false;
+		sol.points[0] = OP.Init;
+		sol.tspan = new double[2];
+		sol.tspan[0] = OP.tspan[0];
+		sol.tspan[1] = OP.tspan[1];
+
+		double t = sol.tspan[0];
+		double h = sol.step;
+		Point<dim> k[4];
+		for (int i = 0; i < intCount; i++)
+		{
+			k[0] = OP.f(t, sol.points[i]) * h;
+			k[1] = OP.f(t + 0.5 * h, sol.points[i] + k[0] * 0.5) * h;
+			k[2] = OP.f(t + 0.5 * h, sol.points[i] + k[1] * 0.5) * h;
+			k[3] = OP.f(t + h, sol.points[i] + k[2]) * h;
+
+			sol.points[i + 1] = sol.points[i] + (k[0] + k[1] * 2.0 + k[2] * 2.0 + k[3]) * (1.0 / 6.0);
+
+			if (sol.points[i + 1].abs() > UPPER_BOUND)
+			{
+				sol.isInfinit = true;
+				sol.tspan[1] = t;
+				sol.nodesCount = i;
+				return sol;
+			}
+			t += h;
+		}
+		return sol;
+	}
+};
+
+//class Timer
+/*{
+public:
[…]

### 2017-03-15 hegel/mex/functions.h

@@ -1,0 +1,22 @@
+#ifndef FUNCTIONS_H_
+#define FUNCTIONS_H_
+
+#include "Point.h"
+using namespace NR;
+
+// Lyuba Hegel task.
+// NLS with presence of quadratic linear potential and cosine nonlinear potential
+// Equation for nonlinear stationary modes
+// u_{xx} + (\omega - x^2) u - \cos{2 \Omega x} u^3 = 0
+// Parameters: [\omega \Omega]
+Point<2> hegel(double x, Point<2> u, double* param)
+{
+	Point<2> du;
+	double omega = param[0], Omega = param[1];
+	
+	du[0] = u[1];
+	du[1] = -(omega - pow(x, 2)) * u[0] + (cos(2 * Omega * x)) * pow(u[0], 3);
+	return du;
+}
+
+#endif

### 2017-03-15 hegel/newton.m

@@ -1,0 +1,21 @@
+function x_root = newton( f, df, x0 )
+%
+% INPUT:
+%	
+
+eps = 1e-6;
+
+while true
+	x1 = x0 - f(x0) / df(x0);
+	
+	if abs(x1 - x0) < eps
+		break
+	else
+		x0 = x1;
+	end
+end
+
+x_root = x1;
+
+end
+

### 2017-03-15 hegel/numerical_diff.m

@@ -1,0 +1,2 @@
+function df = numerical_diff( f, eps )
+df = @(x) (f(x + eps) - f(x - eps)) / (2 * eps);

### 2017-03-15 hegel/ode.m

@@ -1,0 +1,10 @@
+function df = ode( x, f, params )
+% Stationary modes for the GPR problem
+%
+% INPUT:
+%	
+
+[omega, Omega] = parse_params(params);
+df = [f(2), -(omega - x^2) * f(1) + cos(2 * Omega * x) * (f(1)^3) ];
+
+end

### 2017-03-15 hegel/parse_params.m

@@ -1,0 +1,14 @@
+function [ omega, Omega ] = parse_params( params )
+%
+% INPUT:
+%	params - 
+%
+% OUTPUT:
+%	omega - chemical potential (energy level);
+%	Omega - parameter of the nonlinear cosine potential: \cos(2 \Omega x)
+%
+
+omega = params(1); Omega = params(2);
+
+end
+

### 2017-03-15 hegel/test_f_solve.m

@@ -1,0 +1,36 @@
+%% Fidelity test
+clc; clear
+
+omega = 4; Omega = 0.5;
+params = [omega, Omega];
+xspan = [0 3];
+init = [0.1 0.1];
+
+intervals = 1024;
+
+figure; hold on; grid on
+
+% MATLAB solver RK4
+ode_params = @(t, f) ode(t, f, params);
+[X, U] = RK4(ode_params, xspan, init, intervals);
+
+plot(X, U(:, 1), 'Color', 'black', 'LineWidth', 2)
+
+% Low level C++ solver f_solve
+[X, U] = f_solve(params, xspan, init, intervals);
+
+plot(X, U(:, 1), 'Color', 'red')
+
+%% Speed-up test
+
+t_start = cputime;
+
+for i = 1:1000
+	% [~, ~] = RK4(ode_params, xspan, init, intervals);
+	[~, ~] = f_solve(params, xspan, init, intervals);
+end
+
+% t_elapsed_RK4 = cputime - t_start;
+t_elapsed_f_solve = cputime - t_start;
+
+% 200 times speed-up!

### 2017-03-17 hegel/CFDS.m
hegel: evolution, plotting, first results

@@ -1,0 +1,112 @@
+function [Grid, U, Norm] = CFDS( params, X0, U0 )
+% Solving the equation:
+% i \Psi_t = -\Psi_{xx} + x^2 \Psi + \cos(2 \Omega x) |\Psi|^2 \Psi
+
+% Accuracy of interation process
+eps = 1e-12;
+
+% Linear potential
+V = @(x) x .^ 2;
+
+% Nonlinear cosine potential parameter
+Omega = params(2);
+
+% Nonlinear cosine potential
+g = @(x) - cos(2 * Omega * x);
+
+xstep = 0.005;
+xspan = [-6 6];
+xgrid = xspan(1):xstep:xspan(2);
+Nx = length(xgrid);
+
+tstep = 0.01;
+tspan = [0 12];
+tgrid = tspan(1):tstep:tspan(2);
+Nt = length(tgrid);
+
+[Grid{1}, Grid{2}] = meshgrid(xgrid, tgrid);
+U = zeros(Nt, Nx);
+
+% Initial condition
+U(1, :) = resample(X0, U0, xgrid);
+
+% Perturbation
+a = 0.01;
+f = 10;
+U(1, :) = U(1, :) .* (1 + a * (1 + cos(f * xgrid)));
+
+U(1, 1) = 0;
+U(1, end) = 0;
+
+% figure
+% plot(U(1, :))
+
+% Norm of the solution
+Norm = zeros(1, Nt);
+Norm(1) = simpson(abs(U(1, :)) .^ 2, xstep);
+
+% TODO: add energy calculation
+
+% Prepare tridiagonal sparse linear operator: Lv = F(v, v')
+	
+% -1 diagonal
+Ljm1 = 0.5 / (xstep ^ 2) * ones(1, Nx - 2);
+Ljm1 = [Ljm1 0];
+	
+% +1 diagonal
+Ljp1 = 0.5 / (xstep ^ 2) * ones(1, Nx - 2);
+Ljp1 = [0 Ljp1];
+
+
+Dissip = 1i * dissipation(xgrid);
+
+for i = 2:Nt
+	% 0 diagonal
+	Lj = 1i / tstep - 1 / (xstep ^ 2) - 0.5 * (V(xgrid) - 0.5 * g(xgrid) .* (abs(U(i - 1, :)) .^ 2));
+	L = diag(Lj) + diag(Dissip) + diag(Ljm1, -1) + diag(Ljp1, +1);
[…]

### 2017-03-17 hegel/asympt.m

@@ -1,11 +1,0 @@
-function f = asympt( params, C, x )
-% Asymtotical behaviour on the -\infty
-%
-% INPUT:
-%	C - constant of the asymptote
-
-[omega, ~] = parse_params(params);
-
-f = C * (-x)^(0.5 * (omega - 1)) * exp(-(x^2) / 2);
-
-end

### 2017-03-17 hegel/dissipation.m

@@ -1,0 +1,17 @@
+function d = dissipation(xgrid)
+
+dissip_stength = 100;
+
+l = 0.1 * (xgrid(end) - xgrid(1));
+L = xgrid(end);
+
+d = zeros(1, length(xgrid));
+
+sel = (xgrid > (L - l));
+d(sel) = dissip_stength * ((xgrid(sel) - (L - l)) .^ 2);
+
+sel = (xgrid < (-L + l));
+d(sel) = dissip_stength * ((xgrid(sel) + (L - l)) .^ 2);
+
+end
+

### 2017-03-17 hegel/full_scanning.m

@@ -1,0 +1,54 @@
+%% Full scanning
+clc; clear
+
+omega = -5:0.1:5;
+Omega = 1.5;
+params = [4 Omega];
+xspan = [-6 6];
+
+cstep = 0.1;
+cstart = 1.6;
+cend = 2; 
+
+% Dichotomy accuracy
+eps = 1e-6;
+
+% Target function
+get_ux_end_params = @(C) get_ux_end(params, C, xspan);
+
+N = 1000;
+
+C = linspace(0, 5, N);
+ux_end = zeros(1, N);
+
+for i = 1:length(C)
+	ux_end(i) = get_ux_end_params(C(i));
+end
+
+plot(C, ux_end);
+
+%%
+cmode = dichotomy(get_ux_end_params, 1.8, 2, eps);
+[X, U] = get_mode(params, cmode, xspan);
+plot(X, U);
+
+%%
+c0 = cstart;
+
+ux0 = get_ux_end_params(c0)
+
+for i = 1:200
+	c1 = c0 + cstep;
+	ux1 = get_ux_end_params(c1)
+	
+	if sign(ux0) ~= sign(ux1)
+		cmode = dichotomy(get_ux_end_params, c0, c1, eps);
+		break
+	else
+		c0 = c1;
+		ux0 = ux1;
+	end
+end
+
+[X, U] = get_mode(params, cmode, xspan);
+plot(X, U);

### 2017-03-17 hegel/get_mode.m

@@ -1,4 +1,4 @@
-function difference = asympt_diff( params, C, xspan )
+function [ X, U ] = get_mode( params, C, xspan )
 
 xleft = xspan(1);
 xright = xspan(2);
@@ -9,20 +9,19 @@ eps = 1e-6;
 init_left = [asympt_left(params, C, xleft)
 	(asympt_left(params, C, xleft + eps) - asympt_left(params, C, xleft - eps)) / (2 * eps)];
 
-[~, U] = f_solve(params, [xleft 0], init_left, intervals);
-
-u_left = U(end, 1);
-ux_left = U(end, 2);
+[X_left, U_left] = f_solve(params, [xleft 0], init_left, intervals);
 
 init_right = [asympt_right(params, C, xright)
 	(asympt_right(params, C, xright + eps) - asympt_right(params, C, xright - eps)) / (2 * eps)];
 
-[~, U] = f_solve(params, [xright 0], init_right, intervals);
+[X_right, U_right] = f_solve(params, [xright 0], init_right, intervals);
 
-u_right = U(end, 1);
-ux_right = U(end, 2);
+X = [X_left; X_right(end-1:-1:1)];
 
-difference = norm([u_left ux_left] - [u_right ux_right]);
+U = [
+	U_left(:, 1), U_left(:, 2);
+	U_right(end-1:-1:1, 1), U_right(end-1:-1:1, 2)
+];
 
 end
 

### 2017-03-17 hegel/get_norm.m

@@ -1,0 +1,5 @@
+function Norm = get_norm(X, U)
+dx = X(2) - X(1);
+Norm = simpson(U(:, 1) .^ 2, dx);
+end
+

### 2017-03-17 hegel/get_spectrum.m

@@ -1,0 +1,52 @@
+function eigenvalues = get_spectrum( params, X, U, N )
+
+% TODO Symmetrize with respect to the horizontal axis
+
+% Stability of localized nonlinear modes
+% Here we use Jianke Yang method
+
+% INPUT:
+% :params: parameter of NLS with nonlinear potential (see info.txt)
+% :X: grid
+% :U: values on grid
+% :N: number of harmonics in fourie series
+
+% OUTPUT:
+% :eigenvalues: eigen values of differential operator, that correspon to
+%	the evolution of perturbations
+
+period = abs(X(end) - X(1));
+xstep = X(2) - X(1);
+
+% Wavenumber
+k = 2*pi / period;
+
+G{1} = params(1) - (X .^ 2) + f_potential(params, X) .* (U(:, 1).^2);
+G{2} = params(1) - (X .^ 2) + 3*f_potential(params, X) .* (U(:, 1).^2);
+
+for n = -N:N
+	Gf{1}(n+N+1) = (1 / period) * simpson(G{1} .* exp(-1i * k*n*X), xstep);
+	Gf{2}(n+N+1) = (1 / period) * simpson(G{2} .* exp(-1i * k*n*X), xstep);
+end
+
+% Big Gf{:}(end) values indicate bad convergence of the Fourie series
+fprintf('Spectrum localization: Gf(end) = %g, %g\n', Gf{1}(end), Gf{2}(end));
+
+D = -k^2 * (diag(-N:N) .^ 2);
+
+Gt{1} = toeplitz([Gf{1}(N+1:2*N+1) zeros(1, N)],...
+					  [Gf{1}(N+1:-1:1)  zeros(1, N)]);
+Gt{2} = toeplitz([Gf{2}(N+1:2*N+1) zeros(1 ,N)],...
+					  [Gf{2}(N+1:-1:1)  zeros(1 ,N)]);
+
+M = (D + Gt{2}) * (D + Gt{1});
+
+eigenvalues = sqrt(-eig(M));
+eigenvalues = [eigenvalues; -eigenvalues];
+
+end
+
+% ------------------------------------------------------------------------
+function potential = f_potential(params, x)
+potential = - cos(2 * params(2) * x);
+end

### 2017-03-17 hegel/get_symmetric_mode.m

@@ -6,11 +6,11 @@ function [ X, U ] = get_symmetric_mode( params, C, xspan )
 
 xstart = xspan(1);
 
-init = [ asympt(params, C, xstart), asympt_diff(params, C, xstart) ];
+init = asympt_left(params, C, xstart);
 
-[X, U] = f_solve(params, xspan, init, 1024);
+[X, U] = f_solve(params, xspan, init, 2 ^ 10);
 
-X = [X -X(end-1:-1:1)];
+X = [X; -X(end-1:-1:1)];
 U = [
 	U(:, 1), U(:, 2);
 	U(end-1:-1:1, 1), -U(end-1:-1:1, 2)

### 2017-03-17 hegel/get_u_end.m

@@ -1,9 +1,11 @@
 function u_end = get_u_end( params, C, xspan )
 
-xstart = xspan(1);
-init = [asympt(params, C, xstart), asympt_diff(params, C, xstart)];
+eps = 1e-6;
 
-[~, U] = f_solve(params, xspan, init, 1024);
+xstart = xspan(1);
+init = asympt_left(params, C, xstart);
+
+[~, U] = f_solve(params, xspan, init, 2 ^ 12);
 
 u_end = U(end, 1);
 

### 2017-03-17 hegel/get_ux_end.m

@@ -1,9 +1,9 @@
 function ux_end = get_ux_end( params, C, xspan )
 
 xstart = xspan(1);
-init = [asympt(params, C, xstart), asympt_diff(params, C, xstart)];
+init = asympt_left(params, C, xstart);
 
-[~, U] = f_solve(params, xspan, init, 1024);
+[~, U] = f_solve(params, xspan, init, 2 ^ 12);
 
 ux_end = U(end, 2);
 

### 2017-03-17 hegel/main.m

@@ -32,74 +32,79 @@ while true
 end
 
 %%
-% Branch with linear analog; \omega = 1.
 clc; clear
 
-omega = 0.99; Omega = 18;
+omega = 2.9; Omega = 10;
 params = [omega Omega];
-xspan = [-10 0];
+xspan = [-8 0];
 
-get_psix_end_params = @(C) get_psix_end(params, C, xspan);
+get_ux_end_params = @(C) get_ux_end(params, C, xspan);
 
 c0 = 0.01;
 cstep = 0.5;
-psix_end_0 = get_psix_end_params(c0); 
+ux_end_0 = get_ux_end_params(c0);
 
 eps = 1e-6;
 
 while true
 	c1 = c0 + cstep;
-	psix_end_1 = get_psix_end_params(c1)
-	
-	if sign(psix_end_0) ~= sign(psix_end_1)
-		cmode = dichotomy(get_psix_end_params, c0, c1, eps);
+	ux_end_1 = get_ux_end_params(c1);
+		
+	if sign(ux_end_0) ~= sign(ux_end_1)
+		cmode = dichotomy(get_ux_end_params, c0, c1, eps);
 		break
 	else
 		c0 = c1;
+		ux_end_0 = ux_end_1;
 	end
 end
 
-[X, Psi] = get_symmetric_mode(params, cmode, xspan);
-plot(X, Psi)
+[X, U] = get_symmetric_mode(params, cmode, xspan);
+figure
+subplot(1,2,1)
+plot_mode(params, X, U)
 
 %%
-% Continue solution branch on the parameter \omega
+eigs = get_spectrum(params, X, U, 256);
+subplot(1,2,2);
+plot_spectrum(params, eigs);
 
-omega_shift = omega - 0.001;
-params_shift = [omega_shift, Omega];
+%%
+[Grid, U, Norm] = CFDS(params, X, U(:, 1));
 
-get_psix_end_params_shift = @(C) get_psix_end(params_shift, C, xspan);
-cmode_shift = newton( ...
-	get_psix_end_params_shift, ...
-	numerical_diff(get_psix_end_params, 1e-6), ...
-	cmode);
+%%
+N = 1000;
+C = linspace(0, 6, N);
+
+ux_end = zeros(1, N);
+
+for i = 1:N
+	ux_end(i) = get_ux_end_params(C(i));
+end
+
+plot(C, ux_end);
 
 %%
[…]

### 2017-03-17 hegel/newton.m

@@ -1,9 +1,11 @@
-function x_root = newton( f, df, x0 )
+function x_root = newton( f, x0 )
 %
 % INPUT:
 %	
 
 eps = 1e-6;
+
+df = @(x) (f(x + eps) - f(x - eps)) / (2 * eps);
 
 while true
 	x1 = x0 - f(x0) / df(x0);

### 2017-03-17 hegel/plot_evolution.m

@@ -1,0 +1,17 @@
+function plot_evolution( params, Grid, U )
+
+xrange = [-5 5];
+X = Grid{1}(1, :);
+T = Grid{2}(:, 1);
+
+sel = ((X > xrange(1)) & (X < xrange(2)));
+
+image([xrange(1) xrange(2)], [T(1) T(end)], abs(U(:, sel)), 'CDataMapping', 'scaled')
+set(gca,'YDir','normal');
+xlabel('X')
+ylabel('T')
+title_str = sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2));
+title(title_str)
+
+end
+

### 2017-03-17 hegel/plot_mode.m

@@ -1,0 +1,27 @@
+function plot_mode( params, X, U )
+
+% INPUT:
+% :params: parameter of NLS with nonlinear potential (see info.txt)
+% :X: grid
+% :U: values on grid
+
+% figure
+hold on
+
+umax = max(U(:, 1));
+umin = min(U(:, 1));
+
+%line([-2*pi:pi:2*pi; -2*pi:pi:2*pi],...
+%	  [repmat(-2*abs(umin), 1, 5); repmat(2*abs(umax), 1, 5)],...
+%	  'Color', 'r', 'LineWidth', 1)
+
+plot(X, U(:, 1), '-k', 'LineWidth', 2)
+
+xlim([-2*pi, 2*pi])
+ylim([1.2 * umin, 1.2 * umax])
+
+title(sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2)))
+grid on
+hold off
+end
+

### 2017-03-17 hegel/plot_spectrum.m

@@ -1,0 +1,33 @@
+function plot_spectrum( params, eigenvalues )
+
+% INPUT:
+% :params: parameter of NLS with nonlinear potential (see info.txt)
+% :eigenvalues: eigen values of differential operator, that correspon to
+%	the evolution of perturbations
+
+% figure
+hold on
+
+% Continuous spectrum
+% line([0 0], [ params(1)  100], 'Color', 'r', 'LineWidth', 2)
+% line([0 0], [-params(1) -100], 'Color', 'r', 'LineWidth', 2)
+
+% Discrete eigenvalues
+plot(eigenvalues, 'o', 'MarkerFaceColor', 'k', 'MarkerSize', 5)
+
+% Axis boundaries
+xmax = max(1, 1.2 * max(real(eigenvalues)));
+ymax = 1.2 * max(imag(eigenvalues(real(eigenvalues) > 1e-5)));
+
+if ~isempty(ymax)
+	ymax = max(15, ymax);
+else
+	ymax = 15;
+end
+
+axis([-xmax xmax -ymax ymax])
+title(sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2)))
+grid on
+
+end
+

### 2017-03-17 hegel/simpson.m

@@ -1,0 +1,3 @@
+function q = simpson( f, dx )
+q = (dx / 3) * sum(f(1:2:end-2) + 4*f(2:2:end-1) + f(3:2:end));
+

### 2017-03-29 writing/phase_transition/phase_transition.tex
Work in progress

@@
 \begin{abstract}
-We consider finite temperature effects in a non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by a complex potential energy landscapes (PEL) consisting of sets of barriers and wells.
-We have shown that the transition between  thermal  activation (classical) and tunneling (quantum) regimes exhibits universal features of the first and second order phase transition (PT) depending on the PEL for two polariton condensates.
-In the presence of dissipation the relative phase of two condensates exhibits non-equilibrium PT from quantum regime characterized by efficient tunneling of polaritons to the regime of permanent Josephson or Rabi oscillations, where the tunneling is suppressed, respectively.
-The obtained results are discussed in details in the framework of the quantum annealing problem with exciton polariton condensates.
+We consider finite temperature effects in a non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by complicated potential energy landscapes (PEL) consisting of sets of barriers and wells.
+We show that the transition between  thermal  activation (classical) and tunneling (quantum) regimes exhibits universal features of the first and second order phase transition (PT) depending on the PEL for two polariton condensates.
+In the presence of dissipation the relative phase of two condensates exhibits non-equilibrium PT from the quantum regime characterized by efficient tunneling of polaritons to the regime of permanent Josephson or Rabi oscillations, where the tunneling is suppressed, respectively.
+This analysis paves way for the application of coupled polariton condensates for the realisation of a quantum annealing algorithm.
 
@@
 
-In the last decade investigations of exciton polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures became and important area of research in photonics and semiconductor physics, see e.g.
+In the XXI century, the studies of exciton-polariton Bose-Einstein condensates (BEC) in various type of semiconductor microstructures have become an important area of research in photonics and semiconductor physics, see e.g.
 \cite{Sanvitto, Guillet}.
-Microcavity exciton polaritons are bosonic quasiparticles representing admixtures of quantized cavity photons mode and quantum well excitons.
-Semiconductor microcavities are promising for various optoelectronic applications where the quantum  matter-field interface plays crucial role.
-In particular, it is worth to mention experimental demonstrations of a polariton laser with electrical injection pump \cite{Bhattacharya,Schneider}, amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
+Microcavity exciton polaritons are bosonic quasiparticles representing admixtures of quantized cavity photons and quantum well excitons.
+Semiconductor microcavities are promising for various optoelectronic applications where the quantum  matter-field interface plays a crucial role.
+In particular, it is worth to mention experimental demonstrations of polariton lasers with electrical injection \cite{Bhattacharya,Schneider}, polariton amplifiers \cite{Niemietz}, switches \cite{Amo_2010}, transistors \cite{Ballarini}, polariton circuits and optical logic elements \cite{Sturm,Liew}.
 Although exciton polariton condensates exhibit the Bose-Einstein statistics above the lasing threshold and are characterized by a macroscopic occupation of the ground state at certain pumping rate that is less than the threshold pumping for convenient lasers, they are not in a true thermodynamic equilibrium state \cite{Byrnes_2014,Sun}.
@@
 
-Recently Yongbao Sun et al, in Ref.
-\cite{Snoke_2017} reported the observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity possessing a comparatively very long photon lifetime of $135ps$.
-Notably, exciton polaritons with long lifetime are promising candidates for quantum technologies, cf.
-\cite{Demirchyan}.
-However, since exciton polariton BEC's in present experiments are observed at high enough temperatures the quantum properties of such a states should be examined even at full thermal equilibrium.
-
-The problem of distinguishability of statistically classical and quantum regimes for exciton polariton condensates is very important for their possible applications in quantum information technologies, see e.g.
+The problem of distinguishability of statistically classical (thermal) and quantum regimes for exciton polariton condensates is very important for their possible applications in quantum information technologies, see e.g.
 \cite{Dominici}.
-Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pump, spin degrees of freedom made microcavity polaritons potentially very promising for quantum computation and quantum information processing objectives, see, e.g.
+Fast switching properties (the typical switching time of a few picoseconds), relatively strong nonlinear response and flexibility to external optical and/or electrical pumping spin degrees of freedom made microcavity polaritons potentially promising for quantum computation and quantum information processing, see, e.g.
 \cite{Demirchyan,Pagel,Kyriienko,Solnyshkov_2015, Dominici}.
 
-Especially, it is important to emphasize here quantum annealing problem physically based on the searching algorithm for the global minimum of a potential energy landscape (PEL) consisting of a set of barriers and wells, see e.g.
+Here we specifically focus on the quantum annealing problem that is relevant to the searching algorithm for the global minimum of the potential energy landscape (PEL) consisting of a set of barriers and wells, see e.g.
 \cite{Santoro, Das}.
-In a purely classical  (thermal) regime the {bosonic quasipartcles cross barriers stochastically} at finite temperature with the help of thermal activation process if the thermal energy is large enough.
+In a purely classical  (thermal) regime the {bosonic quasipartcles cross barriers stochastically} at finite temperature with the help of thermal activation process if the thermal energy is large enough, see Fig.
+\ref{pic:potential_picture}.
 Contrary, in a quantum limit the same system undergoes quantum tunneling through the barrier.
-Obviously, the shape of the barrier plays an essential role in this case, cf.
-\cite{Das, Lewenstein}.
-It has been shown recently in \cite{Lewenstein} that the annealing algorithm relies in general case on combination of thermal annealing and quantum tunneling.
+Obviously, the shape (height and thickness) of the barrier plays an essential role in this case \cite{Das, Lewenstein}.
+It has been shown recently in \cite{Lewenstein} that the annealing algorithm relies in general case on the combination of thermal annealing and quantum tunneling.
 The
 collective (bosonic) character of polariton condensation could be used for the acceleration of the physical implementation of the search algorithm \cite{Yan}.
+The authors of Refs.
+\cite{Lago1, Lago2} propose polariton graphs as an analog platform for minimizing the XY -- Hamiltonian by exploring the non-equilibrium character of exciton polariton condensates and mimicking various magnetic phases with them.
+An original technique of nonresonant spatially  modulated pumping beam  have been used to imprint two-dimensional polariton graphs with different topology and different heights of potential barriers.
+Importantly, the phase-locking  between arbitrary neighboring vertices might be practically achieved in this case.
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/potential_picture.eps}}
+\caption{Scketch of two tunnel coupled exciton condensates.
+The two minima of the trapping potential $U$ are situated in the points $+x_0$ and $-x_0$.
+At thermal equilibrium the interplay between thermal and quantum annealing effects is governed by the blue shift of condensates, effective temperature of exciton-polaritons and the shape of the potential.
+\label{pic:potential_picture}}
+\end{figure} 
+%
+In the present paper we study the effect of a finite effective temperature on the coupling of quasi-equilibrium exciton-polariton condensates accounting for the competing thremal and quantum annealing effects.
 
-In this paper we consider theoretically the finite temperature effects for exciton polariton condensates formed in a semiconductor microcavity in the presence of the Josephson effect, cf.
-\cite{Aleiner, Shelykh_2008, Borgh_2010}.
-In particular, we are interesting in generic problem of quantum-classical phase transition (PT) explicitly examined for a two junction model \cite{Chudnovsky_1997}.
+Recently Yongbao Sun et al \cite{Snoke_2017} reported the observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity characterised by a remarkably long photon lifetime of $135ps$.
+Clearly, exciton polaritons with long lifetime are promising candidates for quantum technologies \cite{Demirchyan}.
+One of the crucial advantages of exciton-polaritons over cold atoms consists in a perspective of room temperature operation of polariton devices.
+In this context, it is very important to reveal the impact of temperature on the physics of interacting polariton condensates.
+It should be also noted that the effective temperature of a polariton gas may be introduced in the quasi-equilibrium approximation, which is not necessarily valid in all cases but constitutes an important starting point of any analysis.
+Further steps would involve a full kinetic modelling for a non-equilibrium polariton gas.
 
-In general, this problem is related to the dissipative tunneling problem or tunneling at finite (non-zero) temperatures, cf. \cite{Caldeira, Larkin, Riseborough}.
+To be specific, here we consider an exciton polariton Josephson junction (EPJJ).
+We study the interplay of two mechanisms of coupling between the condensates in order to reveal the cross-over from the quantum tunneling to the incoherent coupling regime that may occur at finite temperatures \cite{Aleiner, Shelykh_2008, Borgh_2010}.
+In particular, we are interested in a generic problem of the quantum-classical phase transition (PT) applied to two-level (spin) systems \cite{Chudnovsky_1997, Caldeira, Larkin, Riseborough, Zhang, Owerre}.
 Traditionally,  studies in this field are limited by consideration of superconductor devices \cite{Ankerhold} where macroscopic quantum tunneling phenomena plays an essential role.
 In particular, it is worth to mention here the Schr\"odinger cat state formation \cite{Leggett} and the 	design of quantum gates with superconductor qubits for quantum computing where a macroscopic quantum coherence for the phase is important \cite{Makhlin}.
-Recently, the problem of quantum tunneling and quantum-classical PT problem have been examined for other two-level (spin) systems, like atomic BEC's \cite{Zhang}, and small ferromagnetic particles, \cite{Owerre}.
 
-In the paper we consider an \textit{extended model} for exciton polariton Josephson junctions (EPJJs) that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) when energy of polariton-polariton scattering contributes to the tunneling parameter matrix elements, cf.
-\cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
-In particularly, we pay attention to temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
-We aimed at formulating necessary criteria to obtain quantum phase regimes with trapped exciton polaritons suitable for realisation of quantum annealing algorythms and creation of exciton polariton qubit gates.
+We shall consider a generalised model of EPJJ that relates to so-called non-standard Bose-Hubbard models (see \cite{Dutta} and references therein) where the energy of polariton-polariton scattering contributes to the tunneling parameter matrix elements \cite{Aleiner, Shelykh_2008, Borgh_2010, Solnyshkov_2008, Sarchi}.
+In particularly, we pay attention to the temperature dependent quantum critical phenomena occurring in the presence of macroscopic tunneling.
+We aim at the formulating of the criteria for realisation of the quantum tunneling regime that is crucial for the realisation of the quantum annealing algorithms and exciton-polariton quantum gates.
 
@@
 In Sec.
-\ref{sec:quantum_phase} we introduce the quantum phase model for extended model of EPJJ of the coupled condensates and discuss various regimes for it at zero temperature and infinite exciton polariton lifetime.
+\ref{sec:quantum_phase} we introduce the quantum phase model for EPJJ and discuss various regimes of coupling between two condensates at zero temperature and in the limit of an infinite exciton polariton lifetime.
 Section \ref{sec:quantum_classical} presents the results obtained for a quantum-classical PT problem and addresses the quantum phase at finite temperatures.
-The influence of non-equilibrium effects with microcavity exciton polaritons possessing a finite lifetime is discussed in \ref{sec:non-equilibrium}.      
+The influence of non-equilibrium effects involving the microcavity exciton polaritons possessing a finite lifetime is discussed in Sec. \ref{sec:non-equilibrium}.      
 In Conclusion, we summarize the obtained results.
-In the Appendix \ref{sec:model} we explain in details  extended model of EPJJ within the tight-binding approximation.
+In the Supplementary Material we explain in details the extended model of EPJJ formulated within the tight-binding approximation.
 
@@
 
-{\red
+We consider a system of two spinless exciton-polariton condensates localised in lateral potential traps created in a planar semiconductor microcavity.
+The condensates are confined by a W-shape potential $U(x)$ possessing two minima at the points $\pm x_0$, see Fig.1.
+Polaritons are pumped to the condensates from a reservoir of incoherent excitons.
+In this and next Section, we shall neglect the finite polariton lifetime and assume that the polariton gas is at the thermal equilibrium.
+We account for the polariton-polariton repulsion.
 
-We consider a system of two exciton-polariton condensates localised in lateral potential traps in a planar semiconductor microcavity.
-The condensates are separated by a potential barrier $U(x)$.
-Polaritons are pumped to the condensates from a reservoir of incoherent excitons.
-They decay radiatively.
-We account for the repulsive intereaction between exciton-polaritons.
-The finite temperature of the polariton gas is accounted for in the thermal equilibrium approximation.
-We use two-mode representation of the $\hat{\psi}$ - operator that describe the behaviour of the condensates:
+We shall use the pseudo-spin operator representation for the Hamiltonian describing our EPJJ model system that has a form (the details of the model are presented in the Supplementary Material): 
 %
 \begin{equation}
-\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x).
+\hat{H} = \alpha \hat{S}_z^2 + \beta \hat{S}_x^2 - B \hat{S}_x.
+\label{eq:hamiltonian_spin}
 \end{equation}
 %
-Here $\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}$ where $\Phi_{\pm}(x)$ are symmetric and antisymmetric real wavefuntions obeying the stationary Gross-Pitaevsky equation $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$.
+The coefficients in Eq. (1) characterize the tunnel coupling of two trapped condensates:
+the parameters $\alpha$ and $\beta$ are proportional to the overlap integrals of real symmetric ($\Phi_+$) and antisimmetric ($\Phi_-$) wavefunctions of two condensates that are
+$\int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$, $B$ is determined by difference of chemical potentials which obey stationary Gross-Pitaevskii (GP) equations for two trapped condensates.
 
-%
-\begin{figure}[ht]
-\center{\includegraphics[width=0.5\linewidth]{pic/potential_picture.eps}}
-\caption{ \dots \label{pic:potential_picture}}
-\end{figure}
-%
+It is important to note that the last term in Eq. (1) characterizes the familiar XY--model Hamiltonian  considered in
+\cite{Lago1, Lago2}.
+The second term in (1) introduces an additional part that has no analogy in the XY-Hamiltonian; it is proportional to $\cos(2\phi)$, where $\phi$ is the phase difference between two polariton condensates.
+We will show that this term becomes essential if the barrier separating two condensates is sufficiently large.
 
-We can express the Hamiltonian of such systems in terms of pseudo-spin operators as follows:
-%
-\begin{equation}
-\hat{H} = \alpha \hat{S}_z^2 + \beta \hat{S}_x^2 - B \hat{S}_x
-\label{eq:hamiltonian_spin}
-\end{equation}
-Is characterizes a weakly interacting exciton polariton condensate Josephson junction device.
-The parameters $\alpha = 2 \gamma_{+-}$, $\beta = \dfrac{\gamma_{++} + \gamma_{--} - 2 \gamma_{+-}}{2}$ and $B = \mu_- - \mu_+$, $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$ reflect Josephson junction properties, see Appendix \ref{sec:model} for details.
-}
-Here we propose quantum mechanical approach to the EPJJ  phase recasting pseudo-spin operators in  (\ref{eq:hamiltonian_spin}) through the differential representation defined as
+It is convenient to introduce the pseudo-spin operators in a form
 % 
@@
 \quad \hat{S}_y = & s \sin{\phi} + \cos{\phi} \dfrac{d}{d \phi}, \\
-\hat{S}_z = & -i\dfrac{d}{d \phi}
+\hat{S}_z = & -i\dfrac{d}{d \phi},
 \end{align}
@@
 %
-where  $\phi$ is the phase variable.
-The operators determined in Eq. (\ref{eq:pseudo_spin_diff}) in \eqref{eq:hamiltonian_spin}
- obey familiar $SU(2)$ algebra commutation relations $[\hat{S}_i, \hat{S}_j] = i\epsilon_{ijk}\hat{S}_k,  i,j,k=x,y,z$.
-After straightforward calculations from (\ref{eq:hamiltonian_spin}) one can obtain
+The operators defined in Eq. (\ref{eq:pseudo_spin_diff}) obey familiar $SU(2)$ algebra commutation relations $[\hat{S}_i, \hat{S}_j] = i\epsilon_{ijk}\hat{S}_k,  i,j,k=x,y,z$.
+After some straightforward calculations from (\ref{eq:hamiltonian_spin}) one can obtain
 %
@@
 %
-We also assume macroscopically large number of particles, i.e. the $s = N/2 >> 1$ is C - number. Using (\ref{eq:hamiltinian_s})  for Schrodinger equation we obtain   
+Thereafter we assume that both condensates are composed by macroscopically large numbers of particles, i.e. the $s = N/2 >> 1$ is C - number.
+The general stationary Schroedinger equation with a Hamiltonian (\ref{eq:hamiltinian_s}) writes:
 %
@@
 %
-where $\Phi \equiv \Phi(\phi)$ is unknown $2\pi$-periodic wavefunction that characterizes quantum phase properties, cf. \cite{Anglin}.
-%ng that Eqs. (\ref{eq:hamiltinian_s}), (\ref{eq:schrodinger}) can be obtained by applying so-called phase-state representation, {\red cf. [  ]}.
-%
-%\begin{equation}
-%\ket{\psi} = \dfrac{1}{2 \pi} \int_{-\infty}^{+\infty} d \phi \Phi(\phi) \ket{\phi}
-%\end{equation}
-%
-%where
-%
-%\begin{equation}
-%\ket{\phi} = \dfrac{1}{\sqrt{N!}} \Big[ e^{i\phi/2} \psi_1^\dagger + e^{-i \phi/2} \psi_2^\dag \Big]^N \ket{0}_1\ket{0}
-%\end{equation}
-%
-%is macroscopic coherent spin-state (macroscopic qubit state) that plays important role in current quantum information protocols operating with $N$-particle condensates, cf. \cite{Byrnes_2012}.
-It is possible to eliminate the term with first derivative in Eq. (\ref{eq:schrodinger}) applying the transformation
+where $\Phi \equiv \Phi(\phi)$ is some $2\pi$-periodic wavefunction that characterizes quantum phase properties \cite{Anglin}.
+It is possible to eliminate the term with first derivative in Eq. (\ref{eq:schrodinger}).
+In order to find the explicite form of the function $\Phi$, it is convenient to substitute it by:
 %
@@
 %
-where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is new phase variable; $F(\phi, \lambda)$ is incomplete elliptic integral of the first kind.
-In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{B}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$ playing crucial role for our model.
-Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to Schr\"odinger-like equation
+where $z = \int \limits_0^\phi \dfrac{d \xi}{\sqrt{1 - \lambda \sin^2 \xi}} = F(\phi, \lambda)$ is a new phase variable; $F(\phi, \lambda)$ is the incomplete elliptic integral of the first kind.
+In (\ref{eq:transformation_of_phi}) we have introduced dimension-less parameters $\Lambda = \dfrac{B}{\alpha s}$, $\lambda = \dfrac{\beta}{\alpha}$.
+Inserting (\ref{eq:transformation_of_phi}) into (\ref{eq:schrodinger}) we arrive to the familiar form of a Schr\"odinger equation
 % 
 \begin{equation}
-\alpha \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0
+\alpha \frac{d^2\Psi}{dz^2} + (E - V(z))\Psi = 0.
 \label{eq:schrodinger_usual}
@@
 %
-characterizing quantum particle with the ``mass''  $m = \dfrac{\hbar^2}{2 \alpha}$ and energy $E$, that moves in the potential $V(z) = \alpha s^2 V_0(z)$ with
+This equation describes an effective particle with the mass  $m = \dfrac{\hbar^2}{2 \alpha}$ and energy $E$, that is confined by the potential $V(z) = \alpha s^2 V_0(z)$ with
 %
@@
 
-The dependences of trapping potential $V_0(z)$ on phase variable $z$ are shown in Fig. \ref{phase_potential}. The period of the functions is  $4K(\lambda)$.
-The dependence of the $\lambda$ parameter on normalized half of inter-well distance $\dfrac{x_0}{a}$ can be estimated as $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
-The results known for quantum phase mesoscopic Josephson junction model can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
+The dependences of the trapping potential $V_0(z)$ on the phase variable $z$ are shown in Fig. \ref{phase_potential}. The period of the functions is  $4K(\lambda)$.
+The dependence of the $\lambda$ parameter on normalized half of the inter-well distance $\dfrac{x_0}{a}$ can be approximated by $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
+The well-known behaviour of the quantum phase mesoscopic Josephson junction (that map to the XY--model, \citep{Lago1, Lago2} ) can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
 This limit corresponds to  infinitely large inter-well distances, with $x_0 \to \infty$.
-On the other hand, $\lambda$ -- parameter grows rapidly at $\dfrac{x_0}{a} \ll 1$.
-Obviously, in this limit our EPJJ model that based on assumption of relatively weak coupling between the wells breaks down.
-
-Below we are focusing on $\lambda$ -- parameters which belong to segment of $0 < \lambda < 1$ and might be obtained at moderate values of $\dfrac{x_0}{a}$ which are $\dfrac{x_0}{a} \geq 0.45$.
-
+On the other hand, the $\lambda$ -- parameter exhibits a sharp increase at $\dfrac{x_0}{a} \ll 1$.
+Obviously, in this limit our EPJJ model based on the assumption of a relatively weak coupling between trapped condensates breaks down.
+Below we are focusing on $\lambda$ -- parameters which belong to the range of $0 < \lambda < 1$ and correspond to the moderate values of $\dfrac{x_0}{a}$ such as $\dfrac{x_0}{a} \geq 0.45$. 
 %
@@
 \caption{
-Effective dimension-less potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of elliptic integral phase coordinate $z$.
-Points $\pm z_{min}$ and $\pm z_{max}$ in (b) relay to global minima and maxima of the potential, correspondingly, occurring with periodicity $4K(\lambda)$. \label{phase_potential}}
+Effective dimension-less potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of the elliptic integral phase coordinate $z$.
+Points $\pm z_{min}$ and $\pm z_{max}$ in (b) correspond to global minima and maxima of the potential, respectively. \label{phase_potential}}
 \end{figure}
 %
-Analysis of the quantum phase can be performed  in three domains determined by vital $\Lambda$--parameter values, cf. \cite{Anglin}.
+The analysis of the quantum phase can be performed in three domains determined by vital $\Lambda$--parameter values, \cite{Anglin}.
 
-\textit{Rabi regime} $\Lambda \gg 1$. In this limit the trapping potential reads $V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}$.
-Physically, for any value of $\lambda$ -- parameter taken from the domain 0$<\lambda <1$ we can obtain (Rabi) oscillations for quantum phase.
-In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and cf. \cite{Anglin}.
+\textit{Rabi regime} $\Lambda \gg 1$. In this limit the trapping potential can be approximated by $V_R(z) = \dfrac{1}{4} \Lambda^2 \sd^2{z}$.
+Physically, for any value of $\lambda$ -- parameter belonging to the domain 0$<\lambda <1$ the system exhibits (Rabi) oscillations for the phase.
+In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and \cite{Anglin}.
 
 \textit{Fock regime} $\Lambda \ll 1/N^2$.
-In purely quantum limit 
-%the two mode system approaches by the state $\ket{\psi} \propto (\psi_1^\dag)^s (\psi_1^\dag)^s \ket{0}_1 \ket{0}_2$%
-the phase wavefunction approaches $\Phi(\phi) \to (2\pi)^{-1/2}$.
-In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms into Mathieu equation that implies spectrum consisting from all Mathieu functions.
+In purely quantum limit $\Phi(\phi) \to (2\pi)^{-1/2}$.
+In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms to the Mathieu equation that is characterised by the set of eignen states consisting of all Mathieu functions.
 
 \textit{Josephson regime} $1/N^2\ll\Lambda <1$.
-This regime represents intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
-The behavior of the phase depends on the ratio between parameters $\Lambda$ and $\lambda$.
-If $\Lambda \ge 2\lambda$ the $V_0(z)$ posses only one minima at $z = 0$ and $V(0) = -\Lambda$. 
-%Frequency of small amplitude ($z \ll 1$) oscillations %can be obtained from (\ref{eq:potential}) and looks like { \red $\omega_{0, quantum} = \frac{2 \alpha s}{\hbar} \sqrt{\frac{1}{4} \Lambda^2 - \frac{\Lambda}{2} (2\lambda - 1) - \lambda(1 - \lambda)}$ }.
+This regime corresponds to the intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
+The behavior of the phase depends on the ratio between the parameters $\Lambda$ and $\lambda$.
+If $\Lambda \ge 2\lambda$ the potential $V_0(z)$ possesses only one minimum at $z = 0$ and $V(0) = -\Lambda$.
 
-In the other limit, for $\Lambda < 2 \lambda$, quantum "particle" is trapped at two minima of $V_0(z)$ that corresponds to $W$ -- like potential with coordinates $\cn{z_{min}} = \frac{\Lambda}{2 \lambda}$ and appearing for both of Josephson and Fock regimes, cf.
-Fig.
+In the opposite limit, for $\Lambda < 2 \lambda$, the effective quantum ``particle'' described by Eq.
+(\ref{eq:schrodinger_usual}) is trapped at the two minima of $V_0(z)$ that correspond to the $W$ -- like potential with coordinates $z_{min} = \pm \cn^{-1}{\frac{\Lambda}{2 \lambda}}$ and appearing for both of Josephson and Fock regimes, see Fig.
 \ref{phase_potential}b,c.
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for $\Lambda > 2(1 - \lambda)$ potential $V_0(z)$ presumes local minimum at $\pm 2 K(\lambda)$, see Fig. 1b.
-
-% $ce_0(z, q)$, $ce_1(z, q)$, $se_1(z, q)$, \dots, which are $2\pi$-periodic, and corresponding eigenvalues $a$ can be found using series expansions in powers of $q$.
-%from (\ref{eq:potential}) one can obtain
-%
-%{\red
-
-%
-%\begin{equation}
-%V_F(z) \simeq -\lambda (1 - \lambda) \sin^2{z},
-%\end{equation}
-%
-%and our 
-%transforms into Mathieu equation;
-%
-%\begin{equation}
-%\frac{d^2 \Psi}{d z^2} + (a - 2q  \cos{2z}) \Psi = 0.
-%\end{equation}
-%
-%where $a = E / \alpha + s^2 \lambda(1 - \lambda) / 2$, $q = s^2 \lambda (1 - \lambda)/ 4$.
-%We recall our boundary condition: $\Psi(z + 2\pi) = \Psi(z)$.
-
-%In another limit $\lambda \ll \Lambda$ 
-%that might  be studied within Fock regime is relevant to condition . In this case from (\ref{eq:potential}) 
-%we have $V_0(z) \simeq -\Lambda \cos{z}$.
-%In fact, this limit that deals with negligible $\lambda$ reproduces results for convenient quantum phase model \cite{Anglin}.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ the potential $V_0(z)$ possesses a local minimum at $\pm 2 K(\lambda)$, see Fig. 1b.
 
@@
 
-In current experiments with exciton polaritons  the condensate is observed at finite and high enough temperatures \cite{Sanvitto,Guillet}.
-In this section we find conditions when quantum approach to the phase problem for Josephson junction with coupled exciton polariton condensates is valid.
-This conditions, in fact, responsible for ability of our system to perform quantum annealing algorithm \cite{Das}.
+Experimentally, exciton-polariton condensates are being observed at elevated temperatures, un to the room temperature in wide-gap semiconductor microcavities \cite{Sanvitto,Guillet}.
+At high temperatures the validity of the quantum coherent treatment of the Josephson problem is limited.
+In this section, we study the limits of validity of the quantum approach which also set the limits of the system suitability for quantum annealing \cite{Das}.
 
-To  be more specific we consider the tunneling in  effective $W$ -- like potential represented in Fig.
-\ref{phase_potential}b  inherent to  Josephson regime.
-We examine thermodynamically equilibrium  system of exciton polaritons at finite temperature $T$ that is the system with infinitely large  exciton polariton lifetime.
-Noticing, that in  recent experiments  described in Ref.
-\cite{Snoke_2017} polariton lifetime attains  $275ps$ at resonance that seems to be enough to justify the equilibrium  processes described below.
+To be more specific we consider the tunneling in an effective $W$ -- like potential shown in Fig.
+\ref{phase_potential}b.
+We assume the thremal equilibrium condition to be fulfilled for an ensamble of exciton-polaritons at finite temperatures $T$, that would correspond to a hypothetic case of polaritons with the infinite life-time.
+We note in this connection that in the recent experiments \cite{Snoke_2017} the measured polariton lifetime was as long as $275ps$, which would be sufficient to justify the above approximation.
 
-Transition between two stable states (say, between points $-z_{min}$ and $+z_{min}$ in Fig.
+A transition between two stable states (say, between points $-z_{min}$ and $+z_{min}$ in Fig.
 \ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
-Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is height of the barrier between two states with minimum of potential energy) the particle jumps over the barrier governed by familiar thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$, cf.
-\cite{Larkin}.
-This process inherent to classical (thermal) annealing problem \cite{Das}.
-In the ``low temperature'' limit $k_{B}T\ll\Delta V$ particle undergoes quantum tunneling through the barrier with vanishing rate, that is important especially for quantum annealing scheme. 
-%with the rate $\Gamma \sim e^{-B/\hbar}$, where $B$ is the instanton action.
-%Now we elucidate conditions for their realization for exciton polariton Josephson junction problem.
+Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is the height of the barrier between two states with minimum of potential energy) the particle jumps over the barrier governed by the thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$ \cite{Larkin}.
+This process is inherent to the classical (thermal) annealing problem \cite{Das}.
+In the ``low temperature'' limit $k_{B}T\ll\Delta V$ polaritons undergo quantum tunneling through the barrier with a vanishing rate, that excludes realisation of the quantum annealing scheme.
 
-Our description is based on imaginary time path integral approach, cf. \cite{Ankerhold}.
-The imaginary-time action obtained within WKB method approaches as $S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau$.
-%
-%\begin{equation}
-%S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau.
-%\label{eq:thermon_action_1}
-%\end{equation}
-%
-The decay rate $\Gamma \sim e^{-S_{min}/\hbar}$ according to our approach can be expressed through the minimal value $S_{min}$ of the action.
-The trajectories which are minimize the action $S_T$ satisfy to classical equation of motion $m \ddot{z} = \frac{d V}{dz}$ written for the thermon "particle" that  oscillates inside the inverted potential $-V(z)$.
-%
-%\begin{equation}
-%m \ddot{z} = \frac{d V}{dz}.
-%\label{eq:thermon}
-%\end{equation}
-%
+Our description is based on imaginary time path integral approach \cite{Ankerhold}.
+The imaginary-time action obtained within the WKB method approaches as $S(E) = \oint (\tfrac{1}{2} m \dot{z}^2 + V(z)) d \tau$.
+The decay rate $\Gamma \sim e^{-S_{min}/\hbar}$ in our approach can be expressed through the minimal value $S_{min}$ of the action.
+The trajectories which minimize the action $S_T$ obey the classical equation of motion $m \ddot{z} = \frac{d V}{dz}$ written for the thermon ``particle'' that oscillates within the inverted potential $-V(z)$.
 Periodic solutions of this equation satisfy
@@
 %
-In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are turning points, cf. Fig. \ref{phase_potential}b.
-The Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at energy $E = 0$ and temperature $T = 0$ characterize instanton solution with infinite period.
-Combining  equation for $S(E)$ 
+In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are the turning points, see Fig. \ref{phase_potential}b.
+Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at the energy $E = 0$ and temperature $T = 0$ characterize the instanton solution with an infinite period.
+Combining the equation for $S(E)$ 
 %(\ref{eq:thermon_action_1}) 
@@
 
-To determine thermodynamic properties of the system it is necessary to know small amplitude oscillations  at the bottom, $z=0$, of inverted potential $-V(z)$.
+To reveal the thermodynamic properties of the system it is necessary to consider the small amplitude oscillations at the bottom, $z=0$, of the inverted potential $-V(z)$.
 The action in this case reads: 
@@
 
-Expansion of the potential $V(z)$ excluding constant value $V(0)$ gives:
+The expansion of the potential $V(z)$ into a series and excluding the constant value $V(0)$ gives:
 %
@@
 %
-In particularly, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the second order phase transition occurs.
-If $-V(z)$ behaves as $z^2 + z^4$ first order phase transition take place.
-Phase boundary between 1st and 2nd order phase transitions is determined by the relation
+In particular, if the inverted potential $-V(z)$ has the form $z^2 - z^4$ the second order phase transition occurs.
+If $-V(z)$ behaves as $z^2 + z^4$ the first order phase transition take place.
+The phase boundary between the 1st and 2nd order phase transitions is determined by the relation
 %
@@
 \ref{pic:phase_boundary_combined}.
-An insets demonstrate various type of  phase potentials $V_0(z)$ inherent to our EPJJ model.
-First order PT occurs for two type of potentials in the shaded region bounded by bold  (red) curve.
-Second order PT's appear for potential landscapes taken from  dark area.
+An inset demonstrates various types of  phase potentials $V_0(z)$ inherent to our EPJJ model.
+The first order PT occurs for two type of potentials in the shaded region bounded by bold  (red) curve.
+Second order PT's appear for the potential landscapes taken from the dark area.
 %
@@
 \center{\includegraphics[width=0.5\linewidth]{pic/phase_transition_diagram_combined.eps}}
-\caption{Diagram of the phase boundary for  1st- and 2nd-order  PT's in $\Lambda$,$\lambda$-parameters plane. The PEL's are shown in the windows. \label{pic:phase_boundary_combined}}
+\caption{Diagram of the phase boundary for the 1st- and 2nd-order PT's in $\Lambda$, $\lambda$ -- parameters plane.
+The potential energy landscapes (PEL's) are shown in the windows. \label{pic:phase_boundary_combined}}
 \end{figure}
@@
 %
-where  $\omega_0 = \frac{2 \alpha s}{\hbar} \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is small oscillation frequency of thermon "particle" near the bottom of inverted potential,  $T_{0}=\alpha N / 2\pi k_B$ is some characteristic temperature that inherent to exciton polariton system.
+where  $\omega_0 = \frac{2 \alpha s}{\hbar} \sqrt{\lambda (1 - \lambda) + \tfrac{1}{2} (2 \lambda - 1) \Lambda - \tfrac{1}{4} \Lambda^2}$ is a frequency of small oscillations of the thermon ``particle'' near the bottom of inverted potential,  $T_{0}=\alpha N / 2\pi k_B$ is a characteristic temperature that inherent to exciton polariton system.
 The $T_{0}$  implies important time scale $\tau_0=2\pi\hbar/ \alpha N$ that can be understood as thermon particle ``lifetime''.
-Notably, as it is follows from (\ref{eq:second_order}) there is no barrier at $z = 0$ for $\Lambda \ge 2\lambda$ -- see white domain in Fig.
+Notably, as it is follows from (\ref{eq:second_order}) there is no barrier at $z = 0$ for $\Lambda \ge 2\lambda$ -- see the white domain in Fig.
 \ref{pic:phase_boundary_combined}.
 
-Figure \ref{pic:action_period}a displays 2nd-order PT from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
-The crossover occurs at the critical temperature $T_{c}^{(2)}$ where $S_T = S_0$ and {$E = E_0$}.
-The inset demonstrate monotonic dependence of normalized thermon period $\tau_p/\tau_0$ on energy $E$ that is inherent to second-order phase transition.
-Closest to the critical point with energy $E=E_0$ thermon undergoes small amplitude oscillations.
+In Fig. \ref{pic:action_period}a we represent the results exhibiting 1st-order PT inherent to narrow shadow domain in Fig.\ref{pic:phase_boundary_combined}.
+It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of the normalized thermon period  $\tau_p / \tau_0$ on the energy $E$ is non-monotonic, see the inset in Fig.
+\ref{pic:action_period}a.
+The critical temperature $T_{c}^{(1)}$ belongs to the temperature domain $T_{min} < T_{c}^{(1)} < T_{max}$ and it can be found out numerically by solving Eqs.(\ref{eq:thermon_period}) - (\ref{eq:thermal_action}) in the particular case of $S_T = S_0$.
 
-%
-\begin{figure}[ht]
-\begin{minipage}[h]{0.49\linewidth}
-\center{\includegraphics[width=1\linewidth]{pic/action_period_2nd_order_transition.eps} \\ (a)}
-\end{minipage}
-\hfill
-\begin{minipage}[h]{0.49\linewidth}
-\center{\includegraphics[width=1\linewidth]{pic/action_period_1st_order_transition.eps} \\ (b)}
-\end{minipage}
-\caption{Dependences of  minimal action $S_{min}$ (ABC-(blue) curve) taken in $s\hbar$ units as a function of normalized temperature $ T/T_{0}$ for (a) 2nd-order PT, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 1st-order PT, $\lambda = 0.5$, $\Lambda = 0.5$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
-The inset shows dependences of normalized thermon period $\tau_p / \tau_0$ versus energy $E$ given in  $\alpha s^2$ units.
-\label{pic:action_period}}
-\end{figure}
-%
-
-In Fig. \ref{pic:action_period}b we represent results exhibiting 1st-order PT inherent to narrow shadow domain in Fig.\ref{pic:phase_boundary_combined}.
-It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of normalized thermon period  $\tau_p / \tau_0$ on energy $E$ is non-monotonic, see inset in Fig.
-\ref{pic:action_period}b.
-The critical temperature $T_{c}^{(1)}$ belongs to the temperature domain $T_{min} < T_{c}^{(1)} < T_{max}$ and can be find out numerically by solving Eqs.(\ref{eq:thermon_period}) - (\ref{eq:thermal_action}) under the condition $S_T = S_0$.
-
-Analytically critical temperature $T_{c}^{(1)}$ might be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is a instanton action that can be represented as $B = S(E_{min})$.
+Analytically, the critical temperature $T_{c}^{(1)}$ may be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is an instanton action that can be represented as $B = S(E_{min})$.
 After some straightforward calculations for $B$ we obtain
@@
 
-In experiments with exciton polaritons it is much more easier to manipulate by polariton density instead of the temperature, see e.g. \cite{Sanvitto,Guillet}.
-For instance, the density of polariton gas can be changed by using external optical pump.
+%
+\begin{figure}[ht]
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_1st_order_transition.eps} \\ (a)}
+\end{minipage}
+\hfill
+\begin{minipage}[h]{0.49\linewidth}
+\center{\includegraphics[width=1\linewidth]{pic/action_period_2nd_order_transition.eps} \\ (b)}
+\end{minipage}
+\caption{Dependences of the minimal action $S_{min}$ (ABC-(blue) curve) taken in $s\hbar$ units as a function of the normalized temperature $ T/T_{0}$ for (a) 1st-order PT, $\lambda = 0.9$, $\Lambda = 0.1$; and, (b) 2nd-order PT, $\lambda = 0.5$, $\Lambda = 0.5$; the solid (bold) line corresponds to the thermon action, $S_T$; the dashed line corresponds to the thermodynamic action, $S_0 = \hbar \Delta V / k_B T$, $S_{min} = \min \{S_0, S_T\}$.
+The inset shows the dependences of normalized thermon period $\tau_p / \tau_0$ on energy $E$ expressed in $\alpha s^2$ units.
+\label{pic:action_period}}
+\end{figure}
+%
+
+Figure \ref{pic:action_period}b displays 2nd-order PT from quantum (solid bold line of $S_T$) to thermal (classical) regimes --- dashed bold line of $S_0$.
+The crossover occurs at the critical temperature $T_{c}^{(2)}$ where $S_T = S_0$ and {$E = E_0$}.
+The inset demonstrates a monotonic dependence of normalized thermon period $\tau_p/\tau_0$ on energy $E$ that is inherent to second-order phase transition.
+Closest to the critical point with energy $E=E_0$ the thermon undergoes small amplitude oscillations.
+
+{\red
+%
+\begin{equation}
+P = \sqrt{\frac{V(0) - E}{\Delta V}}.
+\label{eq:p_parameter}
+\end{equation}
+%
+}
+
+%
+\begin{figure}[ht]
+\center{\includegraphics[width=0.5\linewidth]{pic/p_parameter.eps}}
+\caption
+{The dependence of the $P$ -- parameter on the normalized temperature $T/T_{0}$.
+\label{pic:temperatures}}
+\end{figure}
+%
+
+In the optical experiments one usually has a better control of the exciton-polariton density than their effective temperature, see e.g. \cite{Sanvitto,Guillet}.
+For instance, the density of polariton gas can be changed by varying the optical pump intensity.
 In Fig.
-\ref{pic:temperatures} we plot numerically calculated critical temperature of 1st and 2nd order PTs against $\Lambda$-parameter for experimentally accessible semiconductor Josephson junction samples.
-Bold (green) line corresponds to analytical solution obtained with  Eq. (\ref{eq:B_action}).
-Since the $\Lambda$-parameter is inversionally proportional to the density of exciton polariton gas (so-called blue shift) Fig.
-\ref{pic:temperatures} establishes important correspondence between critical temperatures discussed in the paper and relevant exciton polariton densities.
+\ref{pic:temperatures} we plot a numerically calculated critical temperature of the 1st and 2nd order PTs as a function of the $\Lambda$-parameter for experimentally accessible semiconductor Josephson junction samples.
+The bold (green) line corresponds to the analytical solution obtained with  Eq. (\ref{eq:B_action}).
+Since the $\Lambda$-parameter is inversely proportional to the density of the exciton polariton gas (and the blue-shift of the energy of the corresponding photoluminescence peak) Fig.
+\ref{pic:temperatures} establishes an important relation between the critical temperatures discussed in the paper and the relevant exciton polariton densities.
 %
@@
 \caption
-{Dependence of normalized critical temperature $T_{c}/T_{0}$ as a function of parameter $\Lambda$. Bold (green) line corresponds to analytical solution for  $T_{c}^{(1)}$.     
+{The dependence of the normalized critical temperature $T_{c}/T_{0}$ as a function of the parameter $\Lambda$.
+The bold (green) line corresponds to the analytical expression for  $T_{c}^{(1)}$ given by Eq.
+(\ref{eq:B_action}).
 \label{pic:temperatures}}
@@
 
-Now let us consider decay of the upper state that is relevant to  upper minima located at $\pm 2K(\lambda)$ in Fig.\ref{phase_potential}b and exists for $\Lambda > 2(1 - \lambda)$.
-Physically this problem presumes tunneling through the barrier located at one of the point $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
-%small ocsillation frequency near the bottom $z_{max}$ of the inverted potential $\omega_0 = \frac{\alpha s}{\hbar} \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$.
-By expanding the potential $V(z)$ near the vicinity of $z_{max}$ it is possible to show that only 2nd-order PT with temperature $T_{c}^{(2)} = (T_{0}/ 2) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$ appear in this case.
+Now let us consider the decay of the state of the system that corresponds to the upper minimum of the potential $V(z)$ located at $\pm 2K(\lambda)$ in Fig.\ref{phase_potential}b and exists for $\Lambda > 2(1 - \lambda)$.
+Physically, the decay takes place because of the tunneling of our effective particle through the barrier located at one of the points $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
+By expanding the potential $V(z)$ in the vicinity of $z_{max}$ it is possible to show that only the 2nd-order PT with a temperature $T_{c}^{(2)} = (T_{0}/ 2) \sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}$ may take place in this case.
 
-Let us briefly discuss observation feasibility of quantum-classical PT for exciton polariton BEC's obtained in experiments.
-In particular, for experimentally accessible polariton interaction strength $\alpha N=0.6meV$, given for narrow-band semiconductor samples, the  $T_{0}$ is about $1.2K$ that corresponds to to thermon effective lifetime  $\tau_{0}=3.5ps$.
-The value of $T_{0}$ is comparable with typical temperature of condensation, or, with temperature of Berezinsky-Kosterlitz-Thouless PT considered for dilute weakly interacting exciton polariton gas being at thermal equilibrium,cf.
-\cite{Sanvitto,Guillet}.
-Practically some enhancement of $T_{0}$ is possible by increasing of exciton polariton density and by improvement of experiment conditions, cf.
-\cite{Snoke_2017}.
-%
-%\begin{equation}
-%T_{c}^{(2)} = (T_{0}/ 2) %\sqrt{\frac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda)}.
-%\label{eq:second_order_2}
-%\end{equation}
-%
+Let us briefly discuss methods of the experimental study of the quantum-classical PT for the polariton Josephson junctions.
+Our estimations show that, for the experimentally accessible polariton interaction strength of $\alpha N=0.6meV$, characteristic of narrow-band semiconductor samples, $T_{0}$ is about $1.2K$ that corresponds to the thermon effective lifetime of $\tau_{0}=3.5ps$.
+The value of $T_{0}$ is comparable with a typical temperature of a Bose-Einstein condensation, or, with temperature of the Berezinsky-Kosterlitz-Thouless PT predicted for the dilute weakly interacting exciton polariton gas at thermal equilibrium \cite{Sanvitto,Guillet}.
+Some further enhancement of $T_{0}$ may be achieved by the increase of the optical pumping intensity and varying the detuning of exciton and photon modes in a microcavity \cite{Snoke_2017}.
 
-%With the aim of analytical determining of the phase transition order let's write the Taylor series for $V(z)$ near the vicinity of $z_{max}$.
-%Expansion of the potential $V(z)$ excluding constant value $V(z_{max})$ gives:
-%
-%\begin{equation}
-%V(\tilde{z}) = \alpha s^2 \Big[ -\tfrac{1}{4} \left( \tfrac{\Lambda^2}{1 - \lambda} - 4(1 - \lambda) \right) \tilde{z}^2 
-%+ \tfrac{1}{2} \tfrac{\Lambda \sqrt{\Lambda^2 - 4(1 - \lambda)^2}}{\sqrt{1 - \lambda} \sqrt{\Lambda^2 + 4 \lambda (1 - \lambda}} \tilde{z}^3 + o(\tilde{z}^4) \Big],
-%\label{eq:potential_teylor_2}
-%\end{equation}
-%
-%where $\tilde{z} = z - z_{max}$.
-%It follows from (\ref{eq:potential_teylor_2}) that $-V(\tilde{z})$ aways has the form $\tilde{z}^2 - \tilde{z}^3$, as $\Lambda > 0$, so in this case only second-order phase transition occurs.
-% We plot typical behaviour of the $\tau(E)$, $S(T)$ and $T_{c}^{(2)}$ on Figs. \ref{pic:action_period_temperature_2}, and summarize our results on the Fig. \ref{pic:phase_boundary_combined}.
-%
-%\begin{figure}[ht]
-%\begin{minipage}[h]{0.49\linewidth}
-%\center{\includegraphics[width=\linewidth]{pic/action_period_2nd_order_transition_b2.eps} \\ (a)}
-%\end{minipage}
-%\hfill
-%\begin{minipage}[h]{0.49\linewidth}
-%\center{\includegraphics[width=\linewidth]{pic/phase_transition_temperatures_b2.eps} \\ (b)}
-%\end{minipage}
-%\caption{\dots \label{pic:action_period_temperature_2}}
-%\end{figure}
-%
 \section{PT's in the presence of dissipation 
@@
 
-Let us now consider more realistic physical situation with EPJJ that valid for finite exciton polariton lifetime $\tau_{pol}$.
-Obviously, for finite $\tau_{pol}$  characteristic time $\tau_0$ that is responsible for quantum tunneling effects  should be shorter than typical time scales describing non-equilibrium processes with exciton polaritons.
-More precisely, in this case we require fulfillment of  inequality
+Now let us consider the EPJJ accounting for the finite exciton polariton lifetime $\tau_{pol}$. 
+The finite radiative lifetime is a crucial characteristic of any polariton system and, striktly speaking, can never be ignored.
+Obviously, in order to allow for the Josephson oscillations, the characteristic time $\tau_0$ that is responsible for quantum tunneling effects  should be shorter than all characteristic times describing non-equilibrium processes in the exciton-polariton gas, including the radiative decay.
+Hence,
+%
 \begin{equation}
@@
 \end{equation}
+%
+The condition (\ref{eq:lifetime}) is fulfilled in the experimental work \cite{Dominici}, in particular.
+Here we examine a different situationn amely, the case where the exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
+Note that this situation is realized the multiple experiments dealing with non-equilibrium exciton polariton condensates, see e.g. [1,2, 16-18].
 
-In order,  condition (\ref{eq:lifetime}) is fulfilled in [19].
-Here we examine situation when exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
-Namely  this situation is realized in most of current experiments with non-equilibrium exciton polariton condensates, see e.g.
-[1,2, 16-18].
-
-To be more specific we consider the influence of the dissipation to  EPJJ quantum phase properties in adiabatic limit, cf. \cite{Sols}.
-We start from GP equations obtained from  (\ref{eq:hamiltonian}) for mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$  at $\Gamma = 0$ ($B = G$),  which reads as 
+To be more specific in what follows we shall consider the influence of the dissipation on the EPJJ quantum phase properties in the adiabatic limit \cite{Sols}.
+We start from GP equations obtained from  (\ref{eq:hamiltonian}) for the mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$ at $\Gamma = 0$ ($B = G$), which read as
+%
 \begin{equation}
@@
 \end{equation}
-In (\ref{eq:GP}) we introduced dissipation  term with $\kappa \simeq \hbar/\tau_{pol}$.
-Defining new variables $\Psi_{1,2}$ as  $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for mean field pseudo-spin  parameters (\eqref{eq:pseudo_spin}) from (\ref{eq:GP}) we obtain
 %
-%
+In (\ref{eq:GP}) we have introduced the dissipation term with $\kappa \simeq \hbar/\tau_{pol}$.
+Defining new variables $\Psi_{1,2}$ as $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for the mean field pseudo-spin components (\ref{eq:pseudo_spin}).
+We obtain from (\ref{eq:GP})
 % 
@@
 %
-Here we explore the dimensionless time $t' = t B / \hbar$.
+Here we have introduced the dimensionless time $t' = t B / \hbar$.
 
-Set of Eqs.\ ({\ref{eq:pseudo-spin}}) discrebes dynamics of normalized mean field pseudo-spin parameters on the Bloch sphere with $S_x^2 + S_y^2 + S_z^2 = 1$.
-Equations  \ ({\ref{eq:pseudo-spin}}) looks similar to one taken for non-dissipative system but with time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa' t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa' t')$, $\kappa' = \kappa / B$, cf.\cite{Sedov}.
-Without dissipation Eqs.\ ({\ref{eq:pseudo-spin}}) posses  bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to solid black curve in Fig.1b.
+Set of Eqs.\ ({\ref{eq:pseudo-spin}}) describes the dynamics of normalized mean field pseudo-spin parameters on the Bloch sphere with $S_x^2 + S_y^2 + S_z^2 = 1$.
+Equations ({\ref{eq:pseudo-spin}}) look similar to those written for a non-dissipative system but with the time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa' t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa' t')$, $\kappa' = \kappa / B$ \cite{Sedov}.
+Taken out the dissipation, Eqs.\ ({\ref{eq:pseudo-spin}}) possesses a bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to the solid black curve in Fig.1b.
 
-In Fig.
-\ref{pic:phase}a we plot phase difference $ \phi = \arctan(-S_y / S_x)$ between the junctions as a function on time.
-Non-dissipative system has two different regimes depending on the values of  $\beta$ -- parameter, that is blue  (labeled as 1) and red (labeled as 3) curves in the Fig.
+In Fig. \ref{pic:phase}a we plot the phase difference between the condensates $ \phi = \arctan(-S_y / S_x)$ as a function on time.
+A non-dissipative system has two different regimes depending on the values of the $\beta$ -- parameter, that are blue  (labeled as 1) and red (labeled as 3) curves in Fig.
 \ref{pic:phase}, respectively.
-Blue  curve is plotted under the condition $\beta' > 1/2$ and  corresponds to the quantum regime with existence of barrier for potential energy -- see Fig.
+The blue curve is plotted for the case of $\beta' > 1/2$ and it corresponds to the quantum regime --- see Fig.
 \ref{pic:phase}b.
-Contrary,  red curve establishes phase properties below the threshold ($\beta' <1/2$) that corresponds to the absence of the barrier but upon the same temperature.
+Contrary, the red curve describes the phase between two condensates below the threshold ($\beta' <1/2$) that corresponds to the absence of the barrier.
 
-In the presence of dissipation (solid black curve in Fig.
-\ref{pic:phase}a) phase of EPJJ starts from one of potential  minimum.
-We suppose that the temperature of the system is not sufficient for thermal activation and quantum tunneling is possible.
-Then, the system evolves adiabatically and then  crosses the critical value 1/2
-due to decreasing of total number of particles. The final (temporal) state represents Josephson or, Rabi oscillation regime.
-%It can be transformed to the equation on the phase difference $\phi$ and $S_z$ as follows
-%
-%\begin{equation}
-%\begin{array}{lcl}
-%\dot{S}_z & = & B \sqrt{1 - S_z^2} \sin \phi - 2 \beta(t) (1 - S_z^2) \sin \phi \cos \phi; \\[10pt]
-%\dot{\phi} & = &  -2 \alpha(t) S_z + 2 %\beta(t) S_z \cos^2 \phi - \dfrac{B S_z \cos \phi}{\sqrt{1 - S_z^2}}.
-%\end{array}
-%\end{equation}
-%
-%We studied its dynamic numerically.
+In the presence of dissipation (solid black curve in Fig. \ref{pic:phase}a) the phase of EPJJ starts from one of the potential minima.
+We assume here that the temperature of the system is not sufficient for thermal activation and the quantum tunneling is possible.
+The system evolves adiabatically and then  crosses the critical value $\beta = 1/2$
+due to the decrease of the total number of particles caused by the radiative decay.
+The final (temporal) state represents the Josephson or, Rabi oscillation regime.
 %
@@
 \center{\includegraphics[width=\linewidth]{pic/phase_potential_dissipation.eps}}
-\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \alpha s / \hbar$) vs time for $\kappa/\hbar = 0.1 THz$.
+\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves, respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \alpha s / \hbar$) vs time for $\kappa/\hbar = 0.1 THz$.
 Initial conditions are $S_z(0) = S_x(0) = 0$, $S_y(0) = 1$, and $\phi(0) = \pi / 2$, respectively.
@@
 %
-%\begin{figure}[ht]
-%\center{\includegraphics[width=0.5\linewidth]{pic/temperature_on_dissipation.eps}}
-%\caption{Dependance of $T_c^{(2)}$ on $\kappa t$ for $\kappa / \hbar = 0.04 \cdot 10^{12}$ $1 / sec$, $B = 1$
-%\label{pic:temperature_dissipation}}
-%\end{figure}
-%
 
-Figures \ref{pic:phase}b and \ref{pic:phase}c  exhibits suppression of of $W$--like potential and relevant enhancement of reduced thermon period $\tau_{p} / \tau_0$ which occur  at timepoint $t_0 = 11.5 ps$ for  $\tau_{pol} \sim \hbar/\kappa= 10 ps$, respectively.
+Figures \ref{pic:phase}b and \ref{pic:phase}c demonstrate the suppression of $W$ -- like potential and the relevant enhancement of the reduced thermon period $\tau_{p} / \tau_0$ which occurs at $t_0 = 11.5 ps$ for  $\tau_{pol} \sim \hbar/\kappa= 10 ps$, respectively.
 
 Thus, behavior of the phase in the presence of dissipation showed in Fig.
-\ref{pic:phase} establishes non-equilibrium PT from regime where tunneling is possible to the regime where tunneling is suppressed.
-However, this regime happening at $t>t_0$ cannot be interpreted immediately as classical one.
-Actually, adiabaticity condition reads, cf. {\cite{Sols}:
+\ref{pic:phase} is characteristic of a established non-equilibrium PT from the regime where tunneling is possible to the regime where tunneling is suppressed.
+However, this regime found at $t>t_0$ cannot be interpreted immediately as the classical one.
+Actually, the adiabaticity condition reads {\cite{Sols}:
 %
@@
 %
-where $\omega(t) = B \sqrt{(1 - 2 \beta'(t))(1 - 2 \beta'(t) + 2 \alpha'(t))}/ \hbar $ is small amplitude oscillations slowly depending on time, cf. {\cite{Sedov}. 
-%It allows us to reduce linear system to the harmonic oscillator equaiton with slowly evolving frequency:
-%
-%\begin{equation}
-%\ddot{\phi} + \omega^2(t) \phi = 0,
-%\end{equation}
-%
-The solution of the phase in this case can be given as 
+where $\omega(t) = B \sqrt{(1 - 2 \beta'(t))(1 - 2 \beta'(t) + 2 \alpha'(t))}/ \hbar $ is the frequency of small oscillations slowly depending on time {\cite{Sedov}. 
+The solution for the phase in this case can be approximated by 
 \begin{equation}
@@
 %
-where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is an amplitude of oscillations at the moment $\tau = 0$. At large enough times 
-$\omega(t) \approx$ $B/ \hbar $  and permanent Rabi  oscillations for the Josephson junction phase $\phi$ are established, see Fig.
-5a and cf.{\cite{Permamemt}.
-To determine quantum (or, classical) character of this oscillations purely quantum approache to the problem should be considered.
+where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is the amplitude of oscillations at $\tau = 0$.
+At large enough times, $\omega(t) \approx$ $B/ \hbar$ and permanent Rabi  oscillations for the Josephson junction phase $\phi$ are established, see Fig. 5a and Ref. {\cite{Permamemt}.
+To distinguish between the quantum and classical character of these oscillations, a purely quantum approache to the problem should be considered.      
+It will be in the scope of our further research.
 
@@
 
-Let us summarize the results obtained.
-In the paper we examine quantum phase properties for  extended EPJJs created with the help of coupled exciton polariton condensates taken at finite temperatures and finite exciton polariton lifetime.
-We have shown that  PEL with set of barriers and wells (various W--like potentials) can be achieved for our model  depending on the $\Lambda$ and $\lambda$ parameters which characterize condensate junctions.
-The W-shape potential at finite temperatures admits two regimes which are  purely quantum tunneling regime through the barrier or classical regime of thermal activation.
-Transition (crossover) between this two limits exhibits universal features of 1st or 2nd order PTs which can be interpreted as PT between classical and quantum regimes.
+We have studied theoretically the coupling of two spacially separated trapped exciton polariton condensates at finite temperatures and accounting for the dissipation.
+We demonstrate the crossover from thermal to quantum annealing regime for a model system of two condensates localised by a W-shape potential.
+Second regime is classical one and characterizes  thermal activation.
+The transition between these two regimes exhibits universal features of the 1st or 2nd order PTs which can be interpreted as PT between classical and quantum regimes.
 It is important that critical temperature of transition depends on some  characteristic temperature  parameter $T_{0}$ (see e.g.
-(\ref{eq:second_order})) that depends on polariton-polariton interaction length (so-called blue shift) $\alpha N$.
+(\ref{eq:second_order})) that that is governed by the polariton-polariton interaction length (so-called blue shift) $\alpha N$.
 It is expected that  at the temperatures sufficiently higher than  $T_{0}$ the EPJJ device operates in classical way.
 
-The influence of dissipation effects to this picture is evident from our analysis.
-The observation of quantum tunneling processes become possible only within short time intervals when the dissipation cannot essentially affected to the system.
-Otherwise, after some time interval dissipation leads to crossover in the phase dynamics and destroy the W--potential as whole, see Fig.
-\ref{pic:phase}.
-In this case permanent Rabi  oscillations of Josephson junction phase occurs within adiabatic approach.
-To determine quantum either classical properties of this oscillations it is necessary to study fluctuations of the exciton polariton system beyond the semiclassical approach represented in Sec.\ref{sec:non-equilibrium}}.
-For moderate dissipation rates and at the temperatures (or relevant polariton gas densities) sufficiently below the temperature of $T_{0}$   the EPJJ device is  capable for various applications where quantum tunneling effect is crucial.
+The influence of dissipation effects originating from the radiative decay of polaritons by photon tunneling through the Bragg mirrors is revealed by our analysis.
+The observation of quantum tunneling processes only becomes possible within short time intervals where the dissipation cannot essentially affected to the system.
+Otherwise, after some time interval the dissipation leads to crossover in the phase dynamics and it damages the W--potential as a whole, see Fig. \ref{pic:phase}.
+In this case permanent Rabi  oscillations of Josephson junction phase occurs within the adiabatic approach.
+To reveal either quantum of classical nature of these oscillations it is necessary to study the fluctuations of the exciton polariton system beyond the semiclassical approach represented in Sec.\ref{sec:non-equilibrium}}.
+For moderate dissipation rates and at temperatures (or relevant polariton gas densities) sufficiently below the temperature of $T_{0}$ the EPJJ device is suitable for various applications where the quantum tunneling effect is crucial.
 
-First, it is quantum information processing and especially quantum annealing problem  with exciton polariton condensates that can be enhanced with the help of bosonic stimulation phenomena {\cite{Yan}.
+First, it is quantum information processing and especially the quantum annealing problem  with exciton polariton condensates that allow for acceleration of the quantum annealing due to the final state bosonic stimulation {\cite{Yan}.
 Notably the results obtained by us can be implemented  here in new way.
-In order, quantum tunneling effect might be utilized  for design exciton polariton phase qubits similarly to superconductor devices, but in optical wavelength domain, cf.
-\cite{Makhlin}.
+In order, quantum tunneling effect might be utilized  for design exciton polariton phase qubits similarly to superconductor devices, but in optical wavelength domain, \cite{Makhlin}.
 Actually,  two minima located at the points $-z_{min}$ and $+z_{max}$ of $W$-shape quantum phase potential in Fig.
 \ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively.
-However, in our case such qubits much more easier to tailor by external optical or electrical pump.
+However, in our case such qubits may be tailored by external optical or electrical pump.
 As a result, quantum annealing problem can be experimentally solved
-with help of this type of qubits, cf.\cite{Johnson}.
+with help of this type of qubits \cite{Johnson}.
 
-Another promising area of potential applications of obtained results with quantum exciton polariton states is connected with quantum metrology purposes.
-More precisely, EPJJs can be useful for creation of interferometers and/or gyroscopes operating with the phase of  exciton polariton condensates in quantum regime, cf.
-\cite{Pezze, Gulevich}.
-We speak here about measurement of the phase shift with high precision accuracy.
-It is possible to show that for the Fock regime described by us in the paper the dispersion of the quantum phase approaches to so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is minimal accessible error for the phase measurement in respect of total particle number.
-The results relate to this problem we will publish in forthcoming papers.
+Another promising area of potential applications of the obtained results is quantum metrology.
+In particular, EPJJs can be useful for realisation of interferometers and/or gyroscopes operating with the phase of  exciton polariton condensates in the quantum regime \cite{Pezze, Gulevich}.
+The high accuracy measurements of the phase relations between polariton condensates would be needed in this case.
+It is possible to show that for the Fock regime the dispersion of the quantum phase approaches the so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is the minimal accessible error for the phase measurement for the given total number of particles.
 
@@
 \label{sec:acknowledgement}}
-We acknowledge financial support from RFBR, Grants No. 15-52-52001 and No. 14-02-97503.
-A. Kavokin acknowledges the support from HORIZON 2020 RISE project CoExAn (Grant No. 644076).
+We acknowledge the financial support from RFBR, Grants No. 15-52-52001 and No. 14-02-97503.
+A. Kavokin acknowledges the support from HORIZON 2020 RISE project CoExAn (Grant No. 644076) and the EPSRC Established Career fellowship on Quantum Polaritonics RP 008833.
 
-\appendix
-\section{EXTENDED  MODEL OF EPJJ \label{sec:model}}
+%% -SUPPLEMENTAL- %%
+\pagebreak
+\widetext
+\begin{center}
+\textbf{Supplemental Materials: Extended  Model of EPJJ}
+\end{center}
 
-To derive Eq.(\ref{eq:hamiltonian_spin}) we consider equilibrium exciton polariton condensate trapped in a symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ defines the distance between potential minima, $h$ is depth of the potential.
-% 
-%\begin{figure}[ht]
-%\center{\includegraphics[width=0.5\linewidth]{pic/potential_sym_asym.png}}
-%\caption{
-%Confined double-well potential for exciton polariton coupled condensate channels with symmetric $(\Phi_+(x))$ and asymmetric $(\Phi_-(x))$ wavefunctions obtained numerically by solving stationary GPE (\ref{eq:stationary}).
-%The dimensionless parameters for the calculations are: $h = 10$, $x_0 = 1$, $\mu_+ = 5.7355$, $\mu_- = 6.5653$.
-%\label{pic:potential_sym_asym}
-%\end{figure}
-%
-The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the second quantized form as:
+\setcounter{equation}{0}
+\makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\citenumfont}[1]{S#1}
+
+To derive Eq.(\ref{eq:hamiltonian_spin}) we consider an equilibrium exciton polariton condensate trapped in a symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ is the distance between potential minima, $h$ is the depth of the potential.
+The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the using the secondary quanttization formalism as:
 %
@@
 %
-where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilate a particle at the position $x$ and time $t$, $g$ describes two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
-In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator supposing
+where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilates a particle at the position $x$ and time $t$, $g$ describes the two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
+In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator:
 %
@@
 %
-where $\hat{\psi}_{1,2}$ are time dependent operators characterizing condensate at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions which are responsible for it spatial distribution.
-It's instructive to represent  $\Phi_{1,2}(x)$ as
+where $\hat{\psi}_{1,2}$ are time dependent operators characterizing the condensates at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions in real space.
+It's convenient to represent $\Phi_{1,2}(x)$ as
 %
@@
 %
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
-%
-%\begin{equation}
-%\mu_{\pm} \Phi_{\m} = -\dfrac{\hbar^2}{2m} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3.
-%\label{eq:stationary}
-%\end{equation}
-%
-and normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is chemical potential.
-As a result an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes total number of particles.
+where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying the stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
+and the normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is a chemical potential.
+As a result, an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes the total number of particles.
 Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
@@
 %
-where we made denotations $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
+where we have denoted $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
 $A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.
 
-Hamiltonian (\ref{eq:hamiltonian}) represents extended model for internal Josephson junction effect with exciton polariton condensates trapped in double-well potential.
-The ``additional'' terms with $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize density induced and pair tunneling, respectively.
-Generally, our model implies existence of quantum tunneling of the particles between wells with effective (nonlinear) tunneling rate $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
+Hamiltonian (\ref{eq:hamiltonian}) describes the non-linear model of a Josephson junction effect with exciton polariton condensates trapped in a double-well potential.
+The terms containing $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize the non-linear contribitions to the tunneling of single polaritons and polariton pairs, respectively.
+The effective (nonlinear) tunneling rate governed by these terms is $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
 
-The contribution from relevant coefficients on can be estimated from variational ansatz $\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]$,
-%
-%\begin{equation}
-%\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big],
-%\label{eq:two_modes_eq}
-%\end{equation}
-%
-where $a$ is width of condensate wavefunctions at each wells (we suppose them equal to each other), defined from normalization conditions.
-% In Fig. \ref{pic:gamma_pm_vs_g} the behavior of normalized coefficients $\dfrac{\gamma_{ij}}{g}$ $i,j \in \{+,-\}$ as a function of half of inter-well distance $x_0$ is shown.
-It is important that differences between various $\gamma_{ij}$ rapidly vanish with increasing the inter-well distance $2x_0$.
-We can suppose $\Gamma = C = 0$ for $x_0 >> a$.
-This limit exactly corresponds to familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
-%
-%\begin{figure}[ht]
-%\center{\includegraphics[width=0.5\linewidth]{pic/ypm_x0.eps}}
-%\caption{Dependences of normalized matrix elements $\gamma_{ij} / g$ on $x_0 / a$. \label{pic:gamma_pm_vs_g}}
-%\end{figure}
-%
+The relevant coefficients can be estimated using the variational ansatz $\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]$, where $a$ is the localisation length of the condensate wavefunctions in each of two potential wells which are assumed identical.
+The amplitudes $A_+$ and $A_-$ are given by the normalization conditions.
+It is important that differences between various rates $\gamma_{ij}$ rapidly vanish with the increasing the inter-well distance $2x_0$.
+We shall assume $\Gamma = C = 0$ for $x_0 >> a$.
+This limit corresponds to the familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
 Now let us introduce the pseudo spin operators
@@
 %
-Inserting (\ref{eq:pseudo_spin}) into the (\ref{eq:hamiltonian}) we arrive at Eq.(1)  
-with 
-%the equation
-%
-%\begin{equation}
-%\hat{H} = \alpha \hat{S}_z^2 + \beta %\hat{S}_x^2 - B \hat{S}_x,
-%\label{eq:hamiltonain_spin_appendix}
-%\end{equation}
-%
-$\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
-We also chose $x_0$ obeying the condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ supposing $\Gamma = 0$ for simplicity.
+Inserting (\ref{eq:pseudo_spin}) into the (\ref{eq:hamiltonian}) we obtain Eq.(1) with $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
+We also chose $x_0$ obeying the condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ assuming $\Gamma = 0$ for simplicity.
 

### 2017-03-29 hegel/CFDS.m

@@ -12,15 +12,15 @@ V = @(x) x .^ 2;
 Omega = params(2);
 
 % Nonlinear cosine potential
-g = @(x) - cos(2 * Omega * x);
+g = @(x) cos(2 * Omega * x);
 
 xstep = 0.005;
 xspan = [-6 6];
 xgrid = xspan(1):xstep:xspan(2);
 Nx = length(xgrid);
 
-tstep = 0.01;
-tspan = [0 12];
+tstep = 0.02;
+tspan = [0 36];
 tgrid = tspan(1):tstep:tspan(2);
 Nt = length(tgrid);
 

### 2017-03-29 hegel/get_antisymmetric_mode.m

@@ -1,4 +1,4 @@
-function [ X, U ] = get_symmetric_mode( params, C, xspan )
+function [ X, U ] = get_antisymmetric_mode( params, C, xspan )
 % Calculate a symmetric mode using the parameter C of the asymptotic 'asympt'
 %
 % INPUT:
@@ -8,12 +8,12 @@ xstart = xspan(1);
 
 init = asympt_left(params, C, xstart);
 
-[X, U] = f_solve(params, xspan, init, 2 ^ 12);
+[X, U] = f_solve(params, xspan, init, 2 ^ 14);
 
 X = [X; -X(end-1:-1:1)];
 U = [
 	U(:, 1), U(:, 2);
-	U(end-1:-1:1, 1), -U(end-1:-1:1, 2)
+	-U(end-1:-1:1, 1), U(end-1:-1:1, 2)
 ];
 
 end

### 2017-03-29 hegel/get_spectrum.m

@@ -48,5 +48,5 @@ end
 
 % ------------------------------------------------------------------------
 function potential = f_potential(params, x)
-potential = - cos(2 * params(2) * x);
+potential = cos(2 * params(2) * x);
 end

### 2017-03-29 hegel/get_u_end.m

@@ -5,7 +5,7 @@ eps = 1e-6;
 xstart = xspan(1);
 init = asympt_left(params, C, xstart);
 
-[~, U] = f_solve(params, xspan, init, 2 ^ 12);
+[~, U] = f_solve(params, xspan, init, 2 ^ 14);
 
 u_end = U(end, 1);
 

### 2017-03-29 hegel/get_ux_end.m

@@ -5,6 +5,10 @@ init = asympt_left(params, C, xstart);
 
 [~, U] = f_solve(params, xspan, init, 2 ^ 12);
 
-ux_end = U(end, 2);
+if isempty(U)
+    ux_end = NaN;
+else
+    ux_end = U(end, 2);
+end
 
 end

### 2017-03-29 hegel/main.m

@@ -34,9 +34,59 @@ end
 %%
 clc; clear
 
-omega = 2.9; Omega = 10;
+omega = 1.3; Omega = 8;
 params = [omega Omega];
-xspan = [-8 0];
+xspan = [-5 0];
+
+get_u_end_params = @(C) get_u_end(params, C, xspan);
+
+c0 = 0.01;
+cstep = 0.5;
+u_end_0 = get_u_end_params(c0);
+
+eps = 1e-6;
+
+while true
+	c1 = c0 + cstep;
+	u_end_1 = get_u_end_params(c1);
+		
+	if sign(u_end_0) ~= sign(u_end_1)
+		cmode = dichotomy(get_u_end_params, c0, c1, eps);
+		break
+	else
+		c0 = c1;
+		u_end_0 = u_end_1;
+	end
+end
+
+[X, U] = get_antisymmetric_mode(params, cmode, xspan);
+figure
+subplot(1,2,1)
+plot_mode(params, X, U)
+
+eigs = get_spectrum(params, X, U, 128);
+subplot(1,2,2);
+plot_spectrum(params, eigs);
+
+%%
+[Grid, U, Norm] = CFDS(params, X, U(:, 1));
+
+%%
+N = 1000;
+C = linspace(0, 6, N);
+
+ux_end = zeros(1, N);
+
+for i = 1:N
+	ux_end(i) = get_ux_end_params(C(i));
+end
+
+plot(C, ux_end);
+
+%%
+omega = 26.17; Omega = 8;
+params = [omega Omega];
+xspan = [-5 0];
 
 get_ux_end_params = @(C) get_ux_end(params, C, xspan);
 
@@ -64,53 +114,61 @@ figure
 subplot(1,2,1)
 plot_mode(params, X, U)
 
-%%
-eigs = get_spectrum(params, X, U, 256);
+eigs = get_spectrum(params, X, U, 128);
 subplot(1,2,2);
 plot_spectrum(params, eigs);
 
 %%
-[Grid, U, Norm] = CFDS(params, X, U(:, 1));
+
+for i = -15:15
+    plot([(pi + 2 * pi * i) / (2 * Omega), (pi + 2 * pi * i) / (2 * Omega)], [0, 12], 'Color', 'red', 'LineWidth', 2);
+end
 
 %%
-N = 1000;
-C = linspace(0, 6, N);
+clc; clear
 
-ux_end = zeros(1, N);
+omega = -26.17; Omega = 8;
+params = [omega Omega];
[…]

### 2017-03-29 hegel/mex/functions.h

@@ -15,7 +15,7 @@ Point<2> hegel(double x, Point<2> u, double* param)
 	double omega = param[0], Omega = param[1];
 	
 	du[0] = u[1];
-	du[1] = -(omega - pow(x, 2)) * u[0] + (cos(2 * Omega * x)) * pow(u[0], 3);
+	du[1] = -(omega - pow(x, 2)) * u[0] - (cos(2 * Omega * x)) * pow(u[0], 3);
 	return du;
 }
 

### 2017-03-29 hegel/ode.m

@@ -5,6 +5,6 @@ function df = ode( x, f, params )
 %	
 
 [omega, Omega] = parse_params(params);
-df = [f(2), -(omega - x^2) * f(1) + cos(2 * Omega * x) * (f(1)^3) ];
+df = [f(2), -(omega - x^2) * f(1) - cos(2 * Omega * x) * (f(1)^3) ];
 
 end

### 2017-03-29 phase_transition/preparing_paper.m

@@ -269,8 +269,8 @@ alpha = 1; % Parameter, lambda = beta / alpha
 mass = 1 / (2 * alpha);
 
 % Potential
-lambda = 0.5; Lambda = 0.5; % 1st-order transition
-% lambda = 0.5; Lambda = 0.5; % 2nd-order transition
+% lambda = (?); Lambda = (?); % 1st-order transition
+lambda = 0.5; Lambda = 0.5; % 2nd-order transition
 
 % V = @(x) alpha * (s^2) * ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
 %	- Lambda * cn(x, lambda) ) ./ (dn(x, lambda) .^ 2);
@@ -336,6 +336,15 @@ xlabel('E'); ylabel('h \tau_p / \alpha s')
 
 plot(E, tau_p, 'LineWidth', 2, 'Color', 'black')
 
+%% Something else
+P = (V0 - E) / V0;
+
+figure('Position', [100 100 325 225]);
+plot(T, (P), 'Color', 'black');
+axis([0, (max(T) + max(T)*0.5), -0.1, 1.1]);
+
+xlabel('T'); h = ylabel('$$\sqrt{P}$$');
+set(h, 'Interpreter','latex','fontsize',9) 
 %% Transition temperature
 
 % 2nd order

### 2017-03-31 writing/phase_transition/phase_transition.tex
Work in progress

@@
 We consider a system of two spinless exciton-polariton condensates localised in lateral potential traps created in a planar semiconductor microcavity.
-The condensates are confined by a W-shape potential $U(x)$ possessing two minima at the points $\pm x_0$, see Fig.1.
+The condensates are confined by a W-shape potential $U(x)$ possessing two minima at the points $\pm x_0$, see Fig. \ref{pic:potential_picture}.
 Polaritons are pumped to the condensates from a reservoir of incoherent excitons.
@@
 
-The dependences of the trapping potential $V_0(z)$ on the phase variable $z$ are shown in Fig. \ref{phase_potential}. The period of the functions is  $4K(\lambda)$.
-The dependence of the $\lambda$ parameter on normalized half of the inter-well distance $\dfrac{x_0}{a}$ can be approximated by $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$.
-The well-known behaviour of the quantum phase mesoscopic Josephson junction (that map to the XY--model, \citep{Lago1, Lago2} ) can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in  Fig.\ref{phase_potential}.
+The dependences of the trapping potential $V_0(z)$ on the phase variable $z$ are shown in Fig. \ref{pic:phase_potential}. The period of the functions is  $4K(\lambda)$.
+The dependence of the $\lambda$ parameter on normalized half of the inter-well distance $\dfrac{x_0}{a}$ can be approximated by $\lambda = 0.5 \Big( \exp \Big[ \dfrac{2 x_0^2}{a^2} \Big] - 1 \Big)^{-1}$ by using variational approach,  see Suppl.
+Materials.
+The well-known behaviour of the quantum phase mesoscopic Josephson junction (that map to the XY--model, \citep{Lago1, Lago2} ) can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in Fig.
+\ref{pic:phase_potential}.
 This limit corresponds to  infinitely large inter-well distances, with $x_0 \to \infty$.
@@
 Effective dimension-less potential $V_0(z)$ for (a) $\Lambda = 100$, (b) $\Lambda = 0.5$ , and (c) $\Lambda = 0.01$ as a function of the elliptic integral phase coordinate $z$.
-Points $\pm z_{min}$ and $\pm z_{max}$ in (b) correspond to global minima and maxima of the potential, respectively. \label{phase_potential}}
+Points $\pm z_{min}$ and $\pm z_{max}$ in (b) correspond to global minima and maxima of the potential, respectively; $E$ is the energy of the particle that experiences either quantum tunneling or thermal activation, see Section \ref{sec:quantum_classical}.
+\label{pic:phase_potential}}
 \end{figure}
@@
 Physically, for any value of $\lambda$ -- parameter belonging to the domain 0$<\lambda <1$ the system exhibits (Rabi) oscillations for the phase.
-In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{phase_potential}a and \cite{Anglin}.
+In particular, small amplitude oscillations which are inherent to familiar Rabi regime can be achieved for negligable $\lambda$ --- see Fig. \ref{pic:phase_potential}a and \cite{Anglin}.
 
@@
 In purely quantum limit $\Phi(\phi) \to (2\pi)^{-1/2}$.
-In this regime, when inequality $\Lambda \ll \lambda < 1$ is holds, Eq.(\ref{eq:schrodinger_usual}) transforms to the Mathieu equation that is characterised by the set of eignen states consisting of all Mathieu functions.
+In this regime, when inequality $\Lambda \ll \lambda < 1$ is held, Eq.(\ref{eq:schrodinger_usual}) transforms to the Mathieu equation that is characterised by the set of eignen states consisting of all Mathieu functions.
 
 \textit{Josephson regime} $1/N^2\ll\Lambda <1$.
-This regime corresponds to the intermediate case between Rabi and Fock limits --- see Fig. \ref{phase_potential}b.
+This regime corresponds to the intermediate case between Rabi and Fock limits --- see Fig. \ref{pic:phase_potential}b.
 The behavior of the phase depends on the ratio between the parameters $\Lambda$ and $\lambda$.
@@
 (\ref{eq:schrodinger_usual}) is trapped at the two minima of $V_0(z)$ that correspond to the $W$ -- like potential with coordinates $z_{min} = \pm \cn^{-1}{\frac{\Lambda}{2 \lambda}}$ and appearing for both of Josephson and Fock regimes, see Fig.
-\ref{phase_potential}b,c.
+\ref{pic:phase_potential}b,c.
 The depth of the potential minima depends on the $\lambda$ parameter.
-It is interesting to note that for $\Lambda > 2(1 - \lambda)$ the potential $V_0(z)$ possesses a local minimum at $\pm 2 K(\lambda)$, see Fig. 1b.
+It is interesting to note that for $\Lambda > 2(1 - \lambda)$ the potential $V_0(z)$ possesses a local minimum at $\pm 2 K(\lambda)$, see Fig. \ref{pic:potential_picture}b.
 
@@
 
-Experimentally, exciton-polariton condensates are being observed at elevated temperatures, un to the room temperature in wide-gap semiconductor microcavities \cite{Sanvitto,Guillet}.
+Experimentally, exciton-polariton condensates are being observed at elevated temperatures, up to the room temperature in wide-gap semiconductor microcavities \cite{Sanvitto,Guillet}.
 At high temperatures the validity of the quantum coherent treatment of the Josephson problem is limited.
@@
 To be more specific we consider the tunneling in an effective $W$ -- like potential shown in Fig.
-\ref{phase_potential}b.
+\ref{pic:phase_potential}b.
 We assume the thremal equilibrium condition to be fulfilled for an ensamble of exciton-polaritons at finite temperatures $T$, that would correspond to a hypothetic case of polaritons with the infinite life-time.
@@
 A transition between two stable states (say, between points $-z_{min}$ and $+z_{min}$ in Fig.
-\ref{phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
+\ref{pic:phase_potential}b) can happen  either through the quantum tunneling or, in classical way, due to the thermal activation.
 Obviously, at high temperatures such as $k_{B}T\ge\Delta V$ ($\Delta V$ is the height of the barrier between two states with minimum of potential energy) the particle jumps over the barrier governed by the thermoactivation (Arrhenius) escape rate $\Gamma \sim e^{-\Delta V /k_{B}T}$ \cite{Larkin}.
@@
 %
-where $\tau_p = \hbar / k_B T$ is a thermon period corresponding to the energy $E(\tau_p)$;
+where $\tau_p = \hbar / k_B T$ is a thermon period corresponding to the energy $E(\tau_p)$ and shown in Fig. \ref{pic:phase_potential}b;
 %
@@
 %
-In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are the turning points, see Fig. \ref{phase_potential}b.
+In (\ref{eq:thermon_period}) the $z_{1,2}(E)$ are the turning points, see Fig. \ref{pic:phase_potential}b.
 Eqs.(\ref{eq:total_energy}),(\ref{eq:thermon_period}) taken at the energy $E = 0$ and temperature $T = 0$ characterize the instanton solution with an infinite period.
@@
 
-In Fig. \ref{pic:action_period}a we represent the results exhibiting 1st-order PT inherent to narrow shadow domain in Fig.\ref{pic:phase_boundary_combined}.
+In Fig.
+\ref{pic:action_period}a we represent the results exhibiting 1st-order PT inherent to narrow shadow domain in Fig.
+\ref{pic:phase_boundary_combined} where discontinuity of the derivative $dS / dT$ occurs.
 It is clearly seen that the first derivative of $S_{min}$ is discontinuous in this case and the dependence of the normalized thermon period  $\tau_p / \tau_0$ on the energy $E$ is non-monotonic, see the inset in Fig.
@@
 
-Analytically, the critical temperature $T_{c}^{(1)}$ may be estimated from $T_{c}^{(1)} = \Delta V / B$, where $B$ is an instanton action that can be represented as $B = S(E_{min})$.
+Analytically, the critical temperature $T_{c}^{(1)}$ may be estimated from $T_{c}^{(1)} = \Delta V / S_{inst}$, where $S_{inst}$ is an instanton action that can be represented as $S_{inst} = S(E_{min})$.
 After some straightforward calculations for $B$ we obtain
@@
 \begin{array}{c}
-B = S(E_{min}) = 2 s \hbar \left[ \ln \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right].
+S_{inst} = S(E_{min}) = 2 s \hbar \left[ \ln \frac{2 \sqrt{\lambda} + \sqrt{4 \lambda^2 - \Lambda^2}}{2 \sqrt{\lambda} - \sqrt{4 \lambda^2 - \Lambda^2}} - \frac{\Lambda}{\sqrt{\lambda (1 - \lambda)}} \arctan \left( \frac{\sqrt{(1 - \lambda) (4 \lambda^2 - \Lambda^2)}}{\Lambda} \right) \right].
 \end{array}
@@
 
-{\red
+The connection with phenomenological Landau theory of phase transitions  (cf. \cite{Lif}) can be obtained by introducing the ``order parameter'' $P$ that is  (cf. [34]).
 %
 \begin{equation}
-P = \sqrt{\frac{V(0) - E}{\Delta V}}.
+P = \sqrt{\dfrac{V(0) - E}{\Delta V}}.
 \label{eq:p_parameter}
@@
 %
-}
+
+Physically, $P$ -- parameter describes  seminal features of potential shape for the ``particle'' possessing energy $E$ -- see Fig. \ref{pic:phase_potential}b.
+Figure \ref{pic:p_parameter} shows the behaviour of the introduced order parameter.
+One can see that the phases corresponding to the quantum tunneling and classical thermal activations are separated by the second order phase transition.
 
@@
 \caption
-{The dependence of the $P$ -- parameter on the normalized temperature $T/T_{0}$.
-\label{pic:temperatures}}
+{The dependence of the $P$ -- parameter on the normalized temperature $T/T_{0}$.  The parameters $\lambda$, $\Lambda$ are the same as in Fig. \ref{pic:action_period}b.
+\label{pic:p_parameter}}
 \end{figure}
 %
-
 In the optical experiments one usually has a better control of the exciton-polariton density than their effective temperature, see e.g. \cite{Sanvitto,Guillet}.
@@
 
-Now let us consider the decay of the state of the system that corresponds to the upper minimum of the potential $V(z)$ located at $\pm 2K(\lambda)$ in Fig.\ref{phase_potential}b and exists for $\Lambda > 2(1 - \lambda)$.
+Now let us consider the decay of the state of the system that corresponds to the upper minimum of the potential $V(z)$ located at $\pm 2K(\lambda)$ in Fig.
+\ref{pic:phase_potential}b and exists for $\Lambda > 2(1 - \lambda)$.
 Physically, the decay takes place because of the tunneling of our effective particle through the barrier located at one of the points $z_{max} = \pm \cn^{-1} \left( -\frac{2(1 - \lambda)}{\Lambda} \right)$.
@@
 Now let us consider the EPJJ accounting for the finite exciton polariton lifetime $\tau_{pol}$. 
-The finite radiative lifetime is a crucial characteristic of any polariton system and, striktly speaking, can never be ignored.
+The finite radiative lifetime is a crucial characteristic of any polariton system and, strictly speaking, can never be ignored.
 Obviously, in order to allow for the Josephson oscillations, the characteristic time $\tau_0$ that is responsible for quantum tunneling effects  should be shorter than all characteristic times describing non-equilibrium processes in the exciton-polariton gas, including the radiative decay.
@@
 %
-The condition (\ref{eq:lifetime}) is fulfilled in the experimental work \cite{Dominici}, in particular.
-Here we examine a different situationn amely, the case where the exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
+The condition (\ref{eq:lifetime}) is fulfilled in the experimental work [30], in particular.
+Here we examine a different situation namely, the case where the exciton polariton lifetime $\tau_{pol}$ is comparable with $\tau_{0}$.
 Note that this situation is realized the multiple experiments dealing with non-equilibrium exciton polariton condensates, see e.g. [1,2, 16-18].
@@
 Equations ({\ref{eq:pseudo-spin}}) look similar to those written for a non-dissipative system but with the time dependent parameters $\alpha'(t) = (1/ \Lambda) \exp(-2 \kappa' t')$, $\beta'(t) = (\lambda / \Lambda) \exp(-2 \kappa' t')$, $\kappa' = \kappa / B$ \cite{Sedov}.
-Taken out the dissipation, Eqs.\ ({\ref{eq:pseudo-spin}}) possesses a bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to the solid black curve in Fig.1b.
+Taken out the dissipation, Eqs.\ ({\ref{eq:pseudo-spin}}) possesses a bifurcation point $\lambda / \Lambda= 1 / 2$ that corresponds to the solid black curve in Fig. \ref{pic:phase_potential}b.
 
@@
 \center{\includegraphics[width=\linewidth]{pic/phase_potential_dissipation.eps}}
-\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves, respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \alpha s / \hbar$) vs time for $\kappa/\hbar = 0.1 THz$.
+\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves, respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \pi \hbar / \alpha s $) vs time for $\kappa/\hbar = 0.1 THz$.
 Initial conditions are $S_z(0) = S_x(0) = 0$, $S_y(0) = 1$, and $\phi(0) = \pi / 2$, respectively.
@@
 where $\tau$ is the time elapsed after the oscillation sets in, and $A$ is the amplitude of oscillations at $\tau = 0$.
-At large enough times, $\omega(t) \approx$ $B/ \hbar$ and permanent Rabi  oscillations for the Josephson junction phase $\phi$ are established, see Fig. 5a and Ref. {\cite{Permamemt}.
+At large enough times, $\omega(t) \approx$ $B/ \hbar$ and permanent Rabi  oscillations for the Josephson junction phase $\phi$ are established, see Fig. \ref{pic:phase}a and Ref. {\cite{Permamemt}.
 To distinguish between the quantum and classical character of these oscillations, a purely quantum approache to the problem should be considered.      
@@
 Actually, two minima located at the points $-z_{min}$ and $+z_{max}$ of $W$-shape quantum phase potential in Fig.
-\ref{phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively.
+\ref{pic:phase_potential}b can be used for initialization of exciton polariton qubit states $\ket{0}$ and $\ket{1}$ similarly to superconductor flux qubits, respectively.
 However, in our case such qubits may be tailored by external optical or electrical pump.
-As a result, quantum annealing problem can be experimentally solved
-with help of this type of qubits \cite{Johnson}.
+As a result, quantum annealing problem can be experimentally solved with help of this type of qubits \cite{Johnson}.
 

### 2017-03-31 phase_transition/preparing_paper.m

@@ -269,7 +269,7 @@ alpha = 1; % Parameter, lambda = beta / alpha
 mass = 1 / (2 * alpha);
 
 % Potential
-% lambda = (?); Lambda = (?); % 1st-order transition
+% lambda = 0.9; Lambda = 0.1; % 1st-order transition
 lambda = 0.5; Lambda = 0.5; % 2nd-order transition
 
 % V = @(x) alpha * (s^2) * ( ((1/4) * (Lambda ^ 2) - lambda * (1 - lambda)) * (sn(x, lambda) .^ 2) ...
@@ -305,7 +305,7 @@ for i = 1:length(E)
 	fprintf('%i\n', i);
 	
 	[xleft, xright] = roots_near_x0(@(x) -Vb(x) + E(i), 0);
-	tau_p(i) = integral(@(x) 1 ./ sqrt(Vb(x) - E(i)),...
+	tau_p(i) = (1 / pi) * integral(@(x) 1 ./ sqrt(Vb(x) - E(i)),...
 		xleft, xright, 'AbsTol', 1e-6);
 
 	% T(i) = planck_const / (boltzmann_const * tau_p(i));
@@ -313,14 +313,14 @@ for i = 1:length(E)
 
 	S(i) = 2 * integral(@(x) sqrt(Vb(x) - E(i)),...
 		xleft, xright, 'AbsTol', 1e-6) + ...
-		E(i) * tau_p(i);
+		pi * E(i) * tau_p(i);
 	
 	S0(i) = V0 * tau_p(i);
 end
 
 T_thermal = min(T):0.001:(2*max(T));
 % S_thermal = (planck_const * V0) ./ (boltzmann_const * T_thermal);
-S_thermal = V0 ./ T_thermal;
+S_thermal = pi * V0 ./ T_thermal;
 
 % Plotting
 figure('Position', [100 100 650 225]);
@@ -332,7 +332,7 @@ plot(T, S, 'LineWidth', 2, 'Color', 'black');
 plot(T_thermal, S_thermal, '--', 'Color', 'black');
 
 subplot(1, 2, 2); hold on
-xlabel('E'); ylabel('h \tau_p / \alpha s')
+xlabel('E'); ylabel('\tau_p / \tau_0')
 
 plot(E, tau_p, 'LineWidth', 2, 'Color', 'black')
 
@@ -340,11 +340,11 @@ plot(E, tau_p, 'LineWidth', 2, 'Color', 'black')
 P = (V0 - E) / V0;
 
[…]

### 2017-04-15 writing/phase_transition/phase_transition.tex
srep

@@
-\documentclass[aps, pre, preprint, groupedaddress, superscriptaddress, showkeys, showpacs] {revtex4-1}
+\documentclass[fleqn,10pt]{wlscirep}
 
@@
 
-% Remove ugly line above reverences
-\def\bibsection{\section*{\refname}}
-
 % For the debug usage only
@@
 
-\begin{document}
-
-\title{{Exciton-polariton Josephson junctions at finite temperatures}}
-
-\author{M. E. Lebedev}
-\affiliation{ITMO University, St. Petersburg 197101, Russia}
-
-\author{D. A. Dolinina}
-\affiliation{ITMO University, St. Petersburg 197101, Russia}
-
-\author{S. M. Arakelian}
-\affiliation{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}
-
-\author{Tien-Chang Lu}
-\affiliation{Department of Photonics, National Chiao Tung University, Hsinchu 300, Taiwan}
-
-\author{A. V. Kavokin}
-\affiliation{Spin Optics Laboratory, St. Petersburg State University, Ul’anovskaya, Peterhof, St. Petersburg 198504, Russia}
-\affiliation{School of Physics and Astronomy, University of Southampton, SO17 1BJ Southampton, United Kingdom}
-\affiliation{Istituto CNR-SPIN, Viale del Politecnico 1, I-00133, Rome, Italy}
-
-\author{A. P. Alodjants}
-\email{alexander\_ap@list.ru}
-\affiliation{ITMO University, St. Petersburg 197101, Russia}
-\affiliation{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}
-
-\date{\today}
-
-\begin{abstract}
-We consider finite temperature effects in a non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by complicated potential energy landscapes (PEL) consisting of sets of barriers and wells.
-We show that the transition between  thermal  activation (classical) and tunneling (quantum) regimes exhibits universal features of the first and second order phase transition (PT) depending on the PEL for two polariton condensates.
-In the presence of dissipation the relative phase of two condensates exhibits non-equilibrium PT from the quantum regime characterized by efficient tunneling of polaritons to the regime of permanent Josephson or Rabi oscillations, where the tunneling is suppressed, respectively.
-This analysis paves way for the application of coupled polariton condensates for the realisation of a quantum annealing algorithm.
-
-\end{abstract}
-
-\pacs{\dots}
-\keywords{\dots}
-
-\maketitle
-
+% Elliptic functions
 \newcommand{\sn}{\textrm{sn}}
@@
 
-\section{Introduction \label{sec:introduction}}
+% Title and authors
+\title{Exciton-polariton Josephson junctions at finite temperatures}
+
+\author[1]{M. E. Lebedev}
+\author[1]{D. A. Dolinina}
+\author[2]{Kuo-Bin Hong}
+\author[2]{Tien-Chang Lu}
+\author[3, 4, 5]{A. V. Kavokin}
+\author[1, 6, *]{A. P. Alodjants}
+
+\affil[1]{ITMO University, St. Petersburg 197101, Russia}
+\affil[2]{Department of Photonics, National Chiao Tung University, Hsinchu 300, Taiwan}
+\affil[3]{Spin Optics Laboratory, St. Petersburg State University, Ul’anovskaya, Peterhof, St. Petersburg 198504, Russia}
+\affil[4]{School of Physics and Astronomy, University of Southampton, SO17 1BJ Southampton, United Kingdom}
+\affil[5]{Istituto CNR-SPIN, Viale del Politecnico 1, I-00133, Rome, Italy}
+\affil[6]{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}
+
+\affil[*]{alexander\_ap@list.ru}
+
+% \keywords{\dots}
+
+\begin{abstract}
+
+We consider finite temperature effects in a non-standard Bose-Hubbard model for an exciton polariton Josephson junction (EPJJ) that is characterised by complicated potential energy landscapes (PEL) consisting of sets of barriers and wells.
+We show that the transition between  thermal  activation (classical) and tunneling (quantum) regimes exhibits universal features of the first and second order phase transition (PT) depending on the PEL for two polariton condensates.
+In the presence of dissipation the relative phase of two condensates exhibits non-equilibrium PT from the quantum regime characterized by efficient tunneling of polaritons to the regime of permanent Josephson or Rabi oscillations, where the tunneling is suppressed, respectively.
+This analysis paves way for the application of coupled polariton condensates for the realisation of a quantum annealing algorithm.
+
+\end{abstract}
+
+\begin{document}
+
+\flushbottom
+\maketitle
+
+% (?)
+\thispagestyle{empty}
+
+\section*{Introduction}
 
@@
 %
+
 In the present paper we study the effect of a finite effective temperature on the coupling of quasi-equilibrium exciton-polariton condensates accounting for the competing thremal and quantum annealing effects.
-
 Recently Yongbao Sun et al \cite{Snoke_2017} reported the observation of a quasi-equilibrium low branch exciton polariton condensate in a high Q-factor microcavity characterised by a remarkably long photon lifetime of $135ps$.
@@
 
-\section{The Quantum Phase Model \label{sec:quantum_phase}}
+\section*{Results}
+
+\subsection*{The Quantum Phase Model \label{sec:quantum_phase}}
 
@@
 We will show that this term becomes essential if the barrier separating two condensates is sufficiently large.
-
 It is convenient to introduce the pseudo-spin operators in a form
@@
 Materials.
-The well-known behaviour of the quantum phase mesoscopic Josephson junction (that map to the XY--model, \citep{Lago1, Lago2} ) can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in Fig.
+The well-known behaviour of the quantum phase mesoscopic Josephson junction (that map to the XY--model, \cite{Lago1, Lago2} ) can be recovered from (\ref{eq:hamiltonian_spin}), (\ref{eq:potential}) at $\lambda = 0$ and shown by red curves in Fig.
 \ref{pic:phase_potential}.
@@
 
-\section{Annealing problem versus Quantum-classical PT's \label{sec:quantum_classical}}
+\subsection*{Annealing problem versus Quantum-classical PT's \label{sec:quantum_classical}}
 
@@
 %
-
 The expansion of the potential $V(z)$ into a series and excluding the constant value $V(0)$ gives:
@@
 Let us briefly discuss methods of the experimental study of the quantum-classical PT for the polariton Josephson junctions.
-Our estimations show that, for the experimentally accessible polariton interaction strength of $\alpha N=0.6meV$, characteristic of narrow-band semiconductor samples, $T_{0}$ is about $1.2K$ that corresponds to the thermon effective lifetime of $\tau_{0}=3.5ps$.
+Our estimations show that, for the experimentally accessible polariton interaction strength of $\alpha N=0.6meV$, characteristic of narrow-band semiconductor samples, $T_{0}$ is about $1.1K$ that corresponds to the thermon effective lifetime of $\tau_{0}\approx 7 ps$.
 The value of $T_{0}$ is comparable with a typical temperature of a Bose-Einstein condensation, or, with temperature of the Berezinsky-Kosterlitz-Thouless PT predicted for the dilute weakly interacting exciton polariton gas at thermal equilibrium \cite{Sanvitto,Guillet}.
@@
 
-\section{PT's in the presence of dissipation 
-\label{sec:non-equilibrium}}
+\subsection*{PT's in the presence of dissipation\label{sec:non-equilibrium}}
 
@@
 To be more specific in what follows we shall consider the influence of the dissipation on the EPJJ quantum phase properties in the adiabatic limit \cite{Sols}.
-We start from GP equations obtained from  (\ref{eq:hamiltonian}) for the mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$ at $\Gamma = 0$ ($B = G$), which read as
+We start from GP equations obtained from  (see supplementary equation (S5)) for the mean fields $\psi_{1,2}=<\hat\psi_{1,2}>$ at $\Gamma = 0$ ($B = G$), which read as
 %
@@
 In (\ref{eq:GP}) we have introduced the dissipation term with $\kappa \simeq \hbar/\tau_{pol}$.
-Defining new variables $\Psi_{1,2}$ as $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for the mean field pseudo-spin components (\ref{eq:pseudo_spin}).
+Defining new variables $\Psi_{1,2}$ as $\psi_{1,2} = \Psi_{1,2} \exp(-\kappa t / \hbar)$ for the mean field pseudo-spin components (see supplementary equation (S6)).
 We obtain from (\ref{eq:GP})
@@
 \center{\includegraphics[width=\linewidth]{pic/phase_potential_dissipation.eps}}
-\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves, respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$ ($\tau_0 = \pi \hbar / \alpha s $) vs time for $\kappa/\hbar = 0.1 THz$.
+\caption{(a) -- Normalized phase difference as a function of time; (b) -- effective potential vs phase parameter $z$ for red, black and blue curves, respectively, and (c) -- reduced thermon period $\tau_{p} / \tau_0$  vs time for $\kappa/\hbar = 0.1 THz$.
 Initial conditions are $S_z(0) = S_x(0) = 0$, $S_y(0) = 1$, and $\phi(0) = \pi / 2$, respectively.
@@
 
-\section{Conclusion \label{sec:conclusion}}
+\section*{Discussion \label{sec:conclusion}}
 
@@
 
-First, it is quantum information processing and especially the quantum annealing problem  with exciton polariton condensates that allow for acceleration of the quantum annealing due to the final state bosonic stimulation {\cite{Yan}.
+In order, it is quantum information processing and especially the quantum annealing problem  with exciton polariton condensates that allow for acceleration of the quantum annealing due to the final state bosonic stimulation {\cite{Yan}.
 Notably the results obtained by us can be implemented here in new way.
@@
 
-Another promising area of potential applications of the obtained results is quantum metrology.
-In particular, EPJJs can be useful for realisation of interferometers and/or gyroscopes operating with the phase of  exciton polariton condensates in the quantum regime \cite{Pezze, Gulevich}.
-The high accuracy measurements of the phase relations between polariton condensates would be needed in this case.
-It is possible to show that for the Fock regime the dispersion of the quantum phase approaches the so-called Heisenberg limit ${<(\Delta\phi)^2> \propto \dfrac{1}{N^2}}$ that is the minimal accessible error for the phase measurement for the given total number of particles.
-
-\section{Acknowledgement
-\label{sec:acknowledgement}}
-We acknowledge the financial support from RFBR, Grants No. 15-52-52001 and No. 14-02-97503.
-A. Kavokin acknowledges the support from HORIZON 2020 RISE project CoExAn (Grant No. 644076) and the EPSRC Established Career fellowship on Quantum Polaritonics RP 008833.
-
-%% -SUPPLEMENTAL- %%
-\pagebreak
-\widetext
-\begin{center}
-\textbf{Supplemental Materials: Extended  Model of EPJJ}
-\end{center}
-
-\setcounter{equation}{0}
-\makeatletter
-\renewcommand{\theequation}{S\arabic{equation}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\citenumfont}[1]{S#1}
-
-To derive Eq.(\ref{eq:hamiltonian_spin}) we consider an equilibrium exciton polariton condensate trapped in a symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$; $2x_0$ is the distance between potential minima, $h$ is the depth of the potential.
-The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the using the secondary quanttization formalism as:
-%
-\begin{equation}
-\hat{H} = \int \hat{\psi}^\dag\Big\{ -\dfrac{\hbar^2}{2m_{pol}}  \dfrac{d^2 }{dx^2} + U(x) + \dfrac{g}{2} \hat{\psi}^{\dag} \hat{\psi}  \Big\}\hat{\psi} dx,
-\label{eq:gpe_hamiltonian}
-\end{equation}
-%
-where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilates a particle at the position $x$ and time $t$, $g$ describes the two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
-In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator:
-%
-\begin{equation}
-\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
-\label{eq:two_modes}
-\end{equation}
-%
-where $\hat{\psi}_{1,2}$ are time dependent operators characterizing the condensates at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions in real space.
-It's convenient to represent $\Phi_{1,2}(x)$ as
-%
-\begin{equation}
-\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
-\label{eq:basic_modes}
-\end{equation}
-%
-where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying the stationary Gross-Pitaevskii equations $\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3$
-and the normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is a chemical potential.
-As a result, an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes the total number of particles.
-Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
-% 
-\begin{equation}
-\begin{array}{lcl}
-\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
-& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
-& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
-\end{array}
-\label{eq:hamiltonian}
-\end{equation}
-%
-where we have denoted $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
-$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.
-
-Hamiltonian (\ref{eq:hamiltonian}) describes the non-linear model of a Josephson junction effect with exciton polariton condensates trapped in a double-well potential.
-The terms containing $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize the non-linear contribitions to the tunneling of single polaritons and polariton pairs, respectively.
-The effective (nonlinear) tunneling rate governed by these terms is $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.
-
-The relevant coefficients can be estimated using the variational ansatz $\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]$, where $a$ is the localisation length of the condensate wavefunctions in each of two potential wells which are assumed identical.
-The amplitudes $A_+$ and $A_-$ are given by the normalization conditions.
-It is important that differences between various rates $\gamma_{ij}$ rapidly vanish with the increasing the inter-well distance $2x_0$.
-We shall assume $\Gamma = C = 0$ for $x_0 >> a$.
-This limit corresponds to the familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
-Now let us introduce the pseudo spin operators
-%
-\begin{subequations}
-\begin{align}
-\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\
-\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) \\
-\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 - \hat{\psi}_1^\dag \hat{\psi}_1).
-\end{align}
-\label{eq:pseudo_spin}
-\end{subequations}
-%
-Inserting (\ref{eq:pseudo_spin}) into the (\ref{eq:hamiltonian}) we obtain Eq.(1) with $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
-We also chose $x_0$ obeying the condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ assuming $\Gamma = 0$ for simplicity.
+\section*{Methods}
+\dots
 
@@
 
+\section*{Acknowledgement}
+We acknowledge the financial support from RFBR, Grants No. 15-52-52001 and No. 14-02-97503.
+A. Kavokin acknowledges the support from HORIZON 2020 RISE project CoExAn (Grant No. 644076) and the EPSRC Established Career fellowship on Quantum Polaritonics RP 008833.
+
+\section*{Author contributions statement}
+All authors reviewed the manuscript.
+
 \end{document}

### 2017-04-15 writing/phase_transition/supplementary.tex
srep

\documentclass[10pt]{article}

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{authblk}

% Title and authors
\title{Supplementary materials: \\ Exciton-polariton Josephson junctions at finite temperatures}

\author[1]{M. E. Lebedev\textsuperscript{1}, \\ }
\author[1]{D. A. Dolinina}
\author[2]{Kuo-Bin Hong}
\author[2]{Tien-Chang Lu}
\author[3, 4, 5]{A. V. Kavokin}
\author[1, 6, *]{A. P. Alodjants}

\affil[1]{ITMO University, St. Petersburg 197101, Russia}
\affil[2]{Department of Photonics, National Chiao Tung University, Hsinchu 300, Taiwan}
\affil[3]{Spin Optics Laboratory, St. Petersburg State University, Ul’anovskaya, Peterhof, St. Petersburg 198504, Russia}
\affil[4]{School of Physics and Astronomy, University of Southampton, SO17 1BJ Southampton, United Kingdom}
\affil[5]{Istituto CNR-SPIN, Viale del Politecnico 1, I-00133, Rome, Italy}
\affil[6]{Vladimir State University named after A. G. and N. G. Stoletovs, Gorkii Street 87, Vladimir, Russia}

\affil[*]{alexander\_ap@list.ru}

\date{}

\begin{document}

\maketitle

\setcounter{equation}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}

To derive Eq.(1) we consider an equilibrium exciton polariton condensate trapped in a symmetric one dimensional double-well potential $U(x) = h ((x/x_0)^2 - 1)^2$.
Here $2x_0$ is the distance between potential minima, $h$ is the depth of the potential.
The Hamiltonian for the system of weakly interacting exciton polaritons trapped in an external potential $U(x)$ can be written in the using the secondary quanttization formalism as:
%
\begin{equation}
\hat{H} = \int \hat{\psi}^\dag\Big\{ -\dfrac{\hbar^2}{2m_{pol}}  \dfrac{d^2 }{dx^2} + U(x) + \dfrac{g}{2} \hat{\psi}^{\dag} \hat{\psi}  \Big\}\hat{\psi} dx,
\label{eq:gpe_hamiltonian}
\end{equation}
%
where $\hat{\psi} \equiv \hat{\psi}(x, t)$ is a polariton field operator that annihilates a particle at the position $x$ and time $t$, $g$ describes the two-body (polariton-polariton) scattering length, $m_{pol}$ is low branch polariton effective mass.
In the paper we use so-called two-mode representation of $\hat{\psi}$ - operator:
%
\begin{equation}
\hat{\psi} = \hat{\psi}_1(t) \Phi_1(x) + \hat{\psi}_2(t) \Phi_2(x),
\label{eq:two_modes}
\end{equation}
%
where $\hat{\psi}_{1,2}$ are time dependent operators characterizing the condensates at the left and at the right wells respectively; $\Phi_{1,2}(x)$ are condensate wavefunctions in real space.
It's convenient to represent $\Phi_{1,2}(x)$ as
%
\begin{equation}
\Phi_{1,2} = \dfrac{\Phi_+ \pm \Phi_-}{\sqrt{2}}
\label{eq:basic_modes}
\end{equation}
%
where $\Phi_{\pm}(x) = \pm \Phi_{\pm}(-x)$ are symmetric ($\Phi_+$) and antisymmetric ($\Phi_-$) real wavefunctions obeying the stationary Gross-Pitaevskii equations
%
\begin{equation}
\mu_{\pm} \Phi_{\pm} = -\dfrac{\hbar^2}{2m_{pol}} \dfrac{d^2 \Phi_{\pm}}{dx^2} + U(x) \Phi_{\pm} + g \Phi_{\pm}^3
\end{equation}
%
and the normalization condition $\int \Phi_{\pm}^2 dx = 1$; $\mu_{\pm}$ is a chemical potential.
As a result, an operator $N=\hat{\psi_1}^\dag\hat{\psi_1} + \hat{\psi_2}^\dag\hat{\psi_2}$ characterizes the total number of particles.
Substituting (\ref{eq:basic_modes}), (\ref{eq:two_modes}) into (\ref{eq:gpe_hamiltonian}) we arrive to
% 
\begin{equation}
\begin{array}{lcl}
\hat{H} & = & \dfrac{A}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1^2 + \hat{\psi}_2^{\dag 2} \hat{\psi}_2^2) - \dfrac{G}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\ [8pt]
& & -\dfrac{\Gamma}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_1 \hat{\psi}_2 + \hat{\psi}_1^\dag \hat{\psi}_1^2 \hat{\psi}_2^\dag + \hat{\psi}_1^\dag \hat{\psi}_2^\dag \hat{\psi}_2^2 + \hat{\psi}_1 \hat{\psi}_2^{\dag 2} \hat{\psi}_2) \\ [8pt]
& & +\dfrac{C}{2} (\hat{\psi}_1^{\dag 2} \hat{\psi}_2^2 + 4 \hat{\psi}_1^\dag \hat{\psi}_1 \hat{\psi}_2^\dag \hat{\psi}_2 + \hat{\psi}_1^2 \hat{\psi}_2^{\dag 2}),
\end{array}
\label{eq:hamiltonian}
\end{equation}
%
where we have denoted $\gamma_{ij} = g \int \Phi_i^2 \Phi_j^2 dx, i,j \in \{+,-\}$,
$A = \frac{1}{4} (\gamma_{++} + \gamma_{--} + 6 \gamma_{+-})$, $\Gamma = \frac{1}{2} (\gamma_{--} - \gamma_{++})$, $C = \frac{1}{4} (\gamma_{++} + \gamma_{--} - 2\gamma_{+-})$, $G = \mu_- - \mu_+ - 2\Gamma$.

Hamiltonian (\ref{eq:hamiltonian}) describes the non-linear model of a Josephson junction effect with exciton polariton condensates trapped in a double-well potential.
The terms containing $\Gamma$ and $C$ in (\ref{eq:hamiltonian}) characterize the non-linear contribitions to the tunneling of single polaritons and polariton pairs, respectively.
The effective (nonlinear) tunneling rate governed by these terms is $G_{eff} = \dfrac{1}{2}(G+\Gamma N - C\hat{\psi}_1^\dag\hat{\psi}_2)$.

The relevant coefficients can be estimated using the variational ansatz $\Phi_{\pm} = A_{\pm} \Big[ \exp \Big( -\dfrac{(x - x_0)^2}{2 a^2} \Big) \pm \exp \Big( -\dfrac{(x + x_0)^2}{2 a^2} \Big) \Big]$, where $a$ is the localisation length of the condensate wavefunctions in each of two potential wells which are assumed identical.
The amplitudes $A_+$ and $A_-$ are given by the normalization conditions.
It is important that differences between various rates $\gamma_{ij}$ rapidly vanish with the increasing the inter-well distance $2x_0$.
We shall assume $\Gamma = C = 0$ for $x_0 >> a$.
This limit corresponds to the familiar problem of two weakly linked condensates at zero temperature, see e.g. \cite{Aleiner, Shelykh_2008, Borgh_2010, Raghavan}.
Now let us introduce the pseudo spin operators
%
\begin{subequations}
\begin{align}
\hat{S}_x = & \dfrac{1}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 + \hat{\psi}_1 \hat{\psi}_2^\dag) \\
\quad \hat{S}_y = & \dfrac{i}{2} (\hat{\psi}_1^\dag \hat{\psi}_2 - \hat{\psi}_1 \hat{\psi}_2^\dag) \\
\hat{S}_z = & \dfrac{1}{2} (\hat{\psi}_2^\dag \hat{\psi}_2 - \hat{\psi}_1^\dag \hat{\psi}_1).
\end{align}
\label{eq:pseudo_spin}
\end{subequations}
%
Inserting (\ref{eq:pseudo_spin}) into the (\ref{eq:hamiltonian}) we obtain Eq.(1) with $\alpha = A - C = 2\gamma_{\pm} > 0$, $\beta = 2C > 0$ and $B = \Gamma N + G > 0$.
We also chose $x_0$ obeying the condition $\gamma_{++} \simeq \gamma_{--} = \gamma$ assuming $\Gamma = 0$ for simplicity.

\begin{thebibliography}{9}

\bibitem{Aleiner}
Aleiner, I. L., Altshuler, B. L. and Rubo, Yu. G., Radiative coupling and weak lasing of exciton-polariton condensates. {\it Phys. Rev. B}, {\bf 85} (2012).

\bibitem{Shelykh_2008}
Shelykh, I. A., Solnyshkov, D. D., Pavlovic, G. and Malpuech, G., Josephson effects in condensates of excitons and exciton polaritons. {\it Phys. Rev. B}, {\bf 78} (2008).

\bibitem{Borgh_2010}
Borgh, M. O., Keeling, J. and Berloff, N. G., Spatial pattern formation and polarization dynamics of a nonequilibrium spinor polariton condensate. {\it Phys. Rev. B}, {\bf 81} (2010).

\bibitem{Raghavan}
Raghavan, S., Smerzi, A., Fantoni, S. and Shenoy, S. R., Coherent oscillations between two weakly coupled Bose-Einstein condensates: Josephson effects, $\pi$ oscillations, and macroscopic quantum self-trapping. {\it Phys. Rev. A}, {\bf 59}, (1999).

\end{thebibliography}

\end{document}

### 2017-09-15 hegel/CFDS.m
Merge from flash-card

@@ -19,7 +19,7 @@ xspan = [-6 6];
 xgrid = xspan(1):xstep:xspan(2);
 Nx = length(xgrid);
 
-tstep = 0.02;
+tstep = 0.002;
 tspan = [0 36];
 tgrid = tspan(1):tstep:tspan(2);
 Nt = length(tgrid);
@@ -100,9 +100,10 @@ for i = 2:Nt
 		
 	end
 	
-	% plot(abs(U(i, :))); drawnow
-	% pause(1e-1)
-	Norm(i) = simpson(abs(U(i, :)) .^ 2, xstep);
+	plot(abs(U(i, :))); drawnow
+    pause(1e-1)
+	
+    Norm(i) = simpson(abs(U(i, :)) .^ 2, xstep);
 	% Logging
 	fprintf('iter = %i of %i, max = %g, norm = %g\n', i, Nt, max(abs(U(i, :))), Norm(i));
 	

### 2017-09-15 hegel/get_spectrum.m

@@ -37,7 +37,7 @@ D = -k^2 * (diag(-N:N) .^ 2);
 Gt{1} = toeplitz([Gf{1}(N+1:2*N+1) zeros(1, N)],...
 					  [Gf{1}(N+1:-1:1)  zeros(1, N)]);
 Gt{2} = toeplitz([Gf{2}(N+1:2*N+1) zeros(1 ,N)],...
-					  [Gf{2}(N+1:-1:1)  zeros(1 ,N)]);
+					  [Gf{2}(N+1:-1:1)  zeros(1, N)]);
 
 M = (D + Gt{2}) * (D + Gt{1});
 

### 2017-09-15 hegel/get_ux_end.m

@@ -3,7 +3,7 @@ function ux_end = get_ux_end( params, C, xspan )
 xstart = xspan(1);
 init = asympt_left(params, C, xstart);
 
-[~, U] = f_solve(params, xspan, init, 2 ^ 12);
+[~, U] = f_solve(params, xspan, init, 2 ^ 14);
 
 if isempty(U)
     ux_end = NaN;

### 2017-09-15 hegel/main.m

@@ -34,39 +34,53 @@ end
 %%
 clc; clear
 
-omega = 1.3; Omega = 8;
-params = [omega Omega];
-xspan = [-5 0];
+pool = 4.9:-0.01:2.8;
+for omega = pool
 
-get_u_end_params = @(C) get_u_end(params, C, xspan);
+%omega = 2.9;
+Omega = 18;
+
+params = [omega Omega];
+xspan = [-6 0];
+
+get_ux_end_params = @(C) get_ux_end(params, C, xspan);
 
 c0 = 0.01;
 cstep = 0.5;
-u_end_0 = get_u_end_params(c0);
+ux_end_0 = get_ux_end_params(c0);
 
-eps = 1e-6;
+eps = 1e-8;
 
 while true
 	c1 = c0 + cstep;
-	u_end_1 = get_u_end_params(c1);
-		
-	if sign(u_end_0) ~= sign(u_end_1)
-		cmode = dichotomy(get_u_end_params, c0, c1, eps);
+	ux_end_1 = get_ux_end_params(c1);
+
+	if sign(ux_end_0) ~= sign(ux_end_1)
+		cmode = dichotomy(get_ux_end_params, c0, c1, eps);
 		break
 	else
 		c0 = c1;
-		u_end_0 = u_end_1;
+		ux_end_0 = ux_end_1;
 	end
 end
 
-[X, U] = get_antisymmetric_mode(params, cmode, xspan);
-figure
-subplot(1,2,1)
-plot_mode(params, X, U)
+[X, U] = get_symmetric_mode(params, cmode, xspan);
+% U = -U;
+% figure
+% subplot(1,2,1)
+% plot_mode(params, X, U)
+% plot(X, U);
 
-eigs = get_spectrum(params, X, U, 128);
-subplot(1,2,2);
-plot_spectrum(params, eigs);
+eigs = get_spectrum(params, X, U, 256 );
+% subplot(1,2,2);
+% plot_spectrum(params, eigs);
+
+plot(eigs, 'o', 'MarkerFaceColor', 'k', 'MarkerSize', 5)
+axis([-1 1 0 9])
+
+
+drawnow
+end
 
 %%
 [Grid, U, Norm] = CFDS(params, X, U(:, 1));
@@ -152,23 +166,3 @@ figure
 cmode = dichotomy(get_ux_end_params, 0.03, 0.08, eps);
 [X, U] = get_symmetric_mode(params, cmode, xspan);
[…]

### 2017-09-15 hegel/mex/functions.h

@@ -7,7 +7,7 @@ using namespace NR;
 // Lyuba Hegel task.
 // NLS with presence of quadratic linear potential and cosine nonlinear potential
 // Equation for nonlinear stationary modes
-// u_{xx} + (\omega - x^2) u - \cos{2 \Omega x} u^3 = 0
+// u_{xx} + (\omega - x^2) u - \sin{2 \Omega x} u^3 = 0
 // Parameters: [\omega \Omega]
 Point<2> hegel(double x, Point<2> u, double* param)
 {

### 2017-09-15 hegel/plot_spectrum.m

@@ -20,12 +20,14 @@ xmax = max(1, 1.2 * max(real(eigenvalues)));
 ymax = 1.2 * max(imag(eigenvalues(real(eigenvalues) > 1e-5)));
 
 if ~isempty(ymax)
-	ymax = max(15, ymax);
+	ymax = max(9.8, ymax);
 else
-	ymax = 15;
+	ymax = 9.8;
 end
 
-axis([-xmax xmax -ymax ymax])
+% axis([-xmax xmax -ymax ymax])
+axis([-xmax xmax 0 ymax])
+
 title(sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2)))
 grid on
 

### 2017-09-15 hegel/test_f_solve.m

@@ -3,7 +3,7 @@ clc; clear
 
 omega = 4; Omega = 0.5;
 params = [omega, Omega];
-xspan = [0 3];
+xspan = [0 3.6];
 init = [0.1 0.1];
 
 intervals = 1024;

### 2018-05-28 hegel/CFDS.m
After sending for the review

@@ -10,17 +10,19 @@ V = @(x) x .^ 2;
 
 % Nonlinear cosine potential parameter
 Omega = params(2);
+P1 = params(3);
 
 % Nonlinear cosine potential
-g = @(x) cos(2 * Omega * x);
+% g = @(x) P1 * cos(Omega * x);
+g = @(x) 1 + P1 * cos(Omega * x);
 
-xstep = 0.005;
+xstep = 0.02;
 xspan = [-6 6];
 xgrid = xspan(1):xstep:xspan(2);
 Nx = length(xgrid);
 
-tstep = 0.002;
-tspan = [0 36];
+tstep = 0.005;
+tspan = [0 12];
 tgrid = tspan(1):tstep:tspan(2);
 Nt = length(tgrid);
 
@@ -33,7 +35,7 @@ U(1, :) = resample(X0, U0, xgrid);
 % Perturbation
 a = 0.01;
 f = 10;
-U(1, :) = U(1, :) .* (1 + a * (1 + cos(f * xgrid)));
+U(1, :) = U(1, :) .* (1 + a * (1 + sin(f * xgrid)));
 
 U(1, 1) = 0;
 U(1, end) = 0;

### 2018-05-28 hegel/_tmp.m

@@ -1,0 +1,81 @@
+%% Fig. 3: (N, \mu) and many branches (symmetric)
+% Stability analysis for modes with linear counterpart
+clc; clear
+
+P0 = 1; P1 = 2; Omega = 8;
+xspan = [-8 0];
+
+% Plain of the parameters
+cstart = 0.1; cstep = 0.1; cend = 250;
+c_values = cstart:cstep:cend;
+mu_start = -1; mu_step = 0.1; mu_end = 8;
+mu_values = mu_start:mu_step:mu_end;
+
+Scan_pairs = [];
+
+% Dichotomy precision
+eps = 1e-9; 
+
+% Scaning
+for i = 1:length(mu_values)
+	fprintf('\\mu value: %i of %i\n', i, length(mu_values));
+	
+	params = [mu_values(i) Omega P1];
+	get_u_end_params  = @(C) get_u_end ('f_solve', params, C, xspan);
+	get_ux_end_params = @(C) get_ux_end('f_solve', params, C, xspan);
+	
+	c_prev = c_values(1);
+	
+	u_end_prev  = get_u_end_params (c_prev);
+	ux_end_prev = get_ux_end_params(c_prev);
+	
+	for j = 2:length(c_values);
+		fprintf('\tC value: %i of %i\n', j, length(c_values));
+		c_next = c_values(j);
+		
+		u_end_next  = get_u_end_params (c_next);
+		ux_end_next = get_ux_end_params(c_next);
+		
+		if sign(u_end_prev) ~= sign(u_end_next)
+			cmode = dichotomy(get_u_end_params, c_prev, c_next, eps);
+			[X, U] = get_antisymmetric_mode('f_solve', params, cmode, xspan);
+			
+			% For debug purpose
+			% plot(X, U);
+			% pause();
+			
+			modes_norm = get_norm(X, U);
+			
+			fprintf('\t\tnew pair: %g, %g, %g\n', cmode, mu_values(i), modes_norm);
+			Scan_pairs = [Scan_pairs; [cmode mu_values(i) modes_norm]];
+			
+			% if modes_norm > 30
+			% 	break
+			% end
+		end
+		
+		if sign(ux_end_prev) ~= sign(ux_end_next)
+			cmode = dichotomy(get_ux_end_params, c_prev, c_next, eps);
+			[X, U] = get_symmetric_mode('f_solve', params, cmode, xspan);
+			
+			% For debug purpose
[…]

### 2018-05-28 hegel/alfimov_approximation.m

@@ -67,11 +67,11 @@ clc; clear
 xstart = -6; xend = 6; xstep = 0.01; xspan = [xstart xend];
 x = xstart:xstep:xend;
 
-mu = 1.1; Omega = 16; sigma_1 = 1; params = [mu Omega sigma_1];
-n = 1; mu_analog = 2 * n + 1;
+mu = 0; Omega = 16; sigma_1 = 1; params = [mu Omega sigma_1];
+n = 0; mu_analog = 2 * n + 1;
 
 u_approx = get_alfimov_approximation(params, n, x);
-plot(x, -u_approx, 'blue');
+plot(x, u_approx, 'blue');
 
 hold on;
 

### 2018-05-28 hegel/continue_mode.m

@@ -1,0 +1,99 @@
+function [ Scan_pairs ] = ...
+	continue_mode( mex_solver_name, mu_target, params, xstart, X, U, cmode, symmetricity )
+%
+% INPUT:
+%
+
+mu_start = params(1); Omega = params(2); P1 = params(3);
+
+if strcmp(symmetricity, 'symmetric')
+	% Even solution
+	get_end = @(mex_solver_name, params, C, xspan) get_ux_end(mex_solver_name, params, C, xspan);
+elseif strcmp(symmetricity, 'antisymmetric')
+	% Odd solution
+	get_end = @(mex_solver_name, params, C, xspan) get_u_end(mex_solver_name, params, C, xspan);
+end
+
+% Continue [X, U] solution on the parameter \mu
+
+% Step may be positive or negative depends on the mu_target and mu_start
+abs_mu_step = 0.01; % why not!?
+
+if mu_target > mu_start
+	% To the right
+	mu_intermediate_values = mu_start:abs_mu_step:mu_target;
+else
+	% To the left
+	mu_intermediate_values = mu_start:(-abs_mu_step):mu_target;
+end
+
+if mu_intermediate_values(end) ~= mu_target
+	mu_intermediate_values = [mu_intermediate_values mu_target];
+end
+	
+cmode_intermediate_values = zeros(1, length(mu_intermediate_values));
+cmode_intermediate_values(1) = cmode;
+
+mode_norm = zeros(1, length(mu_intermediate_values));
+
+% For the first mode
+mode_norm(1) = get_norm(X, U);
+
+% Plotting right here? Why not!?
+subplot(1,2,1)
+plot(mu_intermediate_values(1), mode_norm(1), '*', 'Color', 'red')
+subplot(1,2,2)
+plot(mu_intermediate_values(1), cmode_intermediate_values(1), '*', 'Color', 'red')
+pause(1e-5)
+
+Scan_pairs = [mu_intermediate_values(1) cmode_intermediate_values(1) mode_norm(1)];
+for i = 2:length(mu_intermediate_values)
+	% fprintf('\tContinuation: %i of %i\n', i, length(mu_intermediate_values))
+	params = [mu_intermediate_values(i) Omega P1];
+	
+	get_end_params = @(c) get_end(mex_solver_name, params, c, [xstart 0]);
[…]

### 2018-05-28 hegel/dissipation.m

@@ -1,8 +1,8 @@
 function d = dissipation(xgrid)
 
-dissip_stength = 100;
+dissip_stength = 500;
 
-l = 0.1 * (xgrid(end) - xgrid(1));
+l = 0.2 * (xgrid(end) - xgrid(1));
 L = xgrid(end);
 
 d = zeros(1, length(xgrid));

### 2018-05-28 hegel/get_alfimov_approximation.m

@@ -23,5 +23,8 @@ u_approx = ...
 	U0 * sqrt(Omega) * Hn_solution + ...
 	(U0 ^ 3) * (sigma_1 / sqrt(Omega)) * (Hn_solution .^ 3) .* cos(Omega * x);
 
+% u_approx = ...
+% 	U0 * sqrt(Omega) * Hn_solution;
+
 end
 

### 2018-05-28 hegel/get_eigs_on_.m

@@ -1,0 +1,118 @@
+function [ all_mu, all_eigs ] = ...
+	get_eigs_on_( mex_solver_name, mu_analog, params, xstart )
+
+% -----------------------------------------------------------------------------
+% Nonlinear potential
+% nonlinear_potential = @(params, x) 1 + params(3) * cos(params(2) * x);
+nonlinear_potential = @(params, x) params(3) * cos(params(2) * x);
+% -----------------------------------------------------------------------------
+
+% -----------------------------------------------------------------------------
+% Imaginary window: [-12; +12]
+get_from_window = @(x) x(abs(imag(x)) < 13);
+% -----------------------------------------------------------------------------
+
+mu_target = params(1); Omega = params(2); P1 = params(3);
+mu_aug = 0.025; % augmentation to bifurcate from zero solution
+mu_start = mu_analog - mu_aug;
+
+% Numer of the mode: 0, 1, 2, 3, 4, 5 ...
+n = round((mu_analog - 1) / 2); % \mu = 2n + 1
+
+if mod(n, 2) == 0
+	% Even solution
+	get_end = @(mex_solver_name, params, C, xspan) get_ux_end(mex_solver_name, params, C, xspan);
+else
+	% Odd solution
+	get_end = @(mex_solver_name, params, C, xspan) get_u_end(mex_solver_name, params, C, xspan);
+end
+
+% Find solution in \mu_start and continue it on the parameter \mu
+params = [mu_start Omega P1];
+get_end_params = @(c) get_end(mex_solver_name, params, c, [xstart 0]);
+
+% Find cspan for dichotomy solver
+cstep = 0.1; cstart = cstep; cend = cstart + cstep;
+end_cstart = get_end_params(cstart);
+end_cend = get_end_params(cend);
+
+while sign(end_cstart) == sign(end_cend)
+	cend = cend + cstep;
+	end_cend = get_end_params(cend);
+end
+
+% Dichotomy precision
+eps = 1e-9;
+
+cmode = dichotomy(get_end_params, cstart, cend, eps);
+
+if mod(n, 2) == 0
+	% Even solution
+	[X, U] = get_symmetric_mode(mex_solver_name, params, cmode, [xstart 0]);
+else
+	% Odd solution
+	[X, U] = get_antisymmetric_mode(mex_solver_name, params, cmode, [xstart 0]);
+end
[…]

### 2018-05-28 hegel/get_norm_on_chemical_potential.m

@@ -19,11 +19,12 @@ function [ mu_intermediate_values, mode_norm, stability ] = ...
 
 % -----------------------------------------------------------------------------
 % Nonlinear potential
-nonlinear_potential = @(params, x) 1 + params(3) * cos(params(2) * x);
+% nonlinear_potential = @(params, x) 1 + params(3) * cos(params(2) * x);
+nonlinear_potential = @(params, x) params(3) * cos(params(2) * x);
 % -----------------------------------------------------------------------------
 
 mu_target = params(1); Omega = params(2); P1 = params(3);
-mu_aug = 0.05; % augmentation to bifurcate from zero solution
+mu_aug = 0.025; % augmentation to bifurcate from zero solution
 mu_start = mu_analog - mu_aug;
 
 % Numer of the mode: 0, 1, 2, 3, 4, 5 ...
@@ -65,7 +66,9 @@ else
 end
 
 % Continuation on the parameter \mu
-mu_step = mu_aug; % why not!?
+% mu_step = mu_aug; % why not!?
+mu_step = 0.025; % why not!?
+% mu_step = 0.0125; % why not!?
 
 mu_intermediate_values = mu_start:(-mu_step):mu_target;
 
@@ -110,6 +113,11 @@ for i = 2:length(mu_intermediate_values)
 	% For debug purposes
 	% plot(X, U);
 	% pause()
+	
+	% Temporal break
+	if mode_norm(i) > 65
+		break
+	end
 end
 
 end

### 2018-05-28 hegel/is_stable.m

@@ -15,14 +15,16 @@ function [ stable ] = is_stable( params, nonlinear_potential, X, U, N )
 eigenvalues = get_spectrum(params, nonlinear_potential, X, U, N);
 max_real = max(abs(real(eigenvalues)));
 
-% For debug purpoces
-% plot_spectrum(params, eigenvalues);
-
 % Compareson with zero
-if max_real < 1e-3
+if max_real < 1e-2
 	stable = true;
 else
 	stable = false;
+end
 
+% For debug purpoces
+% plot_spectrum(params, eigenvalues);
+% pause()
+	
 end
 

### 2018-05-28 hegel/newton.m

@@ -3,17 +3,27 @@ function x_root = newton( f, x0 )
 % INPUT:
 %	
 
+MAX_ITERATION = 50;
+
 eps = 1e-6;
 
 df = @(x) (f(x + eps) - f(x - eps)) / (2 * eps);
 
+iter = 0;
 while true
+	iter = iter + 1;
+	
 	x1 = x0 - f(x0) / df(x0);
 	
 	if abs(x1 - x0) < eps
 		break
 	else
 		x0 = x1;
+	end
+	
+	if iter > MAX_ITERATION
+		fprintf('--> MAX_ITERATION\n')
+		break
 	end
 end
 

### 2018-05-28 hegel/pic.m

@@ -2,98 +2,694 @@
 % Alfimov create it for himself...?
 
 %% Fig. 2: (N, \mu) diagrams when \Omega grows up + stability
-% clc; clear
+clc; clear
 
 % 0th mode
-n_0 = 0; mu_analog_0 = 2 * n_0 + 1; mu_target_0 = -2; xstart = -8;
+n_0 = 0; mu_analog_0 = 2 * n_0 + 1; mu_target_0 = -1; xstart = -8;
 
 % 0a
 Omega = 0; P1 = 0; params = [mu_target_0 Omega P1];
-[mu_0a, norm_0a, stability_0a] = get_norm_on_chemical_potential('f_solve', mu_analog_0, params, xstart);
+[mu_0a, norm_0a, stability_0a] = get_norm_on_chemical_potential('f_sigma_solve', mu_analog_0, params, xstart);
 
 % 0b
-Omega = 8; P1 = 2; params = [mu_target_0 Omega P1];
-[mu_0b, norm_0b, stability_0b] = get_norm_on_chemical_potential('f_solve', mu_analog_0, params, xstart);
+Omega = 8; P1 = 1; params = [mu_target_0 Omega P1];
+[mu_0b, norm_0b, stability_0b] = get_norm_on_chemical_potential('f_sigma_solve', mu_analog_0, params, xstart);
 
 % 0c
-Omega = 12; P1 = 2; params = [mu_target_0 Omega P1];
-[mu_0c, norm_0c, stability_0c] = get_norm_on_chemical_potential('f_solve', mu_analog_0, params, xstart);
+Omega = 12; P1 = 1; params = [mu_target_0 Omega P1];
+[mu_0c, norm_0c, stability_0c] = get_norm_on_chemical_potential('f_sigma_solve', mu_analog_0, params, xstart);
+
+% 0d
+Omega = 16; P1 = 1; params = [mu_target_0 Omega P1];
+[mu_0d, norm_0d, stability_0d] = get_norm_on_chemical_potential('f_sigma_solve', mu_analog_0, params, xstart);
 
 % 1st mode
-n_1 = 1; mu_analog_1 = 2 * n_1 + 1; mu_target_1 = -0.5; xstart = -8;
+n_1 = 1; mu_analog_1 = 2 * n_1 + 1; mu_target_1 = 0; xstart = -8;
 
 % 1a
 Omega = 0; P1 = 0; params = [mu_target_1 Omega P1];
[…]

### 2018-05-28 hegel/plot_eigs_on_chemical_potential.m

@@ -1,0 +1,14 @@
+function plot_eigs_on_chemical_potential( mu, eigs )
+
+hold on; set(gca, 'XDir','reverse')
+
+for i = 1:length(mu)
+	if abs(real(eigs(i))) < 0.01
+		plot(mu(i), abs(eigs(i)), '.', 'Color', 'black')
+	else
+		plot(mu(i), abs(eigs(i)), '.', 'Color', 'red')
+	end
+end
+
+end
+

### 2018-05-28 hegel/plot_evolution.m

@@ -10,7 +10,7 @@ image([xrange(1) xrange(2)], [T(1) T(end)], abs(U(:, sel)), 'CDataMapping', 'sca
 set(gca,'YDir','normal');
 xlabel('X')
 ylabel('T')
-title_str = sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2));
+title_str = sprintf('Parameters: mu = %g, Omega = %g', params(1), params(2));
 title(title_str)
 
 end

### 2018-05-28 hegel/plot_pairs.m

@@ -1,0 +1,5 @@
+function [  ] = plot_pair(  )
+
+
+end
+

### 2018-05-28 hegel/plot_spectrum.m

@@ -25,10 +25,10 @@ else
 	ymax = 15;
 end
 
-% axis([-xmax xmax -ymax ymax])
 axis([-xmax xmax -ymax ymax])
+% axis([-xmax xmax -3 3])
 
-title(sprintf('Parameters: omega = %g, Omega = %g', params(1), params(2)))
+title(sprintf('Parameters: mu = %g, Omega = %g', params(1), params(2)))
 grid on
 
 end

### 2018-05-28 hegel/stability_plotter_osc.m

@@ -1,0 +1,18 @@
+function stability_plotter_osc( X, Y, stability )
+%
+% INPUT:
+%	:X:
+
+hold on;
+
+for i = 2:length(X)
+	if stability(i - 1)
+		plot([X(i - 1) X(i)], [Y(i - 1) Y(i)], 'LineWidth', 4, 'Color', [0.6 0.6 0.6])
+	else
+		plot([X(i - 1) X(i)], [Y(i - 1) Y(i)], 'LineWidth', 2, 'Color', [0.6 0.6 0.6])
+	end
+end
+
+end
+
+

### 2018-05-28 writing/hegel/AGLMZ06.tex
clean up #2

%\usepackage[russian]{babel}
%\usepackage{graphicx}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{amsmath}
%  ]{geometry}
%\usepackage[cp1251]{inputenc}
%\usepackage[english,russian]{babel}
%\usepackage{indentfirst}
%\graphicspath{{fig/}}
% --------------------------------------------------------------------------

\documentclass[aps,preprint,showkeys,
]{revtex4}
\usepackage{eurosym}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{color}

\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}

\begin{document}

\title{Localized modes in the Gross-Pitaevskii equation with a parabolic
trapping potential and a nonlinear lattice pseudopotential}
\author{G. L. Alfimov$^{1}$}
\author{L. A. Gegel$^{1}$}
\author{M. E. Lebedev$^{1}$}
\author{Boris A. Malomed$^{2,3}$}
\author{D. A. Zezyulin$^{3,4}$}
\affiliation{$^{1}$Moscow Institute of Electronic Engineering, Zelenograd, Moscow,
124498, Russia.}
\affiliation{$^{2}$Department of Physical Electronics, School of Electrical Engineering,
Faculty of Engineering, Tel Aviv University, Tel Aviv 69978, Israel}
\affiliation{$^{3}$ITMO University, St.~Petersburg 197101, Russia}
\affiliation{$^{4}$Institute of Mathematics with Computer Center, Ufa Scientific Center,
Russian Academy of Sciences, Chernyshevskii str., 112, Ufa 450008, Russia}

\begin{abstract}
We study localized modes (LMs) of the one-dimensional
Gross-Pitaevskii/nonlinear Schr\"{o}dinger equation with a
harmonic-oscillator (parabolic) confining potential, %$V(x)$
and a periodically modulated coefficient in front of the cubic term
(nonlinear lattice pseudopotential). The equation applies to a cigar-shaped
Bose-Einstein condensate loaded in the combination of a magnetic trap and an
optical lattice which induces the periodic pseudopotential via the Feshbach
resonance. Families of stable LMs in the model feature specific properties
which result from the interplay between spatial scales introduced by the
parabolic trap and the period of the nonlinear pseudopotential. Asymptotic
results are also obtained in the case of a rapidly oscillating nonlinear
pseudopotential. We show that the presence of the lattice pseudopotential
may result in: (i) creation of new LM families which have no counterparts in
the case of the uniform nonlinearity; (ii) stabilization of some previously
unstable LM species; (iii) evolution of unstable LMs into a breather trapped
in one well of the lattice pseudopotential.
\end{abstract}

\keywords{collisionally inhomogeneous BEC}
\date{\today}
\maketitle

%\date{\date{\today}}
%\documentclass{article}
%\usepackage[utf8]{inputenc}
%\usepackage[T2A]{fontenc}
%\usepackage[english, russian]{babel}
%\usepackage{graphicx}
%\usepackage{subcaption}
%\usepackage{float}
%\usepackage{amssymb,amsmath}

\graphicspath{ {images/} } %\begin{document}

\section{Introduction}

Since the first production of the Bose-Einstein condensate (BEC) in
ultracold gases \cite{AEMWC95,DMADDKK95,BSTH95}, great progress has been
made in the experimental work with BEC, leading to the observation of
diverse species of matter waves, such as bright and dark solitons, gap
solitons, vortices, and other macroscopic quantum objects \cite{Romanian}.
In particular, apart from temporal or spatial variation of the trap that
confines the BEC, it is possible to control the scattering length (SL) of
interatomic interactions in BEC by means of the Feshbach-resonance (FR)
technique \cite{I98,TT04,KGJ06}. This technique allows one to change the
character of interatomic interactions, switching their sign from repulsive
to attractive ones and vice versa. Being compared to the size of the BEC
cloud, the characteristic scale of the spatial variation of SL may vary from
relatively large (e.g., it is controlled by magnetic FR \cite{Hannaford}) to
moderate or small (for the optically-induced FR \cite{Japan,Cs}). The
interplay of the two characteristic scales, one the trap's size and the
other the scale of the SL variation, opens perspectives for the creation and
handling of novel stable matter-wave patterns \cite{HS}.

The commonly adopted mean-field model for BEC states is based on the
Gross-Pitaevskii equation (GPE) for the macroscopic wave function \cite%
{Pet,Pit}. This equation is, actually, a version of the classical nonlinear
Schr\"{o}dinger equation (NLSE) that takes into account a trapping
potential, $V(x)$, in the linear part of the equation, and a
spatially-dependent coefficient $P(x)$ in front of the cubic term (here,
one-dimensional settings are meant; in more general cases, the effective
one-dimensional nonlinearity, derived by the reduction of the
three-dimensional GPE, may assume algebraic forms, different from the simple
cubic term \cite{Salasnich,Delgado}). The latter $x$-dependent coefficient
defines a \textit{nonlinear pseudopotential }(with the name borrowed from
the theory of metals \cite{pseudo}), which is proportional to the local SL.
Usually, the experimentally relevant magnetic trap is modelled by the
harmonic-oscillator (HO), alias parabolic, potential. As concerns
pseudopotentials, various models have been used, including step \cite%
{ZAKP07,TAM16}, piecewise constant \cite{RKP08}, periodic \cite%
{SM05,WLK13,K17}, linear \cite{TSKF02}, Gaussian \cite{HY08}, and more
sophisticated well-shaped \cite{DM15} functions (for a comprehensive review
on the topic see \cite{KMT11}). In addition to pseudopotentials based in the
self-attractive nonlinearity, spatial modulation of the self-repulsive cubic
nonlinearity induces a new mechanism for the creation of self-trapped modes
in one- two-, and three-dimensional geometries \cite{Barcelona}.

In the present paper we consider the setting with the trapping potential in
the traditional HO form, and a spatially periodic nonlinear pseudopotential
(i.e., a \textit{lattice pseudopotential }\cite{KMT11}). This model
corresponds to atomic-gas BEC loaded in the combination of the HO-shaped
magnetic confinement and the optical lattice which periodically modifies the
local FR strength, cf. settings considered in Refs. \cite{WLK13,K17}, where
it was shown that the periodic modulation of the SL may result in
oscillatory instabilities of simplest dark solitons and stabilization of
more complex states \cite{K17}. It was also shown that the stability of
nonlinear modes depends on mutual position of the nonlinear pseudopotential
and the trapping potential \cite{WLK13}. However, those studies were chiefly
carried out for dark solitons, assuming strictly repulsive interatomic
interactions (in other words, solely positive SL), so that the nonlinear
pseudopotential $P(x)$ does not change its sign. To the best of our
knowledge, a comprehensive analysis of nonlinear localized modes (LMs) in
the HO potential, under the additional action of the periodic (generally,
sign-changing) variation of the SL, has not been reported previously.

The rest of the paper is organized as follows. The model is formulated in
Section II, which is followed by the analysis of small-amplitude LMs in
Section III.

\section{The model and setup}

\label{M_S}

The effectively one-dimensional GPE\ for mean-field wave function $\Psi
\left( x,t\right) $, corresponding to the setting outlined above, is taken,
in a scaled form, as
\begin{equation}
i\Psi _{t}=-\Psi _{xx}+\frac{1}{2}\omega ^{2}x^{2}\Psi -P(x)\Psi |\Psi |^{2},
\label{1D_GP}
\end{equation}%
where $\omega ^{2}$ is the strength of the HO trapping potential, and the
nonlinear-lattice modulation function is periodic,%
\begin{equation}
P(x+2\pi /\Omega )=P(x).  \label{P(x)}
\end{equation}%
Intervals with positive (negative) values of $P(x)$ correspond to spatial
domains with attractive (repulsive) interactions between particles.
Equation~(\ref{1D_GP}) conserves two quantities, \textit{viz}., the energy,
\begin{equation}
E=\frac{1}{2}\int_{-\infty }^{+\infty }\left[ |\nabla \Psi |^{2}+V(x)|\Psi
|^{2}-\frac{P(x)}{2}|\Psi |^{4}\right] dx,  \label{N_E}
\end{equation}%
and the integral norm, which is proportional to the number of atoms in the
condensate:
\begin{equation}
N=\int_{-\infty }^{+\infty }|\Psi |^{2}dx.  \label{N_N}
\end{equation}

The model includes \textit{two scales}: the characteristic HO length $l_{%
\mathrm{HO}}\sim 1/\sqrt{\omega }$, and period $\Lambda =2\pi /\Omega $ of
the nonlinear lattice, introduced by Eq. (\ref{P(x)}). In particular, the
limit case of the wide HO trap, $\Omega \gg 2\pi \sqrt{\omega }$, is a
physically relevant one. Additional rescaling
\begin{equation}
t\rightarrow \frac{\omega }{\sqrt{2}}t,\quad x\rightarrow \sqrt{\frac{\omega
}{\sqrt{2}}}~x,\quad \Psi \rightarrow \sqrt{\frac{\sqrt{2}}{\Gamma }}~\Psi ,
\label{Rescal01}
\end{equation}%
allows one to fix $\omega \equiv 1$, converting Eq. (\ref{1D_GP}) into a
normalized form,
\begin{equation}
i\Psi _{t}=-\Psi _{xx}+x^{2}\Psi -P(x)\Psi |\Psi |^{2},  \label{1D_GP_1}
\end{equation}%
where $P(x)$ is periodic with spatial frequency $\tilde{\Omega}=\Omega /%
\sqrt{\Gamma }$ (in which follows below, symbol $\tilde{\Omega}$ is replaced
by $\Omega $). To estimate physically relevant values of $\Omega $, we note
that, for the condensate of $^{173}$Yb used for the experimental realization
of the periodically-modulated FR in Ref. \cite{Japan}, the HO length
corresponding (for instance) to trapping frequency $\omega \sim 50$ Hz is $%
l_{\mathrm{HO}}\sim 5$ $\mathrm{\mu }$m, while the optical lattice was built
by laser beams with half-wavelength $\Lambda _{0}=0.278$ $\mathrm{\mu }$m,
the corresponding scaled spatial frequency being $\Omega \sim 100$. It can
be made smaller, taking larger $\omega $, and/or building the optical
lattice with larger $\Lambda =\Lambda _{0}/\cos \theta $, if the two laser
beams are launched under angle $\pi -2\theta $ \cite{OL}.

Equation~(\ref{1D_GP_1}) is our basic model. The objective of the analysis
is to construct and investigate stationary LM solutions to Eq. (\ref{1D_GP_1}%
) in the form of
\begin{equation}
\Psi (t,x)=e^{-i\mu t}u(x),
\end{equation}%
with real chemical potential $\mu $, and real \cite{AKS02} spatial wave
function $u(x)$ satisfying equation%
\begin{equation}
\frac{d^{2}u}{dx^{2}}+(\mu -x^{2})u+P(x)u^{3}=0  \label{eq1}
\end{equation}%
with localization boundary conditions,
\begin{equation}
\lim_{|x|\rightarrow \infty }u(x)=0.  \label{eq2}
\end{equation}

LMs are physical relevant ones if they are stable against small
perturbations. The linear stability of the LMs is addressed by taking
perturbed solutions in the form of \cite{JYang}
% using . We consider a perturbation of a NLM $\Psi(x,t)=e^{-i\mu t}u(x)$ for the equation (\ref{1D_GP_1})
\begin{equation}
\Psi (x,t)={u(x)+[v(x)+w(x)]e^{\lambda t}+[v^{\ast }(x)-w^{\ast
}(x)]e^{\lambda ^{\ast }t}}e^{-i\mu t},
\end{equation}%
where $v(x)$ and $w(x)$ are infinitesimal perturbations, and eigenvalues $%
\lambda $ with nonzero real parts give rise to the instability, while pure
imaginary ones correspond to linearly stable eigenmodes. Substituting this
expression in Eq.~(\ref{1D_GP_1}) and performing the linearization with
respect to $v$ and $w$, we arrive at the following linear eigenvalue problem
of the Bogoliubov - de Gennes type,
\begin{equation}
\mathbf{L}\Theta =\lambda \Theta ,  \label{EigProb}
\end{equation}%
with operators
\begin{equation}
\mathbf{L}=i\left(
\begin{array}{cc}
\mathbf{0} & L_{-} \\
L_{+} & \mathbf{0}%
\end{array}%
\right) ,\quad \Theta =i\left(
\begin{array}{c}
v \\
w%
\end{array}%
\right)
\end{equation}%
\begin{align}
L_{-}& =d^{2}/dx^{2}+\mu -x^{2}+P(x)u^{2} \\[2mm]
L_{+}& =d^{2}/dx^{2}+\mu -x^{2}+3P(x)u^{2}.
\end{align}%
Note that, if $\lambda $ is an eigenvalue of Eq. (\ref{EigProb}), then $%
-\lambda $, $\bar{\lambda}$ and $-\bar{\lambda}$ are eigenvalues too.

The eigenvalue problem based on Eq. (\ref{EigProb}) may be rewritten in the
following equivalent form:
\begin{equation}
L_{+}L_{-}w=\Lambda w,\quad \Lambda =-\lambda ^{2}.  \label{EigProb01}
\end{equation}%
In terms of Eq.~(\ref{EigProb01}), a mode $u(x)$ passes the stability test
if the spectrum of eigenvalues $\Lambda $ is all-real and positive.

\section{Small-amplitude localized modes: asymptotic analysis}

\label{SmAmpl}

\subsection{Branches of solutions}

\label{Gammas}

For small norm $N$, the nonlinear term in Eq. (\ref{eq1}) may be neglected,
which leads to the HO equation,
\begin{equation}
\frac{d^{2}u}{dx^{2}}+(\mu -x^{2})u=0,  \label{LinGPE}
\end{equation}%
which produces the commonly known set of eigenvalues and eigenfunctions:%
\begin{equation}
\tilde{\mu}_{n}=2n+1,\quad \tilde{u}_{n}(x)=\frac{1}{\sqrt{2^{n}n!\sqrt{\pi }%
}}H_{n}(x)e^{-\frac{1}{2}x^{2}},\quad n=0,1,\ldots ,  \label{eq:GH}
\end{equation}%
where $H_{n}(x)$ is $n$-th Hermite polynomial. In particular,%
\begin{equation}
H_{0}(x)=1,\quad H_{1}(x)=2x,\quad H_{2}(x)=4x^{2}-2.  \label{012}
\end{equation}%
Eigenmodes $\tilde{u}_{n}(x)$ constitute an orthonormal basis in $L_{2}(%
\mathbf{R})$,
\begin{equation}
\langle \tilde{u}_{n},\tilde{u}_{m}\rangle \equiv \int_{-\infty }^{\infty }%
\tilde{u}_{n}(x)\tilde{u}_{m}(x)~dx=\delta _{m,n}.
\end{equation}

When the nonlinearity is switched on, each linear eigenstate $(\tilde{\mu}%
_{n},\tilde{u}_{n}(x))$ bifurcates into a one-parameter set $\Gamma
_{n}=(\mu _{n},u_{n}(x))$ of small-amplitude LMs. These modes are produced
by Eq.~(\ref{eq1}) and become essentially nonlinear with the increase of $N$
(in other words, with the increase of the distance between $\mu _{n}$ and $%
\tilde{\mu}_{n}$) Following the terminology adopted in Refs. \cite{AMP,AP},
we refer to these solutions as to \textit{nonlinear modes with linear
counterparts}. LMs from family $\Gamma _{n}$ feature the same parity as the
corresponding linear eigenfunction $\tilde{u}_{n}(x)$: the LMs with odd $n$
are even functions of $x$, and those with even $n$ are odd. {\LARGE [Eq. (%
\ref{012}) shows exactly the opposite: even }${\LARGE n}${\LARGE \
correspond to even eigenfunctions.]} LMs belonging to branch $\Gamma _{0}$,
which originates from the HO ground state, are nodeless, resembling the
well-known bright solitons of the NLSE with the attractive nonlinearity.
%The NLMs of the branch $\Gamma_0$ are called {\it bright solitons}.  Typically, these NLMs are highly localized, bell-shaped and has the lowest energy.
The LMs belonging to branch $\Gamma _{1}$, which originates from the first
HO excited state have exactly one node, somewhat resembling dark solitons of
the repulsive NLSE (in fact, they are more similar to the so-called
localized dark solitons of the NLSE with the strength of the local
self-repulsion slowly growing from $x=0$ towards $|x|\rightarrow \infty $
\cite{Zeng}.
% at the origin whin the case of repulsive interactions are called {\it dark solitons}.
They have been studied in many papers, see, e.g. \cite{WLK13,K17,C10,PFK05}.

If the amplitude of $u_{n}(x)$ is small, the LMs from branch $\Gamma _{n}$
are approximated by expansions \cite{KKRF05,ZAKP08,ZK16,K17},
\begin{equation}
u_{n}(x)=\varepsilon \tilde{u}_{n}(x)+o(\varepsilon ),\quad \mu _{n}=\tilde{%
\mu}_{n}-\varepsilon ^{2}\Delta _{n}+o(\varepsilon ^{2}),  \label{AsEx}
\end{equation}%
where $\varepsilon \ll 1$ is a small parameter, and%
\begin{equation}
\Delta _{n}=\int_{-\infty }^{+\infty }P(x)\tilde{u}_{n}^{4}(x)dx=\frac{1}{%
2^{2n}(n!)^{2}\pi }\int_{-\infty }^{+\infty }P(x)H_{n}^{4}(x)e^{-2x^{2}}~dx.
\label{omega2}
\end{equation}

\subsection{The stability of small-amplitude localized modes}

\label{Stab_Gamma}

To address the stability of the small-amplitude nonlinear LMs belonging to
branches $\Gamma _{n}$, $n=0,1,\ldots $, we note that, with the help of
expansion (\ref{AsEx})--(\ref{omega2}), operator $L_{+}L_{-}$ in (\ref%
{EigProb01}) may be considered as a perturbation of operator $\mathcal{L}%
_{n}^{2}$, where
\begin{equation}
\mathcal{L}_{n}=\frac{d^{2}\,}{dx^{2}}+2n+1-x^{2}.
\end{equation}%
Specifically,
\begin{eqnarray}
&&L_{+}=\mathcal{L}_{n}+\varepsilon ^{2}(3P(x)\tilde{u}_{n}^{2}(x)-\Delta
_{n})+o(\varepsilon ^{2}), \\[2mm]
&&L_{-}=\mathcal{L}_{n}+\varepsilon ^{2}(P(x)\tilde{u}_{n}^{2}(x)-\Delta
_{n})+o(\varepsilon ^{2}), \\[2mm]
&&L_{+}L_{-}=\mathcal{L}_{n}^{2}+\varepsilon ^{2}M_{n}+o(\varepsilon ^{2}),
\label{eq:LL}
\end{eqnarray}%
where
\begin{equation}
M_{n}=(3P(x)\tilde{u}_{n}^{2}(x)-\Delta _{n})\mathcal{L}_{n}+\mathcal{L}%
_{n}(P(x)\tilde{u}_{n}^{2}(x)-\Delta _{n}).
\end{equation}%
Operator $\mathcal{L}_{n}$ is self-adjoint in $L^{2}$, and its spectrum
consists of eigenvalues $\varkappa _{k}=2(n-k)$ with corresponding
eigenfunctions $\tilde{u}_{k}(x)$, $k=0,1,\ldots $. The spectrum is
equidistant, all the eigenvalues being non-degenerate. There are infinitely
many negative eigenvalues, $n$ positive eigenvalues and one zero. The
eigenvalues of the operator $\mathcal{L}_{n}^{2}$ are squared eigenvalues of
$\mathcal{L}_{n}$, $\tilde{\Lambda}_{k}=\varkappa _{k}^{2}=4(k-n)^{2}$,
corresponding to the same eigenfunctions $\tilde{u}_{k}(x)$, $k=0,1,\ldots $%
. This means that the spectrum of $\mathcal{L}_{n}^{2}$ includes $n$ \textit{%
double positive eigenvalues} $\tilde{\Lambda}_{k}=4(n-k)^{2}$, $k=0,1,\ldots
(n-1)$, one \textit{simple zero eigenvalue} and \textit{infinitely many
simple positive eigenvalues}. Each of the double eigenvalue has an invariant
subspace spanned by two functions, $\tilde{u}_{k}(x)$ and $\tilde{u}%
_{2n-k}(x)$, there being non double eigenvalues in the case of $n=0$.

Generically, small perturbation of $\mathcal{L}_{n}^{2}$ results in \textit{%
splitting} of the double eigenvalues. Each of them can carry over into (i)
two real eigenvalues of the perturbed operator or (ii) two complex-conjugate
eigenvalues. The difference between these cases is crucial because in case
(i) the small-amplitude LM remains marginally stable, while in case (ii) it
becomes unstable.

To study the splitting of double eigenvalues when passing from operator $%
\mathcal{L}_{n}^{2}$ to the perturbed one, $L_{+}L_{-}$ in Eq.~(\ref{eq:LL}%
), %\begin{eqnarray}
%L_+L_-={\cal L}^2_n+\varepsilon^2 M_n+o(\varepsilon^2)
%\end{eqnarray}
we construct an expansion, following Ref. \cite{ZAKP08}. Under the action of
the perturbation, each double eigenvalue $\tilde{\Lambda}$ splits into two
simple ones:
\begin{equation}
\Lambda _{1}=\tilde{\Lambda}+\varepsilon ^{2}\gamma _{1}+o(\varepsilon
^{2}),\quad \Lambda _{2}=\tilde{\Lambda}+\varepsilon ^{2}\gamma
_{2}+o(\varepsilon ^{2}),
\end{equation}%
where coefficients $\gamma _{1,2}$ are eigenvalues of the $2\times 2$ matrix
\begin{equation}
\tilde{M}_{n}=\left(
\begin{array}{cc}
\langle M_{n}\tilde{u}_{k},\tilde{u}_{k}\rangle & \langle M_{n}\tilde{u}_{k},%
\tilde{u}_{2n-k}\rangle \\[2mm]
\langle M_{n}\tilde{u}_{2n-k},\tilde{u}_{k}\rangle & \langle M_{n}\tilde{u}%
_{2n-k},\tilde{u}_{2n-k}\rangle%
\end{array}%
\right) .  \label{Lambda_12_as}
\end{equation}%
Therefore, if the eigenvalues of $\tilde{M}_{n}$ are real, the spectrum of $%
L_{+}L_{-}$ remains real and the nonlinear LM $u_{n}(x)$ is stable, at least
for sufficiently small $\varepsilon $ (i.e., for sufficiently small number
of particles in the condensate). Otherwise, if eigenvalues of $\tilde{M}$
are complex, the LM solution $u_{n}(x)$ is unstable in a vicinity of the
bifurcation which gives rise to the complex eigenvalue pair. Note that, as
no double eigenvalues exist in the case of $n=0$, the small-amplitude LMs
belonging to the ground-state branch $\Gamma _{0}$ are stable for any $P(x)$.

Using explicit expression for eigenfunction $\tilde{u}_{n}$ from (\ref{eq:GH}%
), one can compute entries of matrix $\tilde{M}_{n}$: %
%Let us calculate elements of the matrix $\tilde M_n$ explicitly. A useful %formula is
%\begin{eqnarray}
%{\cal L}_n\tilde u_m=2(n-m)\tilde u_m,\quad m=0,1,\ldots
%\end{eqnarray}
%Then one has
\begin{align}
\langle M_{n}\tilde{u}_{k}& ,\tilde{u}_{k}\rangle =\frac{8(n-k)}{\pi
2^{(n+k)}n!k!}\int_{-\infty }^{+\infty
}P(x)H_{n}^{2}(x)H_{k}^{2}(x)e^{-2x^{2}}~dx-  \notag \\[2mm]
& -\frac{4(n-k)}{\pi 2^{2n}(n!)^{2}}\int_{-\infty }^{+\infty
}P(x)H_{n}^{4}(x)e^{-2x^{2}}~dx,  \label{11} \\[2mm]
\langle M_{n}\tilde{u}_{k}& ,\tilde{u}_{2n-k}\rangle =-\langle M_{n}\tilde{u}%
_{2n-k},\tilde{u}_{k}\rangle =  \notag \\[2mm]
& =\frac{4(n-k)}{\pi 2^{2n}n!\sqrt{k!(2n-k)!}}\int_{-\infty }^{+\infty
}P(x)H_{n}^{2}(x)H_{2n-k}(x)H_{k}(x)e^{-2x^{2}}~dx,  \label{12} \\[2mm]
\langle M_{n}\tilde{u}_{2n-k}& ,\tilde{u}_{2n-k}\rangle =-\frac{8(n-k)}{\pi
2^{(3n-k)}n!(2n-k)!}\int_{-\infty }^{+\infty
}P(x)H_{n}^{2}(x)H_{2n-k}^{2}(x)e^{-2x^{2}}~dx,+  \notag \\[2mm]
& +\frac{4(n-k)}{\pi 2^{2n}(n!)^{2}}\int_{-\infty }^{\infty
}P(x)H_{n}^{4}(x)e^{-2x^{2}}~dx.  \label{22}
\end{align}

Formulas (\ref{11})-(\ref{22}) with $P(x)=\pm 1$ were used in Ref. \cite%
{ZAKP08} to explore the stability of small-amplitude nonlinear modes %for
%higher branches $\Gamma_k$, $k=2,3,4$,
in the model with constant scattering length.

\section{Branches of nonlinear localized modes: a numerical study}

\label{NLM:general}

We present numerical results for the practically important case when the
nonlinearity-modulation function, $P(x)$ in Eq.~(\ref{1D_GP_1}), is taken as
a sum of its constant (dc) and harmonic (ac) parts:
\begin{equation}
P(x)=P_{0}+P_{1}\cos \left( \Omega x\right) .  \label{TwoH_App}
\end{equation}%
In what follows we conclude (quite naturally) that the relation between the
magnitudes of $|P_{0}|$ and $|P_{1}|$ is important, hence it is necessary to
consider two cases separately: (a) $|P_{0}|\gtrsim |P_{1}|$ ; (b) $%
|P_{0}|\ll |P_{1}|$, with a negligible dc component.

In the \textit{dc-dominated} case (a) one can scale out the absolute value
of the dc component, by replacing
\begin{equation}
{\Psi \rightarrow \Psi /\sqrt{|P_{0}|},~}P_{1}/|P_{0}|\rightarrow P_{1},
\label{Rescal02}
\end{equation}%
and thus casting Eq.~(\ref{1D_GP_1}) in the form of
\begin{equation}
i\Psi _{t}=-\Psi _{xx}+x^{2}\Psi {-}\left[ \sigma _{0}+P_{1}\cos \left(
\Omega x\right) \right] \Psi |\Psi |^{2},\quad {\sigma _{0}\equiv
P_{0}/|P_{0}|=\mathrm{sign}~P_{0}.}  \label{1D_GP_11}
\end{equation}

In case (b), we drop $P_{0}$, and rescale Eq. (\ref{1D_GP_1}) by replacing
\begin{equation}
{\Psi \rightarrow \Psi /\sqrt{|P_{1}|}},
\end{equation}%
which leads to the equation
\begin{equation}
i\Psi _{t}=-\Psi _{xx}+x^{2}\Psi {-}\sigma _{1}\cos \left( \Omega x\right)
\Psi |\Psi |^{2},\quad \sigma _{1}=P_{1}/|P_{1}|=\mathrm{sign}~P_{1}.
\label{1D_GP_12}
\end{equation}%
%
%
%where  $\sigma_1={\rm sign}~P_1$.

\subsection{Nonlinear pseudopotential with nonzero mean}

\label{NonZM}

LMs provided by Eq.~(\ref{1D_GP_11}) satisfy the equation
\begin{equation}
\frac{d^{2}u}{dx^{2}}+(\mu -x^{2})u+\left[ \sigma _{0}+P_{1}\cos \left(
\Omega x\right) \right] u^{3}=0,\quad \sigma _{0}=\mathrm{sign}~P_{0}.
\label{eq1_1}
\end{equation}

\subsubsection{The constant pseudopotential: an overview}

\label{Review_const}

Before presenting new results produced by the current work, it is relevant
to briefly overview previous results pertaining to the well-studied case of
the GPE with constant (negative or positive) scattering length \cite%
{E95,K99, G99, C01, YYB02, KK03, KAT01,AZ07,ZAKP08}. In this case, $%
P_{1}\equiv 0$, and Eq.~(\ref{eq1_1}) becomes
\begin{equation}
\frac{d^{2}u}{dx^{2}}+(\mu -x^{2})u+\sigma _{0}u^{3}=0.  \label{eq1_1_0}
\end{equation}%
We call Eq.~(\ref{eq1_1_0}) a \textit{nonlinear harmonic-oscillator equation}%
. The case of $\sigma _{0}=1$ ($\sigma _{0}=-1$) corresponds to the
attractive (repulsive) interparticle interactions. It is convenient to
illustrate branches of LMs in the nonlinear HO model by means of the
respective $N(\mu )$ curves, which are presented in Fig. \ref{Fig.P_1=1}, as
per Ref. \cite{ZAKP07,ZAKP08}, for both cases of $\sigma _{0}=\pm 1$.\
Branches $\Gamma _{n}$, $n=0,1,2,\ldots $, correspond to the LMs with the
linear counterparts, bifurcating from them at points $\tilde{\mu}_{n}=2n+1$,
$N=0$, all the branches being represented by monotonous functions $N(\mu )$
(at least, for moderate values of $N$, $\mu $ and $n$) . Presumably, there
exist no nonlinear HO modes without linear counterparts \cite{AZ07}.

\begin{figure}[tbp]
\includegraphics[width=0.4\textwidth]{fig1dz.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{$N(\protect\mu )$ curves for the NHO model, based on Eq.~(\protect
\ref{eq1_1_0}), with (a) $\protect\sigma _{0}=1$ and (b) $\protect\sigma %
_{0}=-1$, which correspond, respectively, to the self-attractive and
repulsive signs of the nonlinearity (as per Refs. \protect\cite%
{ZAKP07,ZAKP08}). Bold (thin) segments correspond to stable (unstable)
modes. Insets show schematic profiles $u_{n}(x)$ of modes from each family.}
\label{Fig.P_1=1}
\end{figure}

Analysis of eigenvalues of the matrix $\tilde{M}_{n}$ with $P(x)\equiv 1$ or
$P(x)\equiv -1$ \cite{ZAKP08} shows that LMs corresponding to $\Gamma _{0}$
and $\Gamma _{1}$ are stable in the small-amplitude limit for both signs of
the nonlinearity, $\sigma _{0}=1$ and $\sigma _{0}=-1$ \cite{AZ07,KKRF05}.
Numerical results indicate that these modes remain stable for moderate and
large amplitudes as well. The small-amplitude LMs belonging to branch $%
\Gamma _{2}$ are unstable. For $\sigma _{0}=1$ (self-attraction), the
instability of branch $\Gamma _{2}$ persists for $\mu ^{\ast }<\mu <5$ where
$\mu ^{\ast }\approx 3.83$. At $\mu <\mu ^{\ast }$ these modes was reported
to be stable \cite{AZ07}. For $\sigma _{0}=-1$ (self-repulsion), branch $%
\Gamma _{2}$ are unstable in the whole interval of $\mu $ covered in Fig.~%
\ref{Fig.P_1=1} (however, it may become stable at still larger values of $N,$
not shown in Fig.~\ref{Fig.P_1=1} \cite{C10}). Small-amplitude branches $%
\Gamma _{n}$ with $n=3,4,\ldots $ are also unstable in both cases of $\sigma
_{0}=\pm 1$.
%This is supported by analysis of eigenvalues of the matrix $\tilde M$, see \cite{ZAKP08}.

\subsubsection{The periodic pseudopotential ($P_{1}\neq 0$)}

\label{P1_ne_0}

The setting which was not addressed previously is the combination of the HO
trapping potential with the pseudopotential which contains the periodic
component, i.e., $P_{1}\neq 0$ in Eq. (\ref{eq1_1}). In this case, a general
picture of LM branches can be obtained by means of a numerical shooting
algorithm, which is presented in detail in Ref. \cite{AZ07}.
%Following \cite{AZ07}, we claim that {\it all} existing branches of NLM in the given ranges of $\mu$ and $N$ are found.
A representative example of the respective $N(\mu )$ curves
%for $P(x)=1+2\cos 8 x$
with $\sigma _{0}=1$ (average self-attraction), $P_{1}=2$ (which implies
that the sign of the local nonlinearity periodically flips) and $\Omega =8$
is displayed in Fig.~\ref{FigP_1ne_0_1}, where one immediately observes
that, apart from branches $\Gamma _{n}$ originating from their linear
counterparts, numerous branches of LMs \emph{without linear counterparts}
exist too. Thus, the presence of the ac component in the pseudopotential
essentially enriches the diversity of available solutions. However, no
branch without a linear counterpart is stable (in fact, the only stable
solutions in Fig.~\ref{FigP_1ne_0_1} corresponds to the ground-state branch,
$\Gamma _{0}$).
\begin{figure}[tbp]
\includegraphics[width=0.8\textwidth]{Fig_3_1.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{The main panel: $N(\protect\mu )$ dependences, as obtained from
Eq.~(\protect\ref{eq1_1}) with $\protect\sigma _{0}=1$, $P_{1}=2$, and $%
\Omega =8$. Thin and bold lines show unstable and stable LM families, the
sole stable one being the lowest branch $\Gamma _{0}$. Insets (1)-(3) are
representative profiles $u(x)$ of nonlinear modes originating their linear
counterparts, for branches $\Gamma _{0}$, $\Gamma _{1}$, $\Gamma _{2}$
(labeled by the same numbers $1,2,3$), while insets (4) and (5) show
profiles of modes belonging to some branches without linear counterparts,
which are also labeled $4$ and $5$. }
\label{FigP_1ne_0_1}
\end{figure}

In the limit of the rapidly oscillation ac component, $\Omega \rightarrow
\infty $, LMs %the NLM with $P_1\ne 0$
may be approximated by the nonlinear HO modes. The asymptotic formula can be
obtained by means of averaging with respect to the fast oscillations (see,
e.g., Ref. \cite{Fatkhulla}):
\begin{equation}
u(x)=u^{(0)}(x)+\frac{1}{\Omega ^{2}}\left[ u^{(1)}(x)+P_{1}(u^{(0)}(x))^{3}%
\cos \left( \Omega x\right) \right] +o\left( \frac{1}{\Omega ^{2}}\right)
,\quad \Omega \rightarrow \infty .  \label{Expand_NZM}
\end{equation}%
Here $u^{(0)}(x)$ is a solution of nonlinear HO model corresponding to Eq. (%
\ref{eq1_1_0}), and $u^{(1)}(x)$ is a localized solution of the equation
\begin{equation}
\frac{d^{2}u}{dx^{2}}+\left\{ \mu -x^{2}+3\sigma _{0}\left[ u^{(0)}(x)\right]
^{2}\right\} u=-\frac{3}{2}P_{1}^{2}\left[ u^{(0)}(x)\right] ^{5}.
\end{equation}%
{We stress that asymptotic relation (\ref{Expand_NZM}) is valid for
nonlinear modes of arbitrary amplitudes (i.e., not only in the
small-amplitude limit), provided that $\Omega ^{2}$ is large enough.}

Figure~\ref{FigP_1ne_0} shows branches $\Gamma _{0}$, $\Gamma _{1}$ and $%
\Gamma _{2}$ for % $P(x)=1+2\cos\Omega x$
two different spatial frequencies of the periodic pseudopotential, $\Omega =8
$ and $\Omega =12$. According to the asymptotic prediction (\ref{Expand_NZM}%
), they approach the corresponding branches of the nonlinear HO equation as $%
\Omega $ grows. Additionally, Eq. (\ref{Expand_NZM}) implies that ({in)}%
stability of a LM under the action of the rapidly oscillating
pseudopotential is determined by the ({in)}stability of its counterpart in
the nonlinear HO model. {Indeed, the presence of eigenvalues with nonzero
real parts in the perturbative spectrum of an nonlinear HO state implies the
existence of such eigenvalues in the spectrum of LM if $\Omega $ is large
enough. We also conjecture that the stability of a nonlinear HO mode implies
the stability of its LM counterpart for sufficiently large $\Omega $.}
% Some signature  of this stability correspondence between NHO  equation and the model with the rapidly oscillating pseudopotential is visible in Fig.~\ref{FigP_1ne_0_1}.
For example, the segment of branch $\Gamma _{1}$ shown in Fig.~\ref%
{FigP_1ne_0_1} is completely unstable for $\Omega =8$, but its stability
improves for $\Omega =12$, which agrees with the nonlinear HO limit, where
this branch is entirely stable. For branch $\Gamma _{2}$ the situation is
more complex. Small-amplitude modes belonging to $\Gamma _{2}$ are unstable
for $\Omega =8$, but become stable for $\Omega =12$. However, Eq. (\ref%
{Expand_NZM}) implies that the further increase of $\Omega $ will
necessarily lead to the destabilization of these modes, because in the
nonlinear HO limit the small-amplitude modes belonging to $\Gamma _{2}$ are
unstable. The possibility to manage the stability of small-amplitude
nonlinear LMs by tuning the frequency of the ac component of the
pseudopotential has been recently reported in Ref. \cite{K17}.

%\textcolor{red}{[.. In fact, there is some peculiarity. In my opinion,
%the instability of NHO mode  implies the instability of NLM with $\Omega$ greater then some threshold. This follows from comparison of spectra of NHO and NLM,
%the unstable eigenvalues of NHO mode are approximated by corresponding eigenvalues of NLM when %$\Omega\to\infty$. Converse statement is more problematic:
%for instance, one can imagine a spectrum of NLM with unstable eigenvalues that move to infinity as %$\Omega\to\infty$, in such a way that the limiting NHO has purely imaginary spectrum. So, I would add here some words..]}

%In fact, let $\mu$ be fixed and $u(x)$ be an NLM described by Eq.~ (\ref{eq1_1}). Let the corresponding mode of NHO be unstable. The instability of this mode  implies that the spectrum of eigenvalue problem (\ref{EigProb}) for $u^{(0)}(x)$ includes eigenvalues with nonzero real part. Since $u(x)$ approaches $u^{(0)}(x)$ as $\Omega \to\infty$, the spectrum of (\ref{EigProb}) for $u(x)$ and the same $\mu$ also includes the eigenvalues with nonzero real part, if $\Omega$ is large enough.

\begin{figure}[tbp]
\includegraphics[width=0.8\textwidth]{Fig_2_1dz.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{$N(\protect\mu )$ curves for Eq.~(\protect\ref{eq1_1}) with $%
\protect\sigma _{0}=1$, $P_{1}=2$, and $\Omega =8$ or $\Omega =12$. Only the
branches $\Gamma _{0,1,2}$ are shown. For comparison, the corresponding
dependencies for NHO equation (\protect\ref{eq1_1_0}) with $\protect\sigma %
_{0}=1$ [identical to those in Fig.~\protect\ref{Fig.P_1=1}(a)] are shown
too. Bold black lines (and thin red lines) correspond to stable (unstable)
nonlinear modes.}
\label{FigP_1ne_0}
\end{figure}

%Fig.~\ref{FigP_1ne_0} illustrates the relation between the stability/instability of the modes of NHO and the modes for $P_1\ne 0$, as $\Omega$ being increased. We conjecture that if a mode of NHO is stable, the corresponding NLM  for $P_1\ne 0$ is also stable, if $\Omega$ is large enough. For moderate values of $\Omega$ a modulation of pseudopotential may stabilize the NLMs, at least in small amplitude limit. This effect was predicted in \cite{K17} and it was also observed in our computations. For instance, the small-amplitude NHO modes for $\Gamma_2$ are known to be unstable, but the small-amplitude NLMs for $P(x)=1+2\cos 12 x$ are stable, (see Fig. \ref{FigP_1ne_0}).

%\subsubsection{The evolution of NLM}\label{Evol_NZM}

To check the predictions of the linear-stability analysis, we have performed
simulations of the evolution of LMs in the framework of the time-dependent
GPE~(\ref{1D_GP_11}), using an implicit difference scheme \cite{TP} with
adsorbing boundary conditions. In the simulations, solutions which are
predicted to be linearly stable keep their shape indefinitely long [see Fig. %
\ref{Fig_Comp_NZM}~(1a,b)], whereas the nonlinear modes which are predicted
to be unstable typically transform into a pulsating object localized over
one period of the lattice pseudopotential, see Figs. \ref{Fig_Comp_NZM}%
~(2a,b).

\begin{figure}[tbp]
\includegraphics[width=0.8\textwidth]{Fig_7_NZM_1.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{The case of $P(x)=1+2\cos 16 x$.
 (1a): The
evolution of a stable LM with $\protect\mu =0$, belonging to branch $\Gamma
_{1}$. (1b): The spectrum of the eigenvalue problem (\protect\ref{EigProb})
associated with this LM. (2a): The evolution of an unstable LM with $\protect%
\mu =-3$, belonging to branch $\Gamma _{1}$. (2b) The corresponding spectrum
of the eigenvalue problem (\protect\ref{EigProb}). }
\label{Fig_Comp_NZM}
\end{figure}

\subsection{Nonlinear pseudopotential with zero mean (no dc component)}

\label{ZeroMean}

According to the results of the previous subsection, the effect of a rapidly
oscillating ac component of the pseudopotential, in the presence of the dc
component, may be approximated using the standard nonlinear HO model with
the uniform nonlinearity. However, the situation becomes essentially
different in the absence of the dc component. We address the latter
situation using Eq.~(\ref{1D_GP_12}). The corresponding nonlinear modes can
be found from the equation
\begin{equation}
\frac{d^{2}u}{dx^{2}}+(\mu -x^{2})u+\sigma _{1}\cos \Omega xu^{3}=0.
\label{eq1_2}
\end{equation}%
The so obtained $N(\mu )$ curves are shown in the main panel of Fig.~\ref%
{A0Om8_l}. Here we again observe branches $\Gamma _{n}$ bifurcating from the
linear limit [Fig. \ref{A0Om8_l}, insets (1) and (2)] and various families
without linear counterparts [Fig.~\ref{A0Om8_l}, insets (3-5)]. Branches $%
\Gamma _{n}$ feature stable and unstable segments, all LMs without linear
counterpart being unstable, as above.

\subsubsection{Shapes of solutions with linear counterparts}

\label{Gamma_shapes}

%For numerical computation of the NLM  we used again the shooting algorithm, see \cite{AZ07}.
%The $(N, \mu)$-diagram for $P(x)=\cos 8 x$ is shown in Fig.~\ref{A0Om8_l}.
%It follows from Fig.~\ref{A0Om8_l} that apart from the  branches $\Gamma_n$, $n=0,1,\ldots$, the branches of NLM without linear counterpart also exist.

In the limit $N\ll 1$, weakly nonlinear LMs belonging to branches $\Gamma
_{n}$, $n=0,1,\ldots $, are produced by Eqs. (\ref{AsEx}) where $\Delta _{n}$
is given by Eq. (\ref{omega2}), with $P(x)=\sigma _{1}\cos \left( \Omega
x\right) $. The numerically found values of $\Delta _{n}$, $n=0,1,2$, for $%
\sigma _{1}=1$ and several different values of $\Omega $ are presented in
Table~\ref{T2}.

\begin{table}[tbp]
%[h]
\begin{tabular}{ccccc}
\hline
$\Omega$ & 0 & 2 & 8 & 18 \\[2mm] \hline
$n=0$ & $\quad 3.9894\cdot 10^{-1}$ \quad & \quad $2.4197\cdot 10^{-1}$ \quad
& \quad $1.3383\cdot 10^{-4}$ \quad & \quad $1\cdot 10^{-18}$ \quad \\[2mm]
$n=1$ & $2.9921\cdot 10^{-1}$ & $-1.2100\cdot 10^{-1}$ & $5.4536\cdot
10^{-3} $ & $2\cdot 10^{-15}$ \\[2mm]
$n=2$ & $2.5557\cdot 10^{-1}$ & $-1.3611\cdot 10^{-1}$ & $2.1097\cdot
10^{-2} $ & $5\cdot 10^{-13}$ \\ \hline
\end{tabular}%
\caption{The values of $\Delta _{n}$, $n=0,1,2$, calculated as per Eq. (%
\protect\ref{omega2}), for $P(x)=\cos \left( \Omega x\right) $, $\Omega
=0,2,8,18$. They determine the perturbative shift of chemical potential of
weakly nonlinear LMs, pursuant to Eq. (\protect\ref{AsEx}). }
\label{T2}
\end{table}

\begin{figure}[tbp]
\includegraphics[width=0.9\textwidth]{Fig_4_1.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{The main panel: $N(\protect\mu )$ curves for $P(x)=\cos (8x)$, thin
and bold lines showing unstable and stable LM families, respectively. (1)
and (2) label branches $\Gamma _{2}$, $\Gamma _{3}$, while (3), (4) and (5)
pertain to ones without linear counterparts. Profiles of the LMs for
branches (1)-(5) are depicted in separate panels. }
\label{A0Om8_l}
\end{figure}

To find the asymptotic form of $\Delta _{n}$ for $\Omega \rightarrow \infty $%
, we note that, for arbitrary polynomial $%
Q_{2m}(x)=a_{2m}x^{2m}+a_{2m-1}x^{2m-1}+\ldots +a_{0}$ of degree $2m$, the
following asymptotic relation holds:
\begin{equation}
\int_{-\infty }^{+\infty }Q_{2m}(x)e^{-2x^{2}}\cos \left( \Omega x\right)
~dx\approx (-1)^{m}\frac{a_{2m}\sqrt{2\pi }\Omega ^{2m}}{2^{4m+1}}e^{-\Omega
^{2}/8},\quad \Omega \rightarrow \infty .  \label{AsGauss}
\end{equation}%
Since the coefficient in front of the highest-power term in Hermite
polynomial $H_{n}(x)$ is $2^{n}$, Eq. (\ref{AsGauss}) with $Q_{2m}(x)$
substituted by $H_{n}(x)$ yields
\begin{equation}
\Delta _{n}\approx \frac{\sqrt{2}\Omega ^{4n}}{2^{6n+1}\cdot (n!)^{2}\sqrt{%
\pi }}e^{-\Omega ^{2}/8},\quad \Omega \rightarrow \infty .
\end{equation}%
Therefore, for sufficiently large $\Omega $, $\Delta _{n}$ {are all positive}
and decay exponentially, which agrees with the data in Table~\ref{T2}.

As has been shown above [see Eq.~(\ref{Expand_NZM})], in the model with a
rapidly oscillating pseudopotential and a nonzero dc term, shapes of LMs may
be approximated by the corresponding solutions of the nonlinear HO equation.
However, the asymptotic behavior of LMs in the limit of $\Omega \rightarrow
\infty $ becomes essentially different for the pseudopotential without the
dc term. Indeed, nonlinear mode $u(x)$ belonging to branch $\Gamma _{n}$
which satisfies Eq.~(\ref{eq1_2}), may be looked for as
\begin{equation}
u(x)=W(x)+R(x)\cos \left( \Omega x\right) +\mathrm{higher}~\mathrm{order}~%
\mathrm{terms},  \label{Asym_hyp}
\end{equation}%
where $W(x)$ and $R(x)$ are slowly varying functions in comparison with $%
\cos \left( \Omega x\right) $, one arrives at the balance relation between
the dominating terms:
\begin{equation}
R(x)\Omega ^{2}=\sigma _{1}W^{3}(x).
\end{equation}%
In the next order of $1/\Omega $, one arrives at the equation for $W(x)$,
\begin{equation}
\frac{d^{2}W}{dx^{2}}+(\mu -x^{2})W+\frac{3}{2\Omega ^{2}}W^{5}=0.
\end{equation}%
Introducing a rescaled function, $U(x)=W(x)/\sqrt{\Omega }$, one obtains the
following approximation:
\begin{equation}
u(x)=\sqrt{\Omega }U(x)+\frac{\sigma _{1}}{\sqrt{\Omega }}U^{3}(x)\cos
\Omega x+o\left( \frac{1}{\sqrt{\Omega }}\right) ,  \label{AsRel_u}
\end{equation}%
where $U(x)$ is a localized solution of the equation
\begin{equation}
\frac{d^{2}U}{dx^{2}}+(\mu -x^{2})U+\frac{3}{2}U^{5}=0.  \label{U}
\end{equation}%
While Eq.~(\ref{U}) does not admit any simple analytical solution, its
localized modes can be computed numerically and used in Eq. (\ref{AsRel_u})
to approximate nonlinear modes in the rapidly oscillating pseudopotential
(compare grey and red lines in Fig.~\ref{Fig:Prof}). To obtain an asymptotic
expression for the shapes of nonlinear modes in an explicit analytical form,
%Relation (\ref{AsRel_u}) is useful, but  it still does not yield much information on the explicit shapes of nonlinear modes, since no exact localized solutions of Eq.~(\ref{U}) is readily  available.  %the direct application of the formula (\ref{AsRel_u}) is awkward. Let us
%to derive an explicit approximative formula for NLM corresponding to $\Gamma_n$.
%To develop the obtained result into an explicit expression,
we define $\Delta \mu =\tilde{\mu}_{n}-\mu $ and rewrite Eq.~(\ref{U}) as
\begin{equation}
\frac{d^{2}U}{dx^{2}}+(\tilde{\mu}_{n}-x^{2})U=-\frac{3}{2}U^{5}+\Delta \mu
U.  \label{U0}
\end{equation}%
If $\Delta \mu $ is not large, one may assume that $U(x)\approx
U_{0}H_{n}(x)e^{-x^{2}/2}$, where $U_{0}$ is some constant which can be
found from the requirement for right-hand side of (\ref{U0}) to be
orthogonal to the kernel of the operator on the left-hand side:
\begin{equation}
\int_{-\infty }^{+\infty }\left( -\frac{3}{2}U^{5}(x)+\Delta \mu U(x)\right)
H_{n}(x)e^{-x^{2}/2}~dx=0,  \label{Orthog}
\end{equation}%
which leads to
\begin{equation}
U_{0}=\left( \frac{2{\mathcal{H}}_{n}^{(2)}\Delta \mu }{3{\mathcal{H}}%
_{n}^{(6)}}\right) ^{\frac{1}{4}},  \label{Q_0_formula}
\end{equation}%
\begin{equation}
{\mathcal{H}}_{n}^{(2)}\equiv \int_{-\infty }^{+\infty
}H_{n}^{2}(x)e^{-x^{2}}~dx,\quad {\mathcal{H}}_{n}^{(6)}\equiv \int_{-\infty
}^{+\infty }H_{n}^{6}(x)e^{-3x^{2}}~dx.
\end{equation}

\begin{figure}[tbp]
\includegraphics[width=0.9\textwidth]{Fig_5.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{Profiles of LMs, for $P(x)=\cos \left( 16x\right) $. (1) Branch $%
\Gamma _{0}$, $\protect\mu =0$ ($\Delta \protect\mu =1$). (2) Branch $\Gamma
_{1}$, $\protect\mu =1$ ($\Delta \protect\mu =2$). Gray line: the numerical
solution, red line: approximation (\protect\ref{AsRel_u}), with $U(x)$
obtained by numerical solution of Eq. (\protect\ref{U}). Blue line:
approximation (\protect\ref{u_appr_main}). }
\label{Fig:Prof}
\end{figure}

Combining the obtained results with Eq. (\ref{AsRel_u}), one finally gets
\begin{equation}
u(x)\approx \left( \frac{2{\mathcal{H}}_{n}^{(2)}\Delta \mu }{3{\mathcal{H}}%
_{n}^{(6)}}\right) ^{1/4}\sqrt{\Omega }H_{n}(x)e^{-x^{2}/2}+\left( \frac{2{%
\mathcal{H}}_{n}^{(2)}\Delta \mu }{3{\mathcal{H}}_{n}^{(6)}}\right) ^{3/4}%
\frac{\sigma _{1}}{\sqrt{\Omega }}H_{n}^{3}(x)e^{-3x^{2}/2}\cos \left(
\Omega x\right) .  \label{u_appr_main}
\end{equation}%
For the lowest branch $\Gamma _{0}$ Eq. (\ref{u_appr_main}) yields
\begin{equation}
u(x)\approx \left( \frac{2\Delta \mu }{\sqrt{3}}\right) ^{1/4}\sqrt{\Omega }%
e^{-x^{2}/2}+\left( \frac{2\Delta \mu }{\sqrt{3}}\right) ^{3/4}\frac{\sigma
_{1}}{\sqrt{\Omega }}e^{-3x^{2}/2}\cos \left( \Omega x\right) .
\end{equation}%
For the next branch, $\Gamma _{1}$, one obtains
\begin{equation}
u(x)\approx \left( \frac{216\Delta \mu }{15\sqrt{3}}\right) ^{1/4}\sqrt{%
\Omega }xe^{-x^{2}/2}+\left( \frac{216\Delta \mu }{15\sqrt{3}}\right) ^{3/4}%
\frac{\sigma _{1}}{\sqrt{\Omega }}x^{3}e^{-3x^{2}/2}\cos \left( \Omega
x\right) .
\end{equation}%
The comparison between the numerical solution and approximations (\ref%
{AsRel_u}) and (\ref{u_appr_main}) is illustrated by the Fig.~\ref{Fig:Prof}%
, for $\Omega =16$. The figure shows that approximation (\ref{AsRel_u})
describes the numerical solution very well. Approximation (\ref{u_appr_main}%
) is good too, even if $\Delta \mu $ is not small (compare grey and blue
lines in Fig.~\ref{Fig:Prof}, where $\Delta \mu =1$ and $2$ in the left and
right panels, respectively).

\subsubsection{Stability of localized modes}

\label{Gamma_stab}

In the small-amplitude limit, the stability of LMs is determined by
eigenvalues of matrix $\tilde{M}_{n}$, see Sect.~\ref{SmAmpl}. Using Maple,
one can compute these eigenvalues with any necessary accuracy. The results
for two modulation frequencies ($\Omega =8$ and $16$) are summarized in
Tables~\ref{T4}-\ref{T5}. In these tables, $n$ is the index of branch $%
\Gamma _{n}$ (for instance, $n=2$ means that branch $\Gamma _{2}$, which
starts from $\tilde{\mu}_{2}=2\cdot 2+1=5$, is under consideration), while $%
k $, running from $0$ to $n-1$, enumerates double eigenvalues $\tilde{\Lambda%
}_{k}=4(n-k)^{2}$. Each cell with $n>k$ contains either letter
``C" or two real numbers. These numbers
are the real eigenvalues $\gamma _{1,2}$ of the matrix $\tilde{M}_{n}$,
whereas ``C" means that both eigenvalues
of $\tilde{M}_{n}$ are complex. Dashes imply that the respective eigenvalues
do not exist. {\LARGE [I have added this statement - OK?]}

\begin{table}[tbp]
%[h]
\begin{tabular}{ccccccccccc}
& \phantom{111} & $n=1$ &  & $n=2$ &  & $n=3$ &  & $n=4$ &  & $n=5$ \\ \hline
$k=0$ &  & $%
\begin{array}{c}
0.132 \\
-0.028%
\end{array}%
$ &  & $%
\begin{array}{c}
-0.012 \\
0.203%
\end{array}%
$ &  & C &  & $%
\begin{array}{c}
0.424 \\
-0.828%
\end{array}%
$ &  & $%
\begin{array}{c}
-0.845 \\
-0.660%
\end{array}%
$ \\ \hline
$k=1$ &  & -- &  & $%
\begin{array}{c}
-0.176 \\
0.159%
\end{array}%
$ &  & $%
\begin{array}{c}
0.432 \\
-0.190%
\end{array}%
$ &  & $%
\begin{array}{c}
-0.486 \\
0.048%
\end{array}%
$ &  & $%
\begin{array}{c}
0.356 \\
0.944%
\end{array}%
$ \\ \hline
$k=2$ &  & -- &  & -- &  & $%
\begin{array}{c}
-0.068 \\
-0.132%
\end{array}%
$ &  & $%
\begin{array}{c}
-0.206 \\
0.196%
\end{array}%
$ &  & $%
\begin{array}{c}
0.531 \\
-0.600%
\end{array}%
$ \\ \hline
$k=3$ &  & -- &  & -- &  & -- &  & C &  & $%
\begin{array}{c}
0.166 \\
-0.122%
\end{array}%
$ \\ \hline
$k=4$ &  & -- &  & -- &  & -- &  & -- &  & C \\ \hline
\end{tabular}%
\caption{Eigenvalues of matrix $\tilde{M}$,\ in the case of $P(x)=\cos
\left( 8x\right) $. Here $n$ is the index of branch $\Gamma _{n}$, and $k$
enumerates double eigenvalues $\tilde{\Lambda}_{k}=4(n-k)^{2}$. Each cell
with $n>k$ contains either letter ``C" or
two real numbers. These numbers are real eigenvalues $\protect\gamma _{1,2}$
of matrix $\tilde{M}_{n}$, whereas letter ``C" means that eigenvalues 
of $\tilde{M}_{n}$ are complex.}
\label{T4}
\end{table}

\begin{table}[tbp]
%[h]
\begin{tabular}{ccccccccccc}
& \phantom{111} & $n=1$ &  & $n=2$ &  & $n=3$ &  & $n=4$ &  & $n=5$ \\ \hline
$k=0$ &  & $%
\begin{array}{c}
-2.0\cdot 10^{-11} \\
5.7\cdot 10^{-10}%
\end{array}%
$ &  & $%
\begin{array}{c}
-7.6\cdot 10^{-9} \\
-9.2\cdot 10^{-7}%
\end{array}%
$ &  & $%
\begin{array}{c}
-8.7\cdot 10^{-7} \\
2.2\cdot 10^{-4}%
\end{array}%
$ &  & $%
\begin{array}{c}
-4.0\cdot 10^{-5} \\
-1.2\cdot 10^{-2}%
\end{array}%
$ &  & $%
\begin{array}{c}
-9.5\cdot 10^{-4} \\
1.5\cdot 10^{-1}%
\end{array}%
$ \\ \hline
$k=1$ &  & -- &  & $%
\begin{array}{c}
-4.2\cdot 10^{-9} \\
7.3\cdot 10^{-8}%
\end{array}%
$ &  & $%
\begin{array}{c}
-5.8\cdot 10^{-7} \\
-3.6\cdot 10^{-5}%
\end{array}%
$ &  & $%
\begin{array}{c}
-3.0\cdot 10^{-5} \\
3.3\cdot 10^{-3}%
\end{array}%
$ &  & $%
\begin{array}{c}
-7.6\cdot 10^{-4} \\
-6.8\cdot 10^{-2}%
\end{array}%
$ \\ \hline
$k=2$ &  & -- &  & -- &  & $%
\begin{array}{c}
-3.4\cdot 10^{-7} \\
3.9\cdot 10^{-6}%
\end{array}%
$ &  & $%
\begin{array}{c}
-2.0\cdot 10^{-5} \\
-6.8\cdot 10^{-4}%
\end{array}%
$ &  & $%
\begin{array}{c}
-5.7\cdot 10^{-4} \\
2.6\cdot 10^{-2}%
\end{array}%
$ \\ \hline
$k=3$ &  & -- &  & -- &  & -- &  & $%
\begin{array}{c}
-1.3\cdot 10^{-5} \\
1.0\cdot 10^{-4}%
\end{array}%
$ &  & $%
\begin{array}{c}
-3.6\cdot 10^{-4} \\
-6.8\cdot 10^{-3}%
\end{array}%
$ \\ \hline
$k=4$ &  & -- &  & -- &  & -- &  & -- &  & $%
\begin{array}{c}
-2.7\cdot 10^{-4} \\
1.5\cdot 10^{-3}%
\end{array}%
$ \\ \hline
\end{tabular}%
\caption{Eigenvalues of matrix $\tilde{M}_{n}$ for $P(x)=\cos \left(
16x\right) $. The notation is the same as in Table \protect\ref{T4}.}
\label{T5}
\end{table}

To be specific, let us describe in detail branch $\Gamma _{2}$ in the case
of $P(x)=\cos \left( 8x\right) $, the branch $\Gamma _{2}$ (i.e., $n=2$ in
Table~\ref{T4}). In this case, there are two double eigenvalues in the
spectrum, $\tilde{\Lambda}_{0}=16$ and $\tilde{\Lambda}_{1}=4$. According to
Table~\ref{T4} and Eq. (\ref{Lambda_12_as}), they split as
\begin{equation}
\Lambda _{0}^{(1)}=16-0.012\cdot \varepsilon ^{2}+\ldots ,\quad \Lambda
_{0}^{(2)}=16+0.203\cdot \varepsilon ^{2}\ldots ~
\end{equation}%
and
\begin{equation}
\Lambda _{1}^{(1)}=4-0.176\cdot \varepsilon ^{2}+\ldots ,\quad \Lambda
_{1}^{(2)}=4+0.159\cdot \varepsilon ^{2}\ldots ~,
\end{equation}%
hence the small-amplitude nonlinear LMs belonging to branch $\Gamma _{2}$
are stable in this case. The situation is different for $\Gamma _{3,4,5}$,
since for each of these branches the bifurcation of a complex-conjugate pair
occurs: for $n=3$ the eigenvalue $\tilde{\Lambda}_{0}=36$ splits into
complex eigenvalues,while for $n=4$ and $n=5$ this takes place for $\tilde{%
\Lambda}_{2}=4$. Therefore, for $\Omega =8$ the small-amplitude LMs are
stable in branches $\Gamma _{0}$, $\Gamma _{1}$ and $\Gamma _{2}$, but
unstable in $\Gamma _{3}$, $\Gamma _{4}$ and $\Gamma _{5}$. Table~\ref{T5}
is produced for $\Omega =18$, implying that the small-amplitude LMs are
stable for \textit{all} the branches, $\Gamma _{0,...,5}$.

To explain the different stability of small-amplitude LMs with different
spatial frequencies $\Omega $, we consider the behavior of eigenvalues of $%
\tilde{M}_{n}$ at $\Omega \rightarrow \infty $. Using explicit results given
by Eqs. (\ref{11})--(\ref{22}) and asymptotic relation (\ref{AsGauss}), we
obtain %\begin{align}
%\la M_n\tilde u_k,\tilde u_k\ra&=\frac{8(n-k)}{\pi 2^{(n+k)}n!k!}\int_{-\infty}^\infty
%P(x)H_n^2(x)H_k^2(x)e^{-2x^2}~dx-\\[2mm] &- \frac{4(n-k)}{\pi
%2^{2n}(n!)^2}\int_{-\infty}^\infty P(x)H_n^4(x)e^{-2x^2}~dx\sim\\[2mm]
%&\sim -\frac{2\sqrt{2}(n-k)\Omega^{4n}}{2^{6n}\cdot(n!)^2 \sqrt{\pi} %}e^{-\Omega^2/8}=O(\Omega^{4n}e^{-\Omega^2/8}),
%\end{align}
%(the contribution of the first term in the right hand side of the last formula is of order $\sim \Omega^{2(n+k)} e^{-\Omega^2/8}$ that is small when compared with the second term).
%For the diagonal terms one has
%\begin{align}
%<M_n\tilde u_k,\tilde u_{2n-k}>&=-<M_n\tilde u_{2n-k},\tilde u_k>=\\[2mm]
%&=\frac{4(n-k)}{\pi 2^{2n}n!\sqrt{k!(2n-k)!}}\int_{-\infty}^\infty
%P(x)H_n^2(x)H_{2n-k}(x)H_k(x)e^{-2x^2}~dx\sim\\[2mm]
%&\sim\frac{2\sqrt{2}(n-k)\Omega^{4n}}{2^{6n}n!\sqrt{k!(2n-k)!} \sqrt{\pi} %}e^{-\Omega^2/8}=O(\Omega^{4n}e^{-\Omega^2/8}).
%\end{align}
%The asymptotics of the last entry is
%\begin{align}
%<M_n\tilde u_{2n-k},\tilde u_{2n-k}>&=-\frac{8(n-k)}{\pi 2^{(3n-k)}n!(2n-k)!}\int_{-\infty}^\infty
%P(x)H_n^2(x)H_{2n-k}^2(x)e^{-2x^2}~dx +\\[2mm]
%&\phantom{=}+ \frac{4(n-k)}{\pi
%2^{2n}(n!)^2}\int_{-\infty}^\infty P(x)H_n^4(x)e^{-2x^2}~dx\sim\\[2mm]
%&\sim-\frac{4\sqrt{2}(n-k)\Omega^{2(3n-k)}}{\sqrt{\pi}2^{3(3n-k)}n!(2n-k)!}
%e^{-\Omega^2/8}=O(\Omega^{2(3n-k)}e^{-\Omega^2/8}).
%\end{align}
%(again, due to (\ref{AsGauss}) the contribution of the first term in the sum dominates).
\begin{align}
\langle M_{n}\tilde{u}_{k},\tilde{u}_{k}\rangle & \sim -\frac{2\sqrt{2}%
(n-k)\Omega ^{4n}}{2^{6n}\cdot (n!)^{2}\sqrt{\pi }}e^{-\Omega ^{2}/8}, \\%
[2mm]
\langle M_{n}\tilde{u}_{k},\tilde{u}_{2n-k}\rangle & =-\langle M_{n}\tilde{u}%
_{2n-k},\tilde{u}_{k}\rangle \sim \frac{2\sqrt{2}(n-k)\Omega ^{4n}}{2^{6n}n!%
\sqrt{k!(2n-k)!}\sqrt{\pi }}e^{-\Omega ^{2}/8}, \\
\langle M_{n}\tilde{u}_{2n-k},\tilde{u}_{2n-k}\rangle & \sim -\frac{4\sqrt{2}%
(n-k)\Omega ^{2(3n-k)}}{\sqrt{\pi }2^{3(3n-k)}n!(2n-k)!}e^{-\Omega ^{2}/8}.
\end{align}%
These relations imply that
\begin{equation}
\tilde{M}_{n}=\left(
\begin{array}{cc}
O(\Omega ^{4n}e^{-\Omega ^{2}/8}) & O(\Omega ^{4n}e^{-\Omega ^{2}/8}) \\%
[2mm]
O(\Omega ^{4n}e^{-\Omega ^{2}/8}) & O(\Omega ^{2(3n-k)}e^{-\Omega ^{2}/8})%
\end{array}%
\right) ,\quad \Omega \rightarrow \infty
\end{equation}%
All elements of matrix $\tilde{M}_{n}$ are of the same order, except for the
one in the right lower corner which is of greater order due to $n>k$. This
means that, for\textit{\ }$\Omega $\textit{\ }large enough, eigenvalues of $%
\tilde{M}_{n}$\textit{\ }are real, hence the nonlinear LMs from branch $%
\Gamma _{n}$ for arbitrary $n$ are stable, at least in the small- amplitude
limit. This explains the difference between the results displayed in Tables~%
\ref{T4} and \ref{T5}: the increase of the spatial frequency from $\Omega =8$
to $\Omega =16$ results in stabilization of some small-amplitude LMs which
were originally unstable.
% from  is ``not enough large'' and Table \ref{T4} contains complex eigenvalues that implies the instability of the NLM.

Rigorously speaking, the results for the linear stability of the
small-amplitude LMs are asymptotic, and, while moving along branch $\Gamma
_{n}$ to the region of moderate or large amplitudes, the nonlinear LMs may
change the stability.
%The typical scenario for transition from stability to instability corresponds to the  collision of two reals eigenvalues with ensuing  bifurcations of a complex-conjugate pair.
To illustrate the persistence of the asymptotic predictions for the
(in)stability of the nonlinear LMs, in Fig.~\ref{CollEig} we plot
numerically obtained dependencies of eigenvalues $\lambda $ on $\mu $ for
branches $\Gamma _{0,1,2,3}$ in the case of $P(x)=\cos \left( 16x\right) $.
Each shown branch is stable near the point of its emergence, losing
stability at some threshold value of $\mu $ (which is different for
different branches).

\begin{figure}[tbp]
\includegraphics[width=0.6\textwidth]{Fig_Eigens_1.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{The evolution of eigenvalues of (\protect\ref{EigProb}) as $\protect%
\mu $ varies, for $P(x)=\cos \left( 16x\right) $. Only eigenvalues with $%
\mathrm{Im}~\protect\lambda \geq 0$ are shown. Solid line: pure imaginary
eigenvalues corresponding to stable LMs; dashed line: eigenvalues with a
nonzero real part. (1) Branch $\Gamma _{0}$. No double eigenvalues exist at $%
\protect\mu =1$, all the eigenvalues being pure imaginary and simple, until
the collision at $\mu\approx -1.049$. After the collision a
pair of real eigenvalues emerges. (2) Branch $\Gamma _{1}$. At $\protect\mu %
=3$ there exists one double eigenvalue, $\protect\lambda =2i$. According to
the prediction of the asymptotic analysis, it splits into a pair of pure
imaginary simple eigenvalues. The collision of eigenvalues occurs at
$\mu\approx 1.372$, and a pair of eigenvalues with nonzero
real parts emerges. (3) Branch $\Gamma _{2}$. At $\protect\mu =5$, there
exists two pairs of double eigenvalues, $\protect\lambda =2i$ and $\protect%
\lambda =4i$. Both of them split into pairs of pure imaginary eigenvalues.
The former pair collides again at $\mu\approx 4.801$ and
transforms into a pair of complex eigenvalues with nonzero real parts. At
$\mu\approx 3.519$ , another collision of eigenvalues
occurs. (4) Branch $\Gamma _{3}$. At $\protect\mu =7$, there exist three
pairs of double eigenvalues. The first collision of pure imaginary
eigenvalues takes place at $\mu\approx 5.571$, then two more
collisions occur. They all result in eigenvalues with nonzero real parts.}
\label{CollEig}
\end{figure}

Numerically generated $N(\mu )$ curves for $\Omega =8$, $\Omega =12$, and $%
\Omega =16$ are plotted in Fig.~\ref{Fig_ZM_branches}. It follows from these
plots that branch $\Gamma _{0}$ is the ``most
stable" one for all the three values of $\Omega $. One
also notices that, for the greatest value of $\Omega $ (i.e., $\Omega =16$)
there exists a ``stability window" in a
vicinity of the bifurcations for all branches $\Gamma _{0,1,2,3}$, in
agreement with the asymptotic results presented above.

Numerical study of the temporal evolution of LMs in the framework of
time-dependent GPE~(\ref{1D_GP_12}) confirms the predictions of the
linear-stability analysis, see Fig.~\ref{Fig_Comp_NZM}(2a,b).
% We observe several ways for breaking down of unstable NLMs.
%An example of
As an example of a distinctive pattern of dynamical behavior of unstable
modes, in Fig.~\ref{Fig_Comp_NZM}(2b) we display its transformation into a
pulsating object localized over one period of the lattice pseudopotential.

\begin{figure}[tbp]
\includegraphics[width=0.8\textwidth]{Fig_3_v2_extended.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{$N(\protect\mu )$ curves for $P(x)=\cos \left( \Omega x\right) $, $%
\Omega =8,12,16$. Branches $\Gamma _{0,1,2,3}$ are presented. Black bold
(red thin) lines correspond to stable (unstable) LMs.}
\label{Fig_ZM_branches}
\end{figure}

%\subsubsection{The evolution of NLM}\label{Evol_ZM}

\begin{figure}[tbp]
\includegraphics[width=0.8\textwidth]{Fig_7_ZM_1.eps}%\\
%    \includegraphics[width=0.8\textwidth]{nonlinear.eps}
\caption{The case of $P(x)=\cos \left( 16x\right) $. (1a): The evolution of
a stable nonlinear mode belonging to branch $\Gamma _{1}$, with $\protect\mu %
=2$. (1b): the spectrum of eigenvalues $\protect\lambda $ produced by
numerical solution of Eq. (\protect\ref{EigProb}) associated with this mode.
(2a): The evolution of an unstable mode belonging to branch $\Gamma _{1}$,
with $\protect\mu =0$; (2b) the corresponding spectrum. }
\label{Fig_Comp_ZM}
\end{figure}

\section{Conclusion}

\label{Concl}

In the paper, we have systematically studied nonlinear LMs (localized modes)
of the one-dimensional Gross-Pitaevskii/nonlinear Schr\"{o}dinger equation
with the HO (harmonic-oscillator) trapping potential $V(x)$ and nonlinear
lattice pseudopotential $P(x)$, which is an periodic function oscillating
with spatial frequency $\Omega $. %From the physical viewpoint,
The equation describes a cigar-shaped cloud of BEC confined by the magnetic
trap and manipulated by the optically-induced Feshbach resonance with the
periodically modulated local strength. The model is characterized by the
interplay between two spatial scales: the characteristic size of the HO trap
and the period of the nonlinear lattice pseudopotential. This factor
essentially enriches the variety of nonlinear modes in this model, in
comparison with the well-studied case of the spatially uniform nonlinearity.
We have obtained analytical results of the shape of nonlinear LMs and on
their stability, in the limits of small-amplitude solutions and rapidly
oscillating pseudopotential. The validity and persistence of the asymptotic
predictions has been corroborated by systematically presented numerical
findings.

%. The interplay of the two scales opens new perspectives for creation of novel stable matter waves as well as their handling. The paper is aimed to found NLM in this model and to compare the results with the ones for the case $P(x)={\rm const}$ (called above {\it the nonlinear harmonic oscillator}) that was analysed in many studies.

To conclude the paper, it is relevant, once again, the highlight main
results of the work. %
%We present general pictures of NLM branches for various relations between the characteristic sizes. When the scales are comparable, we employ numerical methods. The computations are based on the algorithm of the paper \cite{AZ07} that allows to find all the NLM in the given range of parameters. Also we used asymptotic methods, if the period of the pseudopotential is small compared with the characteristic size of the parabolic trap.
It was found that there exist two types of branches of LMs, \textit{viz}.,
ones with and without linear counterpart. This is especially interesting in
view of the fact that no modes without linear counterpart exists in the
model with the uniform nonlinearity. However, all these ``exotic" 
nonlinear modes, disconnected from the linear limit, are unstable.
As concerns nonlinear LMs bifurcating from eigenstates of the underlying
linear problem, their properties are essentially different depending on the
presence of the dc term (nonzero mean value) in the periodic
pseudopotential. In the mean is nonzero, then properties of nonlinear modes
in a rapidly oscillating pseudopotential may be approximated using solutions
for the standard HO model with constant nonlinearity. However, the reduction
to the standard model with constant nonlinearity does not work for the
system in a rapidly oscillating pseudopotential without the dc term. Most
interestingly, in this case we have found that the rapidly oscillating
pseudopotential can stabilize small-amplitude LMs belonging to higher
families (excited states, which are unstable in the model including the dc
term). Specifically, for any given branch with index $n$, there exists a
threshold values of the spatial frequency, $\Omega _{n}$, such that the
small-amplitude solutions belonging to this branch are stable for $\Omega
>\Omega _{n}$.

As a continuation of this work, it may be interesting to extend the analysis
to the case of the interplay of the spatially periodic pseudopotential with
the expulsive (anti-HO) potential. A more challenging possibility is to
consider a two-dimensional model featuring the combination of an isotropic
HO trapping potential and two-dimensional lattice quasipotential.
%Using our asymptotic results, the threshold values $\Omega_n$ can be obtained explicitly.\textcolor{red}{[.. Dima, the last sentence: what do you mean?..]}
{\LARGE \ [A general request: in the caption of each figure, please write if
it corresponds to the model with or without the dc term; otherwise, it is
difficult to read the figures.]}

% Any family of NLM with linear counterpart branches off from zero solution and therefore includes NLMs of arbitrarily small amplitude. Contrarily, the families of NLM without linear counterpart have no small amplitude limit. No families without linear counterpart exist in the case $P(x)={\rm const}$, therefore their existence is caused by variable coefficient $P(x)$.

%We consider separately the two cases: the first, when $P(x)$ has nonzero mean and the second, when $P(x)$ has nonzero mean. In the first case, the NLM with linear counterpart approaches the corresponding modes of nonlinear harmonic oscillator, when the period of $P(x)$ tends to zero. In the second case, we show that high frequency oscillations of $P(x)$ can stabilize small amplitude NLM corresponding to higher order branches.

\acknowledgements

The research of G.L.A., M.E.L. and D.A.Z. was supported by Russian Science
Foundation (Grant No. 17-11-01004). The work of B.A.M. is supported, in
part, by the joint program in physics between NSF and Binational (US-Israel)
Science Foundation through project No. 2015616, and by the Israel Science
Foundation through Grant No. 1286/17

\begin{thebibliography}{99}
\bibitem{AEMWC95} M. H. Anderson, J. R. Ensher, M. R. Matthews, C. E.
Wieman, and E. A. Cornell, Observation of Bose-Einstein condensation in a
dilute atomic vapor, Science \textbf{269}, 198 (1995).

\bibitem{DMADDKK95} K. B. Davis, M.-O. Mewes, M. R. Andrews, N. J. van
Druten, D. S. Durfee, D. M. Kurn, and W. Ketterle, Bose-Einstein
condensation in a gas of sodium atoms, Phys. Rev. Lett. \textbf{75}, 3969
(1995).

\bibitem{BSTH95} C. C. Bradley, C. A. Sackett, J. J. Tollett, and R. G.
Hulet, Evidence of Bose-Einstein condensation in an atomic gas with
attractive interactions, Phys. Rev. Lett. \textbf{75}, 1687 (1995).

\bibitem{Romanian} V. S. Bagnato, D. J. Frantzeskakis, P. G. Kevrekidis, B.
A. Malomed, and D. Mihalache, Bose-Einstein condensation: Twenty years
after, Rom. Rep. Phys. \textbf{67}, 5-50 (2015).

\bibitem{I98} Inouye, S., M. R. Andrews, J. Stenger, H. J. Miesner, D. M.
Stamper- Kurn, and W. Ketterle, Observation of Feshbach resonances in a
Bose-Einstein condensate, Nature (London) \textbf{392}, 151, (1998).

\bibitem{TT04} Theis, M., G. Thalhammer, K. Winkler, M. Hellwig, G. Ruff, R.
Grimm, and J. H. Denschlag, Tuning the scattering length with an optically
induced Feshbach resonance, Phys. Rev. Lett. \textbf{93}, 123001 (2004).

\bibitem{KGJ06} T. Kohler, K. Goral and P. S. Julienne, Production of cold
molecules via magnetically tunable Feshbach resonances, Rev. Mod. Phys.
\textbf{78}, 1311 (2006).

\bibitem{Hannaford} S. Ghanbari, T. D. Kieu, A. Sidorov, and P. Hannaford,
Permanent magnetic lattices for ultracold atoms and quantum degenerate
gases, J. Phys. B: At. Mol. Opt. Phys. \textbf{39}, 847-860 (2006).

\bibitem{Japan} R. Yamazaki, S. Taie, and S. Sugawa, and Y. Takahashi,
Submicron spatial modulation of an interatomic interaction in a
Bose-Einstein condensate, Phys. Rev. Lett. \textbf{105}, 050405 (2010).

\bibitem{Cs} L. W. Clark, L.-C. Ha, C.-Y. Xu, and C. Chin, Quantum dynamics
with spatiotemporal control of interactions in a stable Bose-Einstein
condensate, Phys. Rev. Lett. \textbf{115}, 155301 (2015).

\bibitem{HS} H. Sakaguchi and B. A. Malomed, Solitons in combined linear and
nonlinear lattice potentials, Phys. Rev. A \textbf{81}, 013624 (2010).

\bibitem{Pet} C. J. Pethick and H. Smith, \textit{Bose-Einstein Condensation
in Dilute Gases} (Cambridge University Press: Cambridge, 2002).

\bibitem{Pit} L. P. Pitaevskii and A. Stringari, \textit{Bose-Einstein
Condensation} (Clarendon Press: Oxford, 2003).

\bibitem{Salasnich} L. Salasnich, A. Parola, and L. Reatto, Effective wave
equations for the dynamics of cigar-shaped and disk-shaped Bose
condensates , Phys. Rev. A \textbf{65}, 043614 (2002).

\bibitem{Delgado} A. Mu\~{n}oz Mateo and V. Delgado, Effective mean-field
equations for cigar-shaped and disk-shaped Bose-Einstein
condensates, Phys. Rev. A \textbf{77}, 013617 (2008).

\bibitem{pseudo} W. A. Harrison, \textit{Pseudopotentials in the Theory of
Metals }(Benjamin: New York, 1966).

\bibitem{ZAKP07} D. A. Zezyulin, G. L. Alfimov, V. V. Konotop and V. M. P%
\'{e}rez-Garc\'{\i}a, Control of nonlinear modes by scattering-length
management in Bose-Einstein condensates, Phys. Rev. A \textbf{76}, 013621
(2007)

\bibitem{TAM16} F. Tsitoura, Z. A. Anastassi, J. L. Marzuola, P. G.
Kevrekidis, and D. J. Frantzeskakis, Dark solitons near potential and
nonlinearity steps, Phys. Rev. A \textbf{94}, 063612 (2016).

\bibitem{RKP08} A. S. Rodrigues, P. G. Kevrekidis, M. A. Porter, D. J.
Frantzeskakis, P. Schmelcher, and A. R. Bishop, Matter-wave solitons with a
periodic, piecewise-constant scattering length, Phys. Rev. A 78, 013611
(2008).

\bibitem{WLK13} C. Wang, K. J. H. Law, P. G. Kevrekidis, and M. A. Porter,
Dark solitary waves in a class of collisionally inhomogeneous Bose-Einstein
condensates, Phys. Rev. A \textbf{87}, 023621 (2013)

\bibitem{SM05} H. Sakaguchi, B. A. Malomed, Matter-wave solitons in
nonlinear optical lattices, Phys. Rev. E 72, 046610 (2005)

\bibitem{K17} P. G. Kevrekidis, R. Carretero-Gonz\'{a}lez, and D. J.
Frantzeskakis, Stability of single and multiple matter-wave dark solitons in
collisionally inhomogeneous Bose Einstein condensates, Intern. J. Mod. Phys.
B \textbf{31}, 1742013 (2017).

\bibitem{OL} O. Morsch and M. Oberthaler, Dynamics of Bose-Einstein
condensates in optical lattices, Rev. Mod. Phys. \textbf{78}, 179-215 (2006).

\bibitem{TSKF02} G. Theocharis, P. Schmelcher, P. G. Kevrekidis, and D. J.
Frantzeskakis,
%G. Theocharis,1,4 P. Schmelcher,1,2 P. G. Kevrekidis,3 and D. J. Frantzeskakis
Phys. Rev. \textbf{72}, 033614 (2005).

\bibitem{HY08} R. Hao, R, Yang, L. Li, and G. Zhou, Solutions for the
propagation of light in nonlinear optical media with spatially inhomogeneous
nonlinearities, Opt. Commun. \textbf{281}, 1256 (2008).

\bibitem{KMT11} Y. V. Kartashov, B. A. Malomed, and L. Torner, Solitons in
nonlinear lattices, Rev. Mod. Phys. \textbf{83}, 247-306 (2011).

\bibitem{Barcelona} O. V. Borovkova, Y. V. Kartashov, L. Torner, and B. A.
Malomed, Bright solitons from defocusing nonlinearities, Phys. Rev. E
\textbf{84}, 035602 (R) (2011).

\bibitem{C10} M. P. Coles, D. E. Pelinovsky, and P. G. Kevrekidis, Excited
states in the large density limit: a variational approach, Nonlinearity
\textbf{23}, 1753-1770 (2010).

\bibitem{PFK05} D. E. Pelinovsky, D. J. Frantzeskakis, and P. G. Kevrekidis,
Oscillations of dark solitons in trapped Bose-Einstein condensates, Phys.
Rev. E \textbf{72}, 016615 (2005).

\bibitem{DM15} N. Dror and B. A. Malomed, Solitons and vortices in nonlinear
potential wells, J. Opt. \textbf{18}, 014003 (2016).

\bibitem{AZ07} G. L. Alfimov and D. A. Zezyulin, Nonlinear modes for the
Gross-Pitaevskii equation -- a demonstrative computation approach,
Nonlinearity \textbf{20}, 2075-2092 (2007).

%\bibitem{BerShub}
%     F.A. Berezin and M.A. Shubin M A, {\it The Shr\"odinder equation}, Kluwer Academic  Publisher, 1991.
%\bibitem{Fedoryuk}
%     M.V. Fedoryuk {\it Asymptotic Analysis. Linear Ordinary Differential Equations}, Springer, 1993
%\bibitem{inWasov}
%     M.V. Fedoryuk, Asymptotics of solutions of linear differential
%     equations of the second order in complex domain, Addendum 1 to russian translation of: Wasov W 1968 {\it Asymptotic Expansions for Ordinary Differential Equations}. Moscow: Mir, 1968, (in Russian).

\bibitem{AKS02} G. L. Alfimov, V. V. Konotop and M. Salerno, Matter solitons
in Bose-Einstein Condensates with optical lattices, Europhys. Lett. \textbf{%
58}, 7-13 (2002).

\bibitem{JYang} J. Yang, \textit{Nonlinear Waves in Integrable and
Nonintegrable Systems} (Society for Industrial and Applied Mathematics:
Philadelphia, 2010).

\bibitem{AMP} R. D'Agosta, B. A. Malomed and C. Presilla, Laser Phys.
\textbf{12}, 37 (2002).

\bibitem{AP} R. D'Agosta and C. Presilla 2002 Phys. Rev. A \textbf{65},
043609.

\bibitem{Zeng} J. Zeng and B. A. Malomed, Localized dark solitons and
vortices in defocusing media with spatially inhomogeneous nonlinearity,
Phys. Rev. E \textbf{95}, 052214 (2017).

\bibitem{E95} M. Edwards and K. Burnett,
% Numerical Solution of the Nonlinear Schrödinger Equation for Small Samples of Trapped Neutral Atoms.
Phys. Rev. A \textbf{51}, 1382-1386 (1995).

\bibitem{K99} M. Kunze, T. K\"upper, V. K. Mezentsev, E. G. Shapiro, S.
Turitsyn, % Nonlinear Solitary Waves with Gaussian Tails.
Physica D \textbf{128}, 273--295 (1999).

\bibitem{G99} A. Gammal, T. Frederico, and L. Tomio,
%Improved numerical approach for the time-independent Gross-Pitaevskii nonlinear Schro¨dinger equation
Phys. Rev. E \textbf{60}, 2421 (1999).

\bibitem{KAT01} Yu. S. Kivshar, T. J. Alexander and S. K. Turitsyn, Phys.
Lett. A \textbf{278}, 225 (2001).

\bibitem{C01} L. D. Carr, J. N. Kutz, and W. P. Reinhardt, Phys. Rev. E
\textbf{63}, 066604 (2001).

\bibitem{YYB02} V. I. Yukalov, E. P. Yukalova, and V. S. Bagnato, Phys. Rev.
A \textbf{66}, 043602 (2002).

\bibitem{KK03} V. V. Konotop and P. G. Kevrekidis,
%V.V. Konotop1 and P. G. Kevrekidis
Phys. Rev. Lett. \textbf{91}, 230402 (2003).

\bibitem{ZAKP08} D. A. Zezyulin, G. L. Alfimov, V. V. Konotop, V. M. P\'{e}%
rez-Garc\'{\i}a, Stability of excited states of a Bose-Einstein condensate
in an anharmonic trap, Phys. Rev. A \textbf{78}, 013606 (2008).

\bibitem{KKRF05} P. G. Kevrekidis, V. V. Konotop, A. Rodrigues, and D. J.
Frantzeskakis, Dynamic generation of matter solitons from linear states via
time-dependent scattering lengths, J. Phys. B: At. Mol. Opt. Phys. \textbf{38%
}, 1173-1178 (2005).

\bibitem{ZK16} D. A. Zezyulin and V. V. Konotop, Small-amplitude nonlinear
modes under the combined effect of the parabolic potential, nonlocality and $%
\mathcal{PT}$ Symmetry, Symmetry \textbf{8}, 72 (2016).

\bibitem{Fatkhulla} F. Kh. Abdullaev, J. G. Caputo, R. A. Kraenkel, and B.
A. Malomed, Controlling collapse in Bose-Einstein condensation by temporal
modulation of the scattering length, Phys. Rev. A \textbf{67}, 013605 (2003).

\bibitem{TP} V. A. Trofimov and N. V. Peskov, Comparison of
finite-difference schemes for the Gross-Pitaevskii equation, Mathematical
Modelling and Analysis \textbf{14}, 109 (2009).
\end{thebibliography}

\end{document}
